### 2012-08-28 paper.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@805 df1a90cd-247b-4364-bdaf-287a704eb499

\documentclass[conference]{IEEEtran}
\title{Mitigating (D)DoS in Named-Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}
\date{}
\begin{document}
\maketitle

\begin{abstract}
%
abstract
%
\end{abstract}

\noindent {\bf Keywords:} Future Internet Architectures;
Content-Centric Networks; Information-Centric Networks, Named-data
Networking; Security; Denial-of-Service; Distributed
Denial-of-Service.

\section{Introduction \label{intro}}

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2012-09-04 paper.tex
Adding Section/subsection heading
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@806 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \section{Introduction \label{intro}}
+Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.
+
+Our contributions.
+
+Paper organization.
+
+\section{ CCN Overview\label{ccn-intro}}
+
+\section { DDoS Attacks in CCN \label{ccn-ddos}}
+Brief overview of possible attacks in CCN, and scope of what we will tackle in this paper (Interest flooding).
+
+\section { Interest Flooding in CCN }
+
+\section {Countermeasures against Interest flooding}
+
+Basic limits, probablity based on statistics, and dynamic window adjustment
+
+(Description of each of the above, and their implications)
+
+\section {Evaluation}
+ Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
+List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
+
+Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).
+
+\subsection{Simulation versus Emulation}
+Results establishing validity of  simulator.
+
+\subsection{Results from probability based on statistics}
+
+\subsection{Results from dynamic window adjustment}
+
+\section{Implications/Analysis}
+Lessons we learnt, comparison of different mitigation techniques. 
+Adapting these to mitigate other DDoS attacks.
+
+\section{Conclusions and Future Work}
 

### 2012-10-07 selected-results.tex
Adding some selected (available) results (selected-results.pdf combines some of the available graphs)
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@812 df1a90cd-247b-4364-bdaf-287a704eb499

\documentclass[onecolumn]{IEEEtran}
% \include{graphicx}
\usepackage{pdfpages}
\usepackage{hyperref}

\begin{document}

\tableofcontents

\clearpage

\textbf{\color{red}Left graphs show bandwidths of data/interset stream\\
Right graphs show the same data but in number of packets}

\section{Large Tree}

\begin{figure}[h]
  \centering

\includegraphics[scale=1]{selected-results/topo-large-tree.pdf}

  \caption{128-node binary tree topology}
\end{figure}

The following presents results for three independent runs of the simulation, varying number of good and bad clients.

\clearpage

\subsection{\textbf{4 evil nodes}, 60 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-large-tree-evil-4.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-large-tree-evil-4.pdf}
\end{minipage}

% \clearpage

% \subsubsection{Physical Limits, Run 1-3}

% \begin{minipage}[b]{\textwidth}
% \includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/simple-limits-topo-large-tree-evil-4.pdf}
% \end{minipage}

% \clearpage

% \subsubsection{No Limits, Run 1-3}

% \begin{minipage}[b]{\textwidth}
% \includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/no-limits-topo-large-tree-evil-4.pdf}
% \end{minipage}

\clearpage
\subsection{\textbf{8 evil nodes}, 56 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-large-tree-evil-8.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-large-tree-evil-8.pdf}
\end{minipage}

\clearpage
\subsection{\textbf{12 evil nodes}, 52 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-large-tree-evil-12.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-large-tree-evil-12.pdf}
\end{minipage}

\clearpage
\subsection{\textbf{16 evil nodes}, 48 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-large-tree-evil-16.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-large-tree-evil-16.pdf}
\end{minipage}

\clearpage
\subsection{\textbf{20 evil nodes}, 44 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-large-tree-evil-20.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-large-tree-evil-20.pdf}
\end{minipage}

\clearpage
\subsection{\textbf{24 evil nodes}, 40 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-large-tree-evil-24.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-large-tree-evil-24.pdf}
\end{minipage}

\clearpage
\subsection{\textbf{28 evil nodes}, 36 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-large-tree-evil-28.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-large-tree-evil-28.pdf}
\end{minipage}

% \clearpage
% \subsection{\textbf{32 evil nodes}, 32 good nodes}

% \subsubsection{Dynamic Limits, Run 1-3}

% \begin{minipage}[b]{\textwidth}
% \includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-large-tree-evil-32.pdf}
% \end{minipage}

% \clearpage

% \subsubsection{Probabilistic Interest accept, Run 1-3}

% \begin{minipage}[b]{\textwidth}
% \includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-large-tree-evil-32.pdf}
% \end{minipage}

\clearpage

\textbf{\color{red}Left graphs show bandwidths of data/interset stream\\
Right graphs show the same data but in number of packets}

\section{Tree}

\begin{figure}[h]
  \centering

\includegraphics[scale=1]{selected-results/topo-tree.pdf}

  \caption{32-node binary tree topology}
\end{figure}

The following presents results for three independent runs of the simulation, varying number of good and bad clients.

\clearpage
\subsection{\textbf{1 evil node}, 15 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-tree-evil-1.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-tree-evil-1.pdf}
\end{minipage}

\clearpage

\subsubsection{Physical Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/simple-limits-topo-tree-evil-1.pdf}
\end{minipage}

% \clearpage

% \subsubsection{No Limits, Run 1-3}

% \begin{minipage}[b]{\textwidth}
% \includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/no-limits-topo-tree-evil-1.pdf}
% \end{minipage}

\clearpage
\subsection{\textbf{2 evil nodes}, 14 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-tree-evil-2.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-tree-evil-2.pdf}
\end{minipage}

\clearpage

\subsubsection{Physical Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/simple-limits-topo-tree-evil-2.pdf}
\end{minipage}

\clearpage
\subsection{\textbf{3 evil nodes}, 13 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-tree-evil-3.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-tree-evil-3.pdf}
\end{minipage}

\clearpage

\subsubsection{Physical Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/simple-limits-topo-tree-evil-3.pdf}
\end{minipage}

\clearpage
\subsection{\textbf{4 evil nodes}, 12 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-tree-evil-4.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-tree-evil-4.pdf}
\end{minipage}

\clearpage

\subsubsection{Physical Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/simple-limits-topo-tree-evil-4.pdf}
\end{minipage}

\clearpage
\subsection{\textbf{5 evil nodes}, 11 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-tree-evil-5.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-tree-evil-5.pdf}
\end{minipage}

\clearpage

\subsubsection{Physical Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/simple-limits-topo-tree-evil-5.pdf}
\end{minipage}

\clearpage
\subsection{\textbf{6 evil nodes}, 10 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-tree-evil-6.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-tree-evil-6.pdf}
\end{minipage}

\clearpage

\subsubsection{Physical Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/simple-limits-topo-tree-evil-6.pdf}
\end{minipage}

\clearpage
\subsection{\textbf{7 evil nodes}, 9 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-tree-evil-7.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-tree-evil-7.pdf}
\end{minipage}

\clearpage

\subsubsection{Physical Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/simple-limits-topo-tree-evil-7.pdf}
\end{minipage}

% \clearpage
\subsection{\textbf{8 evil nodes}, 8 good nodes}

\subsubsection{Dynamic Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.85,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/dynamic-topo-tree-evil-8.pdf}
\end{minipage}

\clearpage

\subsubsection{Probabilistic Interest accept, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/probabilistic-topo-tree-evil-8.pdf}
\end{minipage}

\clearpage

\subsubsection{Physical Limits, Run 1-3}

\begin{minipage}[b]{\textwidth}
\includepdf[scale=0.9,nup=2x3,pages=1-6]{selected-results/near-tree-root-bandwidhts-and-packets/simple-limits-topo-tree-evil-8.pdf}
\end{minipage}

\end{document}

### 2012-10-22 algos/dynamic-limits.tex
Small update
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@814 df1a90cd-247b-4364-bdaf-287a704eb499

% \subsection{Dynamic limits}

\subsection{Dynamic limits assignment algorithm}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:

### 2012-10-22 algos/physical-limits.tex
Small update
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@814 df1a90cd-247b-4364-bdaf-287a704eb499

\subsection{Physical limits}

The requirement to send an Interest in order to receive Data packet, provides an NDN consumer a unique opportunity to request the right amount of Data.
Moreover, the same opportunity to control the amount of data flow is given not only to consumers, but all routers between consumer and producer (or nearby caches).  
In other words, every node, either a consumer or an intermediate router, is able to control how much data it wants to receive by limiting the number of forwarded Interests.

The limitation can implemented in a number of different ways, including leaky bucket scheduling and window-based flow control.
We decided to following TCP-like window-based flow control and applied the sliding window approach to implement Interest limits.

The size of the window defines how many Interests can be send out before Interests get satisfied or expired.
From the one hand, this size should be large enough to ``fill the pipe,'' meaning that a node needs to send enough Interests to receive Data at full capacity of the incoming link.
On the other hand, the window's size should not be too large to avoid excessive buffering and congestion of the Data packet.
Thus, the ideal size for such a window need to be defined proportional to link's bandwidth-delay product~\cite{tcp-survey}.
With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:

\[
\mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
\]

Note that the value of \textit{Delay} is not known a priory and varies between different Interest-Data flows.
However, we do not need to know the exact value of the delay and can set it as an average round trip delay among all flows (with a reasonable filtering of outliers).
This way, the statistical traffic multiplexing with link-level buffering will allow full utilization of the downstream link.
Exactly the same reasoning can be applied to the \textit{Data packet size} parameter, which can also be set to an average observed Data packet size.

Unlike rate-based approaches, window-based limiting does not require precise knowledge about the rate, as well does not need precise scheduling mechanisms.
Like in TCP, the window-based flow is self-clocking, easily adjusting itself to any traffic patterns.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:

### 2012-10-23 algos/fair-queueing.tex
Adding fair-queueing algorithm description
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@815 df1a90cd-247b-4364-bdaf-287a704eb499

\subsection{Physical limits with ``fair'' queuing}
\label{sec:queuing}

Physical limits (per-outgoing-interface) described in Section~\ref{sec:physical limits} provide ability to fully utilize a downstream link, (almost completely) avoiding congestion in the link.
However, this limitation approach does not attempt to utilize data plane performance knowledge (i.e., Interest satisfaction ratio statistics) to discriminate good and malicious Interests.

One way of augmenting the physical limits method with data performance knowledge is to perform some sort of class-based Interest queueing and weighted scheduling (e.g., weighted round-robin) of the enqueued interests with the weight equal to the Interest satisfaction ratio for the class (see Algorithm~\ref{alg:queuing}).
For example, Interests can be divided into separate classes based on incoming interface, where Interests arriving from different incoming interfaces are treated differently:
an Interest from an interface with higher satisfaction ratio will have more priority than an Interest from an interface with lower satisfaction ratio.

\floatname{algorithm}{Pseudocode}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{algorithm}[h]
\caption{Physical limits with ``fair'' queueing}
\label{alg:queuing}
\begin{algorithmic}[1]
\Function{InInterest}{Interest $i$, InFace $if$}
\For{\textbf{each} OutFace $of$ \textbf{in} ForwardingDecision($i,if$)}
    \If{$of$ is under physical limits}
        \State Forward($i$, $of$)
    \Else
        \State Queue $q \leftarrow of$.GetQueueByClass($if$)
        \State $q$.PushInterest($i$)
        \State $q$.UpdateWeight($if$.GetSatisfactionRatio())
    \EndIf
\EndFor
\EndFunction

\vspace{0.2cm}
\State{} \Comment{\textit{Called when an Interest is satisfied or times out}}
\Function{OnReady}{OutFace $of$}
\State{} \Comment{\textit{get a non-empty queue using weighted round-robin}}
\State Queue $q \leftarrow$ $of$.GetNonEmptyQueue 
\State $i \leftarrow$ $q$.PopInterest
\State Forward($i$, $of$)
\EndFunction
\end{algorithmic}
\end{algorithm}

A couple of notable comments.
First, queueing is not (and should not be) active until there is something to enqueue.
In our case, until physical limits are reached, all Interests are not subjected to any additional queueing.
Second, there should be a reasonable limit (smaller that Interest lifetime) of how long Interests are stayed in the queues.
Otherwise, there could be a case when Interests is still in a queue upstream, while pending Interest state already gone (timed out) downstream, effectively making such an Interest useless.%
\footnote{Additional mechanisms of pair-wise agreements between NDN routers and period Interest refresh can solve this particular problem, but it is out of the scope of the present paper.}

While we experimented with more complicated classes (see Sections~\ref{sec:dynamic limits} and \ref{sec:probabilistic model}), limitations of the queuing method nullify benefits of implementing such classes.
In particular, weighted round-robin scheduling can effectively work only if queues are not empty.
But, as we evaluation results in Section~\ref{sec:evaluation} show, queues are tend to be empty, when number of bottlenecks (mixing points, nodes that receive more Interests that they can forward on a face) on paths more than one.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:

### 2012-10-23 algos/dynamic-limits.tex
Adding fair-queueing algorithm description
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@815 df1a90cd-247b-4364-bdaf-287a704eb499
Adding draft for dynamic limits algorithm
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@816 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \subsection{Dynamic limits assignment algorithm}
+\label{sec:dynamic limits}
+
+A notable problem of the queuing method is that the method tries to differentiate between good and malicious Interests, but does not effectively limit the amount of malicious Interests.
+That is, if an attacker has a large number of malicious Interests to send, it will receive a slightly lower priority in sending these Interests (some will be delayed more, some number will be dropped), but a lot of these Interests will get through.
+To solve this problem, we propose announcing and dynamically readjusting Interest limits for classes (e.g., per prefix and per incoming face), based on Interest satisfaction ratios for those classes. 
+Pseudocode~\ref{alg:dynamic limits} summarizes our proposal, which is a variation of a well-known push-back mechanism.
+
+\floatname{algorithm}{Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\caption{Dynamic limits}
+\label{alg:dynamic limits}
+\begin{algorithmic}[1]
+\Function{InInterest}{Interest $i$, InFace $if$}
+\For{\textbf{each} OutFace $of$ \textbf{in} ForwardingDecision($i,if$)}
+    \State $l \leftarrow of$.GetPerPrefixLimit($i$)
+    \If{$l$ is under dynamics limits \textbf{and} $of$ is under physical limits}
+        \State Forward($i$, $of$)
+    \Else
+        \State Drop or enqueue Interest $i$
+    \EndIf
+\EndFor
+\EndFunction
+
+\vspace{0.2cm}
+
+\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
+\For{\textbf{each} prefix $p$ in FIB}
+    % \State{} \Comment{Get total limit for the prefix $p$}
+    \State $L \leftarrow \displaystyle\sum\limits_{\mathrm{\forall \mathit{of} \in FIB(\mathit{p})}}{}{}of$.GetPerPrefixLimit($p$)
+    \State $R \leftarrow 0$
+    \For{\textbf{each} available face $f$}
+        \State $l_f \leftarrow L \times p$.$f$.GetSatisfactionRatio()
+        \State $R \leftarrow R + p$.$f$.GetSatisfactionRatio()
+    \EndFor
+
+    \If{$\displaystyle\sum\limits_{\forall f}^{}l_f < l$} \Comment{If under-utilization detected}
+        \State $\forall f : l_f \leftarrow \displaystyle\frac{l_f}{R}$ \Comment{Normalize limits}
+    \EndIf
+
+        \State AnnounceLimit($f$, $p$, $l$)
+\EndFor
+\EndFunction
+
+\vspace{0.2cm}
+
+\State{} \Comment{\textit{When announcement from the neighbor is received}}
+\Function{InLimits}{InFace $if$, Prefix $p$, Limit $l$}
+    \State $if$.GetPerPrefixLimit($p$) $\leftarrow l$ 
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+When an Interest arrives, in addition to be checked against per-outgoing interface limits, it is subjected to per-prefix per-incoming interface limits (lines 3 and 4 in Pseudocode~\ref{alg:dynamic limits}).
+In other words, for each prefix in FIB a node cannot send more Interests than a specified limit for this prefix (``dynamic limits''), as well as the node cannot send out more Interests out of the face, than the limit specified for this face (``physical limit'').
+While the latter is defined in the same manner as in Section~\ref{sec:physical limits}, ``dynamic limits'' are periodically announced to all neighbors (\textit{AnnounceLimits} function) and adjusted based on received announcements from neighbors (\textit{InLimits} function).%
+\footnote{The initial value (not specified in the pseudocode) for the dynamic limits is the corresponding physical limits.}
+
+During the announcement phase, a node tries to determine ``quality'' of neighbors in terms of Interest satisfaction rations and tries to give more resources (accept more Interests from) neighbors with better satisfaction ratios.
+At the same time, it is undesirable to over-limit neighbors when there are available resources.
+That is, when the sum of all limits calculated by directly applying the satisfaction ratios to the total available limit (lines 15-18 in Pseudocode~\ref{alg:dynamic limits}), limits should be normalized so the sum of all announced limits is at least equal to the total available limit (lines 19-21).
+
+When the satisfaction ratio for a particular prefix and incoming interface becomes close to zero, a node starts announcing (and in real implementation, enforcing) the zero limit.
+The node will keep announcing this zero limit for a time period, depending on statistics degradation curve (see more in Section~\ref{sec:stats}).
+
+The dynamic limits method can work as standalone algorithm, as well as it can be (and we believe that it should be, and all results presented in this paper are based on) coupled with the queuing algorithms.
+This way, the dynamic limits part pushes back malicious traffic, while queueing part provides limited per-incoming interface fairness for good traffic.
 

### 2012-10-23 algos/fair-queueing.tex
Adding draft for dynamic limits algorithm
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@816 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-One way of augmenting the physical limits method with data performance knowledge is to perform some sort of class-based Interest queueing and weighted scheduling (e.g., weighted round-robin) of the enqueued interests with the weight equal to the Interest satisfaction ratio for the class (see Algorithm~\ref{alg:queuing}).
+One way of augmenting the physical limits method with data performance knowledge is to perform some sort of class-based Interest queueing and weighted scheduling (e.g., weighted round-robin) of the enqueued interests with the weight equal to the Interest satisfaction ratio for the class (see Pseudocode~\ref{alg:queuing}).
 For example, Interests can be divided into separate classes based on incoming interface, where Interests arriving from different incoming interfaces are treated differently:
@@
 
-While we experimented with more complicated classes (see Sections~\ref{sec:dynamic limits} and \ref{sec:probabilistic model}), limitations of the queuing method nullify benefits of implementing such classes.
+While we experimented with more complicated classes (see Sections~\ref{sec:dynamic limits} and \ref{sec:probabilistic}), limitations of the queuing method nullify benefits of implementing such classes.
 In particular, weighted round-robin scheduling can effectively work only if queues are not empty.

### 2012-10-23 algos/dynamic-limits.tex
Adding algo and some text for probabilistic model
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@817 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 That is, if an attacker has a large number of malicious Interests to send, it will receive a slightly lower priority in sending these Interests (some will be delayed more, some number will be dropped), but a lot of these Interests will get through.
-To solve this problem, we propose announcing and dynamically readjusting Interest limits for classes (e.g., per prefix and per incoming face), based on Interest satisfaction ratios for those classes. 
+
+One way to solve this problem is announce and dynamically readjust Interest limits for classes (e.g., per prefix and per incoming face), based on Interest satisfaction ratios for those classes. 
 Pseudocode~\ref{alg:dynamic limits} summarizes our proposal, which is a variation of a well-known push-back mechanism.

### 2012-10-23 algos/probabilistic.tex
Adding draft for dynamic limits algorithm
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@816 df1a90cd-247b-4364-bdaf-287a704eb499
Adding algo and some text for probabilistic model
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@817 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-08-28 paper.tex
@@
-\documentclass[conference]{IEEEtran}
-\title{Mitigating (D)DoS in Named-Data Networking}%:\\ Cache/Content Poisoning}
-\author{anonymous}
-\date{}
-\begin{document}
-\maketitle
+\subsection{Probabilistic Interest accept algorithm}
+\label{sec:probabilistic}
 
-\begin{abstract}
-%
-abstract
-%
-\end{abstract}
+The basic idea of the dynamic limits algorithm is to treat differently (accept different amounts of) Interests belonging to different classes.
+The high-level implementation of this in the dynamic limits algorithm is based explicit limits that are announced to each neighbor of the node.
+While the control overhead generated by such announcements can be manageable (i.e., similar to the routing updates in dynamic routing protocols, limit announcements can be paced out, as well as generated only when change is detected), some can consider such overhead undesirable.
 
-\noindent {\bf Keywords:} Future Internet Architectures;
-Content-Centric Networks; Information-Centric Networks, Named-data
-Networking; Security; Denial-of-Service; Distributed
-Denial-of-Service.
+The same goal of differential treatment of Interests, and in particular ``suppression'' of malicious Interests, can also achieved in a slightly different way, which does not require any additional communication between routers.
+Instead of announce and explicitly apply limits on the number of accepted Interests for each incoming interface (and optionally for each prefix in FIB), a node can accept new incoming Interests based on some probabilistic model, which incorporates satisfaction ratios for the desired Interest classes.
+For example, this could be a simple uniform distribution, where the satisfaction ratio directly defines probability to accept or reject an incoming Interests (see Pseudocode~\ref{alg:probabilistic model}).
+For simplicity, for the example we are using Interest differentiation only per incoming interface, but the algorithm can be generalized to more granular Interest classes.
 
-\section{Introduction \label{intro}}
+\floatname{algorithm}{Pseudocode}
 
-\bibliographystyle{plain}
-\bibliography{references}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\end{document}
+\begin{algorithm}[h]
+\caption{Probabilistic model}
+\label{alg:probabilistic model}
+\begin{algorithmic}[1]
+
+\Function{InInterest}{Interest $i$, InFace $if$}
+
+    \State{} \Comment{Use uniform probability distribution model $P(X)$}
+    \State{} \Comment{$P(X) : \forall x \in [0,1] \Rightarrow P(x) = x$}
+
+    \For{\textbf{each} OutFace $of$ \textbf{in} ForwardingDecision($i,if$)}
+        \State $s \leftarrow if$.GetSatisfactionRatio()
+        \If{$s \in [0,1]$} \Comment{A valid stats exists}
+            \State Stop processing with probability $P(s)$
+        \EndIf
+        \If{$of$ is under physical limits}
+            \State Forward($i$, $of$)
+        \EndIf
+    \EndFor
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+The definition of the probabilistic Interest accept is very straightforward and seems to be trivial to implement.
+However, there are a couple of implementation caveats that complicate matters.
+Note that there is a condition (line 6 on Pseudocode~\ref{alg:probabilistic mode}) to check if there is a valid statistics point.
+This condition is extremely important, because it first provides a basis to distinguish between known facts (i.e., good or bad satisfaction ratio for the incoming interface) and unknown facts (e.g., the first time an Interests arrives on the interfaces).
+Second, it gives an opportunity to recover from a bad history (history of unsatisfied Interests) after malicious Interests are ceased to flow in.
+Essentially, this recovery relies on statistics module to perform time-based invalidation of historical data (timely, but not too quickly\footnote{Otherwise, attackers may send short bursts of malicious Interests, successfully avoiding differential Interest treatment}).
+As described in Section~\ref{sec:stats}, we are currently experimenting with the exponential statistics degradation, while we also planning to apply different approaches in the future.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "../paper"
+%%% End:

### 2012-11-27 large-scale.tex
added simulation vs emulation
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@823 df1a90cd-247b-4364-bdaf-287a704eb499

\subsection{Large scale simulations}
\label{sec:largescale}

Large scale, large scale

%\begin{figure}[htpb]
%  \centering
%  \includegraphics[scale=0.5]{figures/sim-emu-power.pdf}
%  \caption{Strength of Interest flooding attack}
%  \label{fig:simemupower}
%\end{figure}

%\begin{figure}[htpb]
%  \centering
%  \includegraphics[scale=0.5]{figures/sim-emu-performance.pdf}
%  \caption{Data retrieval by legitimate clients}
%  \label{fig:simemuperf}
%\end{figure}

### 2012-11-27 paper.tex
Add stats algorithm's pseudocode. "A little bit" overcomplicated right now
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@813 df1a90cd-247b-4364-bdaf-287a704eb499
Small update
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@814 df1a90cd-247b-4364-bdaf-287a704eb499
Adding fair-queueing algorithm description
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@815 df1a90cd-247b-4364-bdaf-287a704eb499
Adding draft for dynamic limits algorithm
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@816 df1a90cd-247b-4364-b

@@
 \author{anonymous}
-\date{}
+
+\usepackage{graphicx}
+% \usepackage[colorlinks]{hyperref}
+\usepackage[]{hyperref}
+\usepackage{breakurl}
+\usepackage{url}
+\usepackage[nocompress]{cite}
+% \usepackage{verbatim}
+% \usepackage{algpseudocode}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+
+\newcommand{\note}[1]{\vspace{2 mm}\par \noindent \textsc{Note}
+\framebox{\begin{minipage}[c]{0.40 \textwidth}
+\tt #1 \end{minipage}}\vspace{5 mm}\par}
+
+\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \textsc{ToDo}
+\framebox{\begin{minipage}[c]{0.42 \textwidth}
+\tt #1 \end{minipage}}\vspace{5 mm}\par}
+
 \begin{document}
@@
 \section {Evaluation}
- Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
+\todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
 List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
 
-Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).
+Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}
 
-\subsection{Simulation versus Emulation}
-Results establishing validity of  simulator.
+We want to explore the effectiveness of designed mitigation techniques in a two distinctive ways.
+First, we need to understand how each method works on a very ground level of a just few nodes and links.
+Second, we want to pick promising techniques and see if they work in a large scale networks of hundreds and thousands of nodes.
+To ensure the correct transition from small scale experiments to large scale experiments we had to use the same evaluation tool in order to eliminate any possibility of implementation discrepancy.
+As of today the only network simulator supporting full NDN logic is the NS-3 based ndnSIM software.
+
+\input{simulation-emulation.tex}
 
@@
 \subsection{Results from dynamic window adjustment}
+
+\input{large-scale.tex}
 
@@
 
+\appendix
+
+\input{algos/physical-limits.tex}
+
+\input{algos/fair-queueing.tex}
+
+\input{algos/dynamic-limits.tex}
+
+\input{algos/probabilistic.tex}
+
+\input{algos/stats.tex}
+
 \end{document}

### 2012-11-27 simulation-emulation.tex
added simulation vs emulation
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@823 df1a90cd-247b-4364-bdaf-287a704eb499

\subsection{Simulation versus Emulation}
\label{sec:simemu}
Before committing significant efforts into simulation-based implementation of designed defensive techniques it was necessary to confirm that ndnSIM has close performance characteristics to the reference NDN implementation - Project CCNx. This will guarantee that evaluation results derived from simulations will be meaningful in real NDN world.

To achieve this goal a comparison of Project CCNx software and ndnSIM software was performed under small scale Interest flooding attack. DETER Testbed was used as emulation tool for CCNx evaluation. Using it we were able to setup non-virtualized Ubuntu nodes running CCNx 0.6.0 software connected in a binary tree topology with 4 leaves and 1 root node. A number of applications running on top of CCNx have been developed, namely:
\begin{itemize}
\item{Producer application serves 1KB data packets under a known for the attacker name prefix}
\item{Legitimate client application requests 5KB of data per second from the producer}
\item{Attacker application tries to fill the channel of the producer by sending 500 Interest packets per second}
\end{itemize}

In this emulation scenario producer application occupied a root node, legitimate clients occupied all even leaves and attacker applications were put on all odd leaves. With 100kb links with 40ms delay such setup leads to no congestion during the period when attackers are turned off and congestion when they are turned on (seconds 60-90). Exactly the same scenario was replicated for ndnSIM evaluation, however, we had to adjust the sending rate of attacker application in order to produce the same amount of congestion in the network. Sending rates are compared in Figure~\ref{fig:simemupower}. To achieve the identical slope and height of sending rate of evil Interests by attacker nodes we had to reduce sending rate of simulation-based attacker application by 30\%. The most likely reason for that is the overhead of Java virtual machine and operating system itself during the emulation of CCNx that results in eventual 30\% slower Interest transmission.

Once we achieved the same characteristics of Interest flooding attack we were able to compare data packet losses by legitimate clients. Figure~\ref{fig:simemuperf} shows the cumulative received data by legitimate consumers in emulation and simulation experiments. NdnSIM performs worse due to its more deterministic nature, while the effects of UDP protocol usage, operating system process scheduling, and other kernel level operations on packet queues provide more randomness and a better intermixing of bad and good traffic which gives a slightly better performance. To summarize, we can use ndnSIM for our evaluations and real world performance is likely to be even better than our evaluation results.

\begin{figure}[htpb]
  \centering
  \includegraphics[scale=0.5]{figures/sim-emu-power.pdf}
  \caption{Strength of Interest flooding attack}
  \label{fig:simemupower}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[scale=0.5]{figures/sim-emu-performance.pdf}
  \caption{Data retrieval by legitimate clients}
  \label{fig:simemuperf}
\end{figure}

### 2012-11-27 sim-emu-source/linear-script.R
source files for sim vs emu comparison
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@824 df1a90cd-247b-4364-bdaf-287a704eb499

@@ -1,0 +1,29 @@
+library(ggplot2)
+simlog = read.table("final4/linear-iliamo.log")
+emulog = read.table("final4/consumer-linear.log")
+summary(emulog)
+summary(simlog)
+emulog$V1 = emulog$V1 + 30
+summary(emulog)
+summary(simlog)
+names(emulog) = c("time","nodeid","prefix","packettype","seqnum")
+names(simlog) = c("time","nodeid","prefix","packettype","seqnum")
+filteredemulog = subset(emulog, packettype == "InData" & prefix == "/good")
+filteredsimlog = subset(simlog, packettype == "InData" & prefix == "/good")
+summary(emulog)
+summary(simlog)
+summary(filteredsimlog)
+summary(filteredemulog)
+filteredemulog$size = 1024
+filteredsimlog$size = 1024
+filteredemulog$goodput = cumsum(filteredemulog$size)
+filteredsimlog$goodput = cumsum(filteredsimlog$size)
+filteredemulog$experiment = "Emulation"
+filteredsimlog$experiment = "Simulation"
+filteredsimlog$experiment = as.factor(filteredsimlog$experiment)
+filteredemulog$experiment = as.factor(filteredemulog$experiment)
+summary(filteredsimlog)
+summary(filteredemulog)
+compositlog = rbind(filteredemulog,filteredsimlog)
+plot = ggplot(compositlog) + geom_point(aes(x=time,y=goodput,shape = experiment))
+plot

### 2012-11-27 sim-emu-source/linear-script2.R

@@ -1,0 +1,28 @@
+library(ggplot2)
+simlog = read.table("final4/linear-iliamo.log")
+emulog1 = read.table("final4/attacker-linear.log")
+emulog2 = read.table("final4/consumer-linear.log")
+
+emulog1$V1 = emulog1$V1 + 60
+emulog2$V1 = emulog2$V1 + 30
+
+emulog = rbind(emulog1,emulog2)
+
+names(emulog) = c("time","nodeid","prefix","packettype","seqnum")
+names(simlog) = c("time","nodeid","prefix","packettype","seqnum")
+emulog$experiment = "Emulation"
+simlog$experiment = "Simulation"
+emulog$experiment = as.factor(emulog$experiment)
+simlog$experiment = as.factor(simlog$experiment)
+
+filteredemulog = subset(emulog, packettype == "OutInterest")
+filteredsimlog = subset(simlog, packettype == "OutInterest")
+
+composite = rbind(filteredemulog, filteredsimlog)
+
+summary(emulog)
+summary(simlog)
+summary(filteredsimlog)
+summary(filteredemulog)
+
+plot = ggplot(composite) + geom_point(aes(x=time,y=seqnum,shape = prefix)) + facet_wrap(~experiment)

### 2012-11-27 sim-emu-source/tree-script.R

@@ -1,0 +1,34 @@
+library(ggplot2)
+simlog = read.table("final4/tree-iliamo.log")
+emulog = read.table("final4/consumer2-longtree.log")
+summary(emulog)
+summary(simlog)
+emulog$V1 = emulog$V1 + 30
+summary(emulog)
+summary(simlog)
+names(emulog) = c("time","nodeid","prefix","packettype","seqnum")
+names(simlog) = c("time","nodeid","prefix","packettype","seqnum")
+filteredemulog = subset(emulog, packettype == "InData" & prefix == "/good")
+filteredsimlog = subset(simlog, packettype == "InData" & prefix == "/good/leaf-3")
+summary(emulog)
+summary(simlog)
+summary(filteredsimlog)
+summary(filteredemulog)
+filteredemulog$size = 1024
+filteredsimlog$size = 1024
+filteredemulog$goodput = cumsum(filteredemulog$size)
+filteredsimlog$goodput = cumsum(filteredsimlog$size)
+filteredemulog$Experiment = "Emulation"
+filteredsimlog$Experiment = "Simulation"
+filteredsimlog$Experiment = as.factor(filteredsimlog$Experiment)
+filteredemulog$Experiment = as.factor(filteredemulog$Experiment)
+summary(filteredsimlog)
+summary(filteredemulog)
+compositlog = rbind(filteredemulog,filteredsimlog)
+
+compositlog = compositlog[sample(1:dim(compositlog)[1],size=500,replace=F),]
+
+plot = ggplot(compositlog) + geom_point(aes(x=time,y=goodput,shape = Experiment)) +scale_shape_manual(values=c(1,3)) + ylab("Total received data (KB)") + xlab("Time (seconds)")
+pdf("tree2.pdf")
+print(plot)
+dev.off()

### 2012-11-27 sim-emu-source/tree-script2.R

@@ -1,0 +1,45 @@
+library(ggplot2)
+library(stringr)
+library(splancs)
+simlog = read.table("final4/tree-iliamo.log")
+emulog1 = read.table("final4/attacker2-longtree.log")
+emulog2 = read.table("final4/consumer2-longtree.log")
+
+emulog1$V1 = emulog1$V1 + 60
+emulog2$V1 = emulog2$V1 + 30
+
+emulog = rbind(emulog1,emulog2)
+
+names(emulog) = c("time","nodeid","prefix","packettype","seqnum")
+names(simlog) = c("time","nodeid","prefix","packettype","seqnum")
+emulog$Experiment = "Emulation"
+simlog$Experiment = "Simulation"
+emulog$Experiment = as.factor(emulog$Experiment)
+simlog$Experiment = as.factor(simlog$Experiment)
+
+simlog$prefix = str_replace_all(simlog$prefix,"/leaf-0","")
+simlog$prefix = str_replace_all(simlog$prefix,"/leaf-1","")
+simlog$prefix = str_replace_all(simlog$prefix,"/leaf-2","")
+simlog$prefix = str_replace_all(simlog$prefix,"/leaf-3","")
+
+filteredemulog = subset(emulog, packettype == "OutInterest")
+filteredemulog = emulog[sample(1:dim(emulog)[1],size=300,replace=F),]
+
+filteredsimlog = subset(simlog, packettype == "OutInterest")
+filteredsimlog = simlog[sample(1:dim(simlog)[1],size=300,replace=F),]
+
+composite = rbind(filteredemulog, filteredsimlog)
+
+summary(emulog)
+summary(simlog)
+summary(filteredsimlog)
+summary(filteredemulog)
+
+#compositesample = composite[sample(1:dim(composite)[1],size=00,replace=F),]
+
+plot = ggplot(composite) + geom_point(aes(x=time,y=seqnum,shape = prefix), size =3) + scale_shape_manual(values=c(1,3)) + facet_wrap(~Experiment) + ylab("Transmitted Interests") + xlab("Time (seconds)")
+
+pdf("tree1.pdf")
+print(plot)
+dev.off()
+

### 2012-11-28 paper.tex
Adding temporary abstract and small title modification (used for paper registration)
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@825 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \documentclass[conference]{IEEEtran}
-\title{Mitigating (D)DoS in Named-Data Networking}%:\\ Cache/Content Poisoning}
+\title{Mitigating DDoS attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
 \author{anonymous}
@@
 %
-abstract
+Distributed Denial of Service attack is a major problem on the existing Internet.
+Named Data Networking (NDN) is a future Internet architecture that makes most existing DDoS attack infeasible.
+At the same, NDN may be vulnerable to NDN-specific attacks, such as Interest flooding attack. 
+This paper presents a simulation-based study on effects of Interset flooding DDoS attack, as well as study of a number of DDoS-attack prevention algorithms that can be implemented on NDN routers.
+The presented results give evidences that flooding-based attacks have much less effective in NDN than in the current Internet, as well as that inherent flow-balance property of NDN (i.e., one Interests brings at most one Data) can be used as a basis for effective DDoS mitigation algorithms.
 %

### 2012-11-29 intro.tex
introduction
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@830 df1a90cd-247b-4364-bdaf-287a704eb499

\section{Introduction \label{intro}}
Denial of service (DoS) and distributed denial of service attacks (DDoS) appeared not very long time after Internet got traction and since then a constant arms race is going on between information providers and attackers who want to knock a certain source of information down. Running a DDoS attack has become a very successful business model due to its general scalable nature, cheapness and lack of protection of information providers by government and law. Most popular and economically effective DDoS attacks are organized with botnets. A botnet agents get installed by many various ways on computers of ordinary people that leads to a very wide geographical distribution of the source of attack that makes blacklisting impossible (in contrast to single source DoS attacks).

In 2011 for the first time IPv6 DDoS attacks on commercial networks were observed. They occur rarely, but it only means that IPv6 is not widespread enough for attackers to put significant resources into such DDoS attacks. Principally, in terms of DDoS security IPv6 didn't advance that much comparing to standard IPv4 networks.

We believe that future Internet architectures can do and must do more for DDoS prevention.

\todo{
Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.

Our contributions.

Paper organization.}

In this paper we analyze all aspects of Interest flooding attack in NDN architecture, propose multiple defensive techniques against such kind of attacks, establish evaluation methodology using ndnSIM simulation software, execute small scale and Internet scale attack scenarios, and analyze our experimental results.

Following this introduction, Section 2 gives a brief overview of NDN architecture, and Section 3 lists and overviews possible attack in NDN. Section 4 thoroughly discusses Interest flooding attack, and Section 5 proposes multiple defensive techniques against it. Section 6 describes evaluation methodology and gives experimental results. Section 7 provides analysis based on our results. Section 8 concludes and describes future work.

%\begin{figure}[htpb]
%  \centering
%  \includegraphics[scale=0.5]{figures/sim-emu-power.pdf}
%  \caption{Strength of Interest flooding attack}
%  \label{fig:simemupower}
%\end{figure}

%\begin{figure}[htpb]
%  \centering
%  \includegraphics[scale=0.5]{figures/sim-emu-performance.pdf}
%  \caption{Data retrieval by legitimate clients}
%  \label{fig:simemuperf}
%\end{figure}

### 2012-11-29 ddos-ndn.tex
restruturing
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@831 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-11-29 intro.tex
@@
-\section{Introduction \label{intro}}
-Denial of service (DoS) and distributed denial of service attacks (DDoS) appeared not very long time after Internet got traction and since then a constant arms race is going on between information providers and attackers who want to knock a certain source of information down.
-Running a DDoS attack has become a very successful business model due to its general scalable nature, cheapness and lack of protection of information providers by government and law.
-Most popular and economically effective DDoS attacks are organized with botnets.
-A botnet agents get installed by many various ways on computers of ordinary people that leads to a very wide geographical distribution of the source of attack that makes blacklisting impossible (in contrast to single source DoS attacks).
-
-In 2011 for the first time IPv6 DDoS attacks on commercial networks were observed.
-They occur rarely, but it only means that IPv6 is not widespread enough for attackers to put significant resources into such DDoS attacks.
-Principally, in terms of DDoS security IPv6 didn't advance that much comparing to standard IPv4 networks.
-
-We believe that future Internet architectures can do and must do more for DDoS prevention.
-
-\todo{
-Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.
-
-Our contributions.
-
-Paper organization.}
-
-In this paper we analyze all aspects of Interest flooding attack in NDN architecture, propose multiple defensive techniques against such kind of attacks, establish evaluation methodology using ndnSIM simulation software, execute small scale and Internet scale attack scenarios, and analyze our experimental results.
-
-Following this introduction, Section 2 gives a brief overview of NDN architecture, and Section 3 lists and overviews possible attack in NDN.
-Section 4 thoroughly discusses Interest flooding attack, and Section 5 proposes multiple defensive techniques against it.
-Section 6 describes evaluation methodology and gives experimental results.
-Section 7 provides analysis based on our results.
-Section 8 concludes and describes future work.
+\section { DDoS Attacks in NDN \label{ddos-ndn}}
+Brief overview of possible attacks in NDN, and scope of what we will tackle in this paper (Interest flooding).
 

### 2012-11-29 paper.tex
introduction
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@829 df1a90cd-247b-4364-bdaf-287a704eb499
restruturing
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@831 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\section{Introduction \label{intro}}
-Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.
-
-Our contributions.
-
-Paper organization.
-
-\section{ CCN Overview\label{ccn-intro}}
-
-\section { DDoS Attacks in CCN \label{ccn-ddos}}
-Brief overview of possible attacks in CCN, and scope of what we will tackle in this paper (Interest flooding).
-
+\input{intro.tex}
+\input{ndn-overview.tex}
+\input{ddos-ndn.tex}
 \section { Interest Flooding in CCN }

### 2012-11-29 paper.tex
Correcting abstract
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@832 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-11-27 paper.tex
@@
-\documentclass[conference]{IEEEtran}
-\title{Mitigating (D)DoS in Named-Data Networking}%:\\ Cache/Content Poisoning}
+\documentclass[10pt, conference, compsocconf]{IEEEtran}
+
+\title{Mitigating DDoS attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
 \author{anonymous}
@@
 \begin{abstract}
-%
-abstract
-%
+
+Distributed Denial of Service attack is an ongoing problem in today's Internet. 
+A newly proposed future Internet architecture, Named Data Networking (NDN), lets end users request desired data by sending Interest packets, and the network forwards data packets to end users upon request only.
+Thus, NDN can effectively defeat the existing DDoS attacks, however it can be subject to new types of DoS attacks, namely Interest packet flooding.  
+In this paper we investigate effective solutions to mitigate Interest flooding attacks. 
+We use simulations to evaluate the design and our results show that our proposed solution can respond to Interest flooding attacks quickly, and that the inherent flow-balance property of NDN (i.e., one Interest packet retrieves at most one Data packet) can be used as a basis for effective DDoS mitigation algorithms.
+
 \end{abstract}
 
-\noindent {\bf Keywords:} Future Internet Architectures;
-Content-Centric Networks; Information-Centric Networks, Named-data
-Networking; Security; Denial-of-Service; Distributed
-Denial-of-Service.
+\begin{IEEEkeywords}
+Information-Centric Networks, Named-data Networking, Denial-of-Service
+\end{IEEEkeywords}
 
-\section{Introduction \label{intro}}
-Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.
-
-Our contributions.
-
-Paper organization.
-
-\section{ CCN Overview\label{ccn-intro}}
-
-\section { DDoS Attacks in CCN \label{ccn-ddos}}
-Brief overview of possible attacks in CCN, and scope of what we will tackle in this paper (Interest flooding).
-
+\input{intro.tex}
+\input{ndn-overview.tex}
+\input{ddos-ndn.tex}
 \section { Interest Flooding in CCN }

### 2012-12-01 ddos-ndn.tex
ddos attacks in ndn
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@840 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \section { DDoS Attacks in NDN \label{ddos-ndn}}
-Brief overview of possible attacks in NDN, and scope of what we will tackle in this paper (Interest flooding).
+Any DoS attack aims to exhaust system resources.
+In the context of NDN by term "system" we understand two things: 1) every individual NDN router 2) a distributed system consisting of some collection of NDN routers.
+In a first case, every major data structure (FIB, CS, PIT) is a potential surface for denial of service attack.
+In a second case, we consider: 1) bandwidth between NDN routers 2) caching capabilities of NDN routers 3) packet processing capabilities of NDN routers.
 
+Let's examine an individual NDN router first.
+Certainly, as any other piece of software each specific NDN implementation can have bugs and exploits e.g.
+buffer overflows leading to data corruption in cache, etc.
+In this paper we are assuming an idealized NDN implementation lacking any implementation bugs.
+
+In a general case, Forwarding Interest Base (FIB) is managed by routing protocol and if attackers have been able to get control over routing, they could advertise a huge number of FIB announcements that will fill up FIB table that may cause Interest processing delays and traffic redirection with amplification or black-holing.
+
+Pending Interest Table (PIT) is used to keep per packet forwarding state in NDN and is critical for Data delivery.
+Though PIT table has an upper limit on its size, it doesn't prevent attacker from injecting a huge number of false Interest packets at a very high rate, which eventually will lead to a situation where the whole PIT table is full of false Interest packets and is not able to keep forwarding state of Interests coming from legitimate users.
+This attack may look similar to TCP SYN-flood attack and we call it Interest flooding.
+
+Content Store (CS) is an effective obstacle for several types of DDoS attacks.
+CS possesses two important characteristics: maximum size and replacement policy.
+However, by knowing replacement policy attacker can construct a specific traffic generator that is using weaknesses of a chosen replacement procedure that will lead to increased processing time, slower packet delivery and in some cases de facto a complete inability to cache legitimate data.
+
+An infrastructure consisting of NDN routers is vulnerable to the following types of attacks: 
+\begin{enumerate}
+\item Interest flooding. 
+\item fkjgkfjgkfg
+\end{enumerate} 
 %\begin{figure}[htpb]

### 2012-12-01 intro.tex
ddos attacks in ndn
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@840 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
+IP architecture has a wide surface for denial of service attacks which takes the beginning from the thin-waist IP protocol, goes through transport level and up to DNS level.
+In IP it is very easy to forge source address and specify the exact destination that needs to be placed under attack that creates possibilities to perform various types of reflection DoS attacks.
+On transport level in TCP/IP SYN flood, RST flood and FIN-way attacks are very effective and popular.
+DNS system can be attacked in multiple ways, e.g.
+DNS amplification attack.
+
 We believe that future Internet architectures can do and must do more for DDoS prevention.
+By its design NDN architecture is not sensitive to any kind of reflection attacks due to the lack of host addresses and ubiquitous data caching.
+NDN architecture can operate without any DNS-like architecture since it routes and forwards packets based on human-readable names instead of IP addresses that need to be resolved with DNS.
 
-\todo{
-Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.
+%\todo{
+%Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.
 
-Our contributions.
+%Our contributions.
 
-Paper organization.}
+%Paper organization.}
 
-In this paper we analyze all aspects of Interest flooding attack in NDN architecture, propose multiple defensive techniques against such kind of attacks, establish evaluation methodology using ndnSIM simulation software, execute small scale and Internet scale attack scenarios, and analyze our experimental results.
+In this paper we provide a brief overview of possible DDoS attacks in NDN architecture, analyze all aspects of Interest flooding attack in NDN architecture, propose multiple defensive techniques against such attacks, establish evaluation methodology using ndnSIM simulation software, execute small scale and Internet scale attack scenarios, and analyze our experimental results.
 

### 2012-12-02 design.tex
Adding a couple of figures, more to come
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@843 df1a90cd-247b-4364-bdaf-287a704eb499

\section{Design}
\label{sec:design}

\subsection{Interest satisfaction statistics}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=4.5cm]{trivial-topo}
  \caption{Trivial topology (all links are 3Mbps/10ms)}
  \label{fig:trivial topology}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=1]{limits}
  \caption{Dynamics of the unsatisfied Interests statistics on gateway's interface towards the attacker}
  \label{fig:ratio example}
\end{figure}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2012-12-02 01-intro.tex
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-01 intro.tex
@@
-\section{Introduction \label{intro}}
+\section{Introduction}
+\label{sec:intro}
+
+% Introduction / Motivation
+% Brief introduction about attacks in NDN
+% Contributions of the paper
+
 Denial of service (DoS) and distributed denial of service attacks (DDoS) appeared not very long time after Internet got traction and since then a constant arms race is going on between information providers and attackers who want to knock a certain source of information down.
@@
 %\end{figure}
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2012-12-02 02-ndn-background.tex
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499

\section{ NDN Overview\label{ccn-intro}}
Named Data Networking (NDN) is a network architecture which aims to replace IP architecture by replacing IP’s host-to-host data delivery model with pull-based information retrieval model. In IP in order to retrieve data, data consumer have to know endpoint location of the desired data, in NDN all they have to know is data name. Names are hierarchical (non-flat) application-defined string names that are used for forwarding, routing and caching. A canonical NDN name looks in a following way: /ndn/ucla/CSdept/faculty/Lixia/webpage.

NDN communication uses two packet types: Interest and Data. An Interest packet contains data name and is issued by the receiver to express what data is needed. The sender puts a data packet into the network in response to an Interest. An Interest is “satisfied” when a Data packet is received with matching data name.

Every NDN node manages three important data structures:
\begin{enumerate}
\item{Forwarding Interest Base (FIB) maps name prefixes and multiple physical network interfaces (where to forward Interests). Having one-to-many relationship in this table allows multipath forwarding of Interests.}
\item{Content Store (CS) temporarily stores Data packets that pass through this node and allows fast Data retrieval.}
\item{Pending Interest Table (PIT) holds all "not yet satisfied" Interests that have been sent upstream. Every element contains a list of incoming and outgoing physical interfaces to enable multipath Interest forwarding and multipath Data delivery.}
\end{enumerate}

So how it works altogether? Every incoming Interest triggers a lookup in the Content Store and if the Data with matching data name have been found, it is sent back to the same physical interface from which the Interest has arrived. If CS lookup is unsuccessful, Interest must be sent further upstream and put in the PIT. However, all recurring Interests with the same prefix name are stacked together in the same PIT entry and are not sent to the upstream again until this PIT entry expires completely because of timeout. If Data returns from some upstream location it is replicated for each incoming physical interface stored in this PIT entry after that it is removed from PIT. In other words, multipath Data delivery is built-in in NDN.

%\begin{figure}[htpb]
%  \centering
%  \includegraphics[scale=0.5]{figures/sim-emu-power.pdf}
%  \caption{Strength of Interest flooding attack}
%  \label{fig:simemupower}
%\end{figure}

%\begin{figure}[htpb]
%  \centering
%  \includegraphics[scale=0.5]{figures/sim-emu-performance.pdf}
%  \caption{Data retrieval by legitimate clients}
%  \label{fig:simemuperf}
%\end{figure}

### 2012-12-02 05-evaluation.tex
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-11-29 paper.tex
@@
-\documentclass[conference]{IEEEtran}
-\title{Mitigating DDoS attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
-\author{anonymous}
+\section{Evaluation of Interest flooding mitigation methods}
+\label{sec:evaluation}
 
-\usepackage{graphicx}
-% \usepackage[colorlinks]{hyperref}
-\usepackage[]{hyperref}
-\usepackage{breakurl}
-\usepackage{url}
-\usepackage[nocompress]{cite}
-% \usepackage{verbatim}
-% \usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-
-\newcommand{\note}[1]{\vspace{2 mm}\par \noindent \textsc{Note}
-\framebox{\begin{minipage}[c]{0.40 \textwidth}
-\tt #1 \end{minipage}}\vspace{5 mm}\par}
-
-\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \textsc{ToDo}
-\framebox{\begin{minipage}[c]{0.42 \textwidth}
-\tt #1 \end{minipage}}\vspace{5 mm}\par}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-%
-Distributed Denial of Service attack is a major problem on the existing Internet.
-Named Data Networking (NDN) is a future Internet architecture that makes most existing DDoS attack infeasible.
-At the same, NDN may be vulnerable to NDN-specific attacks, such as Interest flooding attack. 
-This paper presents a simulation-based study on effects of Interset flooding DDoS attack, as well as study of a number of DDoS-attack prevention algorithms that can be implemented on NDN routers.
-The presented results give evidences that flooding-based attacks have much less effective in NDN than in the current Internet, as well as that inherent flow-balance property of NDN (i.e., one Interests brings at most one Data) can be used as a basis for effective DDoS mitigation algorithms.
-%
-\end{abstract}
-
-\noindent {\bf Keywords:} Future Internet Architectures;
-Content-Centric Networks; Information-Centric Networks, Named-data
-Networking; Security; Denial-of-Service; Distributed
-Denial-of-Service.
-
-\input{intro.tex}
-\input{ndn-overview.tex}
-\input{ddos-ndn.tex}
-\section { Interest Flooding in CCN }
-
-\section {Countermeasures against Interest flooding}
-
-Basic limits, probablity based on statistics, and dynamic window adjustment
-
-(Description of each of the above, and their implications)
-
-\section {Evaluation}
 \todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
@@
 
-\input{simulation-emulation.tex}
+\input{small-scale}
+\input{large-scale}
 
-\subsection{Results from probability based on statistics}
-
-\subsection{Results from dynamic window adjustment}
-
-\input{large-scale.tex}
-
-\section{Implications/Analysis}
-Lessons we learnt, comparison of different mitigation techniques. 
-Adapting these to mitigate other DDoS attacks.
-
-\section{Conclusions and Future Work}
-
-\bibliographystyle{plain}
-\bibliography{references}
-
-\appendix
-
-\input{algos/physical-limits.tex}
-
-\input{algos/fair-queueing.tex}
-
-\input{algos/dynamic-limits.tex}
-
-\input{algos/probabilistic.tex}
-
-\input{algos/stats.tex}
-
-\end{document}
+% \input{simulation-emulation.tex}

### 2012-12-02 07-discussion.tex
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499

\section{Discussion}
\label{sec:discussion}

Lessons we learnt, comparison of different mitigation techniques. 
Adapting these to mitigate other DDoS attacks.

### 2012-12-02 paper.tex
Adding a couple of figures, more to come
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@843 df1a90cd-247b-4364-bdaf-287a704eb499
Adding figures (topology sketch and simulation results) for large scale
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@845 df1a90cd-247b-4364-bdaf-287a704eb499
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\title{Mitigating DDoS attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
+\title{Mitigating Interest Flooding DDoS Attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
 \author{anonymous}
@@
 
-\newcommand{\note}[1]{\vspace{2 mm}\par \noindent \textsc{Note}
-\framebox{\begin{minipage}[c]{0.40 \textwidth}
-\tt #1 \end{minipage}}\vspace{5 mm}\par}
-
-\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \textsc{ToDo}
-\framebox{\begin{minipage}[c]{0.42 \textwidth}
-\tt #1 \end{minipage}}\vspace{5 mm}\par}
+\graphicspath{{figures/}}
 
@@
 
-\input{intro.tex}
-\input{ndn-overview.tex}
-\input{ddos-ndn.tex}
-\section { Interest Flooding in CCN }
+\input{01-intro}
 
-\section {Countermeasures against Interest flooding}
+\input{02-ndn-background}
 
-Basic limits, probablity based on statistics, and dynamic window adjustment
+\input{03-interest-flooding}
 
-(Description of each of the above, and their implications)
+\input{04-design}
 
-\section {Evaluation}
-\todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
-List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
+\input{05-evaluation}
 
-Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}
+\input{06-related}
 
-We want to explore the effectiveness of designed mitigation techniques in a two distinctive ways.
-First, we need to understand how each method works on a very ground level of a just few nodes and links.
-Second, we want to pick promising techniques and see if they work in a large scale networks of hundreds and thousands of nodes.
-To ensure the correct transition from small scale experiments to large scale experiments we had to use the same evaluation tool in order to eliminate any possibility of implementation discrepancy.
-As of today the only network simulator supporting full NDN logic is the NS-3 based ndnSIM software.
+\input{07-discussion}
 
-\input{simulation-emulation.tex}
-
-\subsection{Results from probability based on statistics}
-
-\subsection{Results from dynamic window adjustment}
-
-\input{large-scale.tex}
-
-\section{Implications/Analysis}
-Lessons we learnt, comparison of different mitigation techniques. 
-Adapting these to mitigate other DDoS attacks.
-
-\section{Conclusions and Future Work}
+\input{08-conclusion}
 
@@
 
-\appendix
-
-\input{algos/physical-limits.tex}
-
-\input{algos/fair-queueing.tex}
-
-\input{algos/dynamic-limits.tex}
-
-\input{algos/probabilistic.tex}
-
-\input{algos/stats.tex}
-
 \end{document}

### 2012-12-02 05-evaluation.tex
More reorganization and adding Makefile
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@847 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
-List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
+% \todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
+% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
 
-Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}
+% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}
 
@@
 % \input{simulation-emulation.tex}
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2012-12-02 06-related.tex
More reorganization and adding Makefile
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@847 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-02 05-evaluation.tex
@@
-\section{Evaluation of Interest flooding mitigation methods}
-\label{sec:evaluation}
-
-% \todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
-% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
-
-% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}
-
-We want to explore the effectiveness of designed mitigation techniques in a two distinctive ways.
-First, we need to understand how each method works on a very ground level of a just few nodes and links.
-Second, we want to pick promising techniques and see if they work in a large scale networks of hundreds and thousands of nodes.
-To ensure the correct transition from small scale experiments to large scale experiments we had to use the same evaluation tool in order to eliminate any possibility of implementation discrepancy.
-As of today the only network simulator supporting full NDN logic is the NS-3 based ndnSIM software.
-
-\input{small-scale}
-\input{large-scale}
-
-% \input{simulation-emulation.tex}
-
 %%% Local Variables: 

### 2012-12-02 eval-small-scale.tex
More reorganization and adding Makefile
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@847 df1a90cd-247b-4364-bdaf-287a704eb499

\subsection{Small-scale evaluations}
\label{sec:small-scale}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.3]{topo-tree-evil-5-good-0-producer-gw}
  \caption{Small-scale topology (one of the runs with 30\% of attackers, all links are 10Mbps with randomized delay 1-10ms)}
  \label{fig:small-scale-topo}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min}
  \caption{Average consumer Interest satisfaction ratios (first minute)}
  \label{fig:small-scale-topo 1}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min-after-1-min}
  \caption{Average consumer Interest satisfaction ratios (second minute)}
  \label{fig:small-scale-topo 2}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-dynamics-40}
  \caption{Satisfaction ratio dynamics during the attack (7 attackers / 9 legitimate)}
  \label{fig:small-scale-topo 3}
\end{figure}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2012-12-03 03-interest-flooding.tex
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499
More reorganization and adding Makefile
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@847 df1a90cd-247b-4364-bdaf-287a704eb499
Correcting algorithms. Far far far from perfect...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@849 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-01 ddos-ndn.tex
@@
-\section { DDoS Attacks in NDN \label{ddos-ndn}}
+\section{Interest Flooding in NDN}
+\label{sec:interest flooding}
+
+% Points here:
+% - Definition of the Interest flooding attack
+% - What makes Interest attack effective
+% - Assumptions about the network, attackers, attack traffic, and legitimate consumers
+% - References about other attacks and explicitly stating that this work aims to build a baseline for general Interest Flooding mitigation problem, with other attack profiles and malicious gateways.
+
 Any DoS attack aims to exhaust system resources.
@@
 
-An infrastructure consisting of NDN routers is vulnerable to the following types of attacks: 
-\begin{enumerate}
-\item Interest flooding. 
-\item fkjgkfjgkfg
-\end{enumerate} 
+The primary goal behind any flooding denial of service attack is to overwhelm network, CPU, or memory resources on routers or the target host.
+
+% An infrastructure consisting of NDN routers is vulnerable to the following types of attacks: 
+% \begin{enumerate}
+% \item Interest flooding. 
+% \item fkjgkfjgkfg
+% \end{enumerate}
+
 %\begin{figure}[htpb]

### 2012-12-03 04-design.tex
Initial reorganization
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@846 df1a90cd-247b-4364-bdaf-287a704eb499
Correcting algorithms. Far far far from perfect...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@849 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-02 design.tex
@@
-\section{Design}
+\section{Interest flooding mitigation methods}
 \label{sec:design}
 
-\subsection{Interest satisfaction statistics}
+% Points what should be here:
+% - What can be done (in general) to mitigate flooding attack
+% - Which building blocks NDN architecture gives to mitigate Interest flooding attacks: Interest limits, ability to measure Interest satisfaction performance (Interest satisfaction stats)
+% - Methods to set these limits: static/dynamic
+% - Methods how limits can be applied: best-effort (fifo), "fair" queuing, probabilistic
+% - Reference to caching: we don't consider it here, but caching provides additional level of protection, especially for certain types of attacks
 
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=4.5cm]{trivial-topo}
-  \caption{Trivial topology (all links are 3Mbps/10ms)}
-  \label{fig:trivial topology}
-\end{figure}
+% Our definition of attack mitigation is that good clients are still able to access data on the producer.
 
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[scale=1]{limits}
-  \caption{Dynamics of the unsatisfied Interests statistics on gateway's interface towards the attacker}
-  \label{fig:ratio example}
-\end{figure}
+In this section we present several methods to mitigate Interest flooding attacks in NDN, featuring different degrees of implementation complexity, as well as different degrees of effectiveness.
+
+The presented methods rely on the core NDN principle of the flow balance between Interest and Data packets: Data packet can be forwarded only in response to the incoming Interest and each Interest is satisfied by at most one Data packet.
+As a result of this principle, all traffic on NDN is ``receiver''-driven, where the ``receiver'' is either a user or any router on the path between the user and a Data producer.
+Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
+At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
+
+% Combining per-incoming interface data plane performance statistics with
+
+% Disclaimer
+% The presented solutions to mitigate Interest flooding DDoS attacks
+
+% In particular, we explore different mechanisms to app
+
+% Basic limits, probablity based on statistics, and dynamic window adjustment
+
+\input{algos/physical-limits.tex}
+
+\input{algos/stats.tex}
+
+\input{algos/fair-queueing.tex}
+
+\input{algos/probabilistic.tex}
+
+\input{algos/dynamic-limits.tex}
 

### 2012-12-03 algos/fair-queueing.tex
Correcting algorithms. Far far far from perfect...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@849 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Physical limits (per-outgoing-interface) described in Section~\ref{sec:physical limits} provide ability to fully utilize a downstream link, (almost completely) avoiding congestion in the link.
+Physical limits (per-outgoing-interface) described in Section~\ref{sec:physical limits} provide ability to fully utilize a downstream link, largely avoiding congestion in the link.
 However, this limitation approach does not attempt to utilize data plane performance knowledge (i.e., Interest satisfaction ratio statistics) to discriminate good and malicious Interests.
@@
 \begin{algorithmic}[1]
-\Function{InInterest}{Interest $i$, InFace $if$}
-\For{\textbf{each} OutFace $of$ \textbf{in} ForwardingDecision($i,if$)}
+\Function{InInterest}{Interest $i$, InInterface $if$}
+\For{\textbf{each} OutInterface $of$ \textbf{in} FwDecision($i,if$)}
     \If{$of$ is under physical limits}
@@
         \State $q$.PushInterest($i$)
-        \State $q$.UpdateWeight($if$.GetSatisfactionRatio())
     \EndIf
@@
 \State{} \Comment{\textit{Called when an Interest is satisfied or times out}}
-\Function{OnReady}{OutFace $of$}
-    \State{} \Comment{\textit{get a non-empty queue using weighted round-robin}}
+\Function{OnReady}{OutInterface $of$}
+    \State{} \Comment{\textit{get a non-empty queue using round-robin}}
     \State Queue $q \leftarrow$ $of$.GetNonEmptyQueue 

### 2012-12-03 03-interest-flooding.tex
interest flooding
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@850 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-11-29 ddos-ndn.tex
@@
-\section { DDoS Attacks in NDN \label{ddos-ndn}}
-Brief overview of possible attacks in NDN, and scope of what we will tackle in this paper (Interest flooding).
+\section{Interest Flooding in NDN}
+\label{sec:interest flooding}
+
+% Points here:
+% - Definition of the Interest flooding attack
+% - What makes Interest attack effective
+% - Assumptions about the network, attackers, attack traffic, and legitimate consumers
+% - References about other attacks and explicitly stating that this work aims to build a baseline for general Interest Flooding mitigation problem, with other attack profiles and malicious gateways.
+
+NDN uses a pull-based data retrieval model which means that the network is always open for accepting incoming Interest packets in order to return Data back since NDN does not have any form of client authentication.
+
+Interest flooding attack can be performed by a large set (possibly geographically distributed) of malicious clients (bots) that are injecting Interest packets into the network at a very fast pace.
+Interest flooding attack has devastating effects for the following reasons.
+
+Pending Interest Table (PIT) is used to keep per packet forwarding state in NDN and is critical for Data delivery.
+Though PIT table has an upper limit on its size, it doesn't prevent attacker from injecting a huge number of false Interest packets at a very high rate, which eventually will lead to a situation where the whole PIT table is full of false Interest packets and is not able to keep forwarding state of Interests coming from legitimate users.
+In this view it may look similar to TCP SYN-flood attack.
+
+Another huge negative effect of Interest flooding attack is bandwidth exhaustion.
+In case if Interest flooding attack is performed using existing or static name prefixes, Content Store (CS) effectively prevents bandwidth exhaustion by caching static content along the route and bringing this static Data closer to attacking bots.
+However, if Interest flooding attack is performed using name prefixes for dynamically generated or non-existing content, Content Store can do nothing against this and bandwidth upstream to the content producer will be exhausted.
+
+Interest Flooding attack that uses name prefixes for dynamically generated content belongs to application layer attacks and requires knowing application specific semantics.
+In this paper we are considering network level attacks performed by sending Interests with for non-existing data using prefix names with some random components.
+We make the assumption that the set of malicious clients (botnet) has a greedy behavior and tries to send as many false Interest packets as possible at any time given its connectivity options.
+Though NDN is capable of multipath Interest forwarding and forwarding strategy switching, we are using Best Route (single path) forwarding strategy in all of our experiments.
+
+This work aims to build a baseline for general Interest Flooding mitigation problem, with other attack profiles (smart and non-greedy) and malicious gateways (NDN routers inside the network perimeter) being left for a future work.
+Also we want to mention other possible DoS attacks in NDN architecture, such as
+
+%Any DoS attack aims to exhaust system resources.
+In the context of NDN by term "system" we understand two things: 1) each individual NDN router 2) a distributed system consisting of some collection of NDN routers.
+In a first case, every major data structure (FIB, CS, PIT) is a potential surface for denial of service attack.
+In a second case, we consider: 1) bandwidth between NDN routers 2) caching capabilities of NDN routers 3) packet processing capabilities of NDN routers.
+
+%Let's examine an individual NDN router first.
+Certainly, as any other piece of software each specific NDN implementation can have bugs and exploits e.g.
+buffer overflows leading to data corruption in cache, etc.
+In this paper we are assuming an idealized NDN implementation lacking any implementation bugs.
+
+%In a general case, Forwarding Interest Base (FIB) is managed by routing protocol and if attackers have been able to get control over routing, they could advertise a huge number of FIB announcements that will fill up FIB table that may cause Interest processing delays and traffic redirection with amplification or black-holing.
+
+%Pending Interest Table (PIT) is used to keep per packet forwarding state in NDN and is critical for Data delivery.
+Though PIT table has an upper limit on its size, it doesn't prevent attacker from injecting a huge number of false Interest packets at a very high rate, which eventually will lead to a situation where the whole PIT table is full of false Interest packets and is not able to keep forwarding state of Interests coming from legitimate users.
+This attack may look similar to TCP SYN-flood attack and we call it Interest flooding.
+
+%Content Store (CS) is an effective obstacle for several types of DDoS attacks.
+CS possesses two important characteristics: maximum size and replacement policy.
+However, by knowing replacement policy attacker can construct a specific traffic generator that is using weaknesses of a chosen replacement procedure that will lead to increased processing time, slower packet delivery and in some cases de facto a complete inability to cache legitimate data.
+
+%The primary goal behind any flooding denial of service attack is to overwhelm network, CPU, or memory resources on routers or the target host.
+
+% An infrastructure consisting of NDN routers is vulnerable to the following types of attacks: 
+% \begin{enumerate}
+% \item Interest flooding. 
+% \item fkjgkfjgkfg
+% \end{enumerate}
 

### 2012-12-04 03-interest-flooding.tex
Checkpoint (unfinished section 3, attack description)
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@851 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-01 ddos-ndn.tex
@@
-\section { DDoS Attacks in NDN \label{ddos-ndn}}
-Any DoS attack aims to exhaust system resources.
-In the context of NDN by term "system" we understand two things: 1) every individual NDN router 2) a distributed system consisting of some collection of NDN routers.
-In a first case, every major data structure (FIB, CS, PIT) is a potential surface for denial of service attack.
-In a second case, we consider: 1) bandwidth between NDN routers 2) caching capabilities of NDN routers 3) packet processing capabilities of NDN routers.
+\section{Interest Flooding in NDN}
+\label{sec:interest flooding}
 
-Let's examine an individual NDN router first.
-Certainly, as any other piece of software each specific NDN implementation can have bugs and exploits e.g.
-buffer overflows leading to data corruption in cache, etc.
-In this paper we are assuming an idealized NDN implementation lacking any implementation bugs.
+% Points here:
+% - Classification
+% - Mechanisms: congestion and memory exhaustion
+% - Target
+% - Effectiveness: random names, non-existing content
+% - Assumptions: the network, attackers, attack traffic, and legitimate consumers
 
-In a general case, Forwarding Interest Base (FIB) is managed by routing protocol and if attackers have been able to get control over routing, they could advertise a huge number of FIB announcements that will fill up FIB table that may cause Interest processing delays and traffic redirection with amplification or black-holing.
+%???
+- References about other attacks and explicitly stating that this work aims to build a baseline for general Interest Flooding mitigation problem, with other attack profiles and malicious gateways.
 
-Pending Interest Table (PIT) is used to keep per packet forwarding state in NDN and is critical for Data delivery.
-Though PIT table has an upper limit on its size, it doesn't prevent attacker from injecting a huge number of false Interest packets at a very high rate, which eventually will lead to a situation where the whole PIT table is full of false Interest packets and is not able to keep forwarding state of Interests coming from legitimate users.
-This attack may look similar to TCP SYN-flood attack and we call it Interest flooding.
+\paragraph{Classification}
 
-Content Store (CS) is an effective obstacle for several types of DDoS attacks.
+Interest flooding attack belongs to a class of network-level flooding attacks, where an attacker or a set of distributed attackers inject excessive amounts of Interests in order to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
+%
+% Definition of service
+%
+Service for legitimate users is disrupted when the network fails to satisfy Interests either because the Interests did not get through to (one of) the data producer(s) or nearby caches or the Data were lost on the way back (e.g., because of congested links).
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=\columnwidth]{attack-definition}
+  \caption{Example of the Interest flooding attack}
+  \label{fig:flooding example}
+\end{figure}
+
+\paragraph{Mechanism}
+
+The Interest flooding attack has two-fold effect on service quality in NDN network: \textbf{creates network congestion} and \textbf{exhaust resources on routers}.
+
+Like any other packets in the network, malicious Interests consume a portion network capacity.
+Thus, a large amount of malicious Interests can lead to network congestion and drop of the legitimate Interests and Data packets.
+%  (in case of bidirectional communication)
+% The resource exhaustion effect can be much more ???.
+% and more critical is the effect on memory and CPU resources of NDN routers.
+
+As NDN routers maintain per-packet states for each forwarded Interest (entry in Pending Interests Table), an excessive volume of malicious Interests leads to creating an excessive number of PIT entries and exhaustion of routers' resources.
+When a router has no memory to create a PIT entry for an incoming Interest, it drops this Interest.
+% there is no point in forwarding the Interest further.
+% Otherwise, if Data comes back, it would be considered unsolicited and dropped anyways.
+Therefore, the routers' memory exhaustion effect may disrupt service for legitimate users even without causing network congestion.
+
+\paragraph{Target}
+
+Because communication in NDN is content-centric, it is impossible for an adversary to target specific routers or end-hosts, as neither of them have a global network identity.
+However, an adversary can target a specific namespace, which in NDN network can loosely correspond to a network location or sets of network locations.
+For example on Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace and is single-homed to router B, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.
+It should be noted that if connectivity in NDN network is rich (users are multi-homing to many providers, many interconnections between providers), targeting of specific locations is largely unfeasible, as stateful Interest forwarding strategy in NDN can fully and effectively utilize multiple available paths to destination~\cite{adaptive-forwarding}.
+
+% \paragraph{Countermeasures}?
+
+\paragraph{Effectiveness}
+% Эффективность атаки
+% - как можно повысить эффективность
+
+% Effectiveness of the attack depends on how well volume of the Interests creates congestion near the Data producer, as well as how well r
+
+Effectiveness of the Interest flooding attack directly depends on attack mechanism.
+
+If the attack is primarily implemented using network congestion mechanism, then
+
+One of the key parameters for the effective Interest flooding attack is the way attackers generate names for the malicious Interests.
+The stateful Interest forwarding and in-network data storage in NDN may nullify effect even of the large-scale flooding attack, if names for the malicious Interests are generated in a wrong way.
+In particular, if distributed attackers generate similar names for the Interests, these Interests will be collapsed on NDN routers, resulting in a minuscule volume of the malicious Interests actually reaching the Data producer.
+Also, if attackers express Interests for the data that can be returned from caches (popular Data or Data recently pulled by another attacker), the Data producer may not even receive any malicious Interest.
+
+% Another parameter is how long Interests are sta
+
+To implement an effective Interest flooding attack, one needs to ensure that a large volume of Interests is reaching targe
+
+Increase time Interests are staying on NDN routers.
+
+NDN collapses similar Interests: attackers need to express different Interests in order to avoid collapsing
+NDN caches data: attackers need to express junk Interests in order for interest to reach the data producer.
+
+If malicious Interests can be collapsed or hit caches on the way towards to the Data producer, attack can have no effect at all.
+
+the effect of the attack can be almost nullified.
+
+Lastl
+
+Second factor is how well attack traffic is penetra
+
+% How interest flooding attack can be the most effective
+%
+
+%Content Store (CS) is an effective obstacle for several types of DDoS attacks.
 CS possesses two important characteristics: maximum size and replacement policy.
@@
 
-An infrastructure consisting of NDN routers is vulnerable to the following types of attacks: 
-\begin{enumerate}
-\item Interest flooding. 
-\item fkjgkfjgkfg
-\end{enumerate} 
-%\begin{figure}[htpb]
-%  \centering
-%  \includegraphics[scale=0.5]{figures/sim-emu-power.pdf}
-%  \caption{Strength of Interest flooding attack}
-%  \label{fig:simemupower}
-%\end{figure}
+\paragraph{Assumptions}
+% - assumptions about attacker position
+% - assumptions about the producer / producer namespace
+% - assumptions about the attack traffic / attack pattern
 
-%\begin{figure}[htpb]
-%  \centering
-%  \includegraphics[scale=0.5]{figures/sim-emu-performance.pdf}
-%  \caption{Data retrieval by legitimate clients}
-%  \label{fig:simemuperf}
-%\end{figure}
+Not considering colluding attackers
+
+% In this paper we are making an assumption that the attacker is trying to prevent legitimate users to access data from the producer by sending excessive amounts of Interests for data in the producers namespace, but which cannot be satisfied by the producer.
+% Assuming the network has only static content.  
+% If the network having only static content, then there is no point for the attacker to issue satisfiable interests, as they I'll brig data, which will be cached nearby and future interests for the same name would not even reach vicinity of the producer.
+% That is, the effect of the attack will be minimized.
+% Another point, that is probably is better. 
+% If attacker issues interess that can be satisfied, then such interests will not stay in PITs long, not creating any challenges for the NDN routers' resources.
+
+% In this paper we are considering network level attacks performed by sending Interests with for non-existing data using prefix names with some random components.
+We make the assumption that the set of malicious clients (botnet) has a greedy behavior and tries to send as many false Interest packets as possible at any time given its connectivity options.
+Though NDN is capable of multipath Interest forwarding and forwarding strategy switching, we are using Best Route (single path) forwarding strategy in all of our experiments.
+
+\paragraph{Disclaimer}
+In this paper we are not trying to completely solve all denial of service problems that can be caused by various variations of the Interest flooding attack.
+Our primary focus is to demonstrate that while NDN opens door to new types of denial of service attacks, stateful packet forwarding in NDN makes it possible to mitigate such attacks, adding little additional complexity to the network.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2012-12-04 03-interest-flooding.tex
Section 3 update
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@852 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 %
-Service for legitimate users is disrupted when the network fails to satisfy Interests either because the Interests did not get through to (one of) the data producer(s) or nearby caches or the Data were lost on the way back (e.g., because of congested links).
+Service for legitimate users is disrupted when the network fails to satisfy Interests either because the Interests did not get through to the data producer or nearby cache, or the Data were lost on the way back to the requester (e.g., because of congested links).
 
@@
 
-The Interest flooding attack has two-fold effect on service quality in NDN network: \textbf{creates network congestion} and \textbf{exhaust resources on routers}.
+The Interest flooding attack has two-fold effect on service quality in NDN network: it \textbf{creates network congestion} and \textbf{exhaust resources on routers}.
 
@@
 % Otherwise, if Data comes back, it would be considered unsolicited and dropped anyways.
-Therefore, the routers' memory exhaustion effect may disrupt service for legitimate users even without causing network congestion.
+Therefore, the routers' memory exhaustion effect may disrupt service for legitimate users even without causing network congestion, if the router has limited memory resources.
 
@@
 % Эффективность атаки
-% - как можно повысить эффективность
 
-% Effectiveness of the attack depends on how well volume of the Interests creates congestion near the Data producer, as well as how well r
+To efficiently implement the Interest flooding attack, an adversary needs to make sure that (1) the expressed Interests are getting as close to the Data producer as possible, as well as (2) the corresponding PIT entry (state) is kept on NDN routers for as long as possible.
+In order to achieve effectively the first requirement, the malicious Interests should avoid collapsing and cache hits.
+To keep PIT entry for a prolonged period of time, the malicious Interests should not bring any data.%
+\footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.
+For example, and we assume this in the rest of the paper, the maximum time for which any Interest is admitted is one second.}
 
-Effectiveness of the Interest flooding attack directly depends on attack mechanism.
-
-If the attack is primarily implemented using network congestion mechanism, then
-
-One of the key parameters for the effective Interest flooding attack is the way attackers generate names for the malicious Interests.
-The stateful Interest forwarding and in-network data storage in NDN may nullify effect even of the large-scale flooding attack, if names for the malicious Interests are generated in a wrong way.
-In particular, if distributed attackers generate similar names for the Interests, these Interests will be collapsed on NDN routers, resulting in a minuscule volume of the malicious Interests actually reaching the Data producer.
-Also, if attackers express Interests for the data that can be returned from caches (popular Data or Data recently pulled by another attacker), the Data producer may not even receive any malicious Interest.
-
-% Another parameter is how long Interests are sta
-
-To implement an effective Interest flooding attack, one needs to ensure that a large volume of Interests is reaching targe
-
-Increase time Interests are staying on NDN routers.
-
-NDN collapses similar Interests: attackers need to express different Interests in order to avoid collapsing
-NDN caches data: attackers need to express junk Interests in order for interest to reach the data producer.
-
-If malicious Interests can be collapsed or hit caches on the way towards to the Data producer, attack can have no effect at all.
-
-the effect of the attack can be almost nullified.
-
-Lastl
-
-Second factor is how well attack traffic is penetra
-
-% How interest flooding attack can be the most effective
-%
-
-%Content Store (CS) is an effective obstacle for several types of DDoS attacks.
-CS possesses two important characteristics: maximum size and replacement policy.
-However, by knowing replacement policy attacker can construct a specific traffic generator that is using weaknesses of a chosen replacement procedure that will lead to increased processing time, slower packet delivery and in some cases de facto a complete inability to cache legitimate data.
+In other words, to maximize effect of the attack, each malicious Interest generated by individual attack bots should have a unique name and should not correspond to any existing data (\emph{unique junk Interests}).
 
@@
 
-Not considering colluding attackers
+In this paper we are making the following assumptions about the Interest flooding attack:
+\begin{itemize}
+\item only client nodes can be compromised and become attack bots;
+\item there are no colluding attackers inside the Data producer's network; and
+\item the attack is carried only using unique junk Interests.
+\end{itemize}
 
-% In this paper we are making an assumption that the attacker is trying to prevent legitimate users to access data from the producer by sending excessive amounts of Interests for data in the producers namespace, but which cannot be satisfied by the producer.
-% Assuming the network has only static content.  
-% If the network having only static content, then there is no point for the attacker to issue satisfiable interests, as they I'll brig data, which will be cached nearby and future interests for the same name would not even reach vicinity of the producer.
-% That is, the effect of the attack will be minimized.
-% Another point, that is probably is better. 
-% If attacker issues interess that can be satisfied, then such interests will not stay in PITs long, not creating any challenges for the NDN routers' resources.
+We also assume that NDN forwarding strategy uses only single-path Interest forwarding, always choosing the best-metric route advertised by the routing protocol.
+This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
 
-% In this paper we are considering network level attacks performed by sending Interests with for non-existing data using prefix names with some random components.
-We make the assumption that the set of malicious clients (botnet) has a greedy behavior and tries to send as many false Interest packets as possible at any time given its connectivity options.
-Though NDN is capable of multipath Interest forwarding and forwarding strategy switching, we are using Best Route (single path) forwarding strategy in all of our experiments.
+% Though NDN is capable of multipath Interest forwarding and forwarding strategy switching, we are using Best Route (single path) forwarding strategy in all of our experiments.
 
 \paragraph{Disclaimer}
+
 In this paper we are not trying to completely solve all denial of service problems that can be caused by various variations of the Interest flooding attack.
-Our primary focus is to demonstrate that while NDN opens door to new types of denial of service attacks, stateful packet forwarding in NDN makes it possible to mitigate such attacks, adding little additional complexity to the network.
+Our primary focus is to demonstrate that while NDN opens doors to new types of denial of service attacks, stateful packet forwarding of NDN makes it possible to mitigate such attacks, adding little additional complexity to the network.
+In section~\ref{sec:discussion} we discuss our choice of the assumptions in more detail, as well as discuss potential of the Interest flooding attack under several other attack assumptions.
 

### 2012-12-04 03-interest-flooding.tex
Small corrections
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@853 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 %???
-- References about other attacks and explicitly stating that this work aims to build a baseline for general Interest Flooding mitigation problem, with other attack profiles and malicious gateways.
+- References to the discussion about other types of attacks (ordifferent attack assumptions) about other attacks and explicitly stating that this work aims to build a baseline for general Interest Flooding mitigation problem, with other attack profiles and malicious gateways.
 
@@
 Interest flooding attack belongs to a class of network-level flooding attacks, where an attacker or a set of distributed attackers inject excessive amounts of Interests in order to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-%
-% Definition of service
-%
 Service for legitimate users is disrupted when the network fails to satisfy Interests either because the Interests did not get through to the data producer or nearby cache, or the Data were lost on the way back to the requester (e.g., because of congested links).
@@
 \paragraph{Effectiveness}
-% Эффективность атаки
 
-To efficiently implement the Interest flooding attack, an adversary needs to make sure that (1) the expressed Interests are getting as close to the Data producer as possible, as well as (2) the corresponding PIT entry (state) is kept on NDN routers for as long as possible.
+To efficiently implement the Interest flooding attack, an adversary needs to make sure (1) that the expressed Interests are getting as close to the Data producer as possible, and (2) that the corresponding PIT entries (state) are kept on NDN routers for as long as possible.
 In order to achieve effectively the first requirement, the malicious Interests should avoid collapsing and cache hits.
-To keep PIT entry for a prolonged period of time, the malicious Interests should not bring any data.%
+To keep PIT entries for a prolonged period of time, the malicious Interests should not bring any data.%
 \footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.
@@
 
-In other words, to maximize effect of the attack, each malicious Interest generated by individual attack bots should have a unique name and should not correspond to any existing data (\emph{unique junk Interests}).
+In other words, to maximize effect of the attack, each malicious Interest generated by an individual attack bot should have a unique name and should not correspond to any existing data (\emph{unique junk Interests}).
 
@@
 \item only client nodes can be compromised and become attack bots;
-\item there are no colluding attackers inside the Data producer's network; and
-\item the attack is carried only using unique junk Interests.
+\item there are no colluding attackers inside the Data producer's network;
+\item the attack is carried only using unique junk Interests; and
+\item there is only one Data producer for the attacked prefix.
 \end{itemize}
@@
 This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
-
-% Though NDN is capable of multipath Interest forwarding and forwarding strategy switching, we are using Best Route (single path) forwarding strategy in all of our experiments.
 

### 2012-12-04 03-interest-flooding.tex
Modifying figures in evaluation
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@854 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-The Interest flooding attack has two-fold effect on service quality in NDN network: it \textbf{creates network congestion} and \textbf{exhaust resources on routers}.
+The Interest flooding attack has two-fold effect on service quality in NDN network: it \emph{creates network congestion} and \emph{exhaust resources on routers}.
 

### 2012-12-05 04-design.tex
First part of the design section semi-done
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@855 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-The presented methods rely on the core NDN principle of the flow balance between Interest and Data packets: Data packet can be forwarded only in response to the incoming Interest and each Interest is satisfied by at most one Data packet.
-As a result of this principle, all traffic on NDN is ``receiver''-driven, where the ``receiver'' is either a user or any router on the path between the user and a Data producer.
+%   - Naive approach to Interest Limits (that is called physical limits everywhere else)
+%     Example how this can be implemented in a simple way
+%     Baseline solution
+%   - Interest limits with "fair" queuing
+%     Improving problem of simple limits (no single face can dominate), but doesn't solve the proble
+
+% - Attack mitigation
+%   - Per-incoming interface Interest statistics
+
+%   - Dynamic Interests limit adjustments
+
+%   - Probabilistic Interest accept
+
+Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
+Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
 Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
@@
 
-% Combining per-incoming interface data plane performance statistics with
+\subsection{Na\"{i}ve attack mitigation}
 
-% Disclaimer
-% The presented solutions to mitigate Interest flooding DDoS attacks
+% In a normal network operation, the size of Interests packets is supposed to be significantly smaller than the size of the requested Data.
 
-% In particular, we explore different mechanisms to app
+% All communication in NDN network is host-to-host and receiver-driven.
 
-% Basic limits, probablity based on statistics, and dynamic window adjustment
+The most obvious and na\"{i}ve method to mitigate the Interest flooding attack is to limit the number of forwarded Interests out of each interface. 
+That is, if it is known that the amount of already forwarded Interests can fully utilize the downstream link, an NDN node---an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
+For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
+In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
+
+\subsubsection{Interest limits (physical limits)}
+\label{sec:physical limits}
 
@@
 
-\input{algos/stats.tex}
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Interest limits with per-interface fairness}
+\label{sec:queuing}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Intelligent attack mitigation}
+
+About additional knowledge about interests.
+
+Another unique feature of the NDN architecture is stateful packet forwarding~\cite{adaptive-forwarding} and symmetric flow of Interests and Data packets.
+Every time Interests is send out to the Interface, the router will be able to learn various parameters about this Interest.
+
+From the DDoS mitigation point of view, one of the important parameters is to determine from which interface
+
+In order to mitigate a denial of service attack it is vital to know the origin of the attack.
+I the origin of the attack is known, then the attack can be easily suppressed and eventually localized.
+In our definition of the attack is that
+
+interest of the attackers are not getting satisfied. 
+Every router can learn fro m which interfaces attack traffic is coming and do certain actions to limit forwarding of suspicious interest.
+In other words, without trying to distinguish legitimate and malicious interests on the basis of the Interest prefix, routers distinguish them based on recent performance.
+
+\subsubsection{Data plane performance tracking}
+\label{sec:stats}
+
+\input{algos/stats.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Probabilistic Interest accept}
+\label{sec:probabilistic}
+
 \input{algos/probabilistic.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Dynamic adjustments of window-based limits}
+\label{sec:dynamic limits}
 

### 2012-12-05 algos/physical-limits.tex
Adding fair-queueing algorithm description
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@815 df1a90cd-247b-4364-bdaf-287a704eb499
Correcting algorithms. Far far far from perfect...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@849 df1a90cd-247b-4364-bdaf-287a704eb499
First part of the design section semi-done
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@855 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-\subsection{Physical limits}
+% \subsection{Physical limits}
+% \label{sec:physical limits}
 
-The requirement to send an Interest in order to receive Data packet, provides an NDN consumer a unique opportunity to request the right amount of Data.
-Moreover, the same opportunity to control the amount of data flow is given not only to consumers, but all routers between consumer and producer (or nearby caches).  
-In other words, every node, either a consumer or an intermediate router, is able to control how much data it wants to receive by limiting the number of forwarded Interests.
+One of the promising and simple ways to set and enforce limit on the number of forwarded Interests is a variation of the well-known bag of tokens algorithm, illustrated on Fig.~\ref{fig:bag of tokens}.
+Each router implementing the algorithm maintains a ``bag'' with a limited number of tokens for every outgoing interface.
+Whenever an Interest is ready to be forwarded, the router ``borrows'' a token from the outgoing interface's bag, dropping the Interest if the bag is empty.
+At the same time, when the requested Data comes back or the Interest times out, the token is returned to the appropriate bag based on the information in PIT, ready to be borrowed again by a new incoming Interset.
 
-The limitation can implemented in a number of different ways, including leaky bucket scheduling and window-based flow control.
-We decided to following TCP-like window-based flow control and applied the sliding window approach to implement Interest limits.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.7]{token-bag}
+  \caption{Bag of tokens algorithm: tokens borrowed when Interest is forwarded and returned when Data comes back or Interest times out}
+  \label{fig:bag of tokens}
+\end{figure}
 
-The size of the window defines how many Interests can be send out before Interests get satisfied or expired.
-From the one hand, this size should be large enough to ``fill the pipe,'' meaning that a node needs to send enough Interests to receive Data at full capacity of the incoming link.
-On the other hand, the window's size should not be too large to avoid excessive buffering and congestion of the Data packet.
-Thus, the ideal size for such a window need to be defined proportional to link's bandwidth-delay product~\cite{tcp-survey}.
-With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
+Since the number of tokens in the bag defines how many Interests are forwarded and not yet satisfied or timed out (pending Interests), this number should be large enough to fully utilize the network and small enough to avoid excessive buffering and drops at the upstream routers.
+The ideal value for the number of tokens (interest limit) for each individual link would be defined proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
+This can be formalized in the following way:
+% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
 
-\[
+\begin{equation}
 \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
-\]
+\end{equation}
 
-Note that the value of \textit{Delay} is not known a priory and varies between different Interest-Data flows.
-However, we do not need to know the exact value of the delay and can set it as an average round trip delay among all flows (with a reasonable filtering of outliers).
-This way, the statistical traffic multiplexing with link-level buffering will allow full utilization of the downstream link.
-Exactly the same reasoning can be applied to the \textit{Data packet size} parameter, which can also be set to an average observed Data packet size.
+In this equation, \emph{Delay} is the expected time of Interest being satisfied and \emph{Data packet size} is the size of the returned Data packet.
+Although both these values are not known a priory and vary between different Interest-Data exchanges, it is not really necessary to know their exact values.
+One can simply set the Interest limit based on the average values of round trip time and observed Data packet size, as the network buffers can smooth out most of the network fluctuations.
 
-Unlike rate-based approaches, window-based limiting does not require precise knowledge about the rate, as well does not need precise scheduling mechanisms.
-Like in TCP, the window-based flow is self-clocking, easily adjusting itself to any traffic patterns.
+In the rest of the paper we will refer to Interest limits set based on the bandwidth-delay product as \emph{Physical limits}.
+Pseudocode~\ref{alg:simple limits} shows implementation details of how the Physical limits algorithms.
+Every time an Interest is ready to be send to an outgoing interface $of$ (OutInterest function), we check if the token bag is not empty.
+If there is at least one free token available, we are ``borrowing'' it, forwarding the Interests, and remembering the outgoing interface in the corresponding entry of PIT.
+Functions InData and Timeout ensure that tokens are returned whenever the requested Data is received or Interest times out.
+
+\floatname{algorithm}{Pseudocode}
+
+\begin{algorithm}[h]
+\caption{Physical limits}
+\label{alg:simple limits}
+\begin{algorithmic}[1]
+\For{\textbf{each} interface \em{f}}
+    \State $L_{f} \leftarrow$ Interest Limit according to (1)
+    \State $O_{f} \leftarrow 0$ \Comment{Outstanding Interests on interface \textbf{f}}
+\EndFor
+
+\vspace{0.2cm}
+\Function{OutInterest}{Interest \textbf{i}, OutInterface \textbf{of}}
+    \If{$L_{of} - O_{of} > 0$} \Comment{\textbf{of} is under physical limits}
+        \State $O_{of} \leftarrow O_{of} + 1$  \Comment{``Borrow'' token}
+        \State add \textbf{of} to PIT entry and forward \textbf{i} to \textbf{of}
+    \Else
+        \State drop Interest
+    \EndIf
+\EndFunction
+
+\vspace{0.2cm}
+
+\Function{InData}{Data \textbf{d}}
+   \State lookup PIT entry \textbf{p} for data \textbf{d}
+   \For{\textbf{each} outgoing interface \textbf{of} in \textbf{p}}
+        \State $O_{of} \leftarrow O_{of} - 1$ \Comment{``Return'' token}
+   \EndFor
+\EndFunction
+
+\vspace{0.2cm}
+
+\Function{Timeout}{PIT entry $i$}
+   \For{\textbf{each} outgoing interface \textbf{of} in \textbf{p}}
+        \State $O_{of} \leftarrow O_{of} - 1$ \Comment{``Return'' token}
+   \EndFor
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+% In our experiments Interest/Data size ratio is about 1:30
+Considering the fact that normally the size of the Interests packets is significantly smaller than the size of the requested Data packets, a router needs to consume only a small portion of the upstream link (from A to B) to fully utilize the downstream link (from B to A).
+The direct conclusion from this observation, confirmed by our evaluations in the Section~\ref{sec:evaluation}, is that if a router forwards only the right amount of Interests, both mechanisms of the Interests flooding attack will stop working: the forwarded Interests would neither congest the upstream nor exhaust router's memory resources.
+At the same time, the Physical limits may become a new mechanisms to carry out a denial of service attacks.
+For example, if the router A has forwarded 125 junk Interests, it will not be able to accept any other Interests neither from a legitimate user or an attacker, until these junk Interests start to expire (e.g., within one second).
+This essentially reduces the probability of legitimate Interests getting through and can result in an effective low-rate denial of service attack (e.g., see Fig.~\ref{fig:small-scale-topo 3}).
 

### 2012-12-05 04-design.tex
typos
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@856 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 The most obvious and na\"{i}ve method to mitigate the Interest flooding attack is to limit the number of forwarded Interests out of each interface. 
-That is, if it is known that the amount of already forwarded Interests can fully utilize the downstream link, an NDN node---an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
+That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
 For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.

### 2012-12-05 algos/physical-limits.tex
typos
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@856 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 Since the number of tokens in the bag defines how many Interests are forwarded and not yet satisfied or timed out (pending Interests), this number should be large enough to fully utilize the network and small enough to avoid excessive buffering and drops at the upstream routers.
-The ideal value for the number of tokens (interest limit) for each individual link would be defined proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
+The ideal value for the number of tokens (\emph{Interest Limit}) for each individual link would be defined proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
 This can be formalized in the following way:
@@
 
-In the rest of the paper we will refer to Interest limits set based on the bandwidth-delay product as \emph{Physical limits}.
-Pseudocode~\ref{alg:simple limits} shows implementation details of how the Physical limits algorithms.
-Every time an Interest is ready to be send to an outgoing interface $of$ (OutInterest function), we check if the token bag is not empty.
+In the rest of the paper we will refer to Interest limits set based on the bandwidth-delay product as \emph{Physical limits}, as we set the limit based on the physical link capacity.
+Pseudocode~\ref{alg:simple limits} shows implementation details of the Physical limits algorithms.
+Every time an Interest is ready to be send to an outgoing interface $of$ (\emph{OutInterest} function), we check if the token bag is not empty.
 If there is at least one free token available, we are ``borrowing'' it, forwarding the Interests, and remembering the outgoing interface in the corresponding entry of PIT.
-Functions InData and Timeout ensure that tokens are returned whenever the requested Data is received or Interest times out.
+Functions \emph{InData} and \emph{Timeout} ensure that tokens are ``returned'' whenever the requested Data is received or Interest times out.
 
@@
 The direct conclusion from this observation, confirmed by our evaluations in the Section~\ref{sec:evaluation}, is that if a router forwards only the right amount of Interests, both mechanisms of the Interests flooding attack will stop working: the forwarded Interests would neither congest the upstream nor exhaust router's memory resources.
-At the same time, the Physical limits may become a new mechanisms to carry out a denial of service attacks.
-For example, if the router A has forwarded 125 junk Interests, it will not be able to accept any other Interests neither from a legitimate user or an attacker, until these junk Interests start to expire (e.g., within one second).
-This essentially reduces the probability of legitimate Interests getting through and can result in an effective low-rate denial of service attack (e.g., see Fig.~\ref{fig:small-scale-topo 3}).
+At the same time, the Physical limits may become a new mechanisms to carry out denial of service attacks.
+For example, if the router A has forwarded 125 junk Interests, it will not be able to accept any other Interests neither from a legitimate user or an adversary, until these junk Interests start to expire.
+This essentially reduces the probability of legitimate Interests getting through and can result in an effective low-rate denial of service attack (refer to Section~\ref{sec:small-scale}).
 

### 2012-12-05 algos/fair-queueing.tex
First part of the design section semi-done
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@855 df1a90cd-247b-4364-bdaf-287a704eb499
Semi-finalized fair-queuing description
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@857 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-\subsection{Physical limits with ``fair'' queuing}
-\label{sec:queuing}
+% \subsection{Physical limits with ``fair'' queuing}
+% \label{sec:queuing}
 
-Physical limits (per-outgoing-interface) described in Section~\ref{sec:physical limits} provide ability to fully utilize a downstream link, largely avoiding congestion in the link.
-However, this limitation approach does not attempt to utilize data plane performance knowledge (i.e., Interest satisfaction ratio statistics) to discriminate good and malicious Interests.
+% However, this limitation approach does not attempt to utilize data plane performance knowledge (i.e., Interest satisfaction ratio statistics) to discriminate good and malicious Interests.
 
-One way of augmenting the physical limits method with data performance knowledge is to perform some sort of class-based Interest queueing and weighted scheduling (e.g., weighted round-robin) of the enqueued interests with the weight equal to the Interest satisfaction ratio for the class (see Pseudocode~\ref{alg:queuing}).
-For example, Interests can be divided into separate classes based on incoming interface, where Interests arriving from different incoming interfaces are treated differently:
-an Interest from an interface with higher satisfaction ratio will have more priority than an Interest from an interface with lower satisfaction ratio.
+To partially overcome deficiencies of the Physical limits algorithm we need to ensure that the forwarded Interests represent at least a ``fair'' mix of the Interests received from different neighbors (interfaces).
+That is, if the routers A on Fig.~\ref{fig:flooding example} has a very tight token budget, these tokens should be fairly distributed between incoming interfaces \texttt{eth0} and \texttt{eth1}.
+Because of the very small volume of Interests, we cannot simply rely on network buffers to do statistical multiplexing of Interests, as they would almost never be buffered.
+At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests will arrive in the future.
+Therefore, in order to achieve the goal of ``fair'' mixing of Interests, we need to implement additional mechanisms to buffer and mix incoming Interests, only if they cannot be immediately forwarded.
+
+For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}). 
+As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
+It should be noted that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
+This way, PIT entry can be quickly updated when the Interest is actually forwarded, as well as the element can be removed from the queue when the Interest expires.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.65]{queue}
+  \caption{Interest queuing: if tokens are unavailable, the router creates PIT entry, but instead of forwarding, enqueued the Interest}
+  \label{fig:queueing}
+\end{figure}
+
+A more formalized description of the Physical limits algorithms with per-interface fairness is presented in Pseudocode~\ref{alg:queuing}.
+The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
+At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
 
@@
 \begin{algorithm}[h]
-\caption{Physical limits with ``fair'' queueing}
+\caption{Physical limits with per-interface fairness}
 \label{alg:queuing}
 \begin{algorithmic}[1]
-\Function{InInterest}{Interest $i$, InInterface $if$}
-\For{\textbf{each} OutInterface $of$ \textbf{in} FwDecision($i,if$)}
-    \If{$of$ is under physical limits}
-        \State Forward($i$, $of$)
+\State{} \Comment{Same initialization, InData and Timeout functions as in Physical Limits algorithm}
+
+\vspace{0.2cm}
+
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{if}, OutInterface \textbf{of}}
+    \If{$L_{of} - O_{of} > 0$} \Comment{\textbf{of} is under physical limits}
+        \State $O_{of} \leftarrow O_{of} + 1$  \Comment{``Borrow'' token}
+        \State add \textbf{of} to PIT entry and forward \textbf{i} to \textbf{of}
     \Else
-        \State Queue $q \leftarrow of$.GetQueueByClass($if$)
+        \State Queue $q \leftarrow of$.GetSubQueue($if$)
+        \If{$Size(q) < L_{of}$}
            \State $q$.PushInterest($i$)
+           \State add \textbf{of} to PIT entry, and link PIT entry with the queue
+        \Else
+           \State drop Interest
         \EndIf
-\EndFor
+    \EndIf
 \EndFunction
@@
 \vspace{0.2cm}
-\State{} \Comment{\textit{Called when an Interest is satisfied or times out}}
-\Function{OnReady}{OutInterface $of$}
-    \State{} \Comment{\textit{get a non-empty queue using round-robin}}
-    \State Queue $q \leftarrow$ $of$.GetNonEmptyQueue 
+\State{} \Comment{\textit{Whenever $L_{of} - O_{of}$ becomes larger than zero}}
+\Function{TokenBecomesAvailable}{}
+    \State Queue $q \leftarrow$ $of$.GetRoundRobinSubQueue 
     \State $i \leftarrow$ $q$.PopInterest
-    \State Forward($i$, $of$)
+    \State update PIT entry and Forward($i$, $of$)
 \EndFunction
@@
 
-A couple of notable comments.
-First, queueing is not (and should not be) active until there is something to enqueue.
-In our case, until physical limits are reached, all Interests are not subjected to any additional queueing.
-Second, there should be a reasonable limit (smaller that Interest lifetime) of how long Interests are stayed in the queues.
-Otherwise, there could be a case when Interests is still in a queue upstream, while pending Interest state already gone (timed out) downstream, effectively making such an Interest useless.%
-\footnote{Additional mechanisms of pair-wise agreements between NDN routers and period Interest refresh can solve this particular problem, but it is out of the scope of the present paper.}
+It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
+Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
+Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
 
-While we experimented with more complicated classes (see Sections~\ref{sec:dynamic limits} and \ref{sec:probabilistic}), limitations of the queuing method nullify benefits of implementing such classes.
-In particular, weighted round-robin scheduling can effectively work only if queues are not empty.
-But, as we evaluation results in Section~\ref{sec:evaluation} show, queues are tend to be empty, when number of bottlenecks (mixing points, nodes that receive more Interests that they can forward on a face) on paths more than one.
+As we show in Section~\ref{sec:evaluation}, fair queueing provides a partial relief from the Interest flooding attack, allowing legitimate users to successfully fetch Data for 15--20\% of the expressed Interests (compared to 0-10\% without fair queueing).
+At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
+Therefore, to successfully solve the problem, we need a more intelligent approach, allowing us to localize the attack traffic as close to the attack origin as possible.
 

### 2012-12-05 06-related.tex
related work
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@858 df1a90cd-247b-4364-bdaf-287a704eb499

@@
+\section{Related work \label{related-section}}
+In this section we provide a classification of mitigation techniques against DDoS flooding attacks in IP networks, because of the lack of any in NDN or other information centric architectures. 
+\begin{itemize}
+\item{Capability-based systems} allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
+Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
+This implies that each client must pass through an authentication process prior to using any bandwidth ~\cite{Capabilities}.
+\item{Computation-based systems} provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
+Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients ~\cite{Portcullis}.
+\item{Push back systems} are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
+This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines ~\cite{Pushback}.
+\item{Congestion control systems} do per flow traffic analysis and drop of packets belonging to misbehaving flows.
+For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
+If largely deployed such techniques could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
+\end{itemize}
+
 %%% Local Variables: 

### 2012-12-05 01-intro.tex
minor changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@859 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-In 2011 for the first time IPv6 DDoS attacks on commercial networks were observed.
-They occur rarely, but it only means that IPv6 is not widespread enough for attackers to put significant resources into such DDoS attacks.
+In 2011 for the first time IPv6 DDoS attacks on commercial networks were observed ~\cite{Arbor}.
+They occur rarely, which only means that IPv6 is not widespread enough for attackers to put significant resources into such DDoS attacks.
 Principally, in terms of DDoS security IPv6 didn't advance that much comparing to standard IPv4 networks.
@@
 IP architecture has a wide surface for denial of service attacks which takes the beginning from the thin-waist IP protocol, goes through transport level and up to DNS level.
-In IP it is very easy to forge source address and specify the exact destination that needs to be placed under attack that creates possibilities to perform various types of reflection DoS attacks.
-On transport level in TCP/IP SYN flood, RST flood and FIN-way attacks are very effective and popular.
+In IP it is very easy to forge source address and specify the exact destination that needs to be placed under attack that creates possibilities for performing various types of reflection DoS attacks.
+On transport level in TCP/IP stack SYN flood, RST flood and FIN-way attacks are very effective and popular.
 DNS system can be attacked in multiple ways, e.g.
@@
 
-We believe that future Internet architectures can do and must do more for DDoS prevention.
+We believe that future Internet architectures can do and must do more for DDoS mitigation.
 By its design NDN architecture is not sensitive to any kind of reflection attacks due to the lack of host addresses and ubiquitous data caching.
-NDN architecture can operate without any DNS-like architecture since it routes and forwards packets based on human-readable names instead of IP addresses that need to be resolved with DNS.
+NDN architecture can operate without any DNS-like architecture since it routes and forwards packets based on human-readable names instead of IP addresses that have been received from DNS.
 
@@
 
-In this paper we provide a brief overview of possible DDoS attacks in NDN architecture, analyze all aspects of Interest flooding attack in NDN architecture, propose multiple defensive techniques against such attacks, establish evaluation methodology using ndnSIM simulation software, execute small scale and Internet scale attack scenarios, and analyze our experimental results.
+In this paper we provide a analyze all aspects of Interest Flooding attack in NDN architecture, propose multiple defensive techniques against such attacks, establish evaluation methodology using ndnSIM simulation software, execute small scale and Internet scale DDoS attack scenarios, and analyze our experimental results.
 
-Following this introduction, Section 2 gives a brief overview of NDN architecture, and Section 3 lists and overviews possible attack in NDN.
-Section 4 thoroughly discusses Interest flooding attack, and Section 5 proposes multiple defensive techniques against it.
-Section 6 describes evaluation methodology and gives experimental results.
+Following this introduction, Section 2 gives a brief overview of NDN architecture.
+Section 3 thoroughly discusses Interest flooding attack, and Section 4 proposes multiple defensive techniques against it.
+Section 5 describes evaluation methodology and gives experimental results.
+Section 6 contains related work.
 Section 7 provides analysis based on our results.

### 2012-12-05 06-related.tex
Tiny formatting changes in the related work section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@860 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-02 06-related.tex
@@
+\section{Related work}
+\label{sec:related work}
+
+In this section we provide a classification of mitigation techniques against DDoS flooding attacks in IP networks, because of the lack of any in NDN or other information centric architectures.
+
+Capability-based systems allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
+Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
+This implies that each client must pass through an authentication process prior to using any bandwidth ~\cite{Capabilities}.
+
+Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
+Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients ~\cite{Portcullis}.
+
+Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
+This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines ~\cite{Pushback}.
+
+Congestion control systems do per flow traffic analysis and drop of packets belonging to misbehaving flows.
+For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
+If largely deployed such techniques could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
+
 %%% Local Variables: 

### 2012-12-05 04-design.tex
Semi-finalized fair-queuing description
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@857 df1a90cd-247b-4364-bdaf-287a704eb499
Stats part
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@861 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\subsubsection{Interest limits (physical limits)}
+\subsubsection{\textbf{Interest limits (physical limits)}}
 \label{sec:physical limits}
@@
 
-\subsubsection{Interest limits with per-interface fairness}
+\subsubsection{\textbf{Physical limits with per-interface fairness}}
 \label{sec:queuing}
@@
 
-About additional knowledge about interests.
+While the Interest limit is the key building block to suppress mechanisms of the Interest flooding attack, legitimate Interests need to be somehow prioritized and malicious Interests need to be somehow penalized in order to completely suppress the attack.
+That is, instead of processing Interests always based on the first-in-first-serve rule, NDN routers need some basis to treat the incoming Interests differently.
+Thus, the primary task in bringing intelligence to the Interest flooding attack mitigation is to proactively distinguish between legitimate and malicious Interests.
 
-Another unique feature of the NDN architecture is stateful packet forwarding~\cite{adaptive-forwarding} and symmetric flow of Interests and Data packets.
-Every time Interests is send out to the Interface, the router will be able to learn various parameters about this Interest.
+To achieve such an Interest differentiation we can leverage another unique feature of the stateful forwarding in NDN---namely, the guaranteed symmetric flow of Interest and Data packets.
+In other words, NDN guarantees that a forwarded Interest would always results in receiving a corresponding Data, provided such Data exists and Interest/Data packets were not lost on the way.
+Therefore, all Interests that result in Data return can be considered legitimate, while the ones that always timeout should be deemed as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest flooding}).
+Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
 
-From the DDoS mitigation point of view, one of the important parameters is to determine from which interface
+Unfortunately, the timeout-based differentiation is reactive by nature: one cannot know in advance that an Interest would timeout or bring Data back.
+What we can do proactively is to keep an up-to-date statistics of Interests satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistics to project outcomes for new Interests.
+For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface can be enough to estimate whether an Interest received from a neighbor will bring Data or time out.
+Statistics can also be kept at more granular levels (e.g., per outgoing interface, per prefix, etc.), which can further improve the estimation quality.
 
-In order to mitigate a denial of service attack it is vital to know the origin of the attack.
-I the origin of the attack is known, then the attack can be easily suppressed and eventually localized.
-In our definition of the attack is that
+The devil is always in the details.
+From the one hand, such statistics needs to start penalizing adversaries as soon as possible (i.e., negative stats should build up fast).
+On the other hand, the positive statistics should not deteriorate too fast (i.e., positive stats should be relatively long-term).
+Our preliminary experiments showed that the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window, provides a good balance between the two contradictory requirements.
 
-interest of the attackers are not getting satisfied. 
-Every router can learn fro m which interfaces attack traffic is coming and do certain actions to limit forwarding of suspicious interest.
-In other words, without trying to distinguish legitimate and malicious interests on the basis of the Interest prefix, routers distinguish them based on recent performance.
-
-\subsubsection{Data plane performance tracking}
-\label{sec:stats}
+% \subsubsection{\textbf{Data plane performance tracking}}
+% \label{sec:stats}
 
@@
 
-\subsubsection{Probabilistic Interest accept}
+\subsubsection{\textbf{Probabilistic Interest accept}}
 \label{sec:probabilistic}
@@
 
-\subsubsection{Dynamic adjustments of window-based limits}
+\subsubsection{\textbf{Dynamic adjustments of window-based limits}}
 \label{sec:dynamic limits}

### 2012-12-05 algos/fair-queueing.tex
Stats part
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@861 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
-Therefore, to successfully solve the problem, we need a more intelligent approach, allowing us to localize the attack traffic as close to the attack origin as possible.
+Therefore, to successfully solve the problem, we need a fundamentally different, more intelligent approach, allowing localization of the attack traffic as close as possible to the attack origin.
 

### 2012-12-05 algos/probabilistic.tex
Correcting algorithms. Far far far from perfect...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@849 df1a90cd-247b-4364-bdaf-287a704eb499
First part of the design section semi-done
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@855 df1a90cd-247b-4364-bdaf-287a704eb499
Stats part
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@861 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-\subsection{Probabilistic Interest accept algorithm}
-\label{sec:probabilistic}
+% \subsection{Probabilistic Interest accept algorithm}
+% \label{sec:probabilistic}
 
@@
 
-\Function{InInterest}{Interest $i$, InFace $if$}
+\Function{InInterest}{Interest $i$, InInterface $if$}
 
@@
 
-    \For{\textbf{each} OutFace $of$ \textbf{in} ForwardingDecision($i,if$)}
-        \State $s \leftarrow if$.GetSatisfactionRatio()
-        \If{$s \in [0,1]$} \Comment{A valid stats exists}
-            \State Stop processing with probability $P(s)$
+    \For{\textbf{each} OutInterface $of$ \textbf{in} FwDecision($i,if$)}
+        \If{$F_{if} > 1$} \Comment{At least one Interest was forwarded}
+            \State $s \leftarrow 1 - \min(0, U_{if} / F_{if})$
+            \State Drop interest with probability $P(s)$
         \EndIf
-        \If{$of$ is under physical limits}
-            \State Forward($i$, $of$)
-        \EndIf
+
+        \State{forward the Interest, subjecting to physical limits}
     \EndFor
@@
 
-The definition of the probabilistic Interest accept is very straightforward and seems to be trivial to implement.
-However, there are a couple of implementation caveats that complicate matters.
-Note that there is a condition (line 6 on Pseudocode~\ref{alg:probabilistic mode}) to check if there is a valid statistics point.
-This condition is extremely important, because it first provides a basis to distinguish between known facts (i.e., good or bad satisfaction ratio for the incoming interface) and unknown facts (e.g., the first time an Interests arrives on the interfaces).
-Second, it gives an opportunity to recover from a bad history (history of unsatisfied Interests) after malicious Interests are ceased to flow in.
-Essentially, this recovery relies on statistics module to perform time-based invalidation of historical data (timely, but not too quickly\footnote{Otherwise, attackers may send short bursts of malicious Interests, successfully avoiding differential Interest treatment}).
-As described in Section~\ref{sec:stats}, we are currently experimenting with the exponential statistics degradation, while we also planning to apply different approaches in the future.
+% The definition of the probabilistic Interest accept is very straightforward and seems to be trivial to implement.
+% However, there are a couple of implementation caveats that complicate matters.
 

### 2012-12-05 06-related.tex
related v2
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@862 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-\section{Related work}
-\label{sec:related work}
-
-In this section we provide a classification of mitigation techniques against DDoS flooding attacks in IP networks, because of the lack of any in NDN or other information centric architectures.
+\section{Related work \label{related-section}}
+NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
+In this section we will overview generic directions of DDoS mitigation designs and try to think about which tricks could be used in NDN.
 
@@
 This implies that each client must pass through an authentication process prior to using any bandwidth ~\cite{Capabilities}.
+We believe that for NDN this method doesn't fit really well for the following reasons.
+First, this method is very questionable in terms of scalability and mobility support since it requires tight trust connections between routers and hosts.
+Thus, it neglects one of the main advantages (mobility) of NDN.
+Second, the design of trust infrastructure for NDN is not well defined yet, which means that we cannot really make assumptions in our design of mitigation techniques.
 
 Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
-Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients ~\cite{Portcullis}.
+Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients.
+One of the main difficulties in such systems is the question of puzzle dessimination.
+In  ~\cite{Portcullis} authors suggested to propagate puzzles using DNS system.
+In NDN since routers have caching abilities, we can propagate puzzles just like a normal data packets, using Interest-Data exchange.
+Overall, this method looks interesting and deserves being investigated in a future work.
 
@@
 This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines ~\cite{Pushback}.
+In general this technique can be applied to NDN architecture thanks to its decentralized coordination of downrating bad traffic flows.
+Moreover, NDN provides better capabilities for accurate flow detection.
 
@@
 For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
-If largely deployed such techniques could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
+Such techniques, if largely deployed, could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
+Since NDN routers maintain a richer per-packet state, which translates into a better per-flow statistics, these techniques can become much more effective when applied to NDN.
+
+%were looking for getting accustomed
 

### 2012-12-05 algos/probabilistic.tex
Semi-finalized probabilistic model
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@863 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-% \subsection{Probabilistic Interest accept algorithm}
-% \label{sec:probabilistic}
-
-The basic idea of the dynamic limits algorithm is to treat differently (accept different amounts of) Interests belonging to different classes.
-The high-level implementation of this in the dynamic limits algorithm is based explicit limits that are announced to each neighbor of the node.
-While the control overhead generated by such announcements can be manageable (i.e., similar to the routing updates in dynamic routing protocols, limit announcements can be paced out, as well as generated only when change is detected), some can consider such overhead undesirable.
-
-The same goal of differential treatment of Interests, and in particular ``suppression'' of malicious Interests, can also achieved in a slightly different way, which does not require any additional communication between routers.
-Instead of announce and explicitly apply limits on the number of accepted Interests for each incoming interface (and optionally for each prefix in FIB), a node can accept new incoming Interests based on some probabilistic model, which incorporates satisfaction ratios for the desired Interest classes.
-For example, this could be a simple uniform distribution, where the satisfaction ratio directly defines probability to accept or reject an incoming Interests (see Pseudocode~\ref{alg:probabilistic model}).
-For simplicity, for the example we are using Interest differentiation only per incoming interface, but the algorithm can be generalized to more granular Interest classes.
+Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
+A straightforward way to achieve this enforcement is to consider Interest satisfaction rate as a direct probability to accept (forward) or reject an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
 
@@
 \begin{algorithmic}[1]
+\State{} \Comment{Same initialization, InData and Timeout functions as in Physical Limits algorithm}
 
-\Function{InInterest}{Interest $i$, InInterface $if$}
+\vspace{0.2cm}
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{if}, OutInterface \textbf{of}}
 
@@
 
-    \For{\textbf{each} OutInterface $of$ \textbf{in} FwDecision($i,if$)}
-        \If{$F_{if} > 1$} \Comment{At least one Interest was forwarded}
-            \State $s \leftarrow 1 - \min(0, U_{if} / F_{if})$
+    \If{$F_{if} > \theta $} \Comment{At least some Interests were forwarded before}
+        \State $s \leftarrow (1 - U_{if} / F_{if})$
         \State Drop interest with probability $P(s)$
@@
     \State{forward the Interest, subjecting to physical limits}
-    \EndFor
 \EndFunction
@@
 
-% The definition of the probabilistic Interest accept is very straightforward and seems to be trivial to implement.
-% However, there are a couple of implementation caveats that complicate matters.
+Parameter $\theta$ on line 5 of the Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not applied when there a very small volume of Interests coming from the particular interface.
+That is, while we want to deny service to the attackers, we also want give an opportunity for the users who do not abuse the network to regain their share of resources after temporary Data delivery failures.
+
+A main drawback of the probabilistic Interests accept method is the fact that each router on the path make an independent decision on what to do with the Interest.
+As a result of such independent decisions, the probability of legitimate Interests not to be dropped quickly decreases as the number of hops between the requester and Data grows, worsening the satisfaction statistics and resulting in further drops of the Interests.
+In example on Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
+At the same time, the router B sees the satisfaction rate for its \texttt{eth0} interface at 30\%.
+Next time a legitimate Interests arrives on the router A, it has 50\% chance to be forwarded further, and if forwarded, it has only $50\% \times 30\% = 15\%$ chance to be actually send towards the Data producer.
+To prevent such overreacting, we need to enable some form of a gossiping protocol between neighboring NDN routers, in order to explicitly specify amount of Interests that each router is willing to forward.
 

### 2012-12-05 07-discussion.tex
More reorganization and adding Makefile
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@847 df1a90cd-247b-4364-bdaf-287a704eb499
some discussion
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@864 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 Adapting these to mitigate other DDoS attacks.
+
+In section ~\ref{sec:interest flooding} we made assumptions regarding the Interest flooding traffic shape (requesting non-existing data with non-aggregatable prefix name ) and single-path forwarding strategy, which jointly create the most powerful congestion at the producer link.
+
+In this paper we are using a simple attacker profile Ñ greedy attacker, which is using all resources (available bandwidth) of its botnet in order to put producer down as quickly as possible.
+However, in a real life not all botnets are greedy and in fact can perform smart actions like constant switching between victims every other hour to fool defensive systems by nullifying gathered bad flow statistics.
+Or they can be non-greedy at all, for instance a large botnet of several hundreds of thousands nodes can perform a non-greedy attack by sending just a few Interests per second from each node.
+Nowadays, this situation is very hard to manage, because of the difficulties in detecting of bad flows in a traffic.
+
+Also, an adversary can mix Interests for non-existing data with Interests for existing-data. Thanks to NDN stateful packet forwarding, bad flows can be easily distinguished and penalized.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2012-12-06 07-discussion.tex
Semi-finalized dynamic limits section, which finally completes the whole design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@865 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-In section ~\ref{sec:interest flooding} we made assumptions regarding the Interest flooding traffic shape (requesting non-existing data with non-aggregatable prefix name ) and single-path forwarding strategy, which jointly create the most powerful congestion at the producer link.
+In section~\ref{sec:interest flooding} we made assumptions regarding the Interest flooding traffic shape (requesting non-existing data with non-aggregatable prefix name ) and single-path forwarding strategy, which jointly create the most powerful congestion at the producer link.
 
-In this paper we are using a simple attacker profile Ñ greedy attacker, which is using all resources (available bandwidth) of its botnet in order to put producer down as quickly as possible.
+In this paper we are using a simple attacker profile and greedy attacker, which is using all resources (available bandwidth) of its botnet in order to put producer down as quickly as possible.
 However, in a real life not all botnets are greedy and in fact can perform smart actions like constant switching between victims every other hour to fool defensive systems by nullifying gathered bad flow statistics.

### 2012-12-06 algos/probabilistic.tex
Semi-finalized dynamic limits section, which finally completes the whole design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@865 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 A main drawback of the probabilistic Interests accept method is the fact that each router on the path make an independent decision on what to do with the Interest.
-As a result of such independent decisions, the probability of legitimate Interests not to be dropped quickly decreases as the number of hops between the requester and Data grows, worsening the satisfaction statistics and resulting in further drops of the Interests.
+As a result of such independent decisions, the probability of legitimate Interests not to be dropped decreases quickly as the number of hops between the requester and Data grows, worsening the satisfaction statistics and resulting in further drops.
 In example on Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
-At the same time, the router B sees the satisfaction rate for its \texttt{eth0} interface at 30\%.
+At the same time, the router B sees the satisfaction rate for its \texttt{eth0} interface at 30\% level.
 Next time a legitimate Interests arrives on the router A, it has 50\% chance to be forwarded further, and if forwarded, it has only $50\% \times 30\% = 15\%$ chance to be actually send towards the Data producer.

### 2012-12-06 03-interest-flooding.tex
small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@866 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\paragraph{Classification}
+% \paragraph{Classification}
 
@@
 
-The Interest flooding attack has two-fold effect on service quality in NDN network: it \emph{creates network congestion} and \emph{exhaust resources on routers}.
+The Interest flooding attack has two main mechanisms to affect service quality in NDN network: it \emph{creates network congestion} and \emph{exhaust resources on routers}.
 

### 2012-12-06 algos/dynamic-limits.tex
Correcting algorithms. Far far far from perfect...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@849 df1a90cd-247b-4364-bdaf-287a704eb499
First part of the design section semi-done
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@855 df1a90cd-247b-4364-bdaf-287a704eb499
did not compile fix
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@867 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-10-22 algos/dynamic-limits.tex
@@
-% \subsection{Dynamic limits}
+% Differential treatment of Interests received from different interfaces can be achieved in a more elegant way, without reverting to probabilistic methods.
 
-\subsection{Dynamic limits assignment algorithm}
+Essentially, the probabilistic Interest accept algorithm divides the available forwarding tokens between interfaces proportionally to their satisfaction ratios.
+Exactly the same effect can be achieved without using probabilistic methods, simply by enabling and enforcing additional Interest limits for each incoming interface, where the values of the limits directly depend on the interface satisfaction ratios.
+Additionally, routers may need to explicitly announce these limits to their downstream neighbors, ensuring that any forwarded Interest from the downstream is actually getting through, resulting in genuine Interest satisfaction statistics.
+
+The formal definition of the dynamic limits algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm would work in our toy example on Fig.~\ref{fig:flooding example}.
+Assuming the initial (physical) limit $L=10$ and the current satisfaction ratios on the the router A are 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and on the router B the ratio is 30\%  \texttt{eth0}, each node would set and announce the following  incoming interface limits $L'$:
+\begin{enumerate}
+\item the router B would set and announce the incoming interface limit $L'=3$;
+\item the router A, after receiving announcement from B would readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
+\item legitimate user and adversary may either obey or ignore the announced limit, which will be in any case enforced by the router A.
+\end{enumerate}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=\columnwidth]{dynamic-limits}
+  \caption{Dynamic limits example: routers explicitly tell neighbors how many Interest can be for sure delivered to the Data producer}
+  \label{fig:dynamic limits example}
+\end{figure}
+
+\floatname{algorithm}{Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\caption{Dynamic limits}
+\label{alg:dynamic limits}
+\begin{algorithmic}[1]
+\State{} \Comment{Same initialization, InData and Timeout functions as in Physical Limits algorithm}
+\vspace{0.2cm}
+\State{$\forall f \in \mathrm{interfaces} : L'_{f} \leftarrow L_{f}$} \Comment{Per-incoming interface Interest limit}
+
+\vspace{0.2cm}
+
+\State{} \Comment{\textit{Announcement from the neighbor}}
+\Function{InLimits}{InInterface $if$, Limit $L'$}
+    \State $L_{if} \leftarrow L'$
+\EndFunction
+
+\vspace{0.2cm}
+
+\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
+\For{\textbf{each} outgoing interface $of$}
+
+   \For{\textbf{each} incoming interface $if$}
+        \State $L'_{if}= {L_{of}} \times (1 - U_{if}/F_{if})$
+        \State AnnounceLimit($if$, $L'_{if}$)
+   \EndFor
+
+\EndFor
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+The zero limit for the adversary's link means that the router A is temporarily not willing to accept any interests from this link, not until the statistics decays to the appropriate level (recall Fig.~\ref{fig:ratio example}).
+At the next iterations of the dynamic limits algorithm, the legitimate user will be able to gradually improve the statistics on both the router A and router B (all his Interests will get through and will return Data), eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and the router A.
+
+It should be noted that while in the description of the dynamic limits algorithm we used notions of ``outgoing'' and ``incoming'' interfaces, in the real system all interfaces can be both incoming and outgoing.
+Thus, it may not be entirely clear which outgoing limit $L_{of}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{if}$.
+To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
+That is, for each FIB entry we set a separate Interest limit for each incoming interface ($L'_{{if}^{FIB}}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{{of}^{FIB}}}$.
+
+% Alex: not sure if this paragraph belongs here
+Essentially, both probabilistic Interest accept and the dynamic limits algorithm are forms of a well-known push-back mechanism~\cite{Pushback}, with several core differences.
+First, we are suppressing (pushing back) unwanted requests for Data, not the actual Data.
+Second, differentiating between good and bad Interests is based on the traffic symmetry property of NDN.
+% Alex: I'm not entirely sure about this point... 
+Finally, both intelligent attack mitigation algorithms can be enabled all the time, without degrading network performance when there are no active attack.
 

### 2012-12-06 algos/dynamic-limits.tex
Revert "did not compile fix"
This reverts commit 16ffa8b68cec7b644034fba24aca885a59e4db59.

git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@868 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
-That is, for each FIB entry we set a separate Interest limit for each incoming interface ($L'_{{if}^{FIB}}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{{of}^{FIB}}}$.
+That is, for each FIB entry we set a separate Interest limit for each incoming interface ($L'_{if}^{FIB}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{of}^{FIB}}$.
 

### 2012-12-06 algos/dynamic-limits.tex
A better way to solve the compilation issue
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@869 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
-That is, for each FIB entry we set a separate Interest limit for each incoming interface ($L'_{if}^{FIB}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{of}^{FIB}}$.
+That is, for each FIB entry we set a separate Interest limit for each incoming interface ($L_{if}^{'FIB}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{of}^{FIB}}$.
 

### 2012-12-07 05-evaluation.tex
Small correction to make sure paper is compilable
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@848 df1a90cd-247b-4364-bdaf-287a704eb499
Initial part of the evaluation section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@870 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-% \todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
 % List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
 
-% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}
+% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers,
 
-We want to explore the effectiveness of designed mitigation techniques in a two distinctive ways.
-First, we need to understand how each method works on a very ground level of a just few nodes and links.
-Second, we want to pick promising techniques and see if they work in a large scale networks of hundreds and thousands of nodes.
-To ensure the correct transition from small scale experiments to large scale experiments we had to use the same evaluation tool in order to eliminate any possibility of implementation discrepancy.
-As of today the only network simulator supporting full NDN logic is the NS-3 based ndnSIM software.
+% alex: what's a point of latency?  it would matter only for queueing method and we not really pushing this method
+% Latency for good clients, good versus bad interests as a function of time
 
-\input{small-scale}
-\input{large-scale}
+In this section present an in-depth study, aiming to explore quality and effectiveness of the designed Interest flooding attack mitigation methods.
+Our study is based on simulations performed with the help of open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator.\footnote{\url{http://www.nsnam.org/}}
+
+% why we chose small scale topology
+% what point we wanted to show we small scale
+% what points we wanted to verify with larger-scale internet like topology
+
+% Metrics
+Quality of the attack mitigation methods directly corresponds to the quality of service for the legitimate users during an ongoing attack, which in NDN network can be quantified through percentage of satisfied Interest.
+For example, if the network implements a mitigation method $X$ and under the attack majority of user-expressed Interests are getting satisfied, then the method $X$ can be seen as highly effective.
+At the same time, if only a small percentage of the expressed Interest are getting satisfied during the attack, the method $X$ can be called ineffective.
+
+% Traffic pattern
+In our experiments we made a simplistic assumption that both legitimate users and adversaries express Interests with constant average rates with randomized (uniform distribution) time gaps between each two consecutive Interests.
+% Alex: not sure how to argue about the traffic pattern
+Although this pattern is not truly realistic, it gives us a good statistical mix of traffic from all network users without excessive network buffering.
+In addition to that, in each run of the simulation we ensure that all Interests expressed by the legitimate users during a no-attack period are satisfied.
+For simplicity and without losing any generality, we also equalized the average rates with which the legitimate users express Interests.
+
+% Fixed parameters
+The \emph{Delay} and \emph{Data size} parameters for the Interest limits calculation (1) were set to fixed values for every node in the simulated topology.
+In particular, for the small-scale experiments we set Delay to 80~ms and for the large-scale experiments we used the value 330~ms (the order of the largest RTT).
+Data size parameter was set to 1100~bytes for all simulation runs and topologies.
+
+\input{eval-small-scale}
+\input{eval-large-scale}
 

### 2012-12-07 eval-large-scale.tex
Initial part of the evaluation section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@870 df1a90cd-247b-4364-bdaf-287a704eb499

\subsection{Large scale simulations}
\label{sec:largescale}

In order to verify that the designed methods can also work in realistic Internet-like topologies, we 
performed large-scale simulations using a modified version of Rocketfuel AT\&T topology~\cite{rocketfuel}.
To approximate structure of the Internet, we selected the largest connected component of 562 nodes and separated nodes in three categories: clients, gateways, and backbones.
All nodes with degrees one, two, and three became clients (344 red nodes on Fig.~\ref{fig:large-scale}), all nodes that are directly connected to clients became gateways (109 green nodes), and the rest became backbones (109 blue nodes).
(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.)
After categorizing the nodes, we randomly assigned bandwidths and link delays based on link types (see Table~\ref{tab:large-scale}).

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.26,angle=90]{7018-r0}
  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
  \label{fig:large-scale-topo}
\end{figure}

\begin{table}[htbp]
\centering
\caption{Large-scale topology parameters}
\label{tab:large-scale}
\begin{tabular}{|l||c|c||c|c|}
  \hline
  \multirow{2}{*}{\bf Link type} &  \multicolumn{2}{|c||}{\bf Delay} &  \multicolumn{2}{|c|}{\bf Bandwidth} \tabularnewline
  \cline{2-5}
                        &  Min & Max                       &  Min & Max \tabularnewline
  \hline \hline
  Backbone--Backbone    & 5~ms & 10~ms   & 40~Mbps & 100~Mbps \tabularnewline
  \hline
  Gateway--Backbone,    & \multirow{2}{*}{5~ms} & \multirow{2}{*}{10~ms}   
                        & \multirow{2}{*}{10~Mbps} & \multirow{2}{*}{20~Mbps} \tabularnewline
  Gateway--Gateway      & & & & \\
  \hline
  Client--Gateway       & 10~ms & 70~ms   & 1~Mbps  & 3~Mbps \\
  \hline

\end{tabular}
\end{table}

\begin{figure*}[t]
 \centering
 \includegraphics[scale=1]{topo-7018-gw-15mins-new/7018-r0-good-0-producer-gw}
 \caption{Satisfaction ratio dynamics during the attack (30\% attackers)}
 % producer on a gateway node
 \label{fig:large-scale}
\end{figure*}

% \begin{figure*}[t]
%  \centering
%  \includegraphics[scale=1]{topo-7018-bb-15mins-new/7018-r0-good-0-producer-bb}
%  \caption{Satisfaction ratio dynamics during the attack (30\% attackers)}
%  % producer on a backbone node
%  \label{fig:large-scale}
% \end{figure*}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2012-12-07 eval-small-scale.tex
Modifying figures in evaluation
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@854 df1a90cd-247b-4364-bdaf-287a704eb499
Initial part of the evaluation section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@870 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
+To assess baseline performance metrics of the designed Interest flooding attack mitigation methods, we evaluated them first using a simplistic small-scale binary tree topology (Fig.~\ref{fig:small-scale}).
+All links in this topology were assigned 10~Mbps bandwidths with randomized propagation delays from the range from one to ten milliseconds.
+Both legitimate users and attackers were placed only on leaf nodes (red), each expressing Interests towards a single producer placed at the root of the tree. 
+% Alex: should we mention that?
+The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS attacks.
+That is, sharing of the network links exponentially increases as decreasing level of the binary tree.
+
 \begin{figure}[htbp]
   \centering
-  \includegraphics[scale=0.3]{topo-tree-evil-5-good-0-producer-gw}
-  \caption{Small-scale topology (one of the runs with 30\% of attackers, all links are 10Mbps with randomized delay 1-10ms)}
-  \label{fig:small-scale-topo}
+  \includegraphics[scale=0.2]{topo-tree-evil-5-good-0-producer-gw}
+  \caption{Small-scale binary tree topology}
+  \label{fig:small-scale}
 \end{figure}
@@
 
-\begin{figure}[htbp]
+\begin{figure*}[t]
   \centering
-  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-dynamics-40}
+  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw}
   \caption{Satisfaction ratio dynamics during the attack (7 attackers / 9 legitimate)}
   \label{fig:small-scale-topo 3}
-\end{figure}
+\end{figure*}
 

### 2012-12-07 eval-small-scale.tex
Most of the evaluation section is semi-done.  I suspect I put too much details and discussion in the evalutions... Not sure
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@871 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-To assess baseline performance metrics of the designed Interest flooding attack mitigation methods, we evaluated them first using a simplistic small-scale binary tree topology (Fig.~\ref{fig:small-scale}).
+% Topology description
+To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a simplistic small-scale binary tree topology (Fig.~\ref{fig:small-scale}).
 All links in this topology were assigned 10~Mbps bandwidths with randomized propagation delays from the range from one to ten milliseconds.
@@
 
-\begin{figure}[htbp]
+% in 10 independent runs of each simulation, where we randomized position of the adversaries along the legitimate users.
+In all runs, the total number of legitimate and malicious uses were fixed, meaning that when we increase number of attackers, we decrease the number of legitimate users.
+
+\subsubsection{Network reaction to the attack}
+
+The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
+For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either physical limits, physical limits with per-interface fairness, probabilistic Interest accept, or dynamic limits (Section~\ref{sec:design}).
+
+For each network scenario we performed ten independent simulation runs, where randomly chosen 7 client nodes represent adversaries (compromised users), and the rest 9 client nodes represent legitimate users.
+In each run we simulated a 10-minute attack window (total simulation time was 30 minutes, with attack starting at 10-minute mark).
+
+The results for all attack mitigation algorithms and all runs are aggregated in Fig.~\ref{fig:small-scale attack progress}, where Y-axis represents a minimum and maximum range for observed Interest satisfaction percentages among all nodes and all simulation runs.
+A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
+
+\begin{figure}[t]
   \centering
-  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min}
-  \caption{Average consumer Interest satisfaction ratios (first minute)}
-  \label{fig:small-scale-topo 1}
+  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw}
+  \caption{Satisfaction ratio dynamics during the attack (7 attackers / 9 legitimate)}
+  \label{fig:small-scale attack progress}
 \end{figure}
+
+\paragraph{\textbf{Physical limits}}
+
+Let us take a deeper look on what is happening with the physical limits algorithm.
+Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as physical limits restricts the number of forwarded Intersets!).
+This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
+In this example we assume that both the legitimate user and the adversary send Interests in about the same time.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[scale=0.3]{physical-limits-sync-problem}
+  \caption{Three-router topology, with one legitimate and one malicious user}
+  \label{fig:three router example}
+\end{figure}
+
+Both router L and router X will forward the Interests, as both of them have a free token available.
+At router A, two cases are possible, either of Interests can arrive first, resulting in a quite different effects.
+When legitimate Interest arrives first, then there are no problem. 
+Router A will capture the token, forward the Interest, which will be quickly satisfied, releasing the token for future uses.
+In the mean time, malicious Interest will be dropped at router A, and router X will release the hold for the token in one second (i.e., after the maximum time Interests are admitted), enabling a new round of competition for router A's resources.
+
+In the case when malicious Interest is sent a little bit earlier, then router A will forward malicious Interests, dropping a legitimate one, and causing ``lock out'' for one second.
+In the instant when the token gets released at router X, an adversary is able to push new Interest towards router A, which may arrive in the exact time A's token gets released (assuming an idealistic environment).
+As a result, the adversary recaptures router A's token and extends the ``lock out'' for another second, denying service to the legitimate user without sending any massive numbers of Interests.
+
+\paragraph{\textbf{Physical limits with per-interface fair queueing}}
+
+The described problem arises from the clocking effect and can be solved in a number different ways.
+Augmenting physical limits algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
+That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
+However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
+Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
+We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.
+
+\paragraph{\textbf{Probabilistic Interest accept}}
+
+When routers apply a more intelligent metod to process incoming Interests (i.e., based on the incoming interface statistics), an Interest flooding attack becomes virtually ineffective.
+That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
+The observed periodicity of the probabilistic Interest accept curve on Fig.~\ref{fig:small-scale attack progress} is a direct result from ``intelligence'' (Interest satisfaction rate statistics) decaying with time.
+The 50-second periods approximately correspond to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx20\%$ within 50~seconds.
+The primary reason that such minimum peaks exist is the fact that when attack Interests start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe traffic mix from legitimate and malicious users).
+This degradation subsequently reduces chances for legitimate Interests get through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' to the edge.
+
+\paragraph{\textbf{Dynamic limits}}
+
+The only potential problem with the dynamic limits algorithm is that it features a sharp dive of the satisfaction ratio curve at the start of the attack.
+That is, until all routers become fully aware of the attack---malicious Interests start to time out---and until explicit Interest limits announcements successfully localize malicious Interests near the attacker, the network for a short period of time (under 10~seconds for all simulation runs) fails to provide 100\% service for the legitimate users.
+At the same time, we do not observe any periodic behavior, as dynamically adjusted limits during an ongoing attack effectively guarantee that once Interest is admitted, it will get through to the Data producer.
+
+\subsubsection{Network reaction with to varying number of attackers}
+
+The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
+To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.
+
+Since at this point the overall attack dynamics of all the attack mitigation algorithms is relatively clear, in Fig.\ref{fig:small-scale-topo boxplot} we show aggregated over 10 individual runs comparison of satisfaction ratio values observed during the first minute of the attack.
+% In other words, each point captured in the box plot graph corresponds to 1-second averaged satisfaction ratio for a user in an individual simulation run.
 
@@
   \centering
-  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min-after-1-min}
-  \caption{Average consumer Interest satisfaction ratios (second minute)}
-  \label{fig:small-scale-topo 2}
+  \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min}
+  \caption{Average consumer Interest satisfaction ratios (first minute)}
+  \label{fig:small-scale-topo boxplot}
 \end{figure}
 
-\begin{figure*}[t]
-  \centering
-  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw}
-  \caption{Satisfaction ratio dynamics during the attack (7 attackers / 9 legitimate)}
-  \label{fig:small-scale-topo 3}
-\end{figure*}
+The presented results demonstrate the overall, and somewhat obvious, trends for all attack mitigation algorithms: the larger is the attack, the lower service quality is observed by the legitimate users.
+Physical limits with and without per-interface fairness give perfect attack instrument even for a small number of attackers: just 3 attackers can either completely shut down or halve the service quality for the rest 13 users.
+At the same time, while both intelligent attack mitigation algorithms also show a decline in service quality, this decline is very subtle: when more than 50\% of users are compromised, service degrades less than by 25\% for probabilistic Interest accept method and less than by 10\% in dynamic limits algorithm.
+
+% \begin{figure}[htbp]
+%   \centering
+%   \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min-after-1-min}
+%   \caption{Average consumer Interest satisfaction ratios (second minute)}
+%   \label{fig:small-scale-topo 2}
+% \end{figure}
 

### 2012-12-07 eval-small-scale.tex
typo
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@872 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-When routers apply a more intelligent metod to process incoming Interests (i.e., based on the incoming interface statistics), an Interest flooding attack becomes virtually ineffective.
+When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
 That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.

### 2012-12-07 eval-large-scale.tex
Semi-finalized evaluations
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@873 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-In order to verify that the designed methods can also work in realistic Internet-like topologies, we 
-performed large-scale simulations using a modified version of Rocketfuel AT\&T topology~\cite{rocketfuel}.
-To approximate structure of the Internet, we selected the largest connected component of 562 nodes and separated nodes in three categories: clients, gateways, and backbones.
+To check validity of the small-scale experiment results, we performed a larger-scale evaluation based on a modified version of Rocketfuel AT\&T topology~\cite{rocketfuel}.
+In order to approximate the general structure of the Internet,
+% (scale-free structure, customer-provider, and peer-to-peer relations)
+we extracted the largest connected component of 562 nodes from the original topology and separated nodes in three categories: clients, gateways, and backbones.
 All nodes with degrees one, two, and three became clients (344 red nodes on Fig.~\ref{fig:large-scale}), all nodes that are directly connected to clients became gateways (109 green nodes), and the rest became backbones (109 blue nodes).
@@
 
-\begin{figure*}[t]
+In an Internet-like topology, the location of the Data producer plays the key part in his ability to sustain flooding attack.
+That is, if the producer has limited network capacity (a personal blog located hosted on a client node), then he will be a really easy target for the attack.
+On the other extreme, when the producer is located at the backbone (Google or Amamzon), then the attack would have a hard time to degrade service, as a lot of legitimate users would not even share paths with attackers.
+To evaluate a balanced network scenario, we placed the Data producer at the gateway node, which randomly picked for each simulation run.
+Similarly to the first set of small-scale evaluations, we fixed the number of malicious nodes at approximately 40\% level (140 out of 344 client nodes in the topology), while randomly varied which locations of compromised nodes.
+
+% The results for all attack mitigation algorithms and all runs are aggregated in Fig.~\ref{fig:small-scale attack progress}, where Y-axis represents a minimum and maximum range for observed Interest satisfaction percentages among all nodes and all simulation runs.
+% A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
+
+The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, for both physical limits algorithms and dynamic limits algorithm show exactly the same trend as in small-scale evaluations, but with larger variations of minimum and maximum instantaneous satisfaction rates.
+
+\begin{figure}[tbh]
  \centering
@@
  \label{fig:large-scale}
-\end{figure*}
+\end{figure}
 
-% \begin{figure*}[t]
-%  \centering
-%  \includegraphics[scale=1]{topo-7018-bb-15mins-new/7018-r0-good-0-producer-bb}
-%  \caption{Satisfaction ratio dynamics during the attack (30\% attackers)}
-%  % producer on a backbone node
-%  \label{fig:large-scale}
-% \end{figure*}
+At the same time, the probabilistic method completely failed to provide an adequate protection against the flooding attack, and in addition degraded service for the legitimate users after the attack finished.
+The main reason for the failure was already explained in Section~\ref{sec:probabilistic}.
+If the number of hops between legitimate users and the Data producer is large (15 on average in the simulated topology) uncoordinated probabilistic Interest drops result in minuscule probability for good Interests to reach the Data producer during an ongoing attack, resulting in negative Interests satisfaction ratio statistics.
+This also explains why until the statistics ages out, not all legitimate users can get satisfy all of their Interests.
+
+In summary, in all of the simulated topologies, the dynamic limits algorithm largely restricts malicious traffic to even enter the network.
+The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
+As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.
+
+% Alex: Anything else here?
+
+% Alex: I also experimented with placing producer at the backbone, getting slightly better results for all algorithms.  Though I'm not sure there is any value to put those results in the paper
 

### 2012-12-07 eval-large-scale.tex
typos and moving discussion section before related work
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@874 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, for both physical limits algorithms and dynamic limits algorithm show exactly the same trend as in small-scale evaluations, but with larger variations of minimum and maximum instantaneous satisfaction rates.
+The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that for both physical limits algorithms and dynamic limits algorithm the performance is about the same as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
 
@@
 
-At the same time, the probabilistic method completely failed to provide an adequate protection against the flooding attack, and in addition degraded service for the legitimate users after the attack finished.
+At the same time, the probabilistic method completely failed to provide an adequate protection against the Interest flooding attack, and in addition degraded service for the legitimate users after the attack finished.
 The main reason for the failure was already explained in Section~\ref{sec:probabilistic}.
-If the number of hops between legitimate users and the Data producer is large (15 on average in the simulated topology) uncoordinated probabilistic Interest drops result in minuscule probability for good Interests to reach the Data producer during an ongoing attack, resulting in negative Interests satisfaction ratio statistics.
+That is, if the number of hops between legitimate users and the Data producer is large (15 on average in the simulated topology) uncoordinated probabilistic Interest drops result in minuscule probability for good Interests to reach the Data producer during an ongoing attack, resulting in negative Interests satisfaction ratio statistics.
 This also explains why until the statistics ages out, not all legitimate users can get satisfy all of their Interests.

### 2012-12-08 06-related.tex
Another variant of discussion section, acknowledging potential problems and handwaving that the problem is not that serious.
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@875 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-05 06-related.tex
@@
 
-In this section we provide a classification of mitigation techniques against DDoS flooding attacks in IP networks, because of the lack of any in NDN or other information centric architectures.
+NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
+In this section we will overview generic directions of DDoS mitigation designs and try to think about which tricks could be used in NDN.
 
-Capability-based systems allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
+% Capability-based systems allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
 Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
 This implies that each client must pass through an authentication process prior to using any bandwidth ~\cite{Capabilities}.
+We believe that for NDN this method doesn't fit really well for the following reasons.
+First, this method is very questionable in terms of scalability and mobility support since it requires tight trust connections between routers and hosts.
+Thus, it neglects one of the main advantages (mobility) of NDN.
+Second, the design of trust infrastructure for NDN is not well defined yet, which means that we cannot really make assumptions in our design of mitigation techniques.
 
-Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
-Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients ~\cite{Portcullis}.
-
-Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
-This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines ~\cite{Pushback}.
+% Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
+Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients.
+One of the main difficulties in such systems is the question of puzzle dessimination.
+In ~\cite{Portcullis} authors suggested to propagate puzzles using DNS system.
+In NDN since routers have caching abilities, we can propagate puzzles just like a normal data packets, using Interest-Data exchange.
+Overall, this method looks interesting and deserves being investigated in a future work.
 
@@
 For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
-If largely deployed such techniques could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
+Such techniques, if largely deployed, could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
+Since NDN routers maintain a richer per-packet state, which translates into a better per-flow statistics, these techniques can become much more effective when applied to NDN.
+
+Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
+This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines~\cite{Pushback}.
+In general this technique can be applied to NDN architecture thanks to its decentralized coordination of downrating bad traffic flows.
+Moreover, NDN provides better capabilities for accurate flow detection.
+
+%were looking for getting accustomed
 

### 2012-12-08 07-discussion.tex
Another variant of discussion section, acknowledging potential problems and handwaving that the problem is not that serious.
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@875 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-02 07-discussion.tex
@@
 
-Lessons we learnt, comparison of different mitigation techniques. 
-Adapting these to mitigate other DDoS attacks.
+% Lessons we learnt, comparison of different mitigation techniques. 
+% Adapting these to mitigate other DDoS attacks.
+
+% In section~\ref{sec:interest flooding} we made assumptions regarding the Interest flooding traffic shape (requesting non-existing data with non-aggregatable prefix name ) and single-path forwarding strategy, which jointly create the most powerful congestion at the producer link.
+
+% In this paper we are using a simple attacker profile and greedy attacker, which is using all resources (available bandwidth) of its botnet in order to put producer down as quickly as possible.
+However, in a real life not all botnets are greedy and in fact can perform smart actions like constant switching between victims every other hour to fool defensive systems by nullifying gathered bad flow statistics.
+Or they can be non-greedy at all, for instance a large botnet of several hundreds of thousands nodes can perform a non-greedy attack by sending just a few Interests per second from each node.
+Nowadays, this situation is very hard to manage, because of the difficulties in detecting of bad flows in a traffic.
+
+% Also, an adversary can mix Interests for non-existing data with Interests for existing-data. Thanks to NDN stateful packet forwarding, bad flows can be easily distinguished and penalized.
+
+% What are the variations of the attack.
+% When defining the Interest flooding attack (Section~\ref{sec:interest flooding}) we made a key assumption that adversaries are trying to achieve the maximum harm (network congestion and router overload) to unprotected NDN network by sending a large volume of \emph{junk Interests}.
+
+The attack mitigation methods studied in this paper provide ways to eliminate network congestion and router overload problems caused by junk Interest flooding (Section~\ref{sec:interest flooding}), but unfortunately not without inducing some new problems.
+In particular, during an ongoing attack, a number of legitimate Interests successfully forwarded towards the Data producer can be substantially larger in unprotected network, then in the network that implements Interests mitigation algorithms.
+This is simply because an unprotected network allows clients to pump more packets and does not impose any artificial restrictions on packet forwarding.
+Therefore, unless a mitigation algorithm uses some form of intelligence (e.g., statistics for Interest satisfiability), a smaller scale flooding attack can cause greater damage to the service quality (recall service quality curves for physical limits in small-scale and larger-scale evaluations, Fig.~\ref{fig:small-scale} and Fig.~\ref{fig:large-scale}).
+
+Let us take one small step back.
+In a general case, the adversaries would not be aware that the network is or is not protected, e.g., using dynamic the limits algorithm.
+As a result, they will try to do as much harm as possible using junk Interests and the mitigation algorithm will work as expected: small service quality degradation during first seconds of the attack, followed by practically full recovery from the attack.
+However, a careful reader may ask a totally legitimate question: what would happen if adversaries know that the network is protected and know that it is using the dynamic limits algorithm?
+Would there be an optimal strategy to deny service for the legitimate users?
+Would it be better to send ``legitimate'' Interests instead, at least partially, and attempt to always keep the network in the transitional state?
+
+% Hopefully, I'll have some results to back up my claims, otherwise these are just words
+
+% We acknowledge that this could be a probl
+Although a complete investigation of this problem deserves a separate study, we anticipate that the problem may not be as severe as it seems.
+When attacker's Interests can be satisfied (e.g., an attacker requesting dynamically generated Data), these Interest would not linger on routers for extended periods of time, giving opportunities for Interests from the legitimate users to get through and bring Data back.
+Essentially, in the worst case scenario (assuming that dynamic limits are augmented with some form fair queuing), legitimate users and attackers would ``fairly'' share the network.
+(Note that router resource overloading is still impossible, as there is always an upper bound of admitted Interets.)
+
+Technically, the ``fair'' sharing of network resources is the only possible way to mitigate the denial of service attacks, if there are no basis to make any distinction between packets, e.g., when attackers are statistically indistinguishable from legitimate users.
+At the same time, fairness can be defined in a number different ways, including per interface fairness, per-flow fairness, or even per-computation fairness~\cite{Capabilities, Portcullis}, resulting in different service qualities depending on how the attack is organized.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2012-12-09 01-intro.tex
New intro, updated discussion
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@876 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Denial of service (DoS) and distributed denial of service attacks (DDoS) appeared not very long time after Internet got traction and since then a constant arms race is going on between information providers and attackers who want to knock a certain source of information down.
-Running a DDoS attack has become a very successful business model due to its general scalable nature, cheapness and lack of protection of information providers by government and law.
-Most popular and economically effective DDoS attacks are organized with botnets.
-A botnet agents get installed by many various ways on computers of ordinary people that leads to a very wide geographical distribution of the source of attack that makes blacklisting impossible (in contrast to single source DoS attacks).
+% Introduction to the problem: ndn, solves many problems, but has potential to introduce new problems.
+% in this paer we are studing a number of remedies to Interest floodig attack, as well as trying to doscover ptential of tjese dolutions and their shortcomings
 
-In 2011 for the first time IPv6 DDoS attacks on commercial networks were observed ~\cite{Arbor}.
-They occur rarely, which only means that IPv6 is not widespread enough for attackers to put significant resources into such DDoS attacks.
-Principally, in terms of DDoS security IPv6 didn't advance that much comparing to standard IPv4 networks.
+% Structure. Hopefully around three paragraps. 
+% - what is happening with ndn and what is interest floodog
+% - what are the general approaches we are taking, ranging from naïve to more intelligent
+% - basic summary of the results
 
-IP architecture has a wide surface for denial of service attacks which takes the beginning from the thin-waist IP protocol, goes through transport level and up to DNS level.
-In IP it is very easy to forge source address and specify the exact destination that needs to be placed under attack that creates possibilities for performing various types of reflection DoS attacks.
-On transport level in TCP/IP stack SYN flood, RST flood and FIN-way attacks are very effective and popular.
-DNS system can be attacked in multiple ways, e.g.
-DNS amplification attack.
+% move disclaimer from section 3 to the intro.
 
-We believe that future Internet architectures can do and must do more for DDoS mitigation.
-By its design NDN architecture is not sensitive to any kind of reflection attacks due to the lack of host addresses and ubiquitous data caching.
-NDN architecture can operate without any DNS-like architecture since it routes and forwards packets based on human-readable names instead of IP addresses that have been received from DNS.
+Various forms of distributed denial of services attack (DDoS) pose a significant and constant threat to the existing Internet infrastructure~\cite{arbor-report}.
+The recently proposed Named Data Networking (NDN) architecture~\cite{ndn-conext, ndn-tr} completely changes the communication paradigm in the network by removing the notion of network host identities and making the application-level Data names the first-class network citizens.
+That is, instead of requiring users to explicitly connect to specific servers and then use application-level protocols to request desired Data, users can directly ask the network for the Data.
+% In other words, NDN changes communication from host-centric to data-centric.
+Such a shift automatically solves several long standing problems, including source address spoofing and reflector DDoS attacks~\cite{mirkovic2004taxonomy}.
 
-%\todo{
-%Current Internet architecture and its resilience to DoS and DDOS. Requirements from a new architecture such as CCN with respect to DoS and DDoS resilience.
+However, as long as there is still a notion of destination, requests (Interests in NDN terms) can still be send towards the destinations,%
+\footnote{Note that ```destination'' is much more vague in NDN than in IP. 
+Copies of the requested Data, towards which Interests may be forwarded, can be in many places, including long-term and short-term caches on NDN routers and alternative locations of the Data producer.}
+potentially disrupting service to legitimate users.
+Taking into account that NDN requires the stateful forwarding of Interets---as the only way for routers to return Data back is to remember from where the Interest came in---an attacker may specifically target the stateful forwarding of NDN, e.g., in a form of Interest flooding attack.
 
-%Our contributions.
+Our primary goal in this paper is not to completely solve all denial of service problems in NDN, but to demonstrate using the Interest flooding attack example (Section~\ref{sec:interest flooding}) that although new NDN-specific DDoS attacks are possible in NDN network, the network is fully equipped to mitigate effects of these attacks.
+In the paper we design several algorithms to mitigate the Interest flooding attack (Section~\ref{sec:design}), exploring the following two unique venues provided by NDN.
+First, an NDN router does not need to accept, create state, and forward all the incoming Interests, but only the amount that would fully utilize downstream link capacity.
+Second, the fact that Data always follows the Interest paths can be used to distinguish between good (e.g., a forwarded Interest gets satisfied) and ``bad'' Interests.
 
-%Paper organization.}
+% Alex: Not sure whether it should be mentioned in intro or not.  If it should, then I don't really like it...
+To quantify the quality of the designed attack mitigation algorithms, we performed a simulation-based study (Section~\ref{sec:evaluation}) based on trivial small-scale and Internet-like larger-scale topologies.
+The results show a great potential of one of the designed algorithms (dynamic limits, Section~\ref{sec:dynamic limits}), where the attack traffic can be effectively localized near the attacker himself.
 
-In this paper we provide a analyze all aspects of Interest Flooding attack in NDN architecture, propose multiple defensive techniques against such attacks, establish evaluation methodology using ndnSIM simulation software, execute small scale and Internet scale DDoS attack scenarios, and analyze our experimental results.
-
-Following this introduction, Section 2 gives a brief overview of NDN architecture.
-Section 3 thoroughly discusses Interest flooding attack, and Section 4 proposes multiple defensive techniques against it.
-Section 5 describes evaluation methodology and gives experimental results.
+% Section 2 gives a brief overview of NDN architecture. 
+% Section 3 defines Interest flooding attack, 
+% Section 4 designes several attack mitigation algorithms.
+% Section 5 describes evaluation methodology and gives experimental results.
 Section 6 contains related work.
@@
 Section 8 concludes and describes future work.
-
-%\begin{figure}[htpb]
-%  \centering
-%  \includegraphics[scale=0.5]{figures/sim-emu-power.pdf}
-%  \caption{Strength of Interest flooding attack}
-%  \label{fig:simemupower}
-%\end{figure}
-
-%\begin{figure}[htpb]
-%  \centering
-%  \includegraphics[scale=0.5]{figures/sim-emu-performance.pdf}
-%  \caption{Data retrieval by legitimate clients}
-%  \label{fig:simemuperf}
-%\end{figure}
 

### 2012-12-09 03-interest-flooding.tex
Most of the evaluation section is semi-done.  I suspect I put too much details and discussion in the evalutions... Not sure
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@871 df1a90cd-247b-4364-bdaf-287a704eb499
New intro, updated discussion
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@876 df1a90cd-247b-4364-bdaf-287a704eb499

@@
   \centering
-  \includegraphics[width=\columnwidth]{attack-definition}
+  \includegraphics[scale=0.39]{attack-definition}
   \caption{Example of the Interest flooding attack}
@@
 
-\paragraph{Disclaimer}
-
-In this paper we are not trying to completely solve all denial of service problems that can be caused by various variations of the Interest flooding attack.
-Our primary focus is to demonstrate that while NDN opens doors to new types of denial of service attacks, stateful packet forwarding of NDN makes it possible to mitigate such attacks, adding little additional complexity to the network.
-In section~\ref{sec:discussion} we discuss our choice of the assumptions in more detail, as well as discuss potential of the Interest flooding attack under several other attack assumptions.
+In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
 

### 2012-12-09 07-discussion.tex
New intro, updated discussion
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@876 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \label{sec:discussion}
-
-% Lessons we learnt, comparison of different mitigation techniques. 
-% Adapting these to mitigate other DDoS attacks.
-
-% In section~\ref{sec:interest flooding} we made assumptions regarding the Interest flooding traffic shape (requesting non-existing data with non-aggregatable prefix name ) and single-path forwarding strategy, which jointly create the most powerful congestion at the producer link.
-
-% In this paper we are using a simple attacker profile and greedy attacker, which is using all resources (available bandwidth) of its botnet in order to put producer down as quickly as possible.
-However, in a real life not all botnets are greedy and in fact can perform smart actions like constant switching between victims every other hour to fool defensive systems by nullifying gathered bad flow statistics.
-Or they can be non-greedy at all, for instance a large botnet of several hundreds of thousands nodes can perform a non-greedy attack by sending just a few Interests per second from each node.
-Nowadays, this situation is very hard to manage, because of the difficulties in detecting of bad flows in a traffic.
-
-% Also, an adversary can mix Interests for non-existing data with Interests for existing-data. Thanks to NDN stateful packet forwarding, bad flows can be easily distinguished and penalized.
 
@@
 The attack mitigation methods studied in this paper provide ways to eliminate network congestion and router overload problems caused by junk Interest flooding (Section~\ref{sec:interest flooding}), but unfortunately not without inducing some new problems.
-In particular, during an ongoing attack, a number of legitimate Interests successfully forwarded towards the Data producer can be substantially larger in unprotected network, then in the network that implements Interests mitigation algorithms.
+In particular, during an ongoing attack, a number of legitimate Interests successfully forwarded towards the Data producer can be substantially larger in unprotected network, then in the network that implements an Interest mitigation algorithm.
 This is simply because an unprotected network allows clients to pump more packets and does not impose any artificial restrictions on packet forwarding.
@@
 
-Let us take one small step back.
-In a general case, the adversaries would not be aware that the network is or is not protected, e.g., using dynamic the limits algorithm.
-As a result, they will try to do as much harm as possible using junk Interests and the mitigation algorithm will work as expected: small service quality degradation during first seconds of the attack, followed by practically full recovery from the attack.
-However, a careful reader may ask a totally legitimate question: what would happen if adversaries know that the network is protected and know that it is using the dynamic limits algorithm?
-Would there be an optimal strategy to deny service for the legitimate users?
-Would it be better to send ``legitimate'' Interests instead, at least partially, and attempt to always keep the network in the transitional state?
+Although the studied attack mitigation algorithms base their intelligence on per interface level, it is also possible to use more granular processing.
+For example, if routers measure satisfaction ratios and limit Interest forwarding independently for each FIB prefix, then an ongoing attack on one Data namespace will not have any effect ob users requesting Data from another namespace.
+ % (assuming that users have to get through te same roiter to get the data)
 
-% Hopefully, I'll have some results to back up my claims, otherwise these are just words
+% (already mentioned in Interest flooding definiton section)
+%  Another thing is that rich interconnectivity (de facto on The Internet) and the multi-path packet forwarding (practically impossible) gives NDN addition leverage points to mitigate / reduce effects of ongoing Interest flooding attack of any form.
 
-% We acknowledge that this could be a probl
+In the definition of the Interests flooding attack we explicitly stated that an attack is carried using junk Interets, which obviously gives us a clear distinction between ``good'' and ``bad'' Interests.
+A curious reader may ask us a valid question: what would happen if an adversary doing something else, e.g., sending sends only ``legitimate'' Interests or intermix them with junk Interests?
 Although a complete investigation of this problem deserves a separate study, we anticipate that the problem may not be as severe as it seems.
-When attacker's Interests can be satisfied (e.g., an attacker requesting dynamically generated Data), these Interest would not linger on routers for extended periods of time, giving opportunities for Interests from the legitimate users to get through and bring Data back.
+First, in a general case, the adversaries would not be aware that the network is or is not protected, e.g., is using the dynamic limits algorithm.
+As a result, adversaries would want to do as much harm as possible, which is to send junk Interests.
+
+% Second, when adversary is aware of the attack mitigation mechanisms and sends 
+Second, a satisfiable Interests does not cause NDN-specific harm, as they would not linger on routers for extended periods of time, giving opportunities for Interests from the legitimate users to get through and bring Data back.
 Essentially, in the worst case scenario (assuming that dynamic limits are augmented with some form fair queuing), legitimate users and attackers would ``fairly'' share the network.
-(Note that router resource overloading is still impossible, as there is always an upper bound of admitted Interets.)
+Note that router resource, as well as upstream link capacity overloading is still impossible, as there is always an upper bound of admitted Interets.
+
+%  and the mitigation algorithm will work as expected: small service quality degradation during first seconds of the attack, followed by practically full recovery from the attack.
+% However, a careful reader may ask a totally legitimate question: what would happen if adversaries know that the network is protected and know that it is using the dynamic limits algorithm?
+% Would there be an optimal strategy to deny service for the legitimate users?
+% Would it be better to send ``legitimate'' Interests instead, at least partially, and attempt to always keep the network in the transitional state?
 

### 2012-12-09 08-conclusion.tex
More reorganization and adding Makefile
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@847 df1a90cd-247b-4364-bdaf-287a704eb499
First draft of the conclusion
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@877 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-02 06-related.tex
@@
+\section{Conclusion}
+\label{sec:conclusion}
+
+% Main take out from the paper:  could be a problem, but problem is solvable.
+
+% one may think that
+
+One of the key components in the Named Data Networking architecture is its stateful data delivery model, which potentially can be abused by new types of denial of service attacks.
+However, one should not forget that the same stateful data delivery provides effective mechanisms to fight back against such attacks.
+In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
+The most effective of the designed algorithms---dynamic limits---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data pah symmetry and full receiver-based traffic control.
+In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Intersets can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
+
+% Alex: I feel that we should say something else in the conclusion, but not sure what...
+
+% In conclusion, we want to emphasize that Named Data Networking architecture has much more potential, even to protect against attacks,
+
+% We hope that this paper will change attitude to NDN design
+% We hope that insights of NDN design potential will 
+% Change thinking 
+% will spark change in thinking about NDN architecture...
+
 %%% Local Variables: 

### 2012-12-10 08-conclusion.tex
Updated conclusion with a final remark
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@878 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-One of the key components in the Named Data Networking architecture is its stateful data delivery model, which potentially can be abused by new types of denial of service attacks.
-However, one should not forget that the same stateful data delivery provides effective mechanisms to fight back against such attacks.
+% One of the key components in the Named Data Networking architecture is its stateful data delivery model, which potentially can be abused by new types of denial of service attacks.
+% However, one should not forget that the same stateful data delivery provides effective mechanisms to fight back against such attacks.
+
 In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
@@
 
-% Alex: I feel that we should say something else in the conclusion, but not sure what...
-
-% In conclusion, we want to emphasize that Named Data Networking architecture has much more potential, even to protect against attacks,
+Other forms of attack may require different mitigation mechanisms.  
+However, the granularity of the NDN state---per each Interest packet---is what giving NDN an opportunity to stand against existing and new forms of attacks.
 

### 2012-12-12 04a-design-naive.tex
Splitting 4-design.tex into 4a-design-naive.tex and 4b-design-intelligent.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@880 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-05 04-design.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Intelligent attack mitigation}
-
-About additional knowledge about interests.
-
-Another unique feature of the NDN architecture is stateful packet forwarding~\cite{adaptive-forwarding} and symmetric flow of Interests and Data packets.
-Every time Interests is send out to the Interface, the router will be able to learn various parameters about this Interest.
-
-From the DDoS mitigation point of view, one of the important parameters is to determine from which interface
-
-In order to mitigate a denial of service attack it is vital to know the origin of the attack.
-I the origin of the attack is known, then the attack can be easily suppressed and eventually localized.
-In our definition of the attack is that
-
-interest of the attackers are not getting satisfied. 
-Every router can learn fro m which interfaces attack traffic is coming and do certain actions to limit forwarding of suspicious interest.
-In other words, without trying to distinguish legitimate and malicious interests on the basis of the Interest prefix, routers distinguish them based on recent performance.
-
-\subsubsection{Data plane performance tracking}
-\label{sec:stats}
-
-\input{algos/stats.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Probabilistic Interest accept}
-\label{sec:probabilistic}
-
-\input{algos/probabilistic.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Dynamic adjustments of window-based limits}
-\label{sec:dynamic limits}
-
-\input{algos/dynamic-limits.tex}
-
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: "paper"
-%%% End:

### 2012-12-12 04b-design-intelligent.tex
Splitting 4-design.tex into 4a-design-naive.tex and 4b-design-intelligent.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@880 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-05 04-design.tex
@@
-\section{Interest flooding mitigation methods}
-\label{sec:design}
-
-% Points what should be here:
-% - What can be done (in general) to mitigate flooding attack
-% - Which building blocks NDN architecture gives to mitigate Interest flooding attacks: Interest limits, ability to measure Interest satisfaction performance (Interest satisfaction stats)
-% - Methods to set these limits: static/dynamic
-% - Methods how limits can be applied: best-effort (fifo), "fair" queuing, probabilistic
-% - Reference to caching: we don't consider it here, but caching provides additional level of protection, especially for certain types of attacks
-
-% Our definition of attack mitigation is that good clients are still able to access data on the producer.
-
-In this section we present several methods to mitigate Interest flooding attacks in NDN, featuring different degrees of implementation complexity, as well as different degrees of effectiveness.
-
-%   - Naive approach to Interest Limits (that is called physical limits everywhere else)
-%     Example how this can be implemented in a simple way
-%     Baseline solution
-%   - Interest limits with "fair" queuing
-%     Improving problem of simple limits (no single face can dominate), but doesn't solve the proble
-
-% - Attack mitigation
-%   - Per-incoming interface Interest statistics
-
-%   - Dynamic Interests limit adjustments
-
-%   - Probabilistic Interest accept
-
-Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
-Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
-Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
-At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
-
-\subsection{Na\"{i}ve attack mitigation}
-
-% In a normal network operation, the size of Interests packets is supposed to be significantly smaller than the size of the requested Data.
-
-% All communication in NDN network is host-to-host and receiver-driven.
-
-The most obvious and na\"{i}ve method to mitigate the Interest flooding attack is to limit the number of forwarded Interests out of each interface. 
-That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
-For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
-In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
-
-\subsubsection{\textbf{Interest limits (physical limits)}}
-\label{sec:physical limits}
-
-\input{algos/physical-limits.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Physical limits with per-interface fairness}}
-\label{sec:queuing}
-
-\input{algos/fair-queueing.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Intelligent attack mitigation}
+\label{sec:intelligent mitigating}
 
@@
 
-\subsubsection{\textbf{Dynamic adjustments of window-based limits}}
+\subsubsection{\textbf{Dynamic limits}}
 \label{sec:dynamic limits}

### 2012-12-17 01-intro.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@884 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 Various forms of distributed denial of services attack (DDoS) pose a significant and constant threat to the existing Internet infrastructure~\cite{arbor-report}.
-The recently proposed Named Data Networking (NDN) architecture~\cite{ndn-conext, ndn-tr} completely changes the communication paradigm in the network by removing the notion of network host identities and making the application-level Data names the first-class network citizens.
-That is, instead of requiring users to explicitly connect to specific servers and then use application-level protocols to request desired Data, users can directly ask the network for the Data.
-% In other words, NDN changes communication from host-centric to data-centric.
-Such a shift automatically solves several long standing problems, including source address spoofing and reflector DDoS attacks~\cite{mirkovic2004taxonomy}.
+The recently proposed Named Data Networking (NDN) architecture~\cite{ndn-conext, ndn-tr} completely changes the communication paradigm in the network by removing the notion of addresses and making data the first-class network entities.
+That is, instead of letting end hosts sending packets to a given IP address, NDN lets end hosts request desired data by sending Interest packets carrying application level data names.
+Such a shift automatically eliminates several long standing DDoS attacks, including both direct flooding as well as reflector attack through source address spoofing~\cite{mirkovic2004taxonomy}.
 
-However, as long as there is still a notion of destination, requests (Interests in NDN terms) can still be send towards the destinations,%
-\footnote{Note that ```destination'' is much more vague in NDN than in IP. 
-Copies of the requested Data, towards which Interests may be forwarded, can be in many places, including long-term and short-term caches on NDN routers and alternative locations of the Data producer.}
-potentially disrupting service to legitimate users.
-Taking into account that NDN requires the stateful forwarding of Interets---as the only way for routers to return Data back is to remember from where the Interest came in---an attacker may specifically target the stateful forwarding of NDN, e.g., in a form of Interest flooding attack.
+However, since NDN allows any host to request any data, malicious users can attack an NDN network by Interest flooding.
+As we explain in the next section, NDN routers perform stateful forwarding of Interests, uncontrolled floods of Interest packets can potentially exhaust router resources, disrupting services for legitimate users.
+One can also attack an NDN network by hijacking Interest packets and then injecting false data replies into the network.
 
-Our primary goal in this paper is not to completely solve all denial of service problems in NDN, but to demonstrate using the Interest flooding attack example (Section~\ref{sec:interest flooding}) that although new NDN-specific DDoS attacks are possible in NDN network, the network is fully equipped to mitigate effects of these attacks.
-In the paper we design several algorithms to mitigate the Interest flooding attack (Section~\ref{sec:design}), exploring the following two unique venues provided by NDN.
-First, an NDN router does not need to accept, create state, and forward all the incoming Interests, but only the amount that would fully utilize downstream link capacity.
-Second, the fact that Data always follows the Interest paths can be used to distinguish between good (e.g., a forwarded Interest gets satisfied) and ``bad'' Interests.
+As a first step towards a complete solution to address various denial of service attack problems in NDN, in this paper we investigate the solution space for Interest flooding attack (Section~\ref{sec:interest flooding}).
+We show how an NDN router can exploit its state information to mitigate Interest flooding (Section~\ref{sec:design}).
+We base our solution on the following two insights.
+First, instead of creating state for all incoming Interests, an NDN router only needs to accept enough Interest packets to fully utilize downstream link capacity.
+Second, because Data packets traverse the path taken by the Interests, an NDN router can observe whether an Interest retrieves Data (good Interest) or not (bad Interest).
+% Alex: Not sure whether it should be mentioned in intro or not.  If it should, then I don't really like it...
 
-% Alex: Not sure whether it should be mentioned in intro or not.  If it should, then I don't really like it...
-To quantify the quality of the designed attack mitigation algorithms, we performed a simulation-based study (Section~\ref{sec:evaluation}) based on trivial small-scale and Internet-like larger-scale topologies.
+We conduct simulation-based evaluations to quantify the effectiveness of our proposed attack mitigation algorithms (Section~\ref{sec:evaluation}).
+%% based on trivial small-scale and Internet-like larger-scale topologies.
 The results show a great potential of one of the designed algorithms (dynamic limits, Section~\ref{sec:dynamic limits}), where the attack traffic can be effectively localized near the attacker himself.
-
-% Section 2 gives a brief overview of NDN architecture. 
-% Section 3 defines Interest flooding attack, 
-% Section 4 designes several attack mitigation algorithms.
-% Section 5 describes evaluation methodology and gives experimental results.
-Section 6 contains related work.
-Section 7 provides analysis based on our results.
-Section 8 concludes and describes future work.
+\todo{LZ: I did not modify this last paragraph; need to see the rest of the paper first.}
 

### 2012-12-17 paper.tex
Checkpoint (unfinished section 3, attack description)
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@851 df1a90cd-247b-4364-bdaf-287a704eb499
Section 3 update
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@852 df1a90cd-247b-4364-bdaf-287a704eb499
Semi-finalized fair-queuing description
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@857 df1a90cd-247b-4364-bdaf-287a704eb499
Semi-finalized dynamic limits section, which finally completes the whole design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protectio

@@
-\documentclass[10pt, conference, compsocconf]{IEEEtran}
+% \documentclass[10pt, conference, compsocconf]{IEEEtran}
+\documentclass[conference]{IEEEtran}
+% http://networking2013.poly.edu/call-for-papers/paper-submission/
+% Page limit 9 pages
 
-\title{Mitigating Interest Flooding DDoS Attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
+\makeatletter
+\def\ps@headings{%
+\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
+\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
+\def\@oddfoot{}%
+\def\@evenfoot{}}
+\makeatother
+
+\pagestyle{headings}
+
+\title{Mitigating Interest Flooding DDoS Attacks in NDN}%:\\ Cache/Content Poisoning}
 \author{anonymous}
+
+\newfont{\nicettfont}{cmtt10}
+\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
+\renewcommand{\texttt}[1]{{\nicettfont #1}}
+\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \marginpar{\textsc{ToDo}}
+\framebox{\begin{minipage}[c]{0.95 \columnwidth}
+\tt #1 \end{minipage}}\vspace{5 mm}\par}
 
@@
 % \usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
+\usepackage{algpseudocode,algorithm}
+% More customizeable version. Probably it would be better to convert pseudocode to 2e format
+% \usepackage{algorithm2e} 
+\usepackage{multirow}
 
@@
 \begin{document}
+
 \maketitle
@@
 \begin{abstract}
-
-Distributed Denial of Service attack is an ongoing problem in today's Internet. 
-A newly proposed future Internet architecture, Named Data Networking (NDN), lets end users request desired data by sending Interest packets, and the network forwards data packets to end users upon request only.
-Thus, NDN can effectively defeat the existing DDoS attacks, however it can be subject to new types of DoS attacks, namely Interest packet flooding.  
-In this paper we investigate effective solutions to mitigate Interest flooding attacks. 
-We use simulations to evaluate the design and our results show that our proposed solution can respond to Interest flooding attacks quickly, and that the inherent flow-balance property of NDN (i.e., one Interest packet retrieves at most one Data packet) can be used as a basis for effective DDoS mitigation algorithms.
-
+Distributed Denial of Service attack is an ongoing problem in today's Internet, where packets from large numbers of compromised hosts thwart the paths to the victim site and/or overload the victim machines.
+In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network forwards data packets upon request only, effectively eliminating the existing DDoS attacks.
+However an NDN network can be subject to a new type of DoS attacks, namely Interest packet flooding.  
+In this paper we investigate effective solutions to mitigate Interest flooding.
+We show that NDN's inherent properties of each router keeping per packet state and flow-balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
+Our evaluation through simulations shows that the solution can quickly and effectively respond to Interest flooding.
 \end{abstract}
@@
 
-\input{04-design}
+\input{04a-design-naive}
+
+\input{04b-design-intelligent}
 
@@
 
+\input{07-discussion}
+
 \input{06-related}
-
-\input{07-discussion}
 
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{IEEEtran}
 \bibliography{references}

### 2012-12-17 02-ndn-background.tex
More reorganization and adding Makefile
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@847 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@885 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-\section{ NDN Overview\label{ccn-intro}}
-Named Data Networking (NDN) is a network architecture which aims to replace IP architecture by replacing IP’s host-to-host data delivery model with pull-based information retrieval model.
+\section{NDN Overview\label{ccn-intro}}
+%Named Data Networking (NDN) is a network architecture which aims to replace IP architecture by replacing IP’s host-to-host data delivery model with pull-based information retrieval model.
 In IP in order to retrieve data, data consumer have to know endpoint location of the desired data, in NDN all they have to know is data name.
@@
 
-NDN communication uses two packet types: Interest and Data.
-An Interest packet contains data name and is issued by the receiver to express what data is needed.
-The sender puts a data packet into the network in response to an Interest.
+In this section we briefly introduce NDN with a focus on its stateful forwarding plane.
+NDN is a receiver-driven, data-centric communication protocol.
+All communication in NDN is performed using two distinct types of packets: \textit{Interest} and \textit{Data}.
+Both types of packets carry a \textit{name}, which uniquely identifies a piece of data that can be carried in one Data packet.
+Data names in NDN are hierarchically structured.
+A canonical NDN name looks in the following way: \texttt{\small /ndn/ucla/CS/www/index.html}.
+
+To retrieve Data, a consumer puts the name of desired data into an Interest packet and sends it to the network.
+Routers use this name to forward the Interest towards the data producer, and the Data packet whose name matches the name in the Interest is returned to the consumer.
+All data packets carry a signature that binds the name to the data.
 An Interest is “satisfied” when a Data packet is received with matching data name.
 
-Every NDN node manages three important data structures:
+Each NDN node maintains three major data structures:
 \begin{enumerate}
@@
 Having one-to-many relationship in this table allows multipath forwarding of Interests.}
-\item{Content Store (CS) temporarily stores Data packets that pass through this node and allows fast Data retrieval.}
-\item{Pending Interest Table (PIT) holds all "not yet satisfied" Interests that have been sent upstream.
-Every element contains a list of incoming and outgoing physical interfaces to enable multipath Interest forwarding and multipath Data delivery.}
+\item{Content Store (CS) temporarily buffers Data packets that pass through this node, allowing fast Data retrieval by different consumers.}
+\item{Pending Interest Table (PIT) holds all ``not yet satisfied'' Interests that have been sent upstream towards data producers.
+Each entry in PIT contains a list of incoming, and outgoing, physical interfaces; the former enables multicast Data delivery, and the latter is needed when the same Interest is forwarded along multiple paths.}
 \end{enumerate}
 
-So how it works altogether?
-Every incoming Interest triggers a lookup in the Content Store and if the Data with matching data name have been found, it is sent back to the same physical interface from which the Interest has arrived.
+When a router receives an Interest packet, it first checks whether there is a matching Data in its Content Store.
+If a match is found, the Data is sent back to the incoming interface of the Interest packet.
+If not, the Interest name is checked against the entries in the PIT. 
+If the name exists in the PIT already, then it can be either a duplicate Interest (i.e., its nonce is remembered in PIT entry) that should be dropped,
+or an Interest from another consumer asking for the same Data which requires the incoming interface of this Interest to be added to the existing PIT entry.
+If the name does not exist in the PIT, the Interest is added into the PIT and further forwarded to the interface chosen by the strategy module.
+
+When a Data packet is received, its name is used to look up the PIT.
+If a matching PIT entry is found,
+the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the Content Store, and removes the PIT entry.
+Otherwise, the Data packet is unsolicited and discarded.
+Each Interest also has an associated lifetime; the PIT entry is removed when the lifetime expires.
+
+%Every incoming Interest triggers a lookup in the Content Store and if the Data with matching data name have been found, it is sent back to the same physical interface from which the Interest has arrived.
 If CS lookup is unsuccessful, Interest must be sent further upstream and put in the PIT.

### 2012-12-18 04a-design-naive.tex
changes to 4a physical limits
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@886 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-In this section we present several methods to mitigate Interest flooding attacks in NDN, featuring different degrees of implementation complexity, as well as different degrees of effectiveness.
+In this section we present several algorithms to mitigate Interest flooding attacks in NDN.
+Our mitigation strategies feature varying degrees of implementation complexity and effectiveness -- the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
+We start by describing two naive strategies and use the insights and lessons learnt from the evaluation of these techniques to inform and design more effective mitigation techniques that work well in a variety of attack scenarios.
 
@@
 
-Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
-Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
-Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
-At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
+Our mitigation strategies are based on two fundamental principles of NDN architecture - flow balance between Interest and Data packets, and Data packets traversing the reverse path taken by Interest packets.
+The flow balance in NDN refers to the fact that one Interest packet can be satisfied with at most one Data packet.
+This principle allows intermediate routers that forward the Interest packets to control the number of outstanding Interests packets in the network.
+The fact that each Data packet takes the reverse path of the corresponding Interest packet allows intermediate routers to match a received Data packet to the corresponding Interest packet and thus determine which Interest packets were satisfied.
+As we describe in the rest of this section,  NDN routers can exploit this information to make informed decisions on which Interest packets to forward, how many Interest packets to forward, and thus effectively defend against DDoS attacks.
 
-\subsection{Na\"{i}ve attack mitigation}
+%Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
+%Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
+%Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
+%At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
+
+%\subsection{Na\"{i}ve attack mitigation}
+
+%We start with a couple of naive strategies that can be used to migitate attacks in an NDN network and describe the pitfalls associated with these strategies.
 
@@
 
-The most obvious and na\"{i}ve method to mitigate the Interest flooding attack is to limit the number of forwarded Interests out of each interface. 
-That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
-For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
-In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
+An obvious and simple strategy that can be used to mitigate the Interest flooding attack is for a router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface.
+This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet switched networks.
+Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of data requested that can fully utilize the downstream link (calculated from the number of pending Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
+Ideally, the number of tokens {\it i.e.} the \emph{Pending Interests Limit} for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
+We can formalize this value as follows:
+% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
 
-\subsubsection{\textbf{Interest limits (physical limits)}}
-\label{sec:physical limits}
+\begin{equation}
+\mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
+\end{equation}
 
-\input{algos/physical-limits.tex}
+In the above equation, \emph{Delay} is the expected time of Interest being satisfied and \emph{Data packet size} is the size of the returned Data packet.
+Although both these values are not known {\it apriori}, it is not really necessary to use their exact values.
+One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as the network buffers can smooth out most of the network fluctuations.
+
+An obvious failure of the above {\it Token Bucket} algorithm is that it can be used as an effective mechanism to carry out denial of service attacks.
+If a router has utilized all its {\it tokens} to forward {\it bad} Interests on an out Interface, it can no longer forward incoming Interests from legitimate users on that out inteface till the pending {\it bad} Interests start to expire.
+One way to get around this issue is to impose a per-interface limit so that {\it bad} Interests are not allowed to entirely consume the limits of a specific interface.
+We describe this technique in greater detail in the next subsection.
+
+%That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
+%For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
+%In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
+%
+%\subsubsection{\textbf{Interest limits (physical limits)}}
+%\label{sec:physical limits}
+%
+%\input{algos/physical-limits.tex}
 

### 2012-12-18 algos/fair-queueing.tex
done with first rounds of edits to Sec 4a naive techniques
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@887 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-05 algos/fair-queueing.tex
@@
 
-To partially overcome deficiencies of the Physical limits algorithm we need to ensure that the forwarded Interests represent at least a ``fair'' mix of the Interests received from different neighbors (interfaces).
-That is, if the routers A on Fig.~\ref{fig:flooding example} has a very tight token budget, these tokens should be fairly distributed between incoming interfaces \texttt{eth0} and \texttt{eth1}.
-Because of the very small volume of Interests, we cannot simply rely on network buffers to do statistical multiplexing of Interests, as they would almost never be buffered.
-At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests will arrive in the future.
-Therefore, in order to achieve the goal of ``fair'' mixing of Interests, we need to implement additional mechanisms to buffer and mix incoming Interests, only if they cannot be immediately forwarded.
+To address the lack of fairness associated with the naive {\it Token Bucket} algorithm, we can modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring interfaces.
+For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  be fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
+%Due to the expected small volume of Interests, we cannot merely rely on network buffers to perform statistical multiplexing of Interests, as they would almost never be %buffered.
+%At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests %will arrive in the future.
+In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring interfaces, 
+%, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
+we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded (see Fig.~\ref{fig:queueing}).
+To support fair queuing, we implement hierarchical queues for each interface as shown in Fig.~\ref{fig:queueing})\footnote{This mechanism is essentially class based queuing, with classes for each outgoing/incoming interface.} As an alternative to hierarchical queues, one can also use an approach based on virtual time.
+For details, please see ~\cite{zhang1990virtual}.
+We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
+Thus, a PIT entry can be quickly updated when the Interest is actually forwarded; further the element can be quickly removed from the queue when the Interest expires.
 
-For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}). 
-As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
-It should be noted that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
-This way, PIT entry can be quickly updated when the Interest is actually forwarded, as well as the element can be removed from the queue when the Interest expires.
+%For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}).
+%As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
 
@@
   \includegraphics[scale=0.65]{queue}
-  \caption{Interest queuing: if tokens are unavailable, the router creates PIT entry, but instead of forwarding, enqueued the Interest}
+  \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
   \label{fig:queueing}
@@
 
-A more formalized description of the Physical limits algorithms with per-interface fairness is presented in Pseudocode~\ref{alg:queuing}.
-The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
-At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
+We present a more formalized description of the Physical limits algorithms with per-interface fairness in Pseudocode~\ref{alg:queuing}.
+We can control the amount of physical resources utilized at a router (such as memory and computation power) by setting appropriate queue sizes.
+It is also important to set apprpriate value for how long an Interest can be enqueued.
+If an Interest is enqueued for a long time, by the time it is dequeued and appropriately forwarded, the resulting Data packet might not be valid due to state expiration at previous downstream routers.
+We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
+{\it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
+
+%It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
+%Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
+%Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
+
+%The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
+%At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
 
@@
 
-It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
-Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
-Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
+As we show in Section~\ref{sec:evaluation}, fair queueing provides partial relief from the Interest flooding attack, allowing legitimate users to successfully fetch Data for 15--20\% of the expressed Interests (compared to 0-10\% without fair queueing).
+While these might be reasonable techniques for preventing congestion in the network and for ensuring fairness, they are far from being effective in protecting legitimate users from malicious attackers.
+Malicious attackers by sending a relatively small volume of Interests are able to successfully impact services for legitimate users.
 
-As we show in Section~\ref{sec:evaluation}, fair queueing provides a partial relief from the Interest flooding attack, allowing legitimate users to successfully fetch Data for 15--20\% of the expressed Interests (compared to 0-10\% without fair queueing).
-At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
-Therefore, to successfully solve the problem, we need a more intelligent approach, allowing us to localize the attack traffic as close to the attack origin as possible.
+The fundamental drawback of the {\it Token Bucket} as well as the fair queuing on a per-interface basis is that they fail to distinguish between good Interests from bad ones.
+Unlike in today's host-based Internet architecture where DDoS mitigation techniques that rely on blacklisting of dark IP prefixes or whitelisting of good IP prefixes are still reasonably effective, in NDN one cannot easily distinguish a 'good' prefix from a 'bad' one.
+Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets -- thus, any  Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
+Thus any DDoS mitigation technique that relies on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
+{\it Priya: Need some text massaging here so it flows well and naturally leads to the intelligent schemes}
+
+%At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
+%Therefore, to successfully solve the problem, we need a fundamentally different, more intelligent approach, allowing localization of the attack traffic as close as possible to the attack origin.
 

### 2012-12-18 04a-design-naive.tex
more updates to sec 4a - naive strategies
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@888 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+The key drawback of the {\it Token Bucket} as well as variations of the {\it Token Bucket} algorithm that rely on fair queuing on a per-interface basis is that they still admit Interst packets from malicious users.
+A sizeable percentage of these malicious Interests are forwarded all the way to content producers, thereby utilizing scarce network resources and reducing resources available to serve legitimate users.
+These algorithms attempt to ensure that each interface does not forward more than its fair share of Interests and in doing so they drop both legitimate Interests as well as malicious Interests.
+Any effective DDoS  mitigation strategy must be able to detect and effectively drop only malicious requests for content.
+Good Interests from legitimate users must be admited and forwarded appropriately.
+The key question is how can we devise mitigation algorithms that allows a router to distinguish between good and bad Interests?
+
+Unlike in today's host-based Internet architecture where DDoS mitigation techniques that rely on blacklisting of dark IP prefixes or whitelisting of good IP prefixes are still reasonably effective, in NDN one cannot easily distinguish a 'good' prefix from a 'bad' one.
+Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets -- thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
+Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone -- DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
+
+{\it Priya: Need some text massaging here so it naturally leads to the intelligent algos}

### 2012-12-18 algos/fair-queueing.tex
more updates to sec 4a - naive strategies
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@888 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 While these might be reasonable techniques for preventing congestion in the network and for ensuring fairness, they are far from being effective in protecting legitimate users from malicious attackers.
-Malicious attackers by sending a relatively small volume of Interests are able to successfully impact services for legitimate users.
-
-The fundamental drawback of the {\it Token Bucket} as well as the fair queuing on a per-interface basis is that they fail to distinguish between good Interests from bad ones.
-Unlike in today's host-based Internet architecture where DDoS mitigation techniques that rely on blacklisting of dark IP prefixes or whitelisting of good IP prefixes are still reasonably effective, in NDN one cannot easily distinguish a 'good' prefix from a 'bad' one.
-Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets -- thus, any  Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
-Thus any DDoS mitigation technique that relies on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
-{\it Priya: Need some text massaging here so it flows well and naturally leads to the intelligent schemes}
+Malicious attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of Interests.
 

### 2012-12-18 04b-design-intelligent.tex
updates to sec 4b - intelligent strategies
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@889 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-While the Interest limit is the key building block to suppress mechanisms of the Interest flooding attack, legitimate Interests need to be somehow prioritized and malicious Interests need to be somehow penalized in order to completely suppress the attack.
-That is, instead of processing Interests always based on the first-in-first-serve rule, NDN routers need some basis to treat the incoming Interests differently.
-Thus, the primary task in bringing intelligence to the Interest flooding attack mitigation is to proactively distinguish between legitimate and malicious Interests.
+%While the Interest limit is the key building block to suppress mechanisms of the Interest flooding attack, legitimate Interests need to be somehow prioritized and malicious Interests need to be somehow penalized in order to completely suppress the attack.
+%That is, instead of processing Interests always based on the first-in-first-serve rule, NDN routers need some basis to treat the incoming Interests differently.
+%Thus, the primary task in bringing intelligence to the Interest flooding attack mitigation is to proactively distinguish between legitimate and malicious Interests.
 
-To achieve such an Interest differentiation we can leverage another unique feature of the stateful forwarding in NDN---namely, the guaranteed symmetric flow of Interest and Data packets.
-In other words, NDN guarantees that a forwarded Interest would always results in receiving a corresponding Data, provided such Data exists and Interest/Data packets were not lost on the way.
-Therefore, all Interests that result in Data return can be considered legitimate, while the ones that always timeout should be deemed as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest flooding}).
-Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
+In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of the stateful forwarding in NDN---namely, the guaranteed symmetric flow of Interest and Data packets.
+Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guarateed to see if an Interest it forwarded resulted in a matching Data packet.
+The only exception being if Interest/Data packets were lost along the way due to congestion.
+Therefore, intermediate routers can classify all Interests that result in matching Data as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest flooding}).}
+%Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
 
-Unfortunately, the timeout-based differentiation is reactive by nature: one cannot know in advance that an Interest would timeout or bring Data back.
-What we can do proactively is to keep an up-to-date statistics of Interests satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistics to project outcomes for new Interests.
-For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface can be enough to estimate whether an Interest received from a neighbor will bring Data or time out.
-Statistics can also be kept at more granular levels (e.g., per outgoing interface, per prefix, etc.), which can further improve the estimation quality.
+This timeout-based differentiation method is reactive by nature: one cannot know in advance that an Interest would timeout or bring Data back.
+However, routers can proactively keep an up-to-date statistics of Interests satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest must be forwarded or dropped.
+For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighboring interface will result in matching Data or a timeout.
+Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
+that can further improve the estimates.
+A router's goal is to penalize malicious Interests as soon as possible -- negative statistics should build up fast, while positive statistics should not deteriorate too quickly.
+Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
+{\it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong here.}
 
-The devil is always in the details.
-From the one hand, such statistics needs to start penalizing adversaries as soon as possible (i.e., negative stats should build up fast).
-On the other hand, the positive statistics should not deteriorate too fast (i.e., positive stats should be relatively long-term).
-Our preliminary experiments showed that the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window, provides a good balance between the two contradictory requirements.
+%The devil is always in the details.
+%From the one hand, such statistics needs to start penalizing adversaries as soon as possible (i.e., negative stats should build up fast).
+%On the other hand, the positive statistics should not deteriorate too fast (i.e., positive stats should be relatively long-term).
+%Our preliminary experiments showed that the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window, provides a good balance between the two contradictory requirements.
 

### 2012-12-18 04a-design-naive.tex
updates to sec 4a
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@890 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-18 04a-design-naive.tex
@@
 Our mitigation strategies feature varying degrees of implementation complexity and effectiveness -- the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
-We start by describing two naive strategies and use the insights and lessons learnt from the evaluation of these techniques to inform and design more effective mitigation techniques that work well in a variety of attack scenarios.
+We start by describing our simple strategies and use the insights and lessons learnt from the deployment of these techniques to inform and design more effective mitigation techniques that work well in a variety of attack scenarios.
 
@@
 
-Our mitigation strategies are based on two fundamental principles of NDN architecture - flow balance between Interest and Data packets, and Data packets traversing the reverse path taken by Interest packets.
-The flow balance in NDN refers to the fact that one Interest packet can be satisfied with at most one Data packet.
-This principle allows intermediate routers that forward the Interest packets to control the number of outstanding Interests packets in the network.
-The fact that each Data packet takes the reverse path of the corresponding Interest packet allows intermediate routers to match a received Data packet to the corresponding Interest packet and thus determine which Interest packets were satisfied.
-As we describe in the rest of this section,  NDN routers can exploit this information to make informed decisions on which Interest packets to forward, how many Interest packets to forward, and thus effectively defend against DDoS attacks.
+%The fact that each Data packet takes the reverse path of the corresponding Interest packet allows intermediate routers to match a received Data packet to the corresponding Interest packet and %thus determine which Interest packets were satisfied.
+As we describe in the rest of this section,  NDN routers can exploit this information to make informed decisions on which Interest packets to %forward, how many Interest packets to forward, and thus effectively defend against DDoS attacks.
 
@@
 
-An obvious and simple strategy that can be used to mitigate the Interest flooding attack is for a router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface.
+An obvious and naive solution to defend against Interest flooding attacks is to restrict the number of Interests that are forwarded in the network. To this end, we exploit a 
+ fundamental principle of NDN architecture - flow balance between Interest and Data packets.
+The flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
+This principle allows intermediate routers that forward the Interest packets to control the number of outstanding Interests in the network.
+One simple and easy method to implement this strategy is for a NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface.
 This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet switched networks.
-Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of data requested that can fully utilize the downstream link (calculated from the number of pending Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
+Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of Data requested that can fully utilize the downstream link (estimated from the number of Interests it forwarded) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
 Ideally, the number of tokens {\it i.e.} the \emph{Pending Interests Limit} for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
@@
 
-An obvious failure of the above {\it Token Bucket} algorithm is that it can be used as an effective mechanism to carry out denial of service attacks.
+This {\it Token Bucket} approach might be exceptionally retrictive in forwarding Interests -- not all Interests will result in a Data packet -- thus underutilizing the network.
+However, the biggest drawback of the algorithm is that it can be used as an effective mechanism to carry out denial of service attacks.
 If a router has utilized all its {\it tokens} to forward {\it bad} Interests on an out Interface, it can no longer forward incoming Interests from legitimate users on that out inteface till the pending {\it bad} Interests start to expire.
 One way to get around this issue is to impose a per-interface limit so that {\it bad} Interests are not allowed to entirely consume the limits of a specific interface.
-We describe this technique in greater detail in the next subsection.
+We describe this technique in greater detail below.
 
@@
 \subsubsection{\textbf{Physical limits with per-interface fairness}}
+{\it Priya: Rename this algo to Token Bucket with per-interface fairness or something similar}
 \label{sec:queuing}
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+The key drawback of the {\it Token Bucket} algorithm as well as its variation that ensures fair queuing on a per-interface basis is that these algorithms still admit Interests from malicious users.
+A sizeable percentage of these malicious Interests are forwarded all the way to content producers, thereby utilizing scarce network resources and reducing resources available to serve legitimate users.
+These algorithms attempt to ensure that each interface does not forward more than its fair share of Interests, but in doing so, they drop both legitimate Interests as well as malicious Interests.
+For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and effectively drop only malicious requests for content.
+`Good' Interests from legitimate users must be admited and forwarded appropriately.
+The key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
+
+Unlike in today's host-based Internet architecture where DDoS mitigation techniques that rely on blacklisting of dark IP prefixes or whitelisting of good IP prefixes are still reasonably effective, in NDN one cannot easily distinguish a `good' prefix from a `bad' one.
+Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets -- thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
+Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone -- DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.

### 2012-12-18 algos/fair-queueing.tex
updates to sec 4a
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@890 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-To address the lack of fairness associated with the naive {\it Token Bucket} algorithm, we can modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring interfaces.
-For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  be fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
+To address the lack of fairness associated with the naive {\it Token Bucket} algorithm, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring interfaces.
+For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
 %Due to the expected small volume of Interests, we cannot merely rely on network buffers to perform statistical multiplexing of Interests, as they would almost never be %buffered.
@@
 
-We present a more formalized description of the Physical limits algorithms with per-interface fairness in Pseudocode~\ref{alg:queuing}.
+We present a more formalized description of this algorithm in Pseudocode~\ref{alg:queuing}.
 We can control the amount of physical resources utilized at a router (such as memory and computation power) by setting appropriate queue sizes.
@@
 As we show in Section~\ref{sec:evaluation}, fair queueing provides partial relief from the Interest flooding attack, allowing legitimate users to successfully fetch Data for 15--20\% of the expressed Interests (compared to 0-10\% without fair queueing).
-While these might be reasonable techniques for preventing congestion in the network and for ensuring fairness, they are far from being effective in protecting legitimate users from malicious attackers.
+While this algorithm might be reasonable for ensuring fairness in an NDN network, it is completely ineffective in protecting legitimate users from malicious attackers.
 Malicious attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of Interests.

### 2012-12-19 04b-design-intelligent.tex
More edits to chapters 4a, 4b
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@891 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of the stateful forwarding in NDN---namely, the guaranteed symmetric flow of Interest and Data packets.
+In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture --- guaranteed symmetric flow of Interest and Data packets.
 Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guarateed to see if an Interest it forwarded resulted in a matching Data packet.
-The only exception being if Interest/Data packets were lost along the way due to congestion.
+The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
 Therefore, intermediate routers can classify all Interests that result in matching Data as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest flooding}).}
@@
 
-This timeout-based differentiation method is reactive by nature: one cannot know in advance that an Interest would timeout or bring Data back.
-However, routers can proactively keep an up-to-date statistics of Interests satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest must be forwarded or dropped.
-For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighboring interface will result in matching Data or a timeout.
+This timeout-based differentiation method is reactive by nature: one cannot determine in advance if an Interest will result in a timeout or in Data being retrieved.
+However, routers can proactively maintain up-to-date statistics of Interests satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest must be forwarded or dropped.
+For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighboring interface will result in a Data packet or a timeout.
 Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
 that can further improve the estimates.
-A router's goal is to penalize malicious Interests as soon as possible -- negative statistics should build up fast, while positive statistics should not deteriorate too quickly.
+A router's goal is to penalize malicious Interests as soon as possible -- negative statistics should be allowed to build up fast, while positive statistics should not be allowed to deteriorate too quickly.
 Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.

### 2012-12-19 algos/dynamic-limits.tex
Most of the evaluation section is semi-done.  I suspect I put too much details and discussion in the evalutions... Not sure
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@871 df1a90cd-247b-4364-bdaf-287a704eb499
More edits to chapters 4a, 4b
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@891 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Essentially, the probabilistic Interest accept algorithm divides the available forwarding tokens between interfaces proportionally to their satisfaction ratios.
-Exactly the same effect can be achieved without using probabilistic methods, simply by enabling and enforcing additional Interest limits for each incoming interface, where the values of the limits directly depend on the interface satisfaction ratios.
+Essentially, the probabilistic Interest accept algorithm divides the available forwarding tokens between interfaces in proportion to their Interest satisfaction ratios.
+Given the drawbacks of this algorithm, the same effect can be achieved without using probabilistic methods.
+An alternate strategy is to enable and enforce additional Interest limits for each incoming interface, where the values of the limits directly depend on the interface satisfaction ratios.
 Additionally, routers may need to explicitly announce these limits to their downstream neighbors, ensuring that any forwarded Interest from the downstream is actually getting through, resulting in genuine Interest satisfaction statistics.
@@
   \centering
-  \includegraphics[width=\columnwidth]{dynamic-limits}
+  \includegraphics[scale=0.3]{dynamic-limits}
   \caption{Dynamic limits example: routers explicitly tell neighbors how many Interest can be for sure delivered to the Data producer}

### 2012-12-19 algos/probabilistic.tex
More edits to chapters 4a, 4b
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@891 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
-A straightforward way to achieve this enforcement is to consider Interest satisfaction rate as a direct probability to accept (forward) or reject an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
+In addition to maintaining statistics on Interest satisfaction ratios, the next challenge is in using these statistics to penalize malicious Interests.
+A straightforward method to achieve this enforcement is to consider Interest satisfaction rate as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
+%Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
 
@@
 
-Parameter $\theta$ on line 5 of the Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not applied when there a very small volume of Interests coming from the particular interface.
-That is, while we want to deny service to the attackers, we also want give an opportunity for the users who do not abuse the network to regain their share of resources after temporary Data delivery failures.
+Parameter $\theta$ on line 5 of the Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
+This step is critical -- while we want to drop Interests from attackers, we also want to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures due to  congestion.
 
-A main drawback of the probabilistic Interests accept method is the fact that each router on the path make an independent decision on what to do with the Interest.
-As a result of such independent decisions, the probability of legitimate Interests not to be dropped decreases quickly as the number of hops between the requester and Data grows, worsening the satisfaction statistics and resulting in further drops.
+A drawback of the probabilistic Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop the Interest. 
+As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
 In example on Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
-At the same time, the router B sees the satisfaction rate for its \texttt{eth0} interface at 30\% level.
-Next time a legitimate Interests arrives on the router A, it has 50\% chance to be forwarded further, and if forwarded, it has only $50\% \times 30\% = 15\%$ chance to be actually send towards the Data producer.
-To prevent such overreacting, we need to enable some form of a gossiping protocol between neighboring NDN routers, in order to explicitly specify amount of Interests that each router is willing to forward.
+At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
+Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the Data producer.
+With each increasing hop in the network, the probability of being forwarded to the next hop decreases significantly.
+One way to prevent this overreaction and unfair penalization is to ensure that the decision taken at each router on whether to forward or drop the Interest is not independent of the decision taken at preceding routers.
+An explicit notification such as a gossip protocol between neighboring NDN routers that specifies the volume of Interests each router is willing to forward will likely address this issue.
 

### 2013-01-10 03-interest-flooding.tex
added few comments before running out of battery..
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@879 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@892 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-\section{Interest Flooding in NDN}
+\section{Interest Flooding Attacks in NDN}
 \label{sec:interest flooding}
@@
 
-% \paragraph{Classification}
+\paragraph{What is it?}
 
-Interest flooding attack belongs to a class of network-level flooding attacks, where an attacker or a set of distributed attackers inject excessive amounts of Interests in order to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-Service for legitimate users is disrupted when the network fails to satisfy Interests either because the Interests did not get through to the data producer or nearby cache, or the Data were lost on the way back to the requester (e.g., because of congested links).
+Unlike data packets, interest packets in NDN are unsolicited, consume state in intervening routers and are routed based on content name prefixes in the network.
+Such properties makes interest packets an effective tool in launching DoS attacks in NDN.
+An attacker or a set of distributed attackers can inject excessive amounts of Interests to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
+We coin in the term \emph{Interest flooding} to refer to these network-level flooding attacks.
 
@@
 
-\paragraph{Mechanism}
+\paragraph{How it works?}
 
-The Interest flooding attack has two main mechanisms to affect service quality in NDN network: it \emph{creates network congestion} and \emph{exhaust resources on routers}.
+The Interest flooding attacks can distrupt service quality in NDN network in two ways: it \emph{creates network congestion} and \emph{exhaust resources on routers}.
 
-Like any other packets in the network, malicious Interests consume a portion network capacity.
-Thus, a large amount of malicious Interests can lead to network congestion and drop of the legitimate Interests and Data packets.
-%  (in case of bidirectional communication)
-% The resource exhaustion effect can be much more ???.
-% and more critical is the effect on memory and CPU resources of NDN routers.
+Like any packet in a network, Interest packets consume a portion of network capacity.
+Thus, Interest Flooding attacks might cause congestion and the drop of legitimate packets in the network.
+Although congestions might occur anywhere in the network, a coordinated DDoS attack would likely target one specific namespace to concentrate attack traffic in certain segments of the network.
+That is feasible for an attacker as the name prefixes loosely correspond to a network location or sets of network locations in network.
 
-As NDN routers maintain per-packet states for each forwarded Interest (entry in Pending Interests Table), an excessive volume of malicious Interests leads to creating an excessive number of PIT entries and exhaustion of routers' resources.
-When a router has no memory to create a PIT entry for an incoming Interest, it drops this Interest.
+As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its Pending Interests Table), an excessive volume of malicious Interests can lead to exhaustion of routers' memory.
+When a router has insufficient memory to create a new PIT entry, it has to drop new incoming Interests.
 % there is no point in forwarding the Interest further.
 % Otherwise, if Data comes back, it would be considered unsolicited and dropped anyways.
-Therefore, the routers' memory exhaustion effect may disrupt service for legitimate users even without causing network congestion, if the router has limited memory resources.
+Therefore, the service for legitimate users can be disrupted due to limited memory resources in routers without saturating communication links to their limits.
 
-\paragraph{Target}
+%\paragraph{Target}
 
-Because communication in NDN is content-centric, it is impossible for an adversary to target specific routers or end-hosts, as neither of them have a global network identity.
-However, an adversary can target a specific namespace, which in NDN network can loosely correspond to a network location or sets of network locations.
+Because communication in NDN is content-centric, it is unlikely for an adversary to be able to target specific routers or end-hosts, as neither of them is required to have a globally routable network identity/address.
+However, an adversary can target a specific namespace.
 For example on Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace and is single-homed to router B, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.
-It should be noted that if connectivity in NDN network is rich (users are multi-homing to many providers, many interconnections between providers), targeting of specific locations is largely unfeasible, as stateful Interest forwarding strategy in NDN can fully and effectively utilize multiple available paths to destination~\cite{adaptive-forwarding}.
+In the case of multi-homed users with rich connectivity through multiple providers, NDN would likely to cope better with DDoS attacks due its native multi-path and adaptive forwarding~\cite{adaptive-forwarding}.
 
@@
 
-\paragraph{Effectiveness}
+%\paragraph{Effectiveness}
 
-To efficiently implement the Interest flooding attack, an adversary needs to make sure (1) that the expressed Interests are getting as close to the Data producer as possible, and (2) that the corresponding PIT entries (state) are kept on NDN routers for as long as possible.
-In order to achieve effectively the first requirement, the malicious Interests should avoid collapsing and cache hits.
-To keep PIT entries for a prolonged period of time, the malicious Interests should not bring any data.%
-\footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.
+To efficiently implement an Interest flooding attack targeting a namespace (e.g., /newtorktimes/), an adversary needs to make sure that (1) the expressed Interests are getting as close to the Data producer as possible, and (2) the corresponding PIT entries (state) are kept on NDN routers for as long as possible \footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.
 For example, and we assume this in the rest of the paper, the maximum time for which any Interest is admitted is one second.}
 
-In other words, to maximize effect of the attack, each malicious Interest generated by an individual attack bot should have a unique name and should not correspond to any existing data (\emph{unique junk Interests}).
+In order to achieve both requirements most effectively, malicious Interests should avoid collapsing (i.e, request a content that is different than existing PIT entries in the network) and cache hits (i.e., request unpopular or non-existing content).
+In other words, to maximize effect of an DDoS attack, each malicious Interest generated by an individual attack bot should request a non-existing content with a unique name (\emph{unique junk Interests}).
+In this paper, we exclusively focus on this particular attack strategy as it maximizes the damaging effect of each malicious interest in the network and the same or similar countermeasures apply to all less-effective strains of the attack.
 
-\paragraph{Assumptions}
+In the rest of this paper, we use the general term \emph{interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only (i.e, we assume the routers in the network and the computers in the victim domain are not compromised).
+
+%\paragraph{Assumptions} 
+%E: These are assumptions for the simulations on hand and particulary to test for the worst case scenario in many aspects.
+They are not the paper's assumption and in fact the paper first should be more general on describing all possibilities.
+Then it should explain the assumptions for the simulations and discuss why they make sense and do NOT favor positive results in some way.
+
 % - assumptions about attacker position
@@
 
-In this paper we are making the following assumptions about the Interest flooding attack:
-\begin{itemize}
-\item only client nodes can be compromised and become attack bots;
-\item there are no colluding attackers inside the Data producer's network;
-\item the attack is carried only using unique junk Interests; and
-\item there is only one Data producer for the attacked prefix.
-\end{itemize}
+%In this paper we are making the following assumptions about the Interest flooding attack:
+%\begin{itemize}
+%\item only client nodes can be compromised and become attack bots;
+%\item there are no colluding attackers inside the Data producer's network;
+%\item the attack is carried only using unique junk Interests; and
+%\item there is only one Data producer for the attacked prefix.
+%\end{itemize}
 
-We also assume that NDN forwarding strategy uses only single-path Interest forwarding, always choosing the best-metric route advertised by the routing protocol.
-This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
+%We also assume that NDN forwarding strategy uses only single-path Interest forwarding, always choosing the best-metric route advertised by the routing protocol.
+%This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
 
-In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
+%In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
 

### 2013-01-11 03-interest-flooding.tex
Algorithm renaming, pseudocodes, consistency in "Interest" word usage, and some minor typos and grammars
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@894 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Unlike data packets, interest packets in NDN are unsolicited, consume state in intervening routers and are routed based on content name prefixes in the network.
-Such properties makes interest packets an effective tool in launching DoS attacks in NDN.
+Unlike data packets, Interest packets in NDN are unsolicited, consume state in intervening routers and are routed based on content name prefixes in the network.
+Such properties makes Interest packets an effective tool in launching DoS attacks in NDN.
 An attacker or a set of distributed attackers can inject excessive amounts of Interests to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
@@
 
-To efficiently implement an Interest flooding attack targeting a namespace (e.g., /newtorktimes/), an adversary needs to make sure that (1) the expressed Interests are getting as close to the Data producer as possible, and (2) the corresponding PIT entries (state) are kept on NDN routers for as long as possible \footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.
+To efficiently implement an Interest flooding attack targeting a namespace (e.g., /newtorktimes/), an adversary needs to make sure that (1) the expressed Interests are getting as close to the Data producer as possible, and (2) the corresponding PIT entries (state) are kept on NDN routers for as long as possible.\footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.
 For example, and we assume this in the rest of the paper, the maximum time for which any Interest is admitted is one second.}
@@
 In other words, to maximize effect of an DDoS attack, each malicious Interest generated by an individual attack bot should request a non-existing content with a unique name (\emph{unique junk Interests}).
-In this paper, we exclusively focus on this particular attack strategy as it maximizes the damaging effect of each malicious interest in the network and the same or similar countermeasures apply to all less-effective strains of the attack.
+In this paper, we exclusively focus on this particular attack strategy as it maximizes the damaging effect of each malicious Interest in the network and the same or similar countermeasures apply to all less-effective strains of the attack.
 
-In the rest of this paper, we use the general term \emph{interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only (i.e, we assume the routers in the network and the computers in the victim domain are not compromised).
+In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only (i.e, we assume the routers in the network and the computers in the victim domain are not compromised).
 

### 2013-01-11 04a-design-naive.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@893 df1a90cd-247b-4364-bdaf-287a704eb499
Algorithm renaming, pseudocodes, consistency in "Interest" word usage, and some minor typos and grammars
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@894 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 In this section we present several algorithms to mitigate Interest flooding attacks in NDN.
-Our mitigation strategies feature varying degrees of implementation complexity and effectiveness -- the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
-We start by describing our simple strategies and use the insights and lessons learnt from the deployment of these techniques to inform and design more effective mitigation techniques that work well in a variety of attack scenarios.
+Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
+We start by describing our simple strategies and use the insights and lessons learnt from the deployment of these techniques to inform and design more effective mitigation techniques that can work well in a variety of attack scenarios.
 
@@
 
-An obvious and naive solution to defend against Interest flooding attacks is to restrict the number of Interests that are forwarded in the network. To this end, we exploit a 
- fundamental principle of NDN architecture - flow balance between Interest and Data packets.
+An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests that are forwarded in the network. To this end, we exploit a 
+ fundamental principle of NDN architecture---flow balance between Interest and Data packets.
 The flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
@@
 
-\subsubsection{\textbf{Physical limits with per-interface fairness}}
-{\it Priya: Rename this algo to Token Bucket with per-interface fairness or something similar}
+\subsubsection{\textbf{Token bucket with per interface fairness}}
 \label{sec:queuing}
@@
 Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone -- DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2013-01-11 04b-design-intelligent.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@893 df1a90cd-247b-4364-bdaf-287a704eb499
Algorithm renaming, pseudocodes, consistency in "Interest" word usage, and some minor typos and grammars
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@894 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture --- guaranteed symmetric flow of Interest and Data packets.
+In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets.
 Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guarateed to see if an Interest it forwarded resulted in a matching Data packet.
@@
 
-This timeout-based differentiation method is reactive by nature: one cannot determine in advance if an Interest will result in a timeout or in Data being retrieved.
+This timeout-based differentiation method is reactive by nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
 However, routers can proactively maintain up-to-date statistics of Interests satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest must be forwarded or dropped.
-For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighboring interface will result in a Data packet or a timeout.
+For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout.
 Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
 that can further improve the estimates.
-A router's goal is to penalize malicious Interests as soon as possible -- negative statistics should be allowed to build up fast, while positive statistics should not be allowed to deteriorate too quickly.
+A router's goal is to penalize malicious Interests as soon as possible---negative statistics should be allowed to build up fast, while positive statistics should not be allowed to deteriorate too quickly.
 Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
-{\it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong here.}
+{\color{red} \it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong here.}
 
@@
 
-\subsubsection{\textbf{Probabilistic Interest accept}}
+\subsubsection{\textbf{Satisfaction-based Interest acceptance}}
 \label{sec:probabilistic}
@@
 
-\subsubsection{\textbf{Dynamic limits}}
+\subsubsection{\textbf{Satisfaction-based pushback}}
 \label{sec:dynamic limits}

### 2013-01-11 05-evaluation.tex
Most of the evaluation section is semi-done.  I suspect I put too much details and discussion in the evalutions... Not sure
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@871 df1a90cd-247b-4364-bdaf-287a704eb499
Algorithm renaming, pseudocodes, consistency in "Interest" word usage, and some minor typos and grammars
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@894 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 % Metrics
+% not sure if i already explained that. our essential qualitative metric is .  
+% To quantify the effectiveness of the mitigation mechanism this  metric we use satisfaction percentages of user Interests.
 Quality of the attack mitigation methods directly corresponds to the quality of service for the legitimate users during an ongoing attack, which in NDN network can be quantified through percentage of satisfied Interest.
@@
 % Alex: not sure how to argue about the traffic pattern
-Although this pattern is not truly realistic, it gives us a good statistical mix of traffic from all network users without excessive network buffering.
+Although this pattern may seem not truly realistic, it approximates a good statistical mix of traffic from all network users without excessive network buffering.
+
 In addition to that, in each run of the simulation we ensure that all Interests expressed by the legitimate users during a no-attack period are satisfied.
-For simplicity and without losing any generality, we also equalized the average rates with which the legitimate users express Interests.
+For simplicity, we also equalized the average rates with which the legitimate users express Interests.
+At the same time, the attackers are sending junk Interests as much as they can get through (remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
 

### 2013-01-11 algos/dynamic-limits.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@893 df1a90cd-247b-4364-bdaf-287a704eb499
Algorithm renaming, pseudocodes, consistency in "Interest" word usage, and some minor typos and grammars
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@894 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Essentially, the probabilistic Interest accept algorithm divides the available forwarding tokens between interfaces in proportion to their Interest satisfaction ratios.
-Given the drawbacks of this algorithm, the same effect can be achieved without using probabilistic methods.
-An alternate strategy is to enable and enforce additional Interest limits for each incoming interface, where the values of the limits directly depend on the interface satisfaction ratios.
-Additionally, routers may need to explicitly announce these limits to their downstream neighbors, ensuring that any forwarded Interest from the downstream is actually getting through, resulting in genuine Interest satisfaction statistics.
+Essentially, the satisfaction-based Interest acceptance algorithm divides the available forwarding tokens between interfaces in proportion to their Interest satisfaction ratios.
+% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
+An alternate strategy, which does not have described drawbacks, is to enable and enforce explicit Interest limits for each incoming interface, where the values of the limits directly depend on the interface satisfaction ratios.
+Routers need to announce these limits to their downstream neighbors, ensuring that any forwarded Interest from the downstream is actually getting through, resulting in genuine Interest satisfaction statistics.
 
-The formal definition of the dynamic limits algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm would work in our toy example on Fig.~\ref{fig:flooding example}.
-Assuming the initial (physical) limit $L=10$ and the current satisfaction ratios on the the router A are 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and on the router B the ratio is 30\%  \texttt{eth0}, each node would set and announce the following  incoming interface limits $L'$:
+The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm would work in our toy example on Fig.~\ref{fig:flooding example}.
+Assuming the initial token bucket limit $L=10$ and the current satisfaction ratios on the the router A are 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and on the router B the ratio is 30\% for \texttt{eth0}, each node would set and announce the following  incoming interface limits $L'$:
 \begin{enumerate}
@@
   \includegraphics[scale=0.3]{dynamic-limits}
-  \caption{Dynamic limits example: routers explicitly tell neighbors how many Interest can be for sure delivered to the Data producer}
+  \caption{Satisfaction-based pushback example: routers explicitly tell neighbors how many Interest can be for sure delivered to the Data producer}
   \label{fig:dynamic limits example}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+{ 
 \begin{algorithm}[h]
-\caption{Dynamic limits}
+\footnotesize
+\caption{\small Satisfaction-based pushback}
 \label{alg:dynamic limits}
 \begin{algorithmic}[1]
-\State{} \Comment{Same initialization, InData and Timeout functions as in Physical Limits algorithm}
-\vspace{0.2cm}
+% \State{}\Comment{Same initialization, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+\vspace{0.1cm}
 \State{$\forall f \in \mathrm{interfaces} : L'_{f} \leftarrow L_{f}$} \Comment{Per-incoming interface Interest limit}
 
-\vspace{0.2cm}
+\vspace{0.1cm}
 
 \State{} \Comment{\textit{Announcement from the neighbor}}
-\Function{InLimits}{InInterface $if$, Limit $L'$}
-    \State $L_{if} \leftarrow L'$
+\Function{InLimits}{InInterface $in$, Limit $L'$}
+    \State $L_{in} \leftarrow L'$
 \EndFunction
 
-\vspace{0.2cm}
+\vspace{0.1cm}
 
 \Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
-\For{\textbf{each} outgoing interface $of$}
+\For{\textbf{each} outgoing interface $out$}
 
-   \For{\textbf{each} incoming interface $if$}
-        \State $L'_{if}= {L_{of}} \times (1 - U_{if}/F_{if})$
-        \State AnnounceLimit($if$, $L'_{if}$)
+   \For{\textbf{each} incoming interface $in$}
+        \State $L'_{in}= {L_{out}} \times (1 - U_{in}/F_{in})$
+        \State AnnounceLimit($in$, $L'_{in}$)
    \EndFor
@@
 
-The zero limit for the adversary's link means that the router A is temporarily not willing to accept any interests from this link, not until the statistics decays to the appropriate level (recall Fig.~\ref{fig:ratio example}).
-At the next iterations of the dynamic limits algorithm, the legitimate user will be able to gradually improve the statistics on both the router A and router B (all his Interests will get through and will return Data), eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and the router A.
+The zero limit for the adversary's link means that the router A is temporarily not willing to accept any Interests from this link, not until the statistics decays to the appropriate level (recall Fig.~\ref{fig:ratio example}).
+At the next iterations of the satisfaction-based pushback algorithm, the legitimate user will be able to gradually improve the statistics on both the router A and router B (all his Interests will get through and will return Data), eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and the router A.
 
-It should be noted that while in the description of the dynamic limits algorithm we used notions of ``outgoing'' and ``incoming'' interfaces, in the real system all interfaces can be both incoming and outgoing.
-Thus, it may not be entirely clear which outgoing limit $L_{of}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{if}$.
+It should be noted that while in the description of the satisfaction-based pushback algorithm we used notions of ``outgoing'' and ``incoming'' interfaces, in the real system all interfaces can be both incoming and outgoing.
+Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
 To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
-That is, for each FIB entry we set a separate Interest limit for each incoming interface ($L_{if}^{'FIB}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{of}^{FIB}}$.
+That is, for each FIB entry we set a separate Interest limit for each incoming interface ($L_{in}^{'FIB}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{FIB}}$.
 
 % Alex: not sure if this paragraph belongs here
-Essentially, both probabilistic Interest accept and the dynamic limits algorithm are forms of a well-known push-back mechanism~\cite{Pushback}, with several core differences.
+Essentially, both satisfaction-based algorithm are forms of a well-known push-back mechanism~\cite{Pushback}, with several core differences.
 First, we are suppressing (pushing back) unwanted requests for Data, not the actual Data.
@@
 % Alex: I'm not entirely sure about this point... 
-Finally, both intelligent attack mitigation algorithms can be enabled all the time, without degrading network performance when there are no active attack.
+Finally, both intelligent attack mitigation algorithms can be enabled all the time, without degrading network performance when there is no active attack.
 

### 2013-01-11 algos/fair-queueing.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@893 df1a90cd-247b-4364-bdaf-287a704eb499
Algorithm renaming, pseudocodes, consistency in "Interest" word usage, and some minor typos and grammars
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@894 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-To address the lack of fairness associated with the naive {\it Token Bucket} algorithm, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring interfaces.
+To address the lack of fairness associated with the na\"ive {\it Token Bucket} algorithm, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring interfaces.
 For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
@@
 We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
-{\it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
+{\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
 
@@
 \begin{algorithm}[h]
-\caption{Physical limits with per-interface fairness}
+\footnotesize
+\caption{\small Token bucket with per interface fairness}
 \label{alg:queuing}
 \begin{algorithmic}[1]
-\State{} \Comment{Same initialization, InData and Timeout functions as in Physical Limits algorithm}
+\For{\textbf{each} interface \textbf{if}}
+    \State{$L_{if} \leftarrow$ Interest Limit according to (1)}
+    \State{$O_{if} \leftarrow 0$} \Comment{Outstanding Interests on interface \textbf{if}}
+\EndFor
 
-\vspace{0.2cm}
+\vspace{0.1cm}
 
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{if}, OutInterface \textbf{of}}
-    \If{$L_{of} - O_{of} > 0$} \Comment{\textbf{of} is under physical limits}
-        \State $O_{of} \leftarrow O_{of} + 1$  \Comment{``Borrow'' token}
-        \State add \textbf{of} to PIT entry and forward \textbf{i} to \textbf{of}
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
+    \If{$L_{out} - O_{out} > 0$} \Comment{\textbf{out} is under limit cap}
+        \State $O_{out} \leftarrow O_{out} + 1$  \Comment{``borrow'' a token from the bucket}
+        \State add \textbf{out} to PIT entry and forward \textbf{i} to \textbf{out}
     \Else
-        \State Queue $q \leftarrow of$.GetSubQueue($if$)
-        \If{$Size(q) < L_{of}$}
+        \State Queue $q \leftarrow out$.GetSubQueue($in$)
+        \If{$Size(q) < L_{out}$}
            \State $q$.PushInterest($i$)
-           \State add \textbf{of} to PIT entry, and link PIT entry with the queue
+           \State add \textbf{out} to PIT entry, and link PIT entry with the queue
         \Else
@@
 
-\vspace{0.2cm}
-\State{} \Comment{\textit{Whenever $L_{of} - O_{of}$ becomes larger than zero}}
+\vspace{0.1cm}
+
+\State{} \Comment{\textit{Whenever $L_{out} - O_{out}$ becomes larger than zero}}
 \Function{TokenBecomesAvailable}{}
-    \State Queue $q \leftarrow$ $of$.GetRoundRobinSubQueue 
-    \State $i \leftarrow$ $q$.PopInterest
-    \State update PIT entry and Forward($i$, $of$)
+    \State Queue $q \leftarrow$ $out$.GetRoundRobinSubQueue 
+    \State Interest $i \leftarrow$ $q$.PopInterest
+    \State update PIT entry and Forward($i$, $out$)
 \EndFunction
+
+\vspace{0.1cm}
+
+\Function{InData}{Data \textbf{d}}
+   \State lookup PIT entry \textbf{p} for data \textbf{d}
+   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
+        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
+   \EndFor
+\EndFunction
+
+\vspace{0.1cm}
+
+\Function{Timeout}{PIT entry $p$}
+   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
+        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
+   \EndFor
+\EndFunction
+
 \end{algorithmic}
@@
 
-As we show in Section~\ref{sec:evaluation}, fair queueing provides partial relief from the Interest flooding attack, allowing legitimate users to successfully fetch Data for 15--20\% of the expressed Interests (compared to 0-10\% without fair queueing).
+As we show in Section~\ref{sec:evaluation}, fair queueing provides partial relief from the Interest flooding attack, allowing legitimate users to successfully fetch Data for 15--20\% of the expressed Interests (compared to 0--10\% without fair queueing).
 While this algorithm might be reasonable for ensuring fairness in an NDN network, it is completely ineffective in protecting legitimate users from malicious attackers.

### 2013-01-11 algos/probabilistic.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@893 df1a90cd-247b-4364-bdaf-287a704eb499
Algorithm renaming, pseudocodes, consistency in "Interest" word usage, and some minor typos and grammars
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@894 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \begin{algorithm}[h]
-\caption{Probabilistic model}
+\footnotesize
+\caption{\small Satisfaction-based Interest acceptance}
 \label{alg:probabilistic model}
 \begin{algorithmic}[1]
-\State{} \Comment{Same initialization, InData and Timeout functions as in Physical Limits algorithm}
+\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
 
-\vspace{0.2cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{if}, OutInterface \textbf{of}}
+\vspace{0.1cm}
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
 
@@
 
-    \If{$F_{if} > \theta $} \Comment{At least some Interests were forwarded before}
-        \State $s \leftarrow (1 - U_{if} / F_{if})$
+    \If{$F_{in} > \theta $} \Comment{At least some Interests were forwarded before}
+        \State $s \leftarrow (1 - U_{in} / F_{in})$
         \State Drop interest with probability $P(s)$
@@
 
-    \State{forward the Interest, subjecting to physical limits}
+    \State{forward the Interest, subjecting to token bucket limits}
 \EndFunction
@@
 Parameter $\theta$ on line 5 of the Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
-This step is critical -- while we want to drop Interests from attackers, we also want to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures due to  congestion.
+This step is critical---while we want to drop Interests from attackers, we also want to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures due to  congestion.
 
-A drawback of the probabilistic Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop the Interest. 
+A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop the Interest. 
 As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
@@
 An explicit notification such as a gossip protocol between neighboring NDN routers that specifies the volume of Interests each router is willing to forward will likely address this issue.
+{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
 

### 2013-01-11 eval-large-scale.tex
Another variant of discussion section, acknowledging potential problems and handwaving that the problem is not that serious.
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@875 df1a90cd-247b-4364-bdaf-287a704eb499
Updates and renaming
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@895 df1a90cd-247b-4364-bdaf-287a704eb499

@@
   \centering
-  \includegraphics[scale=0.26,angle=90]{7018-r0}
+  \includegraphics[scale=0.15,angle=90]{7018-r0}
   \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
@@
 
-The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that for both physical limits algorithms and dynamic limits algorithm the performance is about the same as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
+The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
 
@@
  \centering
- \includegraphics[scale=1]{topo-7018-gw-15mins-new/7018-r0-good-0-producer-gw}
+ \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
  \caption{Satisfaction ratio dynamics during the attack (30\% attackers)}
@@
 
-At the same time, the probabilistic method completely failed to provide an adequate protection against the Interest flooding attack, and in addition degraded service for the legitimate users after the attack finished.
+At the same time, the satisfaction-based Interest acceptance method completely failed to provide an adequate protection against the Interest flooding attack, and in addition degraded service for the legitimate users after the attack finished.
 The main reason for the failure was already explained in Section~\ref{sec:probabilistic}.
@@
 
-In summary, in all of the simulated topologies, the dynamic limits algorithm largely restricts malicious traffic to even enter the network.
+In summary, in all of the simulated topologies, the satisfaction-based pushback algorithm restricts malicious traffic from even entering the network.
 The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).

### 2013-01-11 eval-small-scale.tex
Updates and renaming
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@895 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
-For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either physical limits, physical limits with per-interface fairness, probabilistic Interest accept, or dynamic limits (Section~\ref{sec:design}).
+For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).
 
@@
   \centering
-  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw}
+  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
   \caption{Satisfaction ratio dynamics during the attack (7 attackers / 9 legitimate)}
@@
 
-\paragraph{\textbf{Physical limits}}
+\paragraph{\textbf{Simple token buckets}}
+
+{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}
 
@@
 
-\paragraph{\textbf{Physical limits with per-interface fair queueing}}
+\paragraph{\textbf{Token bucket with per interface fairness}}
 
@@
 
-\paragraph{\textbf{Probabilistic Interest accept}}
+\paragraph{\textbf{Satisfaction-based Interest acceptance}}
 
@@
 That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
-The observed periodicity of the probabilistic Interest accept curve on Fig.~\ref{fig:small-scale attack progress} is a direct result from ``intelligence'' (Interest satisfaction rate statistics) decaying with time.
+The observed periodicity of the satisfaction-based Interest accept curve on Fig.~\ref{fig:small-scale attack progress} is a direct result from ``intelligence'' (Interest satisfaction rate statistics) decaying with time.
 The 50-second periods approximately correspond to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx20\%$ within 50~seconds.
@@
 
-\paragraph{\textbf{Dynamic limits}}
+\paragraph{\textbf{Satisfaction-based pushback}}
 
-The only potential problem with the dynamic limits algorithm is that it features a sharp dive of the satisfaction ratio curve at the start of the attack.
+The only potential problem with the satisfaction-based pushback algorithm is that it features a sharp dive of the satisfaction ratio curve at the start of the attack.
 That is, until all routers become fully aware of the attack---malicious Interests start to time out---and until explicit Interest limits announcements successfully localize malicious Interests near the attacker, the network for a short period of time (under 10~seconds for all simulation runs) fails to provide 100\% service for the legitimate users.
@@
   \centering
-  \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min}
+  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
   \caption{Average consumer Interest satisfaction ratios (first minute)}
@@
 Physical limits with and without per-interface fairness give perfect attack instrument even for a small number of attackers: just 3 attackers can either completely shut down or halve the service quality for the rest 13 users.
-At the same time, while both intelligent attack mitigation algorithms also show a decline in service quality, this decline is very subtle: when more than 50\% of users are compromised, service degrades less than by 25\% for probabilistic Interest accept method and less than by 10\% in dynamic limits algorithm.
+At the same time, while both intelligent attack mitigation algorithms also show a decline in service quality, this decline is very subtle: when more than 50\% of users are compromised, service degrades less than by 25\% for the satisfaction-based Interest accept method and less than by 10\% in the satisfaction-based pushback algorithm.
 

### 2013-01-11 01-intro.tex
More renaming of algorithms
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@896 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 %% based on trivial small-scale and Internet-like larger-scale topologies.
-The results show a great potential of one of the designed algorithms (dynamic limits, Section~\ref{sec:dynamic limits}), where the attack traffic can be effectively localized near the attacker himself.
+The results show a great potential of one of the designed algorithms (satisfaction-based pushback, Section~\ref{sec:dynamic limits}), where the attack traffic can be effectively localized near the attacker himself.
 \todo{LZ: I did not modify this last paragraph; need to see the rest of the paper first.}

### 2013-01-11 07-discussion.tex
More renaming of algorithms
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@896 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 This is simply because an unprotected network allows clients to pump more packets and does not impose any artificial restrictions on packet forwarding.
-Therefore, unless a mitigation algorithm uses some form of intelligence (e.g., statistics for Interest satisfiability), a smaller scale flooding attack can cause greater damage to the service quality (recall service quality curves for physical limits in small-scale and larger-scale evaluations, Fig.~\ref{fig:small-scale} and Fig.~\ref{fig:large-scale}).
+Therefore, unless a mitigation algorithm uses some form of intelligence (e.g., statistics for Interest satisfiability), a smaller scale flooding attack can cause greater damage to the service quality.
+% (recall service quality curves for physical limits in small-scale and larger-scale evaluations, Fig.~\ref{fig:small-scale} and Fig.~\ref{fig:large-scale}).
 
@@
 Although a complete investigation of this problem deserves a separate study, we anticipate that the problem may not be as severe as it seems.
-First, in a general case, the adversaries would not be aware that the network is or is not protected, e.g., is using the dynamic limits algorithm.
+First, in a general case, the adversaries would not be aware that the network is or is not protected, e.g., is using the satisfaction-based pushback algorithm.
 As a result, adversaries would want to do as much harm as possible, which is to send junk Interests.
@@
 Second, a satisfiable Interests does not cause NDN-specific harm, as they would not linger on routers for extended periods of time, giving opportunities for Interests from the legitimate users to get through and bring Data back.
-Essentially, in the worst case scenario (assuming that dynamic limits are augmented with some form fair queuing), legitimate users and attackers would ``fairly'' share the network.
+Essentially, in the worst case scenario (assuming that satisfaction-based pushback is augmented with some form fair queuing), legitimate users and attackers would ``fairly'' share the network.
 Note that router resource, as well as upstream link capacity overloading is still impossible, as there is always an upper bound of admitted Interets.
@@
 %  and the mitigation algorithm will work as expected: small service quality degradation during first seconds of the attack, followed by practically full recovery from the attack.
-% However, a careful reader may ask a totally legitimate question: what would happen if adversaries know that the network is protected and know that it is using the dynamic limits algorithm?
+% However, a careful reader may ask a totally legitimate question: what would happen if adversaries know that the network is protected and know that it is using the satisfaction-based pushback  algorithm?
 % Would there be an optimal strategy to deny service for the legitimate users?

### 2013-01-11 08-conclusion.tex
More renaming of algorithms
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@896 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
-The most effective of the designed algorithms---dynamic limits---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data pah symmetry and full receiver-based traffic control.
+The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data pah symmetry and full receiver-based traffic control.
 In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Intersets can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.

### 2013-01-11 eval-small-scale.tex
More renaming of algorithms
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@896 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\paragraph{\textbf{Simple token buckets}}
+\paragraph{\textbf{Simple token bucket}}
 
@@
 
-Let us take a deeper look on what is happening with the physical limits algorithm.
-Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as physical limits restricts the number of forwarded Intersets!).
+Let us take a deeper look on what is happening with the simple token bucket algorithm.
+Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as token bucket restricts the number of forwarded Intersets!).
 This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
@@
 The described problem arises from the clocking effect and can be solved in a number different ways.
-Augmenting physical limits algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
+Augmenting token bucket algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
 That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
@@
 The presented results demonstrate the overall, and somewhat obvious, trends for all attack mitigation algorithms: the larger is the attack, the lower service quality is observed by the legitimate users.
-Physical limits with and without per-interface fairness give perfect attack instrument even for a small number of attackers: just 3 attackers can either completely shut down or halve the service quality for the rest 13 users.
+Token bucket algorithm with and without per-interface fairness give perfect attack instrument even for a small number of attackers: just 3 attackers can either completely shut down or halve the service quality for the rest 13 users.
 At the same time, while both intelligent attack mitigation algorithms also show a decline in service quality, this decline is very subtle: when more than 50\% of users are compromised, service degrades less than by 25\% for the satisfaction-based Interest accept method and less than by 10\% in the satisfaction-based pushback algorithm.

### 2013-01-11 03-interest-flooding.tex
Edits to Section III
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@897 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\paragraph{What is it?}
+%\paragraph{What is it?}
 
-Unlike data packets, Interest packets in NDN are unsolicited, consume state in intervening routers and are routed based on content name prefixes in the network.
-Such properties makes Interest packets an effective tool in launching DoS attacks in NDN.
+Unlike Data packets, Interest packets in NDN are unsolicited, consume state in intermediate routers and are routed through the network based on their content name prefix.
+These properties make Interest packets an effective tool in launching DoS and DDoS attacks in NDN.
 An attacker or a set of distributed attackers can inject excessive amounts of Interests to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-We coin in the term \emph{Interest flooding} to refer to these network-level flooding attacks.
+We coin the term \emph{Interest flooding} to refer to these network-level flooding attacks.
 
@@
 
-\paragraph{How it works?}
+%\paragraph{How does it work?}
 
-The Interest flooding attacks can distrupt service quality in NDN network in two ways: it \emph{creates network congestion} and \emph{exhaust resources on routers}.
+Since communication in NDN is content-centric, it is unlikely that an adversary can target specific routers or end-hosts, as neither is required to have a globally routable network identity/address.
+However, an adversary can target a specific namespace.
+For example in Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.
+\footnote {In our example, Data producer is single-homed.
+In the case of multi-homed producers with rich connectivity through multiple providers, NDN would likely to cope better with DDoS attacks due its native multi-path and adaptive forwarding~\cite{adaptive-forwarding}.} These large volume of Interests can distrupt service quality in NDN network in two ways: they \emph{create network congestion} and \emph{exhaust resources on routers}.
 
-Like any packet in a network, Interest packets consume a portion of network capacity.
-Thus, Interest Flooding attacks might cause congestion and the drop of legitimate packets in the network.
-Although congestions might occur anywhere in the network, a coordinated DDoS attack would likely target one specific namespace to concentrate attack traffic in certain segments of the network.
-That is feasible for an attacker as the name prefixes loosely correspond to a network location or sets of network locations in network.
+Similar to packets in traditional networks, Interest packets in NDN consume a portion of network capacity.
+A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
+Although congestion might occur anywhere in the network, a coordinated DDoS attack would likely target one specific namespace to concentrate attack traffic in certain segments of the network, typically closest to the publisher serving that namespace since name prefixes in NDN loosely correspond to a network location or sets of network locations.
 
-As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its Pending Interests Table), an excessive volume of malicious Interests can lead to exhaustion of routers' memory.
-When a router has insufficient memory to create a new PIT entry, it has to drop new incoming Interests.
+As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a routers' memory.
+When a router has insufficient memory to create a new PIT entry, it is forced to drop new incoming Interests, thus disrupting service for legitimate users.
 % there is no point in forwarding the Interest further.
 % Otherwise, if Data comes back, it would be considered unsolicited and dropped anyways.
-Therefore, the service for legitimate users can be disrupted due to limited memory resources in routers without saturating communication links to their limits.
+%Therefore, service for legitimate users can be disrupted due to limited memory resources in routers without saturating communication links to their limits.
 
 %\paragraph{Target}
-
-Because communication in NDN is content-centric, it is unlikely for an adversary to be able to target specific routers or end-hosts, as neither of them is required to have a globally routable network identity/address.
-However, an adversary can target a specific namespace.
-For example on Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace and is single-homed to router B, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.
-In the case of multi-homed users with rich connectivity through multiple providers, NDN would likely to cope better with DDoS attacks due its native multi-path and adaptive forwarding~\cite{adaptive-forwarding}.
 
@@
 
-To efficiently implement an Interest flooding attack targeting a namespace (e.g., /newtorktimes/), an adversary needs to make sure that (1) the expressed Interests are getting as close to the Data producer as possible, and (2) the corresponding PIT entries (state) are kept on NDN routers for as long as possible.\footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.
+To efficiently implement an Interest flooding attack targeting a specific namespace (e.g., /newyorktimes/), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries (state) are stored at intermediate NDN routers for as long as possible.\footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.
 For example, and we assume this in the rest of the paper, the maximum time for which any Interest is admitted is one second.}
+In order to achieve both requirements effectively, malicious Interests should avoid collapsing (i.e, request a content that is different than existing PIT entries in the network) and avoid being served from caches of intermediate routers (i.e., request unpopular or non-existing content).
+In other words, to maximize effect of an DDoS attack, each malicious Interest generated by an individual attacker bot should request a non-existing content with a unique name (\emph{unique junk Interests}).
+In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network.
+Other less effective strains of this attack can be mitigated by applying the same or similar countermeasures.
 
-In order to achieve both requirements most effectively, malicious Interests should avoid collapsing (i.e, request a content that is different than existing PIT entries in the network) and cache hits (i.e., request unpopular or non-existing content).
-In other words, to maximize effect of an DDoS attack, each malicious Interest generated by an individual attack bot should request a non-existing content with a unique name (\emph{unique junk Interests}).
-In this paper, we exclusively focus on this particular attack strategy as it maximizes the damaging effect of each malicious Interest in the network and the same or similar countermeasures apply to all less-effective strains of the attack.
-
-In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only (i.e, we assume the routers in the network and the computers in the victim domain are not compromised).
+In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
 

### 2013-01-11 04a-design-naive.tex
Edits to Section 4a and 4b
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@898 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 This principle allows intermediate routers that forward the Interest packets to control the number of outstanding Interests in the network.
-One simple and easy method to implement this strategy is for a NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface.
+One simple implementation technique  is for a NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface.
 This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet switched networks.
@@
 
-The key drawback of the {\it Token Bucket} algorithm as well as its variation that ensures fair queuing on a per-interface basis is that these algorithms still admit Interests from malicious users.
+The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits Interests from malicious users.
 A sizeable percentage of these malicious Interests are forwarded all the way to content producers, thereby utilizing scarce network resources and reducing resources available to serve legitimate users.
-These algorithms attempt to ensure that each interface does not forward more than its fair share of Interests, but in doing so, they drop both legitimate Interests as well as malicious Interests.
+This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate Interests as well as malicious Interests.
 For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and effectively drop only malicious requests for content.

### 2013-01-11 04b-design-intelligent.tex
Edits to Section 4a and 4b
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@898 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-This timeout-based differentiation method is reactive by nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
-However, routers can proactively maintain up-to-date statistics of Interests satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest must be forwarded or dropped.
+This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
+However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest must be forwarded or dropped.
 For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout.
@@
 that can further improve the estimates.
-A router's goal is to penalize malicious Interests as soon as possible---negative statistics should be allowed to build up fast, while positive statistics should not be allowed to deteriorate too quickly.
-Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
-{\color{red} \it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong here.}
+A router's goal should be to penalize malicious Interests as soon as possible---negative statistics should be allowed to build up fast, while positive statistics should not be allowed to deteriorate too quickly.
+We use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window to achieve the above goal.
+
+%Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
+%{\color{red} \it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong %here.}
 

### 2013-01-11 algos/dynamic-limits.tex
Edits to Section 4a and 4b
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@898 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Essentially, the satisfaction-based Interest acceptance algorithm divides the available forwarding tokens between interfaces in proportion to their Interest satisfaction ratios.
+The previous strategy -- the satisfaction-based Interest acceptance -- divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
 % Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
-An alternate strategy, which does not have described drawbacks, is to enable and enforce explicit Interest limits for each incoming interface, where the values of the limits directly depend on the interface satisfaction ratios.
-Routers need to announce these limits to their downstream neighbors, ensuring that any forwarded Interest from the downstream is actually getting through, resulting in genuine Interest satisfaction statistics.
+An alternate strategy, which does not have the described drawbacks, is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
+Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.
 
-The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm would work in our toy example on Fig.~\ref{fig:flooding example}.
-Assuming the initial token bucket limit $L=10$ and the current satisfaction ratios on the the router A are 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and on the router B the ratio is 30\% for \texttt{eth0}, each node would set and announce the following  incoming interface limits $L'$:
+The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm would work in our example in Fig.~\ref{fig:flooding example}.
+Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node would set and announce the following  incoming interface limit $L'$:
 \begin{enumerate}
-\item the router B would set and announce the incoming interface limit $L'=3$;
-\item the router A, after receiving announcement from B would readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
-\item legitimate user and adversary may either obey or ignore the announced limit, which will be in any case enforced by the router A.
+\item router B would set and announce the incoming interface limit $L'=3$;
+\item router A, after receiving announcement from B would readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
+\item both legitimate users and adversaries may either obey or ignore the announced limit, which will be in any case enforced by router A.
 \end{enumerate}
@@
   \includegraphics[scale=0.3]{dynamic-limits}
-  \caption{Satisfaction-based pushback example: routers explicitly tell neighbors how many Interest can be for sure delivered to the Data producer}
+  \caption{Satisfaction-based pushback example: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer}
   \label{fig:dynamic limits example}
@@
 
-The zero limit for the adversary's link means that the router A is temporarily not willing to accept any Interests from this link, not until the statistics decays to the appropriate level (recall Fig.~\ref{fig:ratio example}).
-At the next iterations of the satisfaction-based pushback algorithm, the legitimate user will be able to gradually improve the statistics on both the router A and router B (all his Interests will get through and will return Data), eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and the router A.
+The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to the appropriate level (recall Fig.~\ref{fig:ratio example}).
+At the next iteration of the satisfaction-based pushback algorithm, the legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and will return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
 
-It should be noted that while in the description of the satisfaction-based pushback algorithm we used notions of ``outgoing'' and ``incoming'' interfaces, in the real system all interfaces can be both incoming and outgoing.
+We note that while in the description of the satisfaction-based pushback algorithm we explicitly used ``outgoing'' and ``incoming'' interfaces,  all interfaces can be both incoming and outgoing.
 Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
@@
 % Alex: not sure if this paragraph belongs here
-Essentially, both satisfaction-based algorithm are forms of a well-known push-back mechanism~\cite{Pushback}, with several core differences.
-First, we are suppressing (pushing back) unwanted requests for Data, not the actual Data.
-Second, differentiating between good and bad Interests is based on the traffic symmetry property of NDN.
+Essentially, both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, with several core differences.
+First, we are suppressing (pushing back) unwanted requests for Data, not actual Data itself.
+Second, differentiating between good and bad Interests is based on the traffic symmetry principle of NDN.
 % Alex: I'm not entirely sure about this point... 
-Finally, both intelligent attack mitigation algorithms can be enabled all the time, without degrading network performance when there is no active attack.
+Finally, both intelligent attack mitigation algorithms can be deployed at all times without degrading network performance even when there are no active attackers.
 

### 2013-01-11 algos/fair-queueing.tex
Edits to Section 4a and 4b
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@898 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded (see Fig.~\ref{fig:queueing}).
-To support fair queuing, we implement hierarchical queues for each interface as shown in Fig.~\ref{fig:queueing})\footnote{This mechanism is essentially class based queuing, with classes for each outgoing/incoming interface.} As an alternative to hierarchical queues, one can also use an approach based on virtual time.
-For details, please see ~\cite{zhang1990virtual}.
+To support fair queuing, we implement hierarchical queues for each interface as shown in Fig.~\ref{fig:queueing})\footnote{This mechanism is essentially class based queuing, with classes for each outgoing/incoming interface.}
+%As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
 We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
@@
 
-We present a more formalized description of this algorithm in Pseudocode~\ref{alg:queuing}.
+We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}.
 We can control the amount of physical resources utilized at a router (such as memory and computation power) by setting appropriate queue sizes.
@@
 
-As we show in Section~\ref{sec:evaluation}, fair queueing provides partial relief from the Interest flooding attack, allowing legitimate users to successfully fetch Data for 15--20\% of the expressed Interests (compared to 0--10\% without fair queueing).
-While this algorithm might be reasonable for ensuring fairness in an NDN network, it is completely ineffective in protecting legitimate users from malicious attackers.
+As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
+While this algorithm might be reasonable for ensuring fairness in an NDN network, it is ineffective in protecting legitimate users from malicious attackers.
 Malicious attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of Interests.

### 2013-01-11 algos/probabilistic.tex
Edits to Section 4a and 4b
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@898 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-In addition to maintaining statistics on Interest satisfaction ratios, the next challenge is in using these statistics to penalize malicious Interests.
-A straightforward method to achieve this enforcement is to consider Interest satisfaction rate as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
+Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using this rotio to penalize malicious Interests.
+A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
 %Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
@@
 An explicit notification such as a gossip protocol between neighboring NDN routers that specifies the volume of Interests each router is willing to forward will likely address this issue.
-{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
+We leave the implementation and evaluation of a gossip protocol to future work.
+%{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
 

### 2013-01-12 01-intro.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Various forms of distributed denial of services attack (DDoS) pose a significant and constant threat to the existing Internet infrastructure~\cite{arbor-report}.
+Various forms of distributed denial of services (DDoS) attacks pose a significant and constant threat to the existing Internet infrastructure~\cite{arbor-report}.
 The recently proposed Named Data Networking (NDN) architecture~\cite{ndn-conext, ndn-tr} completely changes the communication paradigm in the network by removing the notion of addresses and making data the first-class network entities.
-That is, instead of letting end hosts sending packets to a given IP address, NDN lets end hosts request desired data by sending Interest packets carrying application level data names.
+That is, instead of letting end hosts send packets to a given IP address, NDN lets end hosts request desired data by sending Interest packets carrying application level data names.
 Such a shift automatically eliminates several long standing DDoS attacks, including both direct flooding as well as reflector attack through source address spoofing~\cite{mirkovic2004taxonomy}.

### 2013-01-12 02-ndn-background.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \section{NDN Overview\label{ccn-intro}}
-%Named Data Networking (NDN) is a network architecture which aims to replace IP architecture by replacing IP’s host-to-host data delivery model with pull-based information retrieval model.
+%Named Data Networking (NDN) is a network architecture which aims to replace IP architecture by replacing IPÕs host-to-host data delivery model with pull-based information retrieval model.
 In IP in order to retrieve data, data consumer have to know endpoint location of the desired data, in NDN all they have to know is data name.
@@
 
-In this section we briefly introduce NDN with a focus on its stateful forwarding plane.
+In this section we briefly introduce NDN with a focus on its stateful forwarding plane (for more details refer to \cite{ndn-conext, ndn-tr, adaptive-forwarding}).
 NDN is a receiver-driven, data-centric communication protocol.
@@
 Data names in NDN are hierarchically structured.
-A canonical NDN name looks in the following way: \texttt{\small /ndn/ucla/CS/www/index.html}.
+A canonical NDN name looks in the following way: \ndnName{/ndn/ucla/CS/www/index.html}.
 
-To retrieve Data, a consumer puts the name of desired data into an Interest packet and sends it to the network.
-Routers use this name to forward the Interest towards the data producer, and the Data packet whose name matches the name in the Interest is returned to the consumer.
-All data packets carry a signature that binds the name to the data.
-An Interest is “satisfied” when a Data packet is received with matching data name.
+To retrieve Data, a consumer puts the name of the desired content into an Interest packet and sends it to the network.
+Routers use this name to forward the Interest towards the Data producer, and the Data packet whose name matches the name in the Interest is returned to the consumer.
+All Data packets carry a signature that binds the name to the Data.
+An Interest is ``satisfied'' when a Data packet is received with matching data name.
 
-Each NDN node maintains three major data structures:
-\begin{enumerate}
-\item{Forwarding Interest Base (FIB) maps name prefixes and multiple physical network interfaces (where to forward Interests).
-Having one-to-many relationship in this table allows multipath forwarding of Interests.}
-\item{Content Store (CS) temporarily buffers Data packets that pass through this node, allowing fast Data retrieval by different consumers.}
-\item{Pending Interest Table (PIT) holds all ``not yet satisfied'' Interests that have been sent upstream towards data producers.
-Each entry in PIT contains a list of incoming, and outgoing, physical interfaces; the former enables multicast Data delivery, and the latter is needed when the same Interest is forwarded along multiple paths.}
-\end{enumerate}
+Each NDN router maintains three major data structures:
+\begin{itemize}
+\item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards data producers.
+Each entry in PIT contains a list of incoming, and outgoing, physical interfaces; the former enables multicast Data delivery, and the latter is needed when the same Interest is forwarded along multiple paths.
+\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, defining allowed (multipath) directions where to forward Interests. 
+% Having one-to-many relationship in this table allows multipath forwarding of Interests.}
+\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this node, allowing fast Data retrieval by different consumers.
+\end{itemize}
 
-When a router receives an Interest packet, it first checks whether there is a matching Data in its Content Store.
+When a router receives an Interest packet, it first checks whether there is a matching Data in its CS.
 If a match is found, the Data is sent back to the incoming interface of the Interest packet.
@@
 If the name exists in the PIT already, then it can be either a duplicate Interest (i.e., its nonce is remembered in PIT entry) that should be dropped,
-or an Interest from another consumer asking for the same Data which requires the incoming interface of this Interest to be added to the existing PIT entry.
-If the name does not exist in the PIT, the Interest is added into the PIT and further forwarded to the interface chosen by the strategy module.
+or an Interest from another consumer asking for the same Data which requires the incoming interface of this Interest to be added to the existing PIT entry (``collapsing'' the Interests).
+If the name does not exist in the PIT, the Interest is added into the PIT and further forwarded to the interface chosen by the strategy module, which uses FIB as input for its decision.
 
@@
 If a matching PIT entry is found,
-the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the Content Store, and removes the PIT entry.
+the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the CS, and removes the PIT entry.
 Otherwise, the Data packet is unsolicited and discarded.
 Each Interest also has an associated lifetime; the PIT entry is removed when the lifetime expires.
+The lifetime is specified by users, but it is ultimately a router's decision for how long it is actually willing to keep the PIT entry.  
+For example, and we assume this in the rest of the paper, the maximum time any Interest is kept in PIT is one second.
 

### 2013-01-12 03-interest-flooding.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Unlike Data packets, Interest packets in NDN are unsolicited, consume state in intermediate routers and are routed through the network based on their content name prefix.
+Unlike Data packets, Interest packets in NDN are unsolicited, consume state in intermediate routers, and are routed through the network based on their content name prefix.
 These properties make Interest packets an effective tool in launching DoS and DDoS attacks in NDN.
@@
 However, an adversary can target a specific namespace.
-For example in Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.
+For example in Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
 \footnote {In our example, Data producer is single-homed.
-In the case of multi-homed producers with rich connectivity through multiple providers, NDN would likely to cope better with DDoS attacks due its native multi-path and adaptive forwarding~\cite{adaptive-forwarding}.} These large volume of Interests can distrupt service quality in NDN network in two ways: they \emph{create network congestion} and \emph{exhaust resources on routers}.
+In the case of multi-homed producers with rich connectivity through multiple providers, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding}.}
+A large volume of these Interests can distrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
 
@@
 
-To efficiently implement an Interest flooding attack targeting a specific namespace (e.g., /newyorktimes/), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries (state) are stored at intermediate NDN routers for as long as possible.\footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.
-For example, and we assume this in the rest of the paper, the maximum time for which any Interest is admitted is one second.}
-In order to achieve both requirements effectively, malicious Interests should avoid collapsing (i.e, request a content that is different than existing PIT entries in the network) and avoid being served from caches of intermediate routers (i.e., request unpopular or non-existing content).
-In other words, to maximize effect of an DDoS attack, each malicious Interest generated by an individual attacker bot should request a non-existing content with a unique name (\emph{unique junk Interests}).
+To efficiently implement an Interest flooding attack targeting a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
+In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and avoid being served from caches of intermediate routers: each malicious Interest generated by an individual attacker bot should request an unpopular or non-existing content (e.g., content with a unique name, \emph{unique junk Interests}).
 In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network.
@@
 
-In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
+In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
 

### 2013-01-12 04a-design-naive.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 This principle allows intermediate routers that forward the Interest packets to control the number of outstanding Interests in the network.
-One simple implementation technique  is for a NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface.
+One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface.
 This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet switched networks.
 Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of Data requested that can fully utilize the downstream link (estimated from the number of Interests it forwarded) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
-Ideally, the number of tokens {\it i.e.} the \emph{Pending Interests Limit} for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
+Ideally, the number of tokens {\it i.e.} the pending \emph{Interests Limit} for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
 We can formalize this value as follows:
 % With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
-
+%
 \begin{equation}
-\mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
+\small \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
 \end{equation}

### 2013-01-12 algos/dynamic-limits.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-The previous strategy -- the satisfaction-based Interest acceptance -- divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
+The previous strategy---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
 % Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 

### 2013-01-12 paper.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@885 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@893 df1a90cd-247b-4364-bdaf-287a704eb499
Algorithm renaming, pseudocodes, consistency in "Interest" word usage, and some minor typos and grammars
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@894 df1a90cd-247b-4364-bdaf-287a704eb499
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \title{Mitigating Interest Flooding DDoS Attacks in NDN}%:\\ Cache/Content Poisoning}
-\author{anonymous}
+\author{Anonymous}
 
@@
 \renewcommand{\texttt}[1]{{\nicettfont #1}}
+
 \newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \marginpar{\textsc{ToDo}}
@@
 \usepackage{multirow}
+\usepackage{times}
+\usepackage{color}
 
@@
 In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network forwards data packets upon request only, effectively eliminating the existing DDoS attacks.
-However an NDN network can be subject to a new type of DoS attacks, namely Interest packet flooding.  
+However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  
 In this paper we investigate effective solutions to mitigate Interest flooding.
-We show that NDN's inherent properties of each router keeping per packet state and flow-balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
+We show that NDN's inherent properties of each router keeping per packet state and flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
 Our evaluation through simulations shows that the solution can quickly and effectively respond to Interest flooding.
@@
 \bibliographystyle{IEEEtran}
+{\small 
 \bibliography{references}
+}
 

### 2013-01-12 04a-design-naive.tex
Update design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@900 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 The flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
-This principle allows intermediate routers that forward the Interest packets to control the number of outstanding Interests in the network.
+This principle allows intermediate routers to control the inbound Data traffic by controlling the number of outstanding Interests in the network.
 One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface.
@@
 Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of Data requested that can fully utilize the downstream link (estimated from the number of Interests it forwarded) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
-Ideally, the number of tokens {\it i.e.} the pending \emph{Interests Limit} for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
+Ideally, the number of tokens (the pending \emph{Interests Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
 We can formalize this value as follows:
@@
 In the above equation, \emph{Delay} is the expected time of Interest being satisfied and \emph{Data packet size} is the size of the returned Data packet.
-Although both these values are not known {\it apriori}, it is not really necessary to use their exact values.
+Although both these values are not known a priori, it is not really necessary to use their exact values.
 One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as the network buffers can smooth out most of the network fluctuations.
 
-This {\it Token Bucket} approach might be exceptionally retrictive in forwarding Interests -- not all Interests will result in a Data packet -- thus underutilizing the network.
+This {\it Token Bucket} approach might be exceptionally retrictive in forwarding Interests---not all Interests will result in a Data packet---thus underutilizing the network.
 However, the biggest drawback of the algorithm is that it can be used as an effective mechanism to carry out denial of service attacks.
-If a router has utilized all its {\it tokens} to forward {\it bad} Interests on an out Interface, it can no longer forward incoming Interests from legitimate users on that out inteface till the pending {\it bad} Interests start to expire.
-One way to get around this issue is to impose a per-interface limit so that {\it bad} Interests are not allowed to entirely consume the limits of a specific interface.
+If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
+One way to get around this issue is to impose a per interface limit, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
 We describe this technique in greater detail below.
@@
 
-The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits Interests from malicious users.
+The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it admits Interests from malicious users.
 A sizeable percentage of these malicious Interests are forwarded all the way to content producers, thereby utilizing scarce network resources and reducing resources available to serve legitimate users.
@@
 The key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
+One can try a black- or whitelisting approach.
+However, besides the fact that source black- and whitelisting cannot work in NDN as it does not feature source addresses, it requires extraneous knowledge to classify the incoming Interests.
 
-Unlike in today's host-based Internet architecture where DDoS mitigation techniques that rely on blacklisting of dark IP prefixes or whitelisting of good IP prefixes are still reasonably effective, in NDN one cannot easily distinguish a `good' prefix from a `bad' one.
-Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets -- thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
-Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone -- DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
+% Alex: I'm not sure that this part is relevant... The point I see is that blacklisting and whitelisting is not 100% effective, but it can be used in both worlds
+
+% In today's host-based Internet architecture where DDoS mitigation techniques rely on blacklisting of ``dark'' IP prefixes or whitelisting of good IP prefixes.
+% Unlike IP, in NDN one cannot easily distinguish a `good' prefix from a `bad' one. 
+% Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
+% Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
 

### 2013-01-12 algos/dynamic-limits.tex
Update design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@900 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-The previous strategy---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
+The previous algorithm---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
 % Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
-An alternate strategy, which does not have the described drawbacks, is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
+An alternate algorithm for proportional token distribution without overreaction is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
 Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.
 
-The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm would work in our example in Fig.~\ref{fig:flooding example}.
-Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node would set and announce the following  incoming interface limit $L'$:
+The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm will work in our example in Fig.~\ref{fig:flooding example}.
+Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node will set and announce the following  incoming interface limit $L'$:
 \begin{enumerate}
-\item router B would set and announce the incoming interface limit $L'=3$;
-\item router A, after receiving announcement from B would readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
+\item router B will set and announce the incoming interface limit $L'=3$;
+\item router A, after receiving announcement from B will readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
 \item both legitimate users and adversaries may either obey or ignore the announced limit, which will be in any case enforced by router A.
@@
   \includegraphics[scale=0.3]{dynamic-limits}
-  \caption{Satisfaction-based pushback example: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer}
+  \caption{Satisfaction-based pushback example
+%: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer%
+}
   \label{fig:dynamic limits example}
@@
 To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
-That is, for each FIB entry we set a separate Interest limit for each incoming interface ($L_{in}^{'FIB}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{FIB}}$.
+That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
 
-% Alex: not sure if this paragraph belongs here
-Essentially, both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, with several core differences.
+Both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, but with several core differences. 
 First, we are suppressing (pushing back) unwanted requests for Data, not actual Data itself.

### 2013-01-12 algos/fair-queueing.tex
Small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@899 df1a90cd-247b-4364-bdaf-287a704eb499
Update design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@900 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 %, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
-we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded (see Fig.~\ref{fig:queueing}).
-To support fair queuing, we implement hierarchical queues for each interface as shown in Fig.~\ref{fig:queueing})\footnote{This mechanism is essentially class based queuing, with classes for each outgoing/incoming interface.}
+we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded and implement hierarchical queues for each interface (see Fig.~\ref{fig:queueing}). 
+This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing/incoming interface.
 %As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
@@
 
-\begin{figure}[htbp]
+\begin{figure}[thb]
   \centering
@@
 We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
-We can control the amount of physical resources utilized at a router (such as memory and computation power) by setting appropriate queue sizes.
+By setting appropriate queue sizes we can control the amount of physical resources utilized at a router (such as memory and computation power). 
 It is also important to set apprpriate value for how long an Interest can be enqueued. 
-If an Interest is enqueued for a long time, by the time it is dequeued and appropriately forwarded, the resulting Data packet might not be valid due to state expiration at previous downstream routers.
-We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
-{\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
+If an Interest is enqueued for a long time, by the time it is dequeued and appropriately forwarded, the resulting Data packet might not be valid due to state expiration at the downstream routers. 
+For our evaluations we chose to enqueue Interests up to 10\% of their original lifetime.
+% We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
+% Alex: I don't believe there is a need for separate discussion about "freshness", as we already introduced concept of lifetime
+% {\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
 
@@
 
-As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
-While this algorithm might be reasonable for ensuring fairness in an NDN network, it is ineffective in protecting legitimate users from malicious attackers.
+As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from the Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
+We note that while this algorithm might be reasonable for ensuring fairness in an NDN network, it is ineffective in protecting legitimate users from malicious attackers. 
 Malicious attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of Interests.

### 2013-01-12 algos/probabilistic.tex
Update design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@900 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 Parameter $\theta$ on line 5 of the Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
-This step is critical---while we want to drop Interests from attackers, we also want to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures due to  congestion.
+This step is critical---while we want to drop Interests from attackers, we also want to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
 

### 2013-01-13 04a-design-naive.tex
Edits to Section 5 and small scale evaluations
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@901 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 The key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
-One can try a black- or whitelisting approach.
-However, besides the fact that source black- and whitelisting cannot work in NDN as it does not feature source addresses, it requires extraneous knowledge to classify the incoming Interests.
+
+%One can try a black- or whitelisting approach.
+However, besides the fact that source black- and whitelisting cannot work in %NDN as it does not feature source addresses, it requires extraneous knowledge to classify the incoming Interests.
+
+%Priya: I have added the below point specifically to point out that a router cannot determine from the prefix name alone whether /parc is good  or bad...
+
+In NDN one cannot easily distinguish a `good' prefix from a `bad' one.
+Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
+Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the prefix name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
 

### 2013-01-13 05-evaluation.tex
Edits to Section 5 and small scale evaluations
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@901 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-02 05-evaluation.tex
@@
 
-% \todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
 % List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
 
-% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}
+% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers,
 
-We want to explore the effectiveness of designed mitigation techniques in a two distinctive ways.
-First, we need to understand how each method works on a very ground level of a just few nodes and links.
-Second, we want to pick promising techniques and see if they work in a large scale networks of hundreds and thousands of nodes.
-To ensure the correct transition from small scale experiments to large scale experiments we had to use the same evaluation tool in order to eliminate any possibility of implementation discrepancy.
-As of today the only network simulator supporting full NDN logic is the NS-3 based ndnSIM software.
+% alex: what's a point of latency?  it would matter only for queueing method and we not really pushing this method
+% Latency for good clients, good versus bad interests as a function of time
 
-\input{small-scale}
-\input{large-scale}
+In this section, we present an in-depth evaluation study, aiming to quantify the effectiveness of all our Interest flooding attack mitigation methods.
+We use the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator\footnote{\url{http://www.nsnam.org/}}, to run simulations for a variety of network topologies and scenarios.
+We implement our three mitigation algorithms --- token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback --- in ndnSIM.
+For evaluating the effectiveness of each mitigation algorithm, every router in the simulated topology runs the mitigation algorithm under study.
+
+% why we chose small scale topology
+% what point we wanted to show we small scale
+% what points we wanted to verify with larger-scale internet like topology
+
+% Metrics
+% not sure if i already explained that. our essential qualitative metric is .  
+% To quantify the effectiveness of the mitigation mechanism this  metric we use satisfaction percentages of user Interests.
+
+The metric we choose to quantify the effectiveness of our defense strategies is the {\it percentage of satisfied Interests for legitimate users}.
+This metric corresponds to the quality of service experienced by legitimate users when the network is under attack.
+In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conlcude that method $X$ is highly effective at mitigating the attack.
+We also ensure that all Interests expressed by legitimate users during a period of no-attack are satisfied.
+
+%Quality of the attack mitigation methods directly corresponds to the quality of service for the legitimate users during an ongoing attack, which in NDN network can be quantified through percentage of satisfied Interest.
+%For example, if the network implements a mitigation method $X$ and under the attack majority of user-expressed Interests are getting satisfied, then the method $X$ can be seen as highly effective.
+%At the same time, if only a small percentage of the expressed Interest are getting satisfied during the attack, the method $X$ can be called ineffective.
+
+% Traffic pattern
+In our experiments, we assume that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution.
+We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
+To quantify the behavior of our mitigation strategies under a worse case attack scenario, we ensure that all the attackers send junk Interests as fast as they can.
+%(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
+
+% Alex: not sure how to argue about the traffic pattern
+%Although this pattern may seem not truly realistic, it approximates a good statistical mix of traffic from all network users without excessive network buffering.
+
+%In addition to that, in each run of the simulation we ensure that all Interests expressed by the legitimate users during a no-attack period are satisfied.
+%For simplicity, we also equalized the average rates with which the legitimate users express Interests.
+%At the same time, the attackers are sending junk Interests as much as they can get through (remember, that Interest limits will not allow real f%looding of Intersests in all of the designed mitigation algorithms).
+
+We ran our simulations on two different network topologies --- a smaller binary tree topology and a much larger ISP topology.
+We use a binary tree topology as it represents one of the worst cases to defend against Interest flooding DDoS attacks.
+The larger ISP topology reflects how our mitigation methods would perform when deployed on the real Internet.
+Again, to study the performance of our mitigation strategies under a range of conditions, we also varied the percentage of attackers in the network - the values ranged from 6\% attackers to over 50\% attackers in the network.
+
+% Fixed parameters
+We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation to a fixed value for every node in the simulated topology.
+In particular, for the small-scale binary tree topology, we set delay to 80~ms, while for the large-scale ISP topology we set it to 330~ms (the order of the largest RTT).
+The data size is 1100~bytes for all simulation runs and topologies.
+
+\input{eval-small-scale}
+\input{eval-large-scale}
 

### 2013-01-13 eval-large-scale.tex
Edits to Section 5 and small scale evaluations
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@901 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-To check validity of the small-scale experiment results, we performed a larger-scale evaluation based on a modified version of Rocketfuel AT\&T topology~\cite{rocketfuel}.
-In order to approximate the general structure of the Internet,
+%To check validity of the small-scale experiment results, we performed a larger-scale evaluation based on a modified version of
+
+Next, our goal is to understand the behavior of our mitigation strategies when deployed on a large-scale realistic topology.
+Our ISP topology is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
+%In order to approximate the general structure of the Internet,
 % (scale-free structure, customer-provider, and peer-to-peer relations)
-we extracted the largest connected component of 562 nodes from the original topology and separated nodes in three categories: clients, gateways, and backbones.
-All nodes with degrees one, two, and three became clients (344 red nodes on Fig.~\ref{fig:large-scale}), all nodes that are directly connected to clients became gateways (109 green nodes), and the rest became backbones (109 blue nodes).
-(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.)
-After categorizing the nodes, we randomly assigned bandwidths and link delays based on link types (see Table~\ref{tab:large-scale}).
+We extract the largest connected component comprising of 562 nodes from the original topology and separate the nodes into three categories: clients, gateways, and backbones.
+Nodes with degrees less than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes as classified as backbones (109 blue nodes).
+%(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
+We assign bandwidth and  delay values to links based on their type --- both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
 
@@
 \centering
-\caption{Large-scale topology parameters}
+\caption{Large-scale topology link bandwidth and delay ranges}
 \label{tab:large-scale}

### 2013-01-13 eval-small-scale.tex
Edits to Section 5 and small scale evaluations
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@901 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2013-01-11 eval-small-scale.tex
@@
 % Topology description
-To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a simplistic small-scale binary tree topology (Fig.~\ref{fig:small-scale}).
-All links in this topology were assigned 10~Mbps bandwidths with randomized propagation delays from the range from one to ten milliseconds.
-Both legitimate users and attackers were placed only on leaf nodes (red), each expressing Interests towards a single producer placed at the root of the tree. 
+%To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a %simplistic small-scale binary tree topology 
+In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we use for our initial experiments.
+Legitimate users as well as attackers were placed on leaf nodes (red nodes) as show in the figure.
+There are 16 end users (both legitimate and attackers) in this topology, each expressing Interests that are routed towards a single data producer placed at the root of the tree.
+Each link in this topology is assigned a bandwidth of 10~Mbps and a randomized propagation delay ranging from 1 to 10 ms.
+
 % Alex: should we mention that?
-The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS attacks.
-That is, sharing of the network links exponentially increases as decreasing level of the binary tree.
+%The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS %attacks.
+%That is, sharing of the network links exponentially increases as decreasing level of the binary tree.
 
@@
 
-\subsubsection{Network reaction to the attack}
+\subsubsection{Effectiveness of the three mitigation algorithms}
 
-The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
-For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).
+%The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
+%For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).
 
-For each network scenario we performed ten independent simulation runs, where randomly chosen 7 client nodes represent adversaries (compromised users), and the rest 9 client nodes represent legitimate users.
-In each run we simulated a 10-minute attack window (total simulation time was 30 minutes, with attack starting at 10-minute mark).
+Our goal is to compare the effectiveness of each mitigation method and quantify the percentage of Interests satisfied for all legitimate users while the network is under attack.
+For each mitigation algorithm, we perform ten independent simulation runs, where we randomly choose 7 client nodes to represent adversaries while the remaining 9 client nodes represent legitimate users.
+In each run we simulate a 10-minute attack window (total simulation time was 30 minutes, with attack starting at the 10-minute mark).
+We plot the minimum and maximum range for observed Interest satisfaction percentages for all legitimate users aggregated across the 10 simulation runs as a function of time for each mitigation algorithm in Fig.~\ref{fig:small-scale attack progress}.
+Token bucket with per-interface fair queuing performs the worst, while satisfaction-based pushback performs the best, with almost a 100\%  satisfied Interests for all legitimate users.
 
-The results for all attack mitigation algorithms and all runs are aggregated in Fig.~\ref{fig:small-scale attack progress}, where Y-axis represents a minimum and maximum range for observed Interest satisfaction percentages among all nodes and all simulation runs.
-A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
+%A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
 
@@
   \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
-  \caption{Satisfaction ratio dynamics during the attack (7 attackers / 9 legitimate)}
+  \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
   \label{fig:small-scale attack progress}
@@
 
-\paragraph{\textbf{Simple token buckets}}
+%\paragraph{\textbf{Simple token bucket}}
 
-{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}
+%{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}
 
-Let us take a deeper look on what is happening with the physical limits algorithm.
-Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as physical limits restricts the number of forwarded Intersets!).
-This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
-In this example we assume that both the legitimate user and the adversary send Interests in about the same time.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{physical-limits-sync-problem}
-  \caption{Three-router topology, with one legitimate and one malicious user}
-  \label{fig:three router example}
-\end{figure}
-
-Both router L and router X will forward the Interests, as both of them have a free token available.
-At router A, two cases are possible, either of Interests can arrive first, resulting in a quite different effects.
-When legitimate Interest arrives first, then there are no problem. 
-Router A will capture the token, forward the Interest, which will be quickly satisfied, releasing the token for future uses.
-In the mean time, malicious Interest will be dropped at router A, and router X will release the hold for the token in one second (i.e., after the maximum time Interests are admitted), enabling a new round of competition for router A's resources.
-
-In the case when malicious Interest is sent a little bit earlier, then router A will forward malicious Interests, dropping a legitimate one, and causing ``lock out'' for one second.
-In the instant when the token gets released at router X, an adversary is able to push new Interest towards router A, which may arrive in the exact time A's token gets released (assuming an idealistic environment).
-As a result, the adversary recaptures router A's token and extends the ``lock out'' for another second, denying service to the legitimate user without sending any massive numbers of Interests.
+%Let us take a deeper look on what is happening with the simple token bucket algorithm.
+%Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as token bucket restricts the number of forwarded Intersets!).
+%This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
+%In this example we assume that both the legitimate user and the adversary send Interests in about the same time.
+%
+%\begin{figure}[t]
+%  \centering
+%  \includegraphics[scale=0.3]{physical-limits-sync-problem}
+%  \caption{Three-router topology, with one legitimate and one malicious user}
+%  \label{fig:three router example}
+%\end{figure}
+%
+%Both router L and router X will forward the Interests, as both of them have a free token available.
+%At router A, two cases are possible, either of Interests can arrive first, resulting in a quite different effects.
+%When legitimate Interest arrives first, then there are no problem. 
+%Router A will capture the token, forward the Interest, which will be quickly satisfied, releasing the token for future uses.
+%In the mean time, malicious Interest will be dropped at router A, and router X will release the hold for the token in one second (i.e., after the maximum time Interests are admitted), enabling a new round of competition for router A's resources.
+%
+%In the case when malicious Interest is sent a little bit earlier, then router A will forward malicious Interests, dropping a legitimate one, and causing ``lock out'' for one second.
+%In the instant when the token gets released at router X, an adversary is able to push new Interest towards router A, which may arrive in the exact time A's token gets released (assuming an idealistic environment).
+%As a result, the adversary recaptures router A's token and extends the ``lock out'' for another second, denying service to the legitimate user without sending any massive numbers of Interests.
 
@@
 
-The described problem arises from the clocking effect and can be solved in a number different ways.
-Augmenting physical limits algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
-That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
-However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
-Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
-We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.
+We observe a successful denial of service attack, where 40\% attackers succeed in significantly shutting down the remaining 60\% legitimate users - a mere 15\% of their Interests are satisfied by Data from the producer.
+Contrary to expectations, the 60\% legitimate users do not receive at least 60\% of network resources.
+As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers, a good percentage of which traverse all the way to the data producer.
+Significantly reducing the number of Interests accepted from attackers is fundamental for improving the effectiveness of any mitigation algorithm.
+
+%The described problem arises from the clocking effect and can be solved in a number different ways.
+%Augmenting token bucket algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
+%That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
+%However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
+%Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
+%We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.
 
@@
 
-When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
-That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
-The observed periodicity of the satisfaction-based Interest accept curve on Fig.~\ref{fig:small-scale attack progress} is a direct result from ``intelligence'' (Interest satisfaction rate statistics) decaying with time.
-The 50-second periods approximately correspond to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx20\%$ within 50~seconds.
-The primary reason that such minimum peaks exist is the fact that when attack Interests start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe traffic mix from legitimate and malicious users).
-This degradation subsequently reduces chances for legitimate Interests get through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' to the edge.
+The effectiveness of this algorithm stems from the fact that routers do not admit malicious Interests into the network, thereby ensuring availability of network resources for serving legitimate users.
+The observed periodic dips in the Interest satisfaction ratios of legitimate users in Fig.~\ref{fig:small-scale attack progress} is a direct result of Interest satisfaction rate statistics decaying with time.
+The 50-second period approximately corresponds to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value that ranges from 30~seconds to 50~seconds.
+%The primary reason that such minimum peaks exist is the fact that 
+When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe traffic mix from legitimate and malicious users).
+Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' to the edge.
+
+%When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
+%That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
 
@@
 
-The only potential problem with the satisfaction-based pushback algorithm is that it features a sharp dive of the satisfaction ratio curve at the start of the attack.
-That is, until all routers become fully aware of the attack---malicious Interests start to time out---and until explicit Interest limits announcements successfully localize malicious Interests near the attacker, the network for a short period of time (under 10~seconds for all simulation runs) fails to provide 100\% service for the legitimate users.
-At the same time, we do not observe any periodic behavior, as dynamically adjusted limits during an ongoing attack effectively guarantee that once Interest is admitted, it will get through to the Data producer.
+This mitigation algorithm is able to effectively shut down attackers and ensure that almost all of the Interests from legitimate users are satisfied. 
+%The only potential problem with the satisfaction-based pushback algorithm is that it features 
+We observe a  sharp dip in the satisfaction ratio curve at the start of the attack.
+It takes a few seconds for all routers to be fully aware of the attack, which happens when malicious Interests start to time out and explicit Interest limit announcements succeed in containing malicious Interests close to the attacker.
+Till then, the network for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
+Once the malicious Interests are effectively shut down, all Interests from legitimate users are satisfied.
+Unlike the satisfaction-based Interest acceptance scenario, we do not observe any periodic dips in the satisfaction curve, as the pushback algorithm effectively guarantees that once an Interest is admitted, it will almost certainly be routed to the data producer.
 
@@
 
-The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
-To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.
+Our next goal is to study the effectiveness of our mitigation algorithms as a function of increasing adversaries in the network.
+To this end, we vary the percentage of attackers in the topology from 6\% to over 50\%.
+Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
+All other parameters and experimental set-up are similar to the previous experiment.
+As before, for each mitigation algorithm, we perform ten independent simulation runs.
+%The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
+%To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.
 
-Since at this point the overall attack dynamics of all the attack mitigation algorithms is relatively clear, in Fig.\ref{fig:small-scale-topo boxplot} we show aggregated over 10 individual runs comparison of satisfaction ratio values observed during the first minute of the attack.
+%Since at this point the overall attack dynamics of all the attack mitigation algorithms is relatively clear, 
 % In other words, each point captured in the box plot graph corresponds to 1-second averaged satisfaction ratio for a user in an individual simulation run.
@@
   \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
-  \caption{Average consumer Interest satisfaction ratios (first minute)}
+  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}
   \label{fig:small-scale-topo boxplot}
@@
 
-The presented results demonstrate the overall, and somewhat obvious, trends for all attack mitigation algorithms: the larger is the attack, the lower service quality is observed by the legitimate users.
-Physical limits with and without per-interface fairness give perfect attack instrument even for a small number of attackers: just 3 attackers can either completely shut down or halve the service quality for the rest 13 users.
-At the same time, while both intelligent attack mitigation algorithms also show a decline in service quality, this decline is very subtle: when more than 50\% of users are compromised, service degrades less than by 25\% for the satisfaction-based Interest accept method and less than by 10\% in the satisfaction-based pushback algorithm.
+In Fig.\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
+The results are as expected --- for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
+In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.
+While both intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual.
+In the case of satisfaction-based pushback algorithm, over 90\% of Interests from legitimate users are satisfied even when over 50\% of the users are malicious.
 

### 2013-01-13 06-related.tex
Add a couple of new citations
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@883 df1a90cd-247b-4364-bdaf-287a704eb499
A new version of related work. May need corrections
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@902 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
+The Named Data Networking is a relatively new communication paradigm, but it already got a limited attention in the security community.
+Lauinger~\cite{Lauinger:2010:Security--scalability} showed several attack vectors that can be applied to NDN.
+However, the work is specifically limited to a particular design choices implemented in CCNx software (\url{http://www.ccnx.org/}), rather than NDN architecture itself.
+W\"ahlisch et al.~\cite{Wahlisch:2012:Backscatter-from} explore security and stability threats in the general area of information-centric networks (ICN), using CCNx software as an example.  
+While this work attempts to generalize findings for all ICNs, it largely does not go beyond the current design choices of CCNx.
+% (which is an example, but not the final word in NDN) 
+% Gasti et al.~\cite{gasti2012ddos} identified several NDN architecture-specific attacks (Interest flooding and content/cache poisoning) and proposed potential solutions, without devising particular algorithms.
+In this paper we follow some suggestions by Gasti et al.~\cite{gasti2012ddos} and explore intrinsic potential of NDN architecture to sustain DDoS attacks, using the Interest flooding attack as a first step in this direction.
+Our design for the attack mitigation relies in part on limiting number of outstanding Interests.  
+Similar techniques were explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr} and Rozhnova and Fdida~\cite{rozhnova2012effective}, but applied only to facilitate performance in the NDN network.
+
+The general area of denial of service attacks and their mitigation methods is one of the hottest topics of the past decade.
+% Among all the body of work, 
+The most related area to this paper is solutions to network-level flooding attacks, which include DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods to pushback of malicious traffic to the edged using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing}, various ticketing systems with conditional admission of traffic to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities}, overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
+
+% Our design for the Interest flooding attack mitigation borrows
+
+% This paper talks about attacks on content centric infrastructure (not specifically to NDN).
+% \cite{Wahlisch:2012:Backscatter-from}
+
+% % Collaborative detection of DDoS attacks over multiple network domains
+% \cite{Chen:2007:Collaborative-detection} distributed change-point detection
+
+% % DDoS flooding attack detection through a step-by-step investigation
+% \cite{Jun:2011:DDoS-flooding}
+
+% % A practical method to counteract denial of service attacks
+% \cite{Tupakula:2003:A-practical-method}
+
+% Alex: We should not include this reference for the review, but afterwards
+% Previous work on DDoS and DoS~\cite{gasti2012ddos}
+
+% Network level (Flooding)
+% % 2002
+% Pushback~\cite{Pushback} (hop-by-hop push back) aggregate- based congestion control/congestion signatures (e.g., per-destination), rate-limiting, explicit notification
+% AITF~\cite{Argyraki:2005:Active-internet} (active filtering requests; path recording, last-point of trust detecting)?
+% DefCOM \cite{Oikonomou:2006:A-framework-for-a-collaborative} Communication between src, core, and dst to provide collaborative defense.
+Dst raises alerts, src differentiate bad/good, packet tagging.
+Core rate-limit, congestion-aware re-tag.
+Traffic prioritization.
+% StopIt \cite{Liu:2008:To-filter-or-to-authorize:} (filtering) tagging with passports, tagged prioritization, dst- invoked filter instantiation
+% NetFence \cite{Liu:2010:NetFence:-preventing} congestion policing: fair queuing (one leaky bucket per {src,L}, L- bottleneck), secure "ticketing" with signals for AIMD to increase/decrease bandwidth allowance
+% PSP \cite{Chou:2009:Proactive-surge} topology as origin-destination pairs, packet tagging, OD traffic isolation, sharing based on historic bandwidth demand
+
+% SIFF~\cite{Yaar:2004:SIFF:-A-stateless} (time-based tickets, capabilities)
+% TVA \cite{Yang:2005:A-DoS-limiting-network} like SIFF, traffic- based tickets, hierarchical per- AS, per-source fair queuing
+% FastPass \cite{Wendlandt:2006:Fastpass:-Providing} (tokens: various puzzles, other methods) traffic authorization, routers verify and filter.
+% \cite{Natu:2007:Fine-grained-capabilities} based on TVA/SIFF: specifies previously unspecified mechanisms to grant "tickets" for requesters, extends capabilities to include priorities, changing tickets to be only destination- dependent, not path dependent
+% % LazySusan \cite{Crowcroft:2007:Lazy-Susan:} TR (latency-based proof of work--- computational puzzles)
+% Portcullis \cite{Portcullis} Protecting connection setup with computational proof of work, tickets and traffic prioritization for the rest, per- computational fairness; DNS to disseminate puzzles
+% There are many other puzzle- based schemes, on which Portcullis is based or which problems it solves
+
+% PacketSymmetry \cite{Kreibich:2005:Using-packet} (leverages packet symmetry to detect and remove bad traffic) packet asymmetry - number of transmitted packets (tx) to received packets (rx); negative values when rx outweighs tx, positive values when tx outweighs rx, and zero in the case of perfectly balanced traffic)
+% % Detecting SYN flooding attacks
+% \cite{Wang:2002:Detecting-SYN-flooding} based on the protocol behavior of TCP SYN-FIN (RST) pairs, and is an instance of the Seqnential Change Point Detection
+% dFence \cite{Mahimkar:2007:dFence:-Transparent} (middleboxes) TCP connection proxying, rate estimation and TCP/ACK modification
+
+% Overlays:
+% CenterTrack \cite{Stone:2000:CenterTrack:-An-IP-overlay} (overlay) reroute suspicious traffic to a special routers with diagnostic capabilities using an overlay
+% SOS \cite{Keromytis:2004:SOS:-An-architecture}
+% Shield \cite{Kline:2011:Shield:-DoS-filtering}
+
+% NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
 In this section we will overview generic directions of DDoS mitigation designs and try to think about which tricks could be used in NDN.
@@
 Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
-This implies that each client must pass through an authentication process prior to using any bandwidth ~\cite{Capabilities}.
+This implies that each client must pass through an authentication process prior to using any bandwidth~\cite{Capabilities}.
 We believe that for NDN this method doesn't fit really well for the following reasons.
@@
 
-Congestion control systems do per flow traffic analysis and drop of packets belonging to misbehaving flows.
+% Congestion control systems do per flow traffic analysis and drop of packets belonging to misbehaving flows.
 For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
@@
 
-Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
+% Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
 This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines~\cite{Pushback}.

### 2013-01-13 01-intro.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@903 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Various forms of distributed denial of services (DDoS) attacks pose a significant and constant threat to the existing Internet infrastructure~\cite{arbor-report}.
-The recently proposed Named Data Networking (NDN) architecture~\cite{ndn-conext, ndn-tr} completely changes the communication paradigm in the network by removing the notion of addresses and making data the first-class network entities.
-That is, instead of letting end hosts send packets to a given IP address, NDN lets end hosts request desired data by sending Interest packets carrying application level data names.
-Such a shift automatically eliminates several long standing DDoS attacks, including both direct flooding as well as reflector attack through source address spoofing~\cite{mirkovic2004taxonomy}.
+The Internet is a unique global success story that earmarked the information age.
+However, the design that fostered its success and wide-adaptation over the last three decades is now aged and became its limitation to effectively accommodate the changing demands of its users.
+Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an active research effort that aims to move the Internet into the future with a new, content-centric design that is capable of efficient content distribution and seamless mobility support.
 
-However, since NDN allows any host to request any data, malicious users can attack an NDN network by Interest flooding.
-As we explain in the next section, NDN routers perform stateful forwarding of Interests, uncontrolled floods of Interest packets can potentially exhaust router resources, disrupting services for legitimate users.
-One can also attack an NDN network by hijacking Interest packets and then injecting false data replies into the network.
+In contrast to today's Internet, another key goal of the NDN project is "security by design".
+In fact, it goes a long way by guaranteeing the integrity and provenance of every data packet with digital signatures and protecting user-privacy with no source addresses carried in packets.
+However one big question that is yet to be answered is: How does the current NDN design fare in terms of its resilience against denial of service attacks?
+Especially since various forms of distributed denial of services (DDoS) attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial for any design aiming to replace it would be free of similar vulnerabilities.
 
-As a first step towards a complete solution to address various denial of service attack problems in NDN, in this paper we investigate the solution space for Interest flooding attack (Section~\ref{sec:interest flooding}).
-We show how an NDN router can exploit its state information to mitigate Interest flooding (Section~\ref{sec:design}).
-We base our solution on the following two insights.
-First, instead of creating state for all incoming Interests, an NDN router only needs to accept enough Interest packets to fully utilize downstream link capacity.
-Second, because Data packets traverse the path taken by the Interests, an NDN router can observe whether an Interest retrieves Data (good Interest) or not (bad Interest).
+NDN makes data the first-class network entity and eliminates host-based addressing. That is, instead of letting end hosts send packets
+to a given IP address, NDN lets end hosts request desired
+data by sending Interest packets carrying application level
+data names. Such a shift automatically eliminates several long
+standing DDoS attacks, including both direct flooding as well
+as reflector attack through source address spoofing~\cite{mirkovic2004taxonomy}.
+
+However, since NDN allows any host to request any data, malicious users can attack the network by sending excessive number of requests.
+Such requests are expressed by sending Interests packets in NDN and each interest leave a state on routers along its way.
+Thus, excessive number of interests can easily disrupt service by exhausting router memory.
+We coin in the term "interest flooding" to refer to such attacks and
+%One can also attack an NDN network by hijacking Interest packets and then injecting false data replies into the network.
+this paper exclusively investigates the problem and the solution space for it.
+In this important first step towards a complete investigation of denial of service attacks in NDN, we use extensive simulations to show the devastating effect of Interest flooding on vanilla NDN and how a router can exploit its state information to effectively mitigate them.
+%(Section~\ref{sec:design}).
+%We base our solutions on the following two insights.
+%First, instead of creating state for all incoming Interests, an NDN router should only needs to accept enough Interest packets to fully utilize downstream link capacity.
+%Second, because Data packets traverse the path taken by the Interests, an NDN router can observe whether an Interest retrieves Data (good %Interest) or not (bad Interest).
 % Alex: Not sure whether it should be mentioned in intro or not.  If it should, then I don't really like it...
+The rest of the paper is organized as follows: We give an overview of NDN architecture in Section~\ref{sec:ccn-intro} and explain interest flooding attacks in Section~\ref{sec:interest-flooding}.
+In Sections~\ref{sec:design},~\ref{sec:evaluation} and~\ref{sec:discussion}, we introduce techniques to mitigate these attacks, evaluate their effectiveness and discuss their limitations respectively.
+We summarize related work in Section~\ref{sec:related-work} and finalize the paper with conclusions and future work in Section~\ref{sec:conclusion}.
 
-We conduct simulation-based evaluations to quantify the effectiveness of our proposed attack mitigation algorithms (Section~\ref{sec:evaluation}).
+%We conduct simulation-based evaluations to quantify the effectiveness of our proposed attack mitigation algorithms %(Section~\ref{sec:evaluation}).
 %% based on trivial small-scale and Internet-like larger-scale topologies.
-The results show a great potential of one of the designed algorithms (satisfaction-based pushback, Section~\ref{sec:dynamic limits}), where the attack traffic can be effectively localized near the attacker himself.
-\todo{LZ: I did not modify this last paragraph; need to see the rest of the paper first.}
+%The results show a great potential of one of the designed algorithms (satisfaction-based pushback, Section~\ref{sec:dynamic limits}), where %the attack traffic can be effectively localized near the attacker himself.
+%\todo{LZ: I did not modify this last paragraph; need to see the rest of the paper first.}
 

### 2013-01-13 06-related.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@903 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@904 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \section{Related work}
-\label{sec:related work}
+\label{sec:related-work}
 
-The Named Data Networking is a relatively new communication paradigm, but it already got a limited attention in the security community.
-Lauinger~\cite{Lauinger:2010:Security--scalability} showed several attack vectors that can be applied to NDN.
-However, the work is specifically limited to a particular design choices implemented in CCNx software (\url{http://www.ccnx.org/}), rather than NDN architecture itself.
+As a new Internet architecture proposal, the Named Data Networking has attracted attention from the security community. 
+Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
 W\"ahlisch et al.~\cite{Wahlisch:2012:Backscatter-from} explore security and stability threats in the general area of information-centric networks (ICN), using CCNx software as an example.  
-While this work attempts to generalize findings for all ICNs, it largely does not go beyond the current design choices of CCNx.
+While this work aims to generalize findings for all ICNs, it largely does not go beyond the current design choices of CCNx.
 % (which is an example, but not the final word in NDN) 
 % Gasti et al.~\cite{gasti2012ddos} identified several NDN architecture-specific attacks (Interest flooding and content/cache poisoning) and proposed potential solutions, without devising particular algorithms.
-In this paper we follow some suggestions by Gasti et al.~\cite{gasti2012ddos} and explore intrinsic potential of NDN architecture to sustain DDoS attacks, using the Interest flooding attack as a first step in this direction.
-Our design for the attack mitigation relies in part on limiting number of outstanding Interests.  
-Similar techniques were explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr} and Rozhnova and Fdida~\cite{rozhnova2012effective}, but applied only to facilitate performance in the NDN network.
+In this paper we follow the suggestions by Gasti et al.~\cite{gasti2012ddos} and utilize the properties provided by the NDN architecture to mitigate DDoS attacks, and tackle the Interest flooding problem as a first step in this direction.
+More specifically our attack mitigation design relies on NDN's stateful forwarding plane 
+which provides statistics on unsatisfied Interests.  
+Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
 
-The general area of denial of service attacks and their mitigation methods is one of the hottest topics of the past decade.
+The general area of denial of service attacks and their mitigation methods is among the hottest topics in recent years.
 % Among all the body of work, 
-The most related area to this paper is solutions to network-level flooding attacks, which include DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods to pushback of malicious traffic to the edged using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing}, various ticketing systems with conditional admission of traffic to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities}, overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
+The efforts that are most relevant works to this paper are solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushbacking malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
+overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
+various ticketing systems with conditional admission of traffic to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
+and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
+Identifying malicious traffic requires state at routers, all these solutions differ in the specifics on what state to use and how to establish it.
+By design NDN's forwarding plane keeps per packet state, one can simply take full advantage of this state to develop effective mitigations.
 

### 2013-01-13 eval-large-scale.tex
Edits to large-scale evaluations with comments in red, awaiting response from Alex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@905 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Next, our goal is to understand the behavior of our mitigation strategies when deployed on a large-scale realistic topology.
+Next, our goal is to understand the behavior of our mitigation strategies when deployed on a large-scale real network topology.
 Our ISP topology is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
@@
 % (scale-free structure, customer-provider, and peer-to-peer relations)
-We extract the largest connected component comprising of 562 nodes from the original topology and separate the nodes into three categories: clients, gateways, and backbones.
-Nodes with degrees less than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes as classified as backbones (109 blue nodes).
+We extract the largest connected component comprising of 562 nodes from this original topology and separate the nodes into three categories: clients, gateways, and backbones.
+Nodes having degree than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes as classified as backbones (109 blue nodes).
 %(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
@@
 
-In an Internet-like topology, the location of the Data producer plays the key part in his ability to sustain flooding attack.
-That is, if the producer has limited network capacity (a personal blog located hosted on a client node), then he will be a really easy target for the attack.
-On the other extreme, when the producer is located at the backbone (Google or Amamzon), then the attack would have a hard time to degrade service, as a lot of legitimate users would not even share paths with attackers.
-To evaluate a balanced network scenario, we placed the Data producer at the gateway node, which randomly picked for each simulation run.
-Similarly to the first set of small-scale evaluations, we fixed the number of malicious nodes at approximately 40\% level (140 out of 344 client nodes in the topology), while randomly varied which locations of compromised nodes.
+{\color{red}Priya: Below para might have to be modified if we conducted expts for producer at backbone and producer at client node. Also need to recheck if attacker percentage was 30\% or 40\%}
+Topological location of the data producer plays a key role in its resilience to Interest flooding attacks.
+For a data producer that is connected to a client node via a low-bandwidth link, even a small number of junk Interests can impact services for legitimate users.
+For a producer located at the backbone with rich connectivity through many high-bandwidth links, an attack might not be as severe as a majority of legitimate users might not be on the attack path.
+Thus, in our experiments, to evaluate a balanced network scenario, we place the data producer at a gateway node, which randomly pick for each simulation run.
+Similar to the binary tree topology experiments, we fix the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly picked these nodes for each simulation run.
+We conduct 10 simulation runs for each mitigation algorithm.
 
@@
 
-The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
+In Fig.~\ref{fig:large-scale}, we summarize our results averaged over 10 simulations runs for each mitigation algorithm.
+As in the case of the binary-tree topology, token bucket with per interface fairness is the most ineffective algorithm and satisfaction-based pushback algorithm is the most effective.
+Interest satisfaction percentages for legitimate users are approximately 25\% and almost 100\% respectively for these two strategies.
+
+%
+%The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
 
@@
 
-At the same time, the satisfaction-based Interest acceptance method completely failed to provide an adequate protection against the Interest flooding attack, and in addition degraded service for the legitimate users after the attack finished.
-The main reason for the failure was already explained in Section~\ref{sec:probabilistic}.
-That is, if the number of hops between legitimate users and the Data producer is large (15 on average in the simulated topology) uncoordinated probabilistic Interest drops result in minuscule probability for good Interests to reach the Data producer during an ongoing attack, resulting in negative Interests satisfaction ratio statistics.
-This also explains why until the statistics ages out, not all legitimate users can get satisfy all of their Interests.
+Satisfaction-based Interest acceptance algorithm, which was very effective for binary-tree topology, is completely ineffective when deployed in a larger realistic topology.
+For the duration of the attack, legitimate users experience poor quality of service with only 25\% of their Interests being satisfied and continue to experience degraded service long after the attack has stopped.
+This poor performance, as detailed in  in Section~\ref{sec:probabilistic}, is due to the fact that each router in the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
+In the case of the larger-topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics, which in turn leads to further penalization of new Interests from them.
 
-In summary, in all of the simulated topologies, the satisfaction-based pushback algorithm restricts malicious traffic from even entering the network.
-The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
+To summarize, in all of our simulations, the satisfaction-based pushback algorithm is the most effective technique as it restricts malicious Interests from even entering the network. 
+%The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
 As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.

### 2013-01-13 05-evaluation.tex
Edits to eval section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@906 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 We use the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator\footnote{\url{http://www.nsnam.org/}}, to run simulations for a variety of network topologies and scenarios.
-We implement our three mitigation algorithms --- token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback --- in ndnSIM.
+We implement our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback---in ndnSIM.
 For evaluating the effectiveness of each mitigation algorithm, every router in the simulated topology runs the mitigation algorithm under study.
@@
 
-We ran our simulations on two different network topologies --- a smaller binary tree topology and a much larger ISP topology.
+We ran our simulations on two different network topologies---a smaller binary tree topology and a much larger ISP topology.
 We use a binary tree topology as it represents one of the worst cases to defend against Interest flooding DDoS attacks.

### 2013-01-13 eval-large-scale.tex
Edits to eval section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@906 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 %(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
-We assign bandwidth and  delay values to links based on their type --- both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
+We assign bandwidth and  delay values to links based on their type---both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
+We experiment with placing the data producer at both a gateway node as well as backbone node, which we randomly pick for each simulation run.
+Similar to the binary tree topology experiments, we fix the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly pick these nodes for each simulation run.
+We conduct 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5 minute interval.
 
@@
 
-{\color{red}Priya: Below para might have to be modified if we conducted expts for producer at backbone and producer at client node. Also need to recheck if attacker percentage was 30\% or 40\%}
-Topological location of the data producer plays a key role in its resilience to Interest flooding attacks.
-For a data producer that is connected to a client node via a low-bandwidth link, even a small number of junk Interests can impact services for legitimate users.
-For a producer located at the backbone with rich connectivity through many high-bandwidth links, an attack might not be as severe as a majority of legitimate users might not be on the attack path.
-Thus, in our experiments, to evaluate a balanced network scenario, we place the data producer at a gateway node, which randomly pick for each simulation run.
-Similar to the binary tree topology experiments, we fix the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly picked these nodes for each simulation run.
-We conduct 10 simulation runs for each mitigation algorithm.
+%Priya: Leaving out this in the interest of space...
+%Topological location of the data producer plays a key role in its resilience to Interest flooding attacks.
+For a data producer that %is connected to a client node via a low-bandwidth link, even a small number of junk Interests can impact services for legitimate %users.
+For a producer located at the backbone with rich connectivity through many high-bandwidth links, an attack might not %be as severe as a majority of legitimate users might not be on the attack path.
 
@@
 
-In Fig.~\ref{fig:large-scale}, we summarize our results averaged over 10 simulations runs for each mitigation algorithm.
-As in the case of the binary-tree topology, token bucket with per interface fairness is the most ineffective algorithm and satisfaction-based pushback algorithm is the most effective.
-Interest satisfaction percentages for legitimate users are approximately 25\% and almost 100\% respectively for these two strategies.
+In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over 10 simulations runs for each mitigation algorithm for the scenario where the data producer is placed at a gateway node.
+We observe similar results for the data producer placed at the backbone node as well.
+As in the case of the binary-tree topology experiments, token bucket with per interface fairness is the most ineffective algorithm and satisfaction-based pushback is the most effective one.
+Interest satisfaction percentage for legitimate users are approximately 25\% and almost 100\% respectively for these two mitigation methodologies.
 
@@
  \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
- \caption{Satisfaction ratio dynamics during the attack (30\% attackers)}
+ \caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}
  % producer on a gateway node

### 2013-01-13 eval-small-scale.tex
Edits to eval section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@906 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 In Fig.\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
-The results are as expected --- for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
+The results are as expected---for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
 In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.

### 2013-01-13 01-intro.tex
small edits to Intro
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@907 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 The Internet is a unique global success story that earmarked the information age.
-However, the design that fostered its success and wide-adaptation over the last three decades is now aged and became its limitation to effectively accommodate the changing demands of its users.
+However, the design that fostered its success and wide-adaptation over the last three decades is now aged and limited in accommodating the changing demands of today's users.
 Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an active research effort that aims to move the Internet into the future with a new, content-centric design that is capable of efficient content distribution and seamless mobility support.
 
-In contrast to today's Internet, another key goal of the NDN project is "security by design".
+In contrast to today's Internet, a key goal of the NDN project is ``security by design".
 In fact, it goes a long way by guaranteeing the integrity and provenance of every data packet with digital signatures and protecting user-privacy with no source addresses carried in packets.
 However one big question that is yet to be answered is: How does the current NDN design fare in terms of its resilience against denial of service attacks?
-Especially since various forms of distributed denial of services (DDoS) attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial for any design aiming to replace it would be free of similar vulnerabilities.
+Especially since various forms of distributed denial of service (DDoS) attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial that any design aiming to replace it would be free of similar vulnerabilities.
 
-NDN makes data the first-class network entity and eliminates host-based addressing. That is, instead of letting end hosts send packets
-to a given IP address, NDN lets end hosts request desired
+NDN makes data the first-class network entity and eliminates host-based addressing. Instead of allowing end hosts to send packets
+to a given IP address, NDN allows end hosts to request desired
 data by sending Interest packets carrying application level
 data names. Such a shift automatically eliminates several long
-standing DDoS attacks, including both direct flooding as well
-as reflector attack through source address spoofing~\cite{mirkovic2004taxonomy}.
+standing DDoS attacks, including direct flooding as well
+as reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
 
-However, since NDN allows any host to request any data, malicious users can attack the network by sending excessive number of requests.
-Such requests are expressed by sending Interests packets in NDN and each interest leave a state on routers along its way.
-Thus, excessive number of interests can easily disrupt service by exhausting router memory.
-We coin in the term "interest flooding" to refer to such attacks and
+However, since NDN allows any host to request any data, malicious users can attack the network by sending excessive number of data requests.
+Such requests are expressed by sending Interests packets and each Interest stores state and consumes resources at intermediate routers as it is routed through the network.
+Thus, excessive number of Interests can easily disrupt service by exhausting router memory.
+We coin in the term {\it Interest flooding} to refer to such attacks and
 %One can also attack an NDN network by hijacking Interest packets and then injecting false data replies into the network.
 this paper exclusively investigates the problem and the solution space for it.
-In this important first step towards a complete investigation of denial of service attacks in NDN, we use extensive simulations to show the devastating effect of Interest flooding on vanilla NDN and how a router can exploit its state information to effectively mitigate them.
+Our effort is an important first step towards a complete investigation of denial of service attacks in NDN.
+We show the devastating effect of Interest flooding on vanilla NDN and propose three algorithms that allow routers to exploit their state information to effectively thwart these attacks.
+Through extensive simulations on real network topologies,  we show how one of our mitigation methodologies effectively shuts down malicious users while allowing legitimate users to not experience any service degradation.
+%We use extensive simulations to show the devastating effect of Interest flooding on vanilla NDN and how a router can effectively exploit its state information to effectively mitigate them. 
  %(Section~\ref{sec:design}).

### 2013-01-14 eval-large-scale.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@910 df1a90cd-247b-4364-bdaf-287a704eb499

@@
   \centering
-  \includegraphics[scale=0.15,angle=90]{7018-r0}
-  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
+  \vspace{-.1cm}\includegraphics[scale=0.15,angle=90]{7018-r0}
+  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}\vspace{-.2cm}
   \label{fig:large-scale-topo}
@@
  \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
- \caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}
+ \vspace{-.7cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.4cm}
  % producer on a gateway node

### 2013-01-14 eval-small-scale.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@910 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\begin{figure}[htbp]
+\begin{figure}[]
   \centering
@@
 
-\begin{figure}[t]
+\begin{figure}[]
   \centering
-  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
-  \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
+  \vspace{-.2cm}\hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
+  \vspace{-.5cm}\caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
   \label{fig:small-scale attack progress}
+\vspace{-.5cm}
 \end{figure}
@@
   \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
-  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}
+  \vspace{-.6cm}\caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}\vspace{-.1cm}
   \label{fig:small-scale-topo boxplot}

### 2013-01-14 01-intro.tex
Alex's "final" pass on abstract and intro section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@912 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-The Internet is a unique global success story that earmarked the information age.
-However, the design that fostered its success and wide-adaptation over the last three decades is now aged and limited in accommodating the changing demands of today's users.
+% The Internet is a unique global success story that earmarked the information age. 
+% However, the design that fostered its success and wide-adaptation over the last three decades is now aged and limited in accommodating the changing demands of today's users. 
 Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an active research effort that aims to move the Internet into the future with a new, content-centric design that is capable of efficient content distribution and seamless mobility support.
+In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in packets.
+However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against distributed denial of service (DDoS) attacks?
+Especially since various forms of DDoS attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial to ensure that the new design is free of similar vulnerabilities.
 
-In contrast to today's Internet, a key goal of the NDN project is ``security by design".
-In fact, it goes a long way by guaranteeing the integrity and provenance of every data packet with digital signatures and protecting user-privacy with no source addresses carried in packets.
-However one big question that is yet to be answered is: How does the current NDN design fare in terms of its resilience against denial of service attacks?
-Especially since various forms of distributed denial of service (DDoS) attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial that any design aiming to replace it would be free of similar vulnerabilities.
-
-NDN makes data the first-class network entity and eliminates host-based addressing. Instead of allowing end hosts to send packets
-to a given IP address, NDN allows end hosts to request desired
-data by sending Interest packets carrying application level
-data names. Such a shift automatically eliminates several long
-standing DDoS attacks, including direct flooding as well
-as reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
-
-However, since NDN allows any host to request any data, malicious users can attack the network by sending excessive number of data requests.
-Such requests are expressed by sending Interests packets and each Interest stores state and consumes resources at intermediate routers as it is routed through the network.
-Thus, excessive number of Interests can easily disrupt service by exhausting router memory.
-We coin in the term {\it Interest flooding} to refer to such attacks and
+NDN eliminates host-based addressing and makes data the first-class network entity. 
+Instead of sending packets to a given IP address, in NDN end hosts request desired data by sending Interest packets carrying application-level data names, and the network returns the requested Data packets following the path of Interests.
+Such a shift automatically eliminates several long-standing DDoS attacks, including direct flooding and reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
+%
+However, since NDN allows any host to request any data, malicious users can attack the network by sending an excessive number of Interests. 
+Because each Interest stores state and consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can easily disrupt service by congesting the network and exhausting routers' memory.
+We coin the term {\it Interest flooding} to refer to such attack and
 %One can also attack an NDN network by hijacking Interest packets and then injecting false data replies into the network.
 this paper exclusively investigates the problem and the solution space for it.
-Our effort is an important first step towards a complete investigation of denial of service attacks in NDN.
+
+Our effort is an important first step towards a complete investigation of DDoS attacks in NDN.
 We show the devastating effect of Interest flooding on vanilla NDN and propose three algorithms that allow routers to exploit their state information to effectively thwart these attacks.
-Through extensive simulations on real network topologies,  we show how one of our mitigation methodologies effectively shuts down malicious users while allowing legitimate users to not experience any service degradation.
+Through extensive simulations,  we show how one of our mitigation methodologies effectively shuts down malicious users while allowing legitimate users to not experience any service degradation.
 %We use extensive simulations to show the devastating effect of Interest flooding on vanilla NDN and how a router can effectively exploit its state information to effectively mitigate them. 
@@
 % Alex: Not sure whether it should be mentioned in intro or not.  If it should, then I don't really like it...
-The rest of the paper is organized as follows: We give an overview of NDN architecture in Section~\ref{sec:ccn-intro} and explain interest flooding attacks in Section~\ref{sec:interest-flooding}.
-In Sections~\ref{sec:design},~\ref{sec:evaluation} and~\ref{sec:discussion}, we introduce techniques to mitigate these attacks, evaluate their effectiveness and discuss their limitations respectively.
+
+% Alex: I generally don't like this section as it is does not bring anything valuable. 
+% My first candidate to be cut
+The rest of the paper is organized as follows.
+We give an overview of NDN architecture in Section~\ref{sec:ccn-intro} and explain interest flooding attacks in Section~\ref{sec:interest-flooding}.
+In Sections~\ref{sec:design},~\ref{sec:evaluation}, and~\ref{sec:discussion}, we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations respectively.
 We summarize related work in Section~\ref{sec:related-work} and finalize the paper with conclusions and future work in Section~\ref{sec:conclusion}.

### 2013-01-14 paper.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@911 df1a90cd-247b-4364-bdaf-287a704eb499
Alex's "final" pass on abstract and intro section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@912 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\title{Mitigating Interest Flooding DDoS Attacks in NDN}%:\\ Cache/Content Poisoning}
-\author{Anonymous}
+\title{Interest Flooding Attacks and countermeasures in Named Data Networking}%:\\ Cache/Content Poisoning}
+%\author{Anonymous}
 
@@
 Distributed Denial of Service attack is an ongoing problem in today's Internet, where packets from large numbers of compromised hosts thwart the paths to the victim site and/or overload the victim machines.
-In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network forwards data packets upon request only, effectively eliminating the existing DDoS attacks.
+In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network forwards Data packets upon request only, effectively eliminating many existing DDoS attacks.
 However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  
 In this paper we investigate effective solutions to mitigate Interest flooding.
-We show that NDN's inherent properties of each router keeping per packet state and flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
-Our evaluation through simulations shows that the solution can quickly and effectively respond to Interest flooding.
+We show that NDN's inherent properties to keep per packet state on each router and flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
+Our evaluation through simulations shows that the solution can quickly and effectively respond and mitigate Interest flooding.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Information-Centric Networks, Named-data Networking, Denial-of-Service
+Information-centric networks, named-data networking, denial-of-service
 \end{IEEEkeywords}

### 2013-01-14 04a-design-naive.tex
Moving text from algos/* to 04a and 04b section files. Small update on background
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@913 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\input{algos/fair-queueing.tex}
+To address the lack of fairness associated with the na\"ive {\it Token Bucket} algorithm, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring interfaces.
+For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
+%Due to the expected small volume of Interests, we cannot merely rely on network buffers to perform statistical multiplexing of Interests, as they would almost never be %buffered.
+%At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests %will arrive in the future.
+In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring interfaces, 
+%, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
+we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded and implement hierarchical queues for each interface (see Fig.~\ref{fig:queueing}). 
+This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing/incoming interface.
+%As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
+We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
+Thus, a PIT entry can be quickly updated when the Interest is actually forwarded; further the element can be quickly removed from the queue when the Interest expires.
+
+%For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}).
+%As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
+
+\begin{figure}[thb]
+  \centering
+  \includegraphics[scale=0.65]{queue}
+  \vspace{-1cm}
+  \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
+  \label{fig:queueing}
+\end{figure}
+
+We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
+By setting appropriate queue sizes we can control the amount of physical resources utilized at a router (such as memory and computation power). 
+It is also important to set apprpriate value for how long an Interest can be enqueued. 
+If an Interest is enqueued for a long time, by the time it is dequeued and appropriately forwarded, the resulting Data packet might not be valid due to state expiration at the downstream routers. 
+For our evaluations we chose to enqueue Interests up to 10\% of their original lifetime.
+% We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
+% Alex: I don't believe there is a need for separate discussion about "freshness", as we already introduced concept of lifetime
+% {\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
+
+%It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
+%Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
+%Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
+
+%The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
+%At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
+
+\floatname{algorithm}{Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Token bucket with per interface fairness}
+\label{alg:queuing}
+\begin{algorithmic}[1]
+\For{\textbf{each} interface \textbf{if}}
+    \State{$L_{if} \leftarrow$ Interest Limit according to (1)}
+    \State{$O_{if} \leftarrow 0$} \Comment{Outstanding Interests on interface \textbf{if}}
+\EndFor
+
+\vspace{0.1cm}
+
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
+    \If{$L_{out} - O_{out} > 0$} \Comment{\textbf{out} is under limit cap}
+        \State $O_{out} \leftarrow O_{out} + 1$  \Comment{``borrow'' a token from the bucket}
+        \State add \textbf{out} to PIT entry and forward \textbf{i} to \textbf{out}
+    \Else
+        \State Queue $q \leftarrow out$.GetSubQueue($in$)
+        \If{$Size(q) < L_{out}$}
+           \State $q$.PushInterest($i$)
+           \State add \textbf{out} to PIT entry, and link PIT entry with the queue
+        \Else
+           \State drop Interest
+        \EndIf
+    \EndIf
+\EndFunction
+
+\vspace{0.1cm}
+
+\State{} \Comment{\textit{Whenever $L_{out} - O_{out}$ becomes larger than zero}}
+\Function{TokenBecomesAvailable}{}
+    \State Queue $q \leftarrow$ $out$.GetRoundRobinSubQueue 
+    \State Interest $i \leftarrow$ $q$.PopInterest
+    \State update PIT entry and Forward($i$, $out$)
+\EndFunction
+
+\vspace{0.1cm}
+
+\Function{InData}{Data \textbf{d}}
+   \State lookup PIT entry \textbf{p} for data \textbf{d}
+   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
+        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
+   \EndFor
+\EndFunction
+
+\vspace{0.1cm}
+
+\Function{Timeout}{PIT entry $p$}
+   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
+        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
+   \EndFor
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from the Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
+We note that while this algorithm might be reasonable for ensuring fairness in an NDN network, it is ineffective in protecting legitimate users from malicious attackers. 
+Malicious attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of Interests.
+
+%At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
+%Therefore, to successfully solve the problem, we need a fundamentally different, more intelligent approach, allowing localization of the attack traffic as close as possible to the attack origin.
 

### 2013-01-14 04b-design-intelligent.tex
Moving text from algos/* to 04a and 04b section files. Small update on background
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@913 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\input{algos/stats.tex}
+% Note that there is a condition (line 6 in Pseudocode~\ref{alg:probabilistic model}) to check if there is a valid statistics point.
+% This condition is extremely important, because it first provides a basis to distinguish between known facts (i.e., good or bad satisfaction ratio for the incoming interface) and unknown facts (e.g., the first time an Interests arrives on the interfaces).
+% Second, it gives an opportunity to recover from a bad history (history of unsatisfied Interests) after malicious Interests are ceased to flow in.
+% Essentially, this recovery relies on statistics module to perform time-based invalidation of historical data (timely, but not too quickly\footnote{Otherwise, attackers may send short bursts of malicious Interests, successfully avoiding differential Interest treatment}).
+
+Pseudocode~\ref{algo:interest stats} formally defines how statistics can be generated for  each incoming interface.
+Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interest), only unsatisfied statistics needs to be exponentially smoothed (lines 23--26).
+
+\floatname{algorithm}{Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Interest satisfaction statistics}
+\label{algo:interest stats}
+\begin{algorithmic}[1]
+
+\For{\textbf{each} interface \textbf{if}}
+    \State $F_{if} \leftarrow 0$ \Comment{forwarded Interests from interface \textbf{if}}
+    \State $\hat F_{if} \leftarrow 0$ \Comment{averaged value of $F_{if}$}
+
+    \State $U_{if} \leftarrow 0$ \Comment{unsatisfied Interests from interface \textbf{if}}
+    \State $\hat U_{if} \leftarrow 0$ \Comment{averaged value of $U_{if}$}
+\EndFor
+
+\vspace{0.1cm}
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}}
+  \State $F_{in} \leftarrow F_{in} + 1$
+  \State record \textbf{\emph{in}} in the list of incoming interfaces for \textbf{\emph{i}}
+\EndFunction
+
+\vspace{0.1cm}
+\Function{InterestTimeout}{Interest \textbf{i}}
+    \State lookup the list of incoming interfaces for \textbf{\emph{i}}
+
+    \For{\textbf{each} interface \textbf{if} in the list}
+        \State $U_{if} \leftarrow U_{if} + 1$
+    \EndFor
+\EndFunction
+
+\vspace{0.1cm}
+
+\State {} \Comment{\textit{Exponentially weighted moving average smoothing}}
+\Function{EWMA}{} \Comment{Every second}
+\State $\alpha \leftarrow e^{-1.0/30.0}$  %\Comment{$\approx$ 30~sec average}
+
+\For{\textbf{each} interface \textbf{if}}
+    \State $\hat U_{if} \leftarrow \alpha \cdot \hat U_{if} + (1 - \alpha) \cdot U_{if}$ 
+    \State $U_{if} \leftarrow 0$
+
+    \If{$F_{if} > 0$} \Comment{To ensure decaying of ratio $U_{if}/F_{if}$}
+        \State $\hat F_{if} \leftarrow \alpha \cdot \hat F_{if} + (1 - \alpha) \cdot I_{if}$ 
+        \State $F_{if} \leftarrow 0$ \Comment{Reset counters}
+    \EndIf
+\EndFor
+
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+Fig.~\ref{fig:ratio example} illustrates the resulting dynamics of the statistic during and after an Interest flooding attack.
+The attack duration is from 10 to 70~seconds.
+Prior to start of the attack, the percentage of unsatisfied Interests is zero.
+The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
+For the duration of the attack (10--70~seconds), the percentage of unsatisfied Interests is close to 100\%: 
+when the ratio is close to 100\%, routers drop all incoming Interests, resulting in decaying of the statistics until a new Interest is admitted, which eventually brings statistics back near 100\% point.
+Finally, the ratio exponentially decays after the attack ceases.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.8]{limits}
+  \caption{Dynamics of the unsatisfied Interests statistics on gateway's interface towards the attacker}
+  \label{fig:ratio example}
+\end{figure}
 
@@
 
-\input{algos/probabilistic.tex}
+Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using this rotio to penalize malicious Interests.
+A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
+%Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
+
+\floatname{algorithm}{Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Satisfaction-based Interest acceptance}
+\label{alg:probabilistic model}
+\begin{algorithmic}[1]
+\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+
+\vspace{0.1cm}
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
+
+    \State{} \Comment{Use uniform probability distribution model $P(X)$}
+    \State{} \Comment{$P(X) : \forall x \in [0,1] \Rightarrow P(x) = x$}
+
+    \If{$F_{in} > \theta $} \Comment{At least some Interests were forwarded before}
+        \State $s \leftarrow (1 - U_{in} / F_{in})$
+        \State Drop interest with probability $P(s)$
+    \EndIf
+
+    \State{forward the Interest, subjecting to token bucket limits}
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+Parameter $\theta$ on line 5 of the Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
+This step is critical---while we want to drop Interests from attackers, we also want to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
+
+A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop the Interest. 
+As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
+In example on Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
+At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
+Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the Data producer.
+With each increasing hop in the network, the probability of being forwarded to the next hop decreases significantly.
+One way to prevent this overreaction and unfair penalization is to ensure that the decision taken at each router on whether to forward or drop the Interest is not independent of the decision taken at preceding routers.
+An explicit notification such as a gossip protocol between neighboring NDN routers that specifies the volume of Interests each router is willing to forward will likely address this issue.
+We leave the implementation and evaluation of a gossip protocol to future work.
+%{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
 
@@
 
-\input{algos/dynamic-limits.tex}
+% Differential treatment of Interests received from different interfaces can be achieved in a more elegant way, without reverting to probabilistic methods.
+
+The previous algorithm---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
+% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
+An alternate algorithm for proportional token distribution without overreaction is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
+Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.
+
+The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm will work in our example in Fig.~\ref{fig:flooding example}.
+Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node will set and announce the following  incoming interface limit $L'$:
+\begin{enumerate}
+\item router B will set and announce the incoming interface limit $L'=3$;
+\item router A, after receiving announcement from B will readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
+\item both legitimate users and adversaries may either obey or ignore the announced limit, which will be in any case enforced by router A.
+\end{enumerate}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.3]{dynamic-limits}
+  \caption{Satisfaction-based pushback example
+%: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer%
+}
+  \label{fig:dynamic limits example}
+\end{figure}
+
+\floatname{algorithm}{Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{ 
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Satisfaction-based pushback}
+\label{alg:dynamic limits}
+\begin{algorithmic}[1]
+% \State{}\Comment{Same initialization, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+\vspace{0.1cm}
+\State{$\forall f \in \mathrm{interfaces} : L'_{f} \leftarrow L_{f}$} \Comment{Per-incoming interface Interest limit}
+
+\vspace{0.1cm}
+
+\State{} \Comment{\textit{Announcement from the neighbor}}
+\Function{InLimits}{InInterface $in$, Limit $L'$}
+    \State $L_{in} \leftarrow L'$
+\EndFunction
+
+\vspace{0.1cm}
+
+\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
+\For{\textbf{each} outgoing interface $out$}
+
+   \For{\textbf{each} incoming interface $in$}
+        \State $L'_{in}= {L_{out}} \times (1 - U_{in}/F_{in})$
+        \State AnnounceLimit($in$, $L'_{in}$)
+   \EndFor
+
+\EndFor
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to the appropriate level (recall Fig.~\ref{fig:ratio example}).
+At the next iteration of the satisfaction-based pushback algorithm, the legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and will return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
+
+We note that while in the description of the satisfaction-based pushback algorithm we explicitly used ``outgoing'' and ``incoming'' interfaces,  all interfaces can be both incoming and outgoing.
+Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
+To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
+That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
+
+Both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, but with several core differences. 
+First, we are suppressing (pushing back) unwanted requests for Data, not actual Data itself.
+Second, differentiating between good and bad Interests is based on the traffic symmetry principle of NDN.
+% Alex: I'm not entirely sure about this point... 
+Finally, both intelligent attack mitigation algorithms can be deployed at all times without degrading network performance even when there are no active attackers.
 

### 2013-01-14 03-interest-flooding.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@903 df1a90cd-247b-4364-bdaf-287a704eb499
Small update on section 3
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@914 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \section{Interest Flooding Attacks in NDN}
-\label{sec:interest flooding}
+\label{sec:interest-flooding}
 
@@
 An attacker or a set of distributed attackers can inject excessive amounts of Interests to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-We coin the term \emph{Interest flooding} to refer to these network-level flooding attacks.
+%%% Alex %%% We have (almost) exactly the same sentence in the intro.
+I think here is kind of redundant, as it is obvious how we call the attack from the section title.
+Also, we are referring to the term again in the last paragraph of the section.
+% We coin the term \emph{Interest flooding} to refer to these network-level flooding attacks.
 
@@
 To efficiently implement an Interest flooding attack targeting a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
-In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and avoid being served from caches of intermediate routers: each malicious Interest generated by an individual attacker bot should request an unpopular or non-existing content (e.g., content with a unique name, \emph{unique junk Interests}).
+In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and avoid being served from caches of intermediate routers: each malicious Interest generated by an individual attacker should request an unpopular or non-existing content, e.g., content with a unique name (\emph{unique junk Interests}).
 In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network.

### 2013-01-14 05-evaluation.tex
Small reorganization of evaluation section. Some spacing changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@915 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\input{eval-small-scale}
-\input{eval-large-scale}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Small-scale evaluations}
+\label{sec:small-scale}
+
+% Topology description
+%To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a %simplistic small-scale binary tree topology 
+In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we use for our initial experiments.
+Legitimate users as well as attackers were placed on leaf nodes (red nodes) as show in the figure.
+There are 16 end users (both legitimate and attackers) in this topology, each expressing Interests that are routed towards a single data producer placed at the root of the tree.
+Each link in this topology is assigned a bandwidth of 10~Mbps and a randomized propagation delay ranging from 1 to 10 ms.
+
+% Alex: should we mention that?
+%The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS %attacks.
+%That is, sharing of the network links exponentially increases as decreasing level of the binary tree.
+
+\begin{figure}[]
+  \centering
+  \includegraphics[scale=0.2]{topo-tree-evil-5-good-0-producer-gw}
+  \caption{Small-scale binary tree topology}
+  \label{fig:small-scale}
+\end{figure}
+
+% in 10 independent runs of each simulation, where we randomized position of the adversaries along the legitimate users.
+In all runs, the total number of legitimate and malicious uses were fixed, meaning that when we increase number of attackers, we decrease the number of legitimate users.
+
+\subsubsection{Effectiveness of the three mitigation algorithms}
+
+%The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
+%For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).
+
+Our goal is to compare the effectiveness of each mitigation method and quantify the percentage of Interests satisfied for all legitimate users while the network is under attack.
+For each mitigation algorithm, we perform ten independent simulation runs, where we randomly choose 7 client nodes to represent adversaries while the remaining 9 client nodes represent legitimate users.
+In each run we simulate a 10-minute attack window (total simulation time was 30 minutes, with attack starting at the 10-minute mark).
+We plot the minimum and maximum range for observed Interest satisfaction percentages for all legitimate users aggregated across the 10 simulation runs as a function of time for each mitigation algorithm in Fig.~\ref{fig:small-scale attack progress}.
+Token bucket with per-interface fair queuing performs the worst, while satisfaction-based pushback performs the best, with almost a 100\%  satisfied Interests for all legitimate users.
+
+%A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
+
+\begin{figure}[]
+  \centering
+  \vspace{-.2cm}\hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
+  \vspace{-.5cm}\caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
+  \label{fig:small-scale attack progress}
+\vspace{-.5cm}
+\end{figure}
+
+%\paragraph{\textbf{Simple token bucket}}
+
+%{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}
+
+%Let us take a deeper look on what is happening with the simple token bucket algorithm.
+%Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as token bucket restricts the number of forwarded Intersets!).
+%This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
+%In this example we assume that both the legitimate user and the adversary send Interests in about the same time.
+%
+%\begin{figure}[t]
+%  \centering
+%  \includegraphics[scale=0.3]{physical-limits-sync-problem}
+%  \caption{Three-router topology, with one legitimate and one malicious user}
+%  \label{fig:three router example}
+%\end{figure}
+%
+%Both router L and router X will forward the Interests, as both of them have a free token available.
+%At router A, two cases are possible, either of Interests can arrive first, resulting in a quite different effects.
+%When legitimate Interest arrives first, then there are no problem. 
+%Router A will capture the token, forward the Interest, which will be quickly satisfied, releasing the token for future uses.
+%In the mean time, malicious Interest will be dropped at router A, and router X will release the hold for the token in one second (i.e., after the maximum time Interests are admitted), enabling a new round of competition for router A's resources.
+%
+%In the case when malicious Interest is sent a little bit earlier, then router A will forward malicious Interests, dropping a legitimate one, and causing ``lock out'' for one second.
+%In the instant when the token gets released at router X, an adversary is able to push new Interest towards router A, which may arrive in the exact time A's token gets released (assuming an idealistic environment).
+%As a result, the adversary recaptures router A's token and extends the ``lock out'' for another second, denying service to the legitimate user without sending any massive numbers of Interests.
+
+\paragraph{\textbf{Token bucket with per interface fairness}}
+
+We observe a successful denial of service attack, where 40\% attackers succeed in significantly shutting down the remaining 60\% legitimate users - a mere 15\% of their Interests are satisfied by Data from the producer.
+Contrary to expectations, the 60\% legitimate users do not receive at least 60\% of network resources.
+As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers, a good percentage of which traverse all the way to the data producer.
+Significantly reducing the number of Interests accepted from attackers is fundamental for improving the effectiveness of any mitigation algorithm.
+
+%The described problem arises from the clocking effect and can be solved in a number different ways.
+%Augmenting token bucket algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
+%That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
+%However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
+%Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
+%We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.
+
+\paragraph{\textbf{Satisfaction-based Interest acceptance}}
+
+The effectiveness of this algorithm stems from the fact that routers do not admit malicious Interests into the network, thereby ensuring availability of network resources for serving legitimate users.
+The observed periodic dips in the Interest satisfaction ratios of legitimate users in Fig.~\ref{fig:small-scale attack progress} is a direct result of Interest satisfaction rate statistics decaying with time.
+The 50-second period approximately corresponds to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value that ranges from 30~seconds to 50~seconds.
+%The primary reason that such minimum peaks exist is the fact that 
+When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe traffic mix from legitimate and malicious users).
+Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' to the edge.
+
+%When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
+%That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
+
+\paragraph{\textbf{Satisfaction-based pushback}}
+
+This mitigation algorithm is able to effectively shut down attackers and ensure that almost all of the Interests from legitimate users are satisfied. 
+%The only potential problem with the satisfaction-based pushback algorithm is that it features 
+We observe a  sharp dip in the satisfaction ratio curve at the start of the attack.
+It takes a few seconds for all routers to be fully aware of the attack, which happens when malicious Interests start to time out and explicit Interest limit announcements succeed in containing malicious Interests close to the attacker.
+Till then, the network for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
+Once the malicious Interests are effectively shut down, all Interests from legitimate users are satisfied.
+Unlike the satisfaction-based Interest acceptance scenario, we do not observe any periodic dips in the satisfaction curve, as the pushback algorithm effectively guarantees that once an Interest is admitted, it will almost certainly be routed to the data producer.
+
+\subsubsection{Network reaction with to varying number of attackers}
+
+Our next goal is to study the effectiveness of our mitigation algorithms as a function of increasing adversaries in the network.
+To this end, we vary the percentage of attackers in the topology from 6\% to over 50\%.
+Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
+All other parameters and experimental set-up are similar to the previous experiment.
+As before, for each mitigation algorithm, we perform ten independent simulation runs.
+%The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
+%To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.
+
+%Since at this point the overall attack dynamics of all the attack mitigation algorithms is relatively clear, 
+% In other words, each point captured in the box plot graph corresponds to 1-second averaged satisfaction ratio for a user in an individual simulation run.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
+  \vspace{-.6cm}\caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}\vspace{-.1cm}
+  \label{fig:small-scale-topo boxplot}
+\end{figure}
+
+In Fig.\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
+The results are as expected---for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
+In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.
+While both intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual.
+In the case of satisfaction-based pushback algorithm, over 90\% of Interests from legitimate users are satisfied even when over 50\% of the users are malicious.
+
+% \begin{figure}[htbp]
+%   \centering
+%   \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min-after-1-min}
+%   \caption{Average consumer Interest satisfaction ratios (second minute)}
+%   \label{fig:small-scale-topo 2}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Large scale simulations}
+\label{sec:largescale}
+
+%To check validity of the small-scale experiment results, we performed a larger-scale evaluation based on a modified version of
+
+Next, our goal is to understand the behavior of our mitigation strategies when deployed on a large-scale real network topology.
+Our ISP topology is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
+%In order to approximate the general structure of the Internet,
+% (scale-free structure, customer-provider, and peer-to-peer relations)
+We extract the largest connected component comprising of 562 nodes from this original topology and separate the nodes into three categories: clients, gateways, and backbones.
+Nodes having degree than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes as classified as backbones (109 blue nodes).
+%(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
+We assign bandwidth and  delay values to links based on their type---both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
+We experiment with placing the data producer at both a gateway node as well as backbone node, which we randomly pick for each simulation run.
+Similar to the binary tree topology experiments, we fix the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly pick these nodes for each simulation run.
+We conduct 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5 minute interval.
+
+\begin{figure}[htbp]
+  \centering
+  \vspace{-.1cm}\includegraphics[scale=0.15,angle=90]{7018-r0}
+  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}\vspace{-.2cm}
+  \label{fig:large-scale-topo}
+\end{figure}
+
+\begin{table}[htbp]
+\centering
+\caption{Large-scale topology link bandwidth and delay ranges}
+\label{tab:large-scale}
+\begin{tabular}{|l||c|c||c|c|}
+  \hline
+  \multirow{2}{*}{\bf Link type} &  \multicolumn{2}{|c||}{\bf Delay} &  \multicolumn{2}{|c|}{\bf Bandwidth} \tabularnewline
+  \cline{2-5}
+                        &  Min & Max                       &  Min & Max \tabularnewline
+  \hline \hline
+  Backbone--Backbone    & 5~ms & 10~ms   & 40~Mbps & 100~Mbps \tabularnewline
+  \hline
+  Gateway--Backbone,    & \multirow{2}{*}{5~ms} & \multirow{2}{*}{10~ms}   
+                        & \multirow{2}{*}{10~Mbps} & \multirow{2}{*}{20~Mbps} \tabularnewline
+  Gateway--Gateway      & & & & \\
+  \hline
+  Client--Gateway       & 10~ms & 70~ms   & 1~Mbps  & 3~Mbps \\
+  \hline
+
+\end{tabular}
+\end{table}
+
+%Priya: Leaving out this in the interest of space...
+%Topological location of the data producer plays a key role in its resilience to Interest flooding attacks.
+For a data producer that %is connected to a client node via a low-bandwidth link, even a small number of junk Interests can impact services for legitimate %users.
+For a producer located at the backbone with rich connectivity through many high-bandwidth links, an attack might not %be as severe as a majority of legitimate users might not be on the attack path.
+
+% The results for all attack mitigation algorithms and all runs are aggregated in Fig.~\ref{fig:small-scale attack progress}, where Y-axis represents a minimum and maximum range for observed Interest satisfaction percentages among all nodes and all simulation runs.
+% A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
+
+In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over 10 simulations runs for each mitigation algorithm for the scenario where the data producer is placed at a gateway node.
+We observe similar results for the data producer placed at the backbone node as well.
+As in the case of the binary-tree topology experiments, token bucket with per interface fairness is the most ineffective algorithm and satisfaction-based pushback is the most effective one.
+Interest satisfaction percentage for legitimate users are approximately 25\% and almost 100\% respectively for these two mitigation methodologies.
+
+%
+%The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
+
+\begin{figure}[tbh]
+ \centering
+ \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
+ \vspace{-.7cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.4cm}
+ % producer on a gateway node
+ \label{fig:large-scale}
+\end{figure}
+
+Satisfaction-based Interest acceptance algorithm, which was very effective for binary-tree topology, is completely ineffective when deployed in a larger realistic topology.
+For the duration of the attack, legitimate users experience poor quality of service with only 25\% of their Interests being satisfied and continue to experience degraded service long after the attack has stopped.
+This poor performance, as detailed in  in Section~\ref{sec:probabilistic}, is due to the fact that each router in the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
+In the case of the larger-topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics, which in turn leads to further penalization of new Interests from them.
+
+To summarize, in all of our simulations, the satisfaction-based pushback algorithm is the most effective technique as it restricts malicious Interests from even entering the network. 
+%The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
+As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.
+
+% Alex: Anything else here?
+
+% Alex: I also experimented with placing producer at the backbone, getting slightly better results for all algorithms.  Though I'm not sure there is any value to put those results in the paper
 

### 2013-01-14 05-evaluation.tex
Small spacing changes (there was text overlapping on figures)
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@916 df1a90cd-247b-4364-bdaf-287a704eb499

@@
   \centering
-  \vspace{-.2cm}\hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
-  \vspace{-.5cm}\caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
+  \hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
+  \vspace{-.3cm}
+  \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
   \label{fig:small-scale attack progress}
-\vspace{-.5cm}
+  \vspace{-.4cm}
 \end{figure}
@@
   \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
-  \vspace{-.6cm}\caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}\vspace{-.1cm}
+  \vspace{-.3cm}
+  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}\vspace{-.1cm}
   \label{fig:small-scale-topo boxplot}
@@
  \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
- \vspace{-.7cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.4cm}
+ \vspace{-.3cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.4cm}
  % producer on a gateway node

### 2013-01-14 04a-design-naive.tex
Small reorganization of evaluation section. Some spacing changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@915 df1a90cd-247b-4364-bdaf-287a704eb499
My pass on section 4 and 5
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@917 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 The flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
-This principle allows intermediate routers to control the inbound Data traffic by controlling the number of outstanding Interests in the network.
-One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding out interface.
+This principle allows intermediate routers to control the inbound data traffic by controlling the number of outstanding Interests in the network.
+One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding interface.
 This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet switched networks.
-Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of Data requested that can fully utilize the downstream link (estimated from the number of Interests it forwarded) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
+Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
 Ideally, the number of tokens (the pending \emph{Interests Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
@@
 
-This {\it Token Bucket} approach might be exceptionally retrictive in forwarding Interests---not all Interests will result in a Data packet---thus underutilizing the network.
-However, the biggest drawback of the algorithm is that it can be used as an effective mechanism to carry out denial of service attacks.
+This {\it Token Bucket} approach might be exceptionally retrictive in forwarding Interests---not all Interests will result in a Data packet---thus, the network can be underutilized.
+However, the biggest drawback of the algorithm is that it itself can be used as an effective mechanism to carry out DDoS attacks.
 If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
@@
 
-To address the lack of fairness associated with the na\"ive {\it Token Bucket} algorithm, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring interfaces.
+To address the lack of fairness associated with the na\"ive {\it Token Bucket} algorithm, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring nodes.
 For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
@@
 %At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests %will arrive in the future.
-In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring interfaces, 
+In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring nodes, 
 %, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
 we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded and implement hierarchical queues for each interface (see Fig.~\ref{fig:queueing}). 
-This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing/incoming interface.
+This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing and incoming interface.
 %As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
@@
   \includegraphics[scale=0.65]{queue}
-  \vspace{-1cm}
+  \vspace{-0.7cm}
   \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
@@
 We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
-By setting appropriate queue sizes we can control the amount of physical resources utilized at a router (such as memory and computation power). 
-It is also important to set apprpriate value for how long an Interest can be enqueued. 
-If an Interest is enqueued for a long time, by the time it is dequeued and appropriately forwarded, the resulting Data packet might not be valid due to state expiration at the downstream routers. 
+By setting appropriate queue sizes we can control the amount of physical resources utilized at a router.
+ % (such as memory and computation power). 
+It is also important to set appropriate value for how long an Interest can be enqueued. 
+If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet could be dropped later due to state expiration at the downstream routers. 
 For our evaluations we chose to enqueue Interests up to 10\% of their original lifetime.
@@
 
-\floatname{algorithm}{Pseudocode}
+\floatname{algorithm}{\small Pseudocode}
 
@@
 As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from the Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
-We note that while this algorithm might be reasonable for ensuring fairness in an NDN network, it is ineffective in protecting legitimate users from malicious attackers. 
+We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is ineffective in protecting legitimate users from malicious attackers. 
 Malicious attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of Interests.
@@
 For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and effectively drop only malicious requests for content.
-`Good' Interests from legitimate users must be admited and forwarded appropriately.
+% `Good' Interests from legitimate users must be admited and forwarded appropriately. 
 The key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
@@
 
-In NDN one cannot easily distinguish a `good' prefix from a `bad' one.
+{\color{red} \textbf{Alex: This paragraph is confusing to me.
+I would remove it.} In NDN one cannot easily distinguish a `good' prefix from a `bad' one.
 Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
 Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the prefix name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
+}
 

### 2013-01-14 04b-design-intelligent.tex
Small reorganization of evaluation section. Some spacing changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@915 df1a90cd-247b-4364-bdaf-287a704eb499
Small spacing changes (there was text overlapping on figures)
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@916 df1a90cd-247b-4364-bdaf-287a704eb499
My pass on section 4 and 5
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@917 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
-Therefore, intermediate routers can classify all Interests that result in matching Data as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest flooding}).}
+Therefore, intermediate routers can classify all Interests that result in matching Data as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}
 %Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
@@
 Prior to start of the attack, the percentage of unsatisfied Interests is zero.
-The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
+The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.%\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
 For the duration of the attack (10--70~seconds), the percentage of unsatisfied Interests is close to 100\%: 
@@
   \includegraphics[scale=0.8]{limits}
+  \vspace{-0.3cm}
   \caption{Dynamics of the unsatisfied Interests statistics on gateway's interface towards the attacker}
@@
 At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
-Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the Data producer.
+Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the data producer.
 With each increasing hop in the network, the probability of being forwarded to the next hop decreases significantly.
@@
   \includegraphics[scale=0.3]{dynamic-limits}
+  \vspace{-0.3cm}
   \caption{Satisfaction-based pushback example
@@
 Both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, but with several core differences. 
-First, we are suppressing (pushing back) unwanted requests for Data, not actual Data itself.
+First, we are suppressing (pushing back) unwanted requests for data, not actual data itself.
 Second, differentiating between good and bad Interests is based on the traffic symmetry principle of NDN.

### 2013-01-14 05-evaluation.tex
My pass on section 4 and 5
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@917 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 In this section, we present an in-depth evaluation study, aiming to quantify the effectiveness of all our Interest flooding attack mitigation methods.
-We use the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator\footnote{\url{http://www.nsnam.org/}}, to run simulations for a variety of network topologies and scenarios.
-We implement our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback---in ndnSIM.
-For evaluating the effectiveness of each mitigation algorithm, every router in the simulated topology runs the mitigation algorithm under study.
+We used the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator (\url{http://www.nsnam.org/}), to run simulations for a variety of network topologies and scenarios.
+We extended ndnSIM with our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback---and evaluated effectiveness of each algorithm independently.
+
+% For evaluating the effectiveness of each mitigation algorithm, every router in the simulated topology runs the mitigation algorithm under study.
 
@@
 
-The metric we choose to quantify the effectiveness of our defense strategies is the {\it percentage of satisfied Interests for legitimate users}.
+The metric we choose to quantify the effectiveness of our algorithms is the {\it percentage of satisfied Interests for legitimate users}.
 This metric corresponds to the quality of service experienced by legitimate users when the network is under attack.
@@
 
-We ran our simulations on two different network topologies---a smaller binary tree topology and a much larger ISP topology.
+We ran our simulations on two different network topologies---a smaller binary tree topology and a much larger ISP-like topology.
 We use a binary tree topology as it represents one of the worst cases to defend against Interest flooding DDoS attacks.
 The larger ISP topology reflects how our mitigation methods would perform when deployed on the real Internet.
-Again, to study the performance of our mitigation strategies under a range of conditions, we also varied the percentage of attackers in the network - the values ranged from 6\% attackers to over 50\% attackers in the network.
+Again, to study the performance of our mitigation strategies under a range of conditions, we also varied the percentage of attackers in the network---the values ranged from 6\% attackers to over 50\% attackers in the network.
 
@@
 %To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a %simplistic small-scale binary tree topology 
-In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we use for our initial experiments.
+In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we used for our initial experiments.
 Legitimate users as well as attackers were placed on leaf nodes (red nodes) as show in the figure.
@@
 Our goal is to compare the effectiveness of each mitigation method and quantify the percentage of Interests satisfied for all legitimate users while the network is under attack.
-For each mitigation algorithm, we perform ten independent simulation runs, where we randomly choose 7 client nodes to represent adversaries while the remaining 9 client nodes represent legitimate users.
+For each mitigation algorithm, we perform 10 independent simulation runs, where we randomly choose 7 client nodes to represent adversaries while the remaining 9 client nodes represent legitimate users.
 In each run we simulate a 10-minute attack window (total simulation time was 30 minutes, with attack starting at the 10-minute mark).
@@
 
-We observe a successful denial of service attack, where 40\% attackers succeed in significantly shutting down the remaining 60\% legitimate users - a mere 15\% of their Interests are satisfied by Data from the producer.
+We observe a successful DDoS attack, where 40\% attackers succeed in significantly shutting down the remaining 60\% legitimate users---a mere 15\% of their Interests are satisfied by Data from the producer.
 Contrary to expectations, the 60\% legitimate users do not receive at least 60\% of network resources.
 As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers, a good percentage of which traverse all the way to the data producer.
-Significantly reducing the number of Interests accepted from attackers is fundamental for improving the effectiveness of any mitigation algorithm.
+Significantly reducing the number of accepted malicious Interests is fundamental for improving the effectiveness of any mitigation algorithm.
 
@@
 All other parameters and experimental set-up are similar to the previous experiment.
-As before, for each mitigation algorithm, we perform ten independent simulation runs.
+As before, for each mitigation algorithm, we perform 10 independent simulation runs.
 %The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
@@
 In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.
-While both intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual.
+While both intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
 In the case of satisfaction-based pushback algorithm, over 90\% of Interests from legitimate users are satisfied even when over 50\% of the users are malicious.
@@
 We extract the largest connected component comprising of 562 nodes from this original topology and separate the nodes into three categories: clients, gateways, and backbones.
-Nodes having degree than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes as classified as backbones (109 blue nodes).
+Nodes having degree less than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes as classified as backbones (109 blue nodes).
 %(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
@@
 Similar to the binary tree topology experiments, we fix the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly pick these nodes for each simulation run.
-We conduct 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5 minute interval.
+We conduct 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5-minute interval.
 
@@
   \centering
-  \vspace{-.1cm}\includegraphics[scale=0.15,angle=90]{7018-r0}
+  \vspace{-.1cm}\includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
   \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}\vspace{-.2cm}
@@
 
-In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over 10 simulations runs for each mitigation algorithm for the scenario where the data producer is placed at a gateway node.
+In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over 10 simulations runs for each mitigation algorithm for the scenario, where the data producer is placed at a gateway node.
 We observe similar results for the data producer placed at the backbone node as well.

### 2013-01-14 04-design.tex
Semi-finalized dynamic limits section, which finally completes the whole design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@865 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@918 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-05 04-design.tex
@@
 
-In this section we present several methods to mitigate Interest flooding attacks in NDN, featuring different degrees of implementation complexity, as well as different degrees of effectiveness.
+In this section we present several algorithms to mitigate Interest flooding attacks in NDN.
+Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
+We start by describing our simple strategies and use the insights and lessons learnt from the deployment of these techniques to inform and design more effective mitigation techniques that can work well in a variety of attack scenarios.
 
@@
 
-Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
-Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
-Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
-At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
+%The fact that each Data packet takes the reverse path of the corresponding Interest packet allows intermediate routers to match a received Data packet to the corresponding Interest packet and %thus determine which Interest packets were satisfied.
+As we describe in the rest of this section,  NDN routers can exploit this information to make informed decisions on which Interest packets to %forward, how many Interest packets to forward, and thus effectively defend against DDoS attacks.
 
-\subsection{Na\"{i}ve attack mitigation}
+%Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
+%Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
+%Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
+%At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
+
+%\subsection{Na\"{i}ve attack mitigation}
+
+%We start with a couple of naive strategies that can be used to migitate attacks in an NDN network and describe the pitfalls associated with these strategies.
 
@@
 
-The most obvious and na\"{i}ve method to mitigate the Interest flooding attack is to limit the number of forwarded Interests out of each interface. 
-That is, if it is known that the amount of already forwarded Interests can fully utilize the downstream link, an NDN node---an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
-For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
-In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
+An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests that are forwarded in the network. To this end, we exploit a 
+ fundamental principle of NDN architecture---flow balance between Interest and Data packets.
+The flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
+This principle allows intermediate routers to control the inbound data traffic by controlling the number of outstanding Interests in the network.
+One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding interface.
+This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet switched networks.
+Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
+Ideally, the number of tokens (the pending \emph{Interests Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
+We can formalize this value as follows:
+% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
+%
+\begin{equation}
+\small \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
+\end{equation}
 
-\subsubsection{Interest limits (physical limits)}
-\label{sec:physical limits}
+In the above equation, \emph{Delay} is the expected time of Interest being satisfied and \emph{Data packet size} is the size of the returned Data packet.
+Although both these values are not known a priori, it is not really necessary to use their exact values.
+One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as the network buffers can smooth out most of the network fluctuations.
 
-\input{algos/physical-limits.tex}
+This {\it Token Bucket} approach might be exceptionally retrictive in forwarding Interests---not all Interests will result in a Data packet---thus, the network can be underutilized.
+However, the biggest drawback of the algorithm is that it itself can be used as an effective mechanism to carry out DDoS attacks.
+If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
+One way to get around this issue is to impose a per interface limit, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
+We describe this technique in greater detail below.
+
+%That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
+%For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
+%In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
+%
+%\subsubsection{\textbf{Interest limits (physical limits)}}
+%\label{sec:physical limits}
+%
+%\input{algos/physical-limits.tex}
 
@@
 
-\subsubsection{Interest limits with per-interface fairness}
+\subsubsection{\textbf{Token bucket with per interface fairness}}
 \label{sec:queuing}
 
-\input{algos/fair-queueing.tex}
+To address the lack of fairness associated with the na\"ive {\it Token Bucket} algorithm, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring nodes.
+For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
+%Due to the expected small volume of Interests, we cannot merely rely on network buffers to perform statistical multiplexing of Interests, as they would almost never be %buffered.
+%At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests %will arrive in the future.
+In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring nodes, 
+%, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
+we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded and implement hierarchical queues for each interface (see Fig.~\ref{fig:queueing}). 
+This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing and incoming interface.
+%As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
+We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
+Thus, a PIT entry can be quickly updated when the Interest is actually forwarded; further the element can be quickly removed from the queue when the Interest expires.
+
+%For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}).
+%As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
+
+\begin{figure}[thb]
+  \centering
+  \includegraphics[scale=0.65]{queue}
+  \vspace{-0.7cm}
+  \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
+  \label{fig:queueing}
+\end{figure}
+
+We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
+By setting appropriate queue sizes we can control the amount of physical resources utilized at a router.
+ % (such as memory and computation power). 
+It is also important to set appropriate value for how long an Interest can be enqueued. 
+If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet could be dropped later due to state expiration at the downstream routers. 
+For our evaluations we chose to enqueue Interests up to 10\% of their original lifetime.
+% We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
+% Alex: I don't believe there is a need for separate discussion about "freshness", as we already introduced concept of lifetime
+% {\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
+
+%It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
+%Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
+%Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
+
+%The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
+%At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
+
+\floatname{algorithm}{\small Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Token bucket with per interface fairness}
+\label{alg:queuing}
+\begin{algorithmic}[1]
+\For{\textbf{each} interface \textbf{if}}
+    \State{$L_{if} \leftarrow$ Interest Limit according to (1)}
+    \State{$O_{if} \leftarrow 0$} \Comment{Outstanding Interests on interface \textbf{if}}
+\EndFor
+
+\vspace{0.1cm}
+
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
+    \If{$L_{out} - O_{out} > 0$} \Comment{\textbf{out} is under limit cap}
+        \State $O_{out} \leftarrow O_{out} + 1$  \Comment{``borrow'' a token from the bucket}
+        \State add \textbf{out} to PIT entry and forward \textbf{i} to \textbf{out}
+    \Else
+        \State Queue $q \leftarrow out$.GetSubQueue($in$)
+        \If{$Size(q) < L_{out}$}
+           \State $q$.PushInterest($i$)
+           \State add \textbf{out} to PIT entry, and link PIT entry with the queue
+        \Else
+           \State drop Interest
+        \EndIf
+    \EndIf
+\EndFunction
+
+\vspace{0.1cm}
+
+\State{} \Comment{\textit{Whenever $L_{out} - O_{out}$ becomes larger than zero}}
+\Function{TokenBecomesAvailable}{}
+    \State Queue $q \leftarrow$ $out$.GetRoundRobinSubQueue 
+    \State Interest $i \leftarrow$ $q$.PopInterest
+    \State update PIT entry and Forward($i$, $out$)
+\EndFunction
+
+\vspace{0.1cm}
+
+\Function{InData}{Data \textbf{d}}
+   \State lookup PIT entry \textbf{p} for data \textbf{d}
+   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
+        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
+   \EndFor
+\EndFunction
+
+\vspace{0.1cm}
+
+\Function{Timeout}{PIT entry $p$}
+   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
+        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
+   \EndFor
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from the Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
+We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is ineffective in protecting legitimate users from malicious attackers. 
+Malicious attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of Interests.
+
+%At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
+%Therefore, to successfully solve the problem, we need a fundamentally different, more intelligent approach, allowing localization of the attack traffic as close as possible to the attack origin.
 
@@
 
+The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it admits Interests from malicious users.
+A sizeable percentage of these malicious Interests are forwarded all the way to content producers, thereby utilizing scarce network resources and reducing resources available to serve legitimate users.
+This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate Interests as well as malicious Interests.
+For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and effectively drop only malicious requests for content.
+% `Good' Interests from legitimate users must be admited and forwarded appropriately. 
+The key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
+
+%One can try a black- or whitelisting approach.
+However, besides the fact that source black- and whitelisting cannot work in %NDN as it does not feature source addresses, it requires extraneous knowledge to classify the incoming Interests.
+
+%Priya: I have added the below point specifically to point out that a router cannot determine from the prefix name alone whether /parc is good  or bad...
+
+%{\color{red} \textbf{Alex: This paragraph is confusing to me.
+I would remove it.} In NDN one cannot easily distinguish a `good' prefix from a `bad' one.
+Content producers must be able to support %dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded %to the producer for possible dynamic Data packet generation.
+%Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the prefix name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain %namespaces  will be inefficient and likely ineffective.
+}
+
+% Alex: I'm not sure that this part is relevant... The point I see is that blacklisting and whitelisting is not 100% effective, but it can be used in both worlds
+
+% In today's host-based Internet architecture where DDoS mitigation techniques rely on blacklisting of ``dark'' IP prefixes or whitelisting of good IP prefixes.
+% Unlike IP, in NDN one cannot easily distinguish a `good' prefix from a `bad' one. 
+% Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
+% Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
+
 \subsection{Intelligent attack mitigation}
+\label{sec:intelligent mitigating}
 
-About additional knowledge about interests.
+%While the Interest limit is the key building block to suppress mechanisms of the Interest flooding attack, legitimate Interests need to be somehow prioritized and malicious Interests need to be somehow penalized in order to completely suppress the attack.
+%That is, instead of processing Interests always based on the first-in-first-serve rule, NDN routers need some basis to treat the incoming Interests differently.
+%Thus, the primary task in bringing intelligence to the Interest flooding attack mitigation is to proactively distinguish between legitimate and malicious Interests.
 
-Another unique feature of the NDN architecture is stateful packet forwarding~\cite{adaptive-forwarding} and symmetric flow of Interests and Data packets.
-Every time Interests is send out to the Interface, the router will be able to learn various parameters about this Interest.
+In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets.
+Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guarateed to see if an Interest it forwarded resulted in a matching Data packet.
+The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
+Therefore, intermediate routers can classify all Interests that result in matching Data as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}
+%Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
 
-From the DDoS mitigation point of view, one of the important parameters is to determine from which interface
+This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
+However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest must be forwarded or dropped.
+For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout.
+Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
+that can further improve the estimates.
+A router's goal should be to penalize malicious Interests as soon as possible---negative statistics should be allowed to build up fast, while positive statistics should not be allowed to deteriorate too quickly.
+We use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window to achieve the above goal.
 
-In order to mitigate a denial of service attack it is vital to know the origin of the attack.
-I the origin of the attack is known, then the attack can be easily suppressed and eventually localized.
-In our definition of the attack is that
+%Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
+%{\color{red} \it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong %here.}
 
-interest of the attackers are not getting satisfied. 
-Every router can learn fro m which interfaces attack traffic is coming and do certain actions to limit forwarding of suspicious interest.
-In other words, without trying to distinguish legitimate and malicious interests on the basis of the Interest prefix, routers distinguish them based on recent performance.
+%The devil is always in the details.
+%From the one hand, such statistics needs to start penalizing adversaries as soon as possible (i.e., negative stats should build up fast).
+%On the other hand, the positive statistics should not deteriorate too fast (i.e., positive stats should be relatively long-term).
+%Our preliminary experiments showed that the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window, provides a good balance between the two contradictory requirements.
 
-\subsubsection{Data plane performance tracking}
-\label{sec:stats}
+% \subsubsection{\textbf{Data plane performance tracking}}
+% \label{sec:stats}
 
-\input{algos/stats.tex}
+% Note that there is a condition (line 6 in Pseudocode~\ref{alg:probabilistic model}) to check if there is a valid statistics point.
+% This condition is extremely important, because it first provides a basis to distinguish between known facts (i.e., good or bad satisfaction ratio for the incoming interface) and unknown facts (e.g., the first time an Interests arrives on the interfaces).
+% Second, it gives an opportunity to recover from a bad history (history of unsatisfied Interests) after malicious Interests are ceased to flow in.
+% Essentially, this recovery relies on statistics module to perform time-based invalidation of historical data (timely, but not too quickly\footnote{Otherwise, attackers may send short bursts of malicious Interests, successfully avoiding differential Interest treatment}).
+
+Pseudocode~\ref{algo:interest stats} formally defines how statistics can be generated for  each incoming interface.
+Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interest), only unsatisfied statistics needs to be exponentially smoothed (lines 23--26).
+
+\floatname{algorithm}{\small Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Interest satisfaction statistics}
+\label{algo:interest stats}
+\begin{algorithmic}[1]
+
+\For{\textbf{each} interface \textbf{if}}
+    \State $F_{if} \leftarrow 0$ \Comment{forwarded Interests from interface \textbf{if}}
+    \State $\hat F_{if} \leftarrow 0$ \Comment{averaged value of $F_{if}$}
+
+    \State $U_{if} \leftarrow 0$ \Comment{unsatisfied Interests from interface \textbf{if}}
+    \State $\hat U_{if} \leftarrow 0$ \Comment{averaged value of $U_{if}$}
+\EndFor
+
+\vspace{0.1cm}
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}}
+  \State $F_{in} \leftarrow F_{in} + 1$
+  \State record \textbf{\emph{in}} in the list of incoming interfaces for \textbf{\emph{i}}
+\EndFunction
+
+\vspace{0.1cm}
+\Function{InterestTimeout}{Interest \textbf{i}}
+    \State lookup the list of incoming interfaces for \textbf{\emph{i}}
+
+    \For{\textbf{each} interface \textbf{if} in the list}
+        \State $U_{if} \leftarrow U_{if} + 1$
+    \EndFor
+\EndFunction
+
+\vspace{0.1cm}
+
+\State {} \Comment{\textit{Exponentially weighted moving average smoothing}}
+\Function{EWMA}{} \Comment{Every second}
+\State $\alpha \leftarrow e^{-1.0/30.0}$  %\Comment{$\approx$ 30~sec average}
+
+\For{\textbf{each} interface \textbf{if}}
+    \State $\hat U_{if} \leftarrow \alpha \cdot \hat U_{if} + (1 - \alpha) \cdot U_{if}$ 
+    \State $U_{if} \leftarrow 0$
+
+    \If{$F_{if} > 0$} \Comment{To ensure decaying of ratio $U_{if}/F_{if}$}
+        \State $\hat F_{if} \leftarrow \alpha \cdot \hat F_{if} + (1 - \alpha) \cdot I_{if}$ 
+        \State $F_{if} \leftarrow 0$ \Comment{Reset counters}
+    \EndIf
+\EndFor
+
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+Fig.~\ref{fig:ratio example} illustrates the resulting dynamics of the statistic during and after an Interest flooding attack.
+The attack duration is from 10 to 70~seconds.
+Prior to start of the attack, the percentage of unsatisfied Interests is zero.
+The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.%\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
+For the duration of the attack (10--70~seconds), the percentage of unsatisfied Interests is close to 100\%: 
+when the ratio is close to 100\%, routers drop all incoming Interests, resulting in decaying of the statistics until a new Interest is admitted, which eventually brings statistics back near 100\% point.
+Finally, the ratio exponentially decays after the attack ceases.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.8]{limits}
+  \vspace{-0.3cm}
+  \caption{Dynamics of the unsatisfied Interests statistics on gateway's interface towards the attacker}
+  \label{fig:ratio example}
+\end{figure}
 
@@
 
-\subsubsection{Probabilistic Interest accept}
+\subsubsection{\textbf{Satisfaction-based Interest acceptance}}
 \label{sec:probabilistic}
 
-\input{algos/probabilistic.tex}
+Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using this rotio to penalize malicious Interests.
+A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
+%Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
+
+\floatname{algorithm}{\small Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Satisfaction-based Interest acceptance}
+\label{alg:probabilistic model}
+\begin{algorithmic}[1]
+\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+
+\vspace{0.1cm}
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
+
+    \State{} \Comment{Use uniform probability distribution model $P(X)$}
+    \State{} \Comment{$P(X) : \forall x \in [0,1] \Rightarrow P(x) = x$}
+
+    \If{$F_{in} > \theta $} \Comment{At least some Interests were forwarded before}
+        \State $s \leftarrow (1 - U_{in} / F_{in})$
+        \State Drop interest with probability $P(s)$
+    \EndIf
+
+    \State{forward the Interest, subjecting to token bucket limits}
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+Parameter $\theta$ on line 5 of the Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
+This step is critical---while we want to drop Interests from attackers, we also want to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
+
+A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop the Interest. 
+As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
+In example on Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
+At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
+Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the data producer.
+With each increasing hop in the network, the probability of being forwarded to the next hop decreases significantly.
+One way to prevent this overreaction and unfair penalization is to ensure that the decision taken at each router on whether to forward or drop the Interest is not independent of the decision taken at preceding routers.
+An explicit notification such as a gossip protocol between neighboring NDN routers that specifies the volume of Interests each router is willing to forward will likely address this issue.
+We leave the implementation and evaluation of a gossip protocol to future work.
+%{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
 
@@
 
-\subsubsection{Dynamic adjustments of window-based limits}
+\subsubsection{\textbf{Satisfaction-based pushback}}
 \label{sec:dynamic limits}
 
-\input{algos/dynamic-limits.tex}
+% Differential treatment of Interests received from different interfaces can be achieved in a more elegant way, without reverting to probabilistic methods.
+
+The previous algorithm---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
+% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
+An alternate algorithm for proportional token distribution without overreaction is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
+Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.
+
+The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm will work in our example in Fig.~\ref{fig:flooding example}.
+Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node will set and announce the following  incoming interface limit $L'$:
+\begin{enumerate}
+\item router B will set and announce the incoming interface limit $L'=3$;
+\item router A, after receiving announcement from B will readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
+\item both legitimate users and adversaries may either obey or ignore the announced limit, which will be in any case enforced by router A.
+\end{enumerate}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.3]{dynamic-limits}
+  \vspace{-0.3cm}
+  \caption{Satisfaction-based pushback example
+%: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer%
+}
+  \label{fig:dynamic limits example}
+\end{figure}
+
+\floatname{algorithm}{\small Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{ 
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Satisfaction-based pushback}
+\label{alg:dynamic limits}
+\begin{algorithmic}[1]
+% \State{}\Comment{Same initialization, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+\vspace{0.1cm}
+\State{$\forall f \in \mathrm{interfaces} : L'_{f} \leftarrow L_{f}$} \Comment{Per-incoming interface Interest limit}
+
+\vspace{0.1cm}
+
+\State{} \Comment{\textit{Announcement from the neighbor}}
+\Function{InLimits}{InInterface $in$, Limit $L'$}
+    \State $L_{in} \leftarrow L'$
+\EndFunction
+
+\vspace{0.1cm}
+
+\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
+\For{\textbf{each} outgoing interface $out$}
+
+   \For{\textbf{each} incoming interface $in$}
+        \State $L'_{in}= {L_{out}} \times (1 - U_{in}/F_{in})$
+        \State AnnounceLimit($in$, $L'_{in}$)
+   \EndFor
+
+\EndFor
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to the appropriate level (recall Fig.~\ref{fig:ratio example}).
+At the next iteration of the satisfaction-based pushback algorithm, the legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and will return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
+
+We note that while in the description of the satisfaction-based pushback algorithm we explicitly used ``outgoing'' and ``incoming'' interfaces,  all interfaces can be both incoming and outgoing.
+Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
+To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
+That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
+
+Both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, but with several core differences. 
+First, we are suppressing (pushing back) unwanted requests for data, not actual data itself.
+Second, differentiating between good and bad Interests is based on the traffic symmetry principle of NDN.
+% Alex: I'm not entirely sure about this point... 
+Finally, both intelligent attack mitigation algorithms can be deployed at all times without degrading network performance even when there are no active attackers.
 

### 2013-01-14 04-design.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@919 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
-We start by describing our simple strategies and use the insights and lessons learnt from the deployment of these techniques to inform and design more effective mitigation techniques that can work well in a variety of attack scenarios.
+We start by describing our simple strategies and use the insights and lessons learned from the deployment of these techniques to inform and design more effective mitigation techniques that can work well in a variety of attack scenarios.
 
@@
 In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets.
-Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guarateed to see if an Interest it forwarded resulted in a matching Data packet.
-The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
-Therefore, intermediate routers can classify all Interests that result in matching Data as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}
+Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guaranteed to see if an Interest it forwarded resulted in a matching Data packet or times out.
+%The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
+Since malicious Interests are not likely to bring data back (as discussed in Section~\ref{sec:interest-flooding}), this information can be utilized by routers in differentiating attack and legitimate traffic.
+%Therefore, intermediate routers can classify the ones that brings data back as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}
 %Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
@@
 This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
-However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest must be forwarded or dropped.
+However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest should be forwarded or dropped.
 For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout.
@@
 that can further improve the estimates.
-A router's goal should be to penalize malicious Interests as soon as possible---negative statistics should be allowed to build up fast, while positive statistics should not be allowed to deteriorate too quickly.
-We use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window to achieve the above goal.
+A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but don't generate a Data stream in return.
+In order to allow negative statistics to build up fast and positive statistics deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.
 

### 2013-01-14 05-evaluation.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@919 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: "paper"
-%%% End:
+\subsection{Limitations}
+{\color{red} I gave up the idea of seperate discussion section as after trying for some time, I realized there is no way to write a reasonably comprehensive and acceptably broad discussion section that touches on algorithms, evaluation and methodology, etc.
+So, I decided to get rid of it and only have a scoped down version here that confesses upon the limiations of our evaluations.
+Whoever has time, please go ahead and write 1-2 paragraphs as outlined below}
+
+This section should roughly say: Our results show that the two features, namely the symmetric traffic and stateful routing, give NDN routers the ability to observe and characterize traffic in real time.
+Through our evaluations, we demonstrated that a mitigation algorithm that leverages such ability has great potential in mitigating various DDoS attacks that could otherwise have grave effect on the network.
+However, as the first step in exploring the problem and the solution space, this paper has obvious limitations: (1) We assume a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations.
+Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step is evaluating the above described solutions with more sophisticated and adaptive attackers.
+(2)   Although most (such as single-path routing, no-caches in the network, single homed victim, etc) are aimed to test the proposed solutions under worst-case scenario, we made many assumptions in simulations/evaluations about the configurations, topology and the traffic that maybe poor-representative of realistic conditions.
+(3) As NDN being an ongoing research effort itself, our evaluations fully depend on simulations and done over a snapshot of its codebase.

### 2013-01-14 paper.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@918 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@919 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\title{Interest Flooding Attacks and countermeasures in Named Data Networking}%:\\ Cache/Content Poisoning}
-%\author{Anonymous}
+\title{Interest Flooding Attacks and Countermeasures in Named Data Networking}%:\\ Cache/Content Poisoning}
+
+%I don't think submission is anonymous...
+% I PUT AUTHOR NAMES IN ALPHEBETICAL ORDER. It is the common practice in security and I always list authors alphebetically in my publications. -Ersin 
+\author{
+    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
+    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
+    \\\{alex, ilya, lixia\}@ucla.edu}
+    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
+    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
+}
 
@@
 
-\input{04a-design-naive}
-
-\input{04b-design-intelligent}
+\input{04-design}
 
 \input{05-evaluation}
-
-\input{07-discussion}
 
@@
 \bibliographystyle{IEEEtran}
-{\small 
 \bibliography{references}
-}
 

### 2013-01-14 05-evaluation.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@921 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \subsection{Limitations}
-{\color{red} I gave up the idea of seperate discussion section as after trying for some time, I realized there is no way to write a reasonably comprehensive and acceptably broad discussion section that touches on algorithms, evaluation and methodology, etc.
-So, I decided to get rid of it and only have a scoped down version here that confesses upon the limiations of our evaluations.
-Whoever has time, please go ahead and write 1-2 paragraphs as outlined below}
+{\color{red} I gave up the idea of seperate discussion section after trying for some time, as given the space limitation, there is no way to write a reasonably comprehensive and  broad discussion section that justifies a separate section.
+Instead, I decided to have a scoped down version here that confesses upon the limiations of our evaluations only.
+Whoever has time (I need to sleep few hours), please go ahead and write 1-2 paragraphs as I outlined below.
+-Ersin}
 

### 2013-01-14 05-evaluation.tex
Limitations section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@923 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2013-01-14 05-evaluation.tex
@@
 
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: "paper"
-%%% End:
+\subsection{Limitations}
+%{\color{red} I gave up the idea of seperate discussion section after trying for some time, as given the space limitation, there is no way to write a reasonably comprehensive and  broad discussion section that justifies a separate section.
+Instead, I decided to have a scoped down version here that confesses upon the limiations of our evaluations only.
+Whoever has time (I need to sleep few hours), please go ahead and write 1-2 paragraphs as I outlined below.
+-Ersin}
+
+%This section should roughly say: Our results show that the two features, namely the symmetric traffic and stateful routing, give NDN routers the ability to observe and characterize traffic in real time.
+Through our evaluations, we demonstrated that a mitigation algorithm that leverages such ability has great potential in mitigating various DDoS attacks that could otherwise have grave effect on the network.
+However, as the first step in exploring the problem and the solution space, this paper has obvious limitations: (1) We assume a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations.
+Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step is evaluating the above described solutions with more sophisticated and adaptive attackers.
+(2)   Although most (such as single-path routing, no-caches in the network, single homed victim, etc) are aimed to test the proposed solutions under worst-case scenario, we made many assumptions in simulations/evaluations about the configurations, topology and the traffic that maybe poor-representative of realistic conditions.
+(3) As NDN being an ongoing research effort itself, our evaluations fully depend on simulations and done over a snapshot of its codebase.
+
+This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space.
+While designing our mitigation algorithms, we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
+We test the efficacy of our algorithms by simulating them on both a binary-tree topology designed to test the worst-case effectiveness of our algorithms as well as on a real ISP topology designed to provide insights our algorithms' behavior when deployed on a real network.
+While our results are promising and show great potential in mitigating Interest flooding DDoS attacks that can cause grave service degradation for legitimate users, we discuss some of the limitations of our evaluations and directions for future research.
+
+The attacker model that we used for our evaluations is simple and static - attackers send junk Interests as fast as possible.
+In future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and junk Interest sending patterns based on the network reaction.
+Further, in our evaluations, we assumed Interests are not satisfied by an intermediate router's cache and forwarded all the way to the producer.
+We also ignored NDN's strategy layer that routes around failure and congestion in the network.
+In future work, we plan to study the impact of turning on these features.
+Finally, we also plan to perform extensive simulations on other real Internet topologies and realistic traffic patterns from legitimate users.

### 2013-01-14 01-intro.tex
Pass on intro (correcting reference) and limitation section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@924 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 We give an overview of NDN architecture in Section~\ref{sec:ccn-intro} and explain interest flooding attacks in Section~\ref{sec:interest-flooding}.
-In Sections~\ref{sec:design},~\ref{sec:evaluation}, and~\ref{sec:discussion}, we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations respectively.
+In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
 We summarize related work in Section~\ref{sec:related-work} and finalize the paper with conclusions and future work in Section~\ref{sec:conclusion}.

### 2013-01-14 05-evaluation.tex
Pass on intro (correcting reference) and limitation section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@924 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
+% The main contribution of the paper and this section in particular is a proof that two inherent properties of NDN architecture, namely the symmetric traffic and stateful forwarding, give NDN routers the ability to characterize traffic and react in real time.
+% We demonstrated that satisfaction-based pushback algorithm, leveraging this ability, has great potential in mitigating various DDoS attacks that could otherwise have a grave effect on the network. 
+% However, as the first step in exploring the problem and the solution space, our paper has obvious limitations.
+% First, we assumed a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations. 
+% Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step that we are leaving out for future work is evaluating the above described solutions with more sophisticated and adaptive attackers.
+% Second, while aiming to test the designed algorithms under worst-case conditions, the future work needs to address behavior in more realistic scenarios, including investigation of multi-path routing, in network caches, as well as multi-homed victims.
+
 This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space. 
 While designing our mitigation algorithms, we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
-We test the efficacy of our algorithms by simulating them on both a binary-tree topology designed to test the worst-case effectiveness of our algorithms as well as on a real ISP topology designed to provide insights our algorithms' behavior when deployed on a real network.
-While our results are promising and show great potential in mitigating Interest flooding DDoS attacks that can cause grave service degradation for legitimate users, we discuss some of the limitations of our evaluations and directions for future research.
+We test the efficacy of our algorithms by simulating them on both a binary-tree topology designed to test the worst-case effectiveness of our algorithms as well as on a realizing ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network.
+While our results are promising and show a great potential in mitigating Interest flooding DDoS attacks, there are certain limitations which should be addressed in future research.
 
-The attacker model that we used for our evaluations is simple and static - attackers send junk Interests as fast as possible.
-In future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and junk Interest sending patterns based on the network reaction.
-Further, in our evaluations, we assumed Interests are not satisfied by an intermediate router's cache and forwarded all the way to the producer.
-We also ignored NDN's strategy layer that routes around failure and congestion in the network.
-In future work, we plan to study the impact of turning on these features.
-Finally, we also plan to perform extensive simulations on other real Internet topologies and realistic traffic patterns from legitimate users.
+First, in our evaluations we used a simple and static attacker model---attackers send junk Interests as fast as possible. 
+In the future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and junk Interest sending patterns based on the network reaction.
+Second, we made an assumption that Interests are not satisfied by an intermediate router's cache and always forwarded all the way to the producer.  
+The future work needs to study impact of Interest flooding attack in more realistic scenarios, including investigation effects of multi-path routing and presence of in network caches.
+% We also ignored NDN's strategy layer that routes around failure and congestion in the network. 
+% In future work, we plan to study the impact of turning on these features. 
+Finally, we also plan to perform more extensive simulations on other realistic Internet-like topologies and traffic patterns.
+
+%%% Local Variables: 
+%%% mode: latex
+%%% TeX-master: "paper"
+%%% End:

### 2013-01-14 04-design.tex
typos
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@926 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding interface.
-This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet switched networks.
+This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet-switched networks.
 Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
@@
 
-Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using this rotio to penalize malicious Interests.
+Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using this ratio to penalize malicious Interests.
 A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).

### 2013-01-14 05-evaluation.tex
more typos
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@927 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 This metric corresponds to the quality of service experienced by legitimate users when the network is under attack.
-In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conlcude that method $X$ is highly effective at mitigating the attack.
+In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conclude that method $X$ is highly effective at mitigating the attack.
 We also ensure that all Interests expressed by legitimate users during a period of no-attack are satisfied.

### 2013-01-14 08-conclusion.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@921 df1a90cd-247b-4364-bdaf-287a704eb499
more typos
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@927 df1a90cd-247b-4364-bdaf-287a704eb499

--- 2012-12-10 08-conclusion.tex
@@
-\section{Conclusion}
+\section{Conclusion{\color{red}-needs a pass}}
 \label{sec:conclusion}
@@
 In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
-The most effective of the designed algorithms---dynamic limits---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data pah symmetry and full receiver-based traffic control.
-In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Intersets can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
+The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data path symmetry and full receiver-based traffic control.
+In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Interests can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
 

### 2013-01-15 08-conclusion.tex
Conclusion
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@928 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
-The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data path symmetry and full receiver-based traffic control.
-In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Interests can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
+%In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
+%The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data path symmetry and full receiver-based traffic control.
+%In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Interests can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
+%
+%Other forms of attack may require different mitigation mechanisms.  
+%However, the granularity of the NDN state---per each Interest packet---is what giving NDN an opportunity to stand against existing and new forms of attacks.
 
-Other forms of attack may require different mitigation mechanisms.  
-However, the granularity of the NDN state---per each Interest packet---is what giving NDN an opportunity to stand against existing and new forms of attacks.
+NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution.
+However, the resilience of this new architecture to DoS and DDoS attacks has been relatively poorly understood.
+As a first step in this unexplored space, we describe a special instance of DDoS attacks in NDN called Interest flooding and the severe service degradation such an attack can cause to legitimate users.
+We leverage and exploit key features of the NDN architecture to design, develop and evaluate three Interest flooding mitigation strategies and perform detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.
+%Our first strategy---Token bucket with per interface fairness---while easy to implement and deploy was ineffective at ensuring an acceptable %quality of service for legitimate users.  
+Our most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers and resulted in minimal to no service impact for legitimate users. 
+Beyond our success with mitigating Interest flooding attacks in NDN, lessons from our experience with these mitigation algorithms as well as the metrics that we used to evaluate the effectiveness of our strategies can be applied to develop mitigation strategies for other classes of DDoS attacks in NDN.
+{\color{red} Priya: Need a  strong concluding line on  how it can be used for other kinds of DDoS mitigation strategies.
+Ersin, can you take a cut at it?}
 

### 2013-01-15 01-intro.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@929 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 % However, the design that fostered its success and wide-adaptation over the last three decades is now aged and limited in accommodating the changing demands of today's users. 
-Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an active research effort that aims to move the Internet into the future with a new, content-centric design that is capable of efficient content distribution and seamless mobility support.
+Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an ongoing research effort that aims to move the Internet into the future with a content-centric design that is capable of efficient content distribution and seamless mobility support.
 In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in packets.
@@
 %
-However, since NDN allows any host to request any data, malicious users can attack the network by sending an excessive number of Interests. 
-Because each Interest stores state and consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can easily disrupt service by congesting the network and exhausting routers' memory.
+However, malicious users can attack the network by sending an excessive number of Interests. 
+Because each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can potentially congest the network and exhaust routers' memory. 
 We coin the term {\it Interest flooding} to refer to such attack and
@@
 Our effort is an important first step towards a complete investigation of DDoS attacks in NDN.
-We show the devastating effect of Interest flooding on vanilla NDN and propose three algorithms that allow routers to exploit their state information to effectively thwart these attacks.
-Through extensive simulations,  we show how one of our mitigation methodologies effectively shuts down malicious users while allowing legitimate users to not experience any service degradation.
+We experiment with three algorithms that allow routers to exploit their state information to thwart these attacks.
+Through extensive simulations, we show how one of our mitigation methodologies effectively shuts down malicious users while preventing legitimate users from service degradation.
 %We use extensive simulations to show the devastating effect of Interest flooding on vanilla NDN and how a router can effectively exploit its state information to effectively mitigate them. 

### 2013-01-15 03-interest-flooding.tex
Small reorganization of evaluation section. Some spacing changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@915 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@930 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-Unlike Data packets, Interest packets in NDN are unsolicited, consume state in intermediate routers, and are routed through the network based on their content name prefix.
-These properties make Interest packets an effective tool in launching DoS and DDoS attacks in NDN.
-An attacker or a set of distributed attackers can inject excessive amounts of Interests to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
+As we explained earlier, Interest packets in NDN are routed through the network based on their content name prefixes and consume memory resources at intermediate routers.
+Thus they can be used to launch DDoS attacks in an NDN network.
+An attacker or a set of distributed attackers can inject excessive amounts of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
 %%% Alex %%% We have (almost) exactly the same sentence in the intro.
@@
   \includegraphics[scale=0.39]{attack-definition}
+  \vspace{-0.4cm}
   \caption{Example of the Interest flooding attack}
@@
 
-Since communication in NDN is content-centric, it is unlikely that an adversary can target specific routers or end-hosts, as neither is required to have a globally routable network identity/address.
+Since an NDN network fetches name data, an adversary cannot target specific routers or end-hosts.
+%% as neither is required to have a globally routable network identity/address.
 However, an adversary can target a specific namespace.
 For example in Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
-\footnote {In our example, Data producer is single-homed.
-In the case of multi-homed producers with rich connectivity through multiple providers, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding}.}
-A large volume of these Interests can distrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
+\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{/foo/bar} prefix to make them effective.
+It also assumes the producer is single-homed and the data is not replicated elsewhere.
+With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding}.}
+A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
 
@@
 A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
-Although congestion might occur anywhere in the network, a coordinated DDoS attack would likely target one specific namespace to concentrate attack traffic in certain segments of the network, typically closest to the publisher serving that namespace since name prefixes in NDN loosely correspond to a network location or sets of network locations.
+In particular a coordinated DDoS attack could target one specific namespace to concentrate attack traffic in certain segments of the network, typically closest to the publisher serving that namespace.
+%% since name prefixes in NDN loosely correspond to a network location or sets of network locations.
 
-As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a routers' memory.
-When a router has insufficient memory to create a new PIT entry, it is forced to drop new incoming Interests, thus disrupting service for legitimate users.
+As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a router's memory, making the router unable to create new PIT entries for incoming Interests, thus disrupting service for legitimate users.
 % there is no point in forwarding the Interest further.
@@
 
-To efficiently implement an Interest flooding attack targeting a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
-In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and avoid being served from caches of intermediate routers: each malicious Interest generated by an individual attacker should request an unpopular or non-existing content, e.g., content with a unique name (\emph{unique junk Interests}).
+An effective Interest flooding attack is non-trivial to create.
+To target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
+%In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and 
+To avoid an Interest being served from caches of intermediate routers, every single malicious Interest has to request an unpopular or non-existing content, e.g., content with a unique name (\emph{unique junk Interests}).
 In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network.
-Other less effective strains of this attack can be mitigated by applying the same or similar countermeasures.
+Other less effective strains of Interest flooding attacks can be mitigated by applying the same or similar countermeasures.
 

### 2013-01-15 06-related.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@931 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-The general area of denial of service attacks and their mitigation methods is among the hottest topics in recent years.
+The general area of mitigating denial of service attacks is among the hottest topics in recent years.
 % Among all the body of work, 
-The efforts that are most relevant works to this paper are solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushbacking malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
+The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushbacking malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
 overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
@@
 and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
-Identifying malicious traffic requires state at routers, all these solutions differ in the specifics on what state to use and how to establish it.
-By design NDN's forwarding plane keeps per packet state, one can simply take full advantage of this state to develop effective mitigations.
+Identifying malicious traffic requires establishing certain state at routers, and the above mentioned solutions differ in the specifics on what state to use and how to establish it.
+By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions.
+Therefore one can simply take full advantage of this state to develop desired solutions.
 

### 2013-01-15 03-interest-flooding.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@932 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 As we explained earlier, Interest packets in NDN are routed through the network based on their content name prefixes and consume memory resources at intermediate routers.
-Thus they can be used to launch DDoS attacks in an NDN network.
+This makes them a potential tool to launch DDoS attacks in an NDN network.
 An attacker or a set of distributed attackers can inject excessive amounts of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
@@
 
-Since an NDN network fetches name data, an adversary cannot target specific routers or end-hosts.
+Since an NDN network fetches data by its name, an adversary cannot target specific routers or end-hosts.
 %% as neither is required to have a globally routable network identity/address.
@@
 In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network.
-Other less effective strains of Interest flooding attacks can be mitigated by applying the same or similar countermeasures.
+However, other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
 

### 2013-01-15 paper.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@920 df1a90cd-247b-4364-bdaf-287a704eb499
Reverting back the old title. Update of email addresses
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@922 df1a90cd-247b-4364-bdaf-287a704eb499
Alex, you cannot copy UCI paper's title...
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@925 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@932 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\title{Interest Flooding Attacks and Countermeasures in Named Data Networking}%:\\ Cache/Content Poisoning}
+%\title{Mitigating Interest Flooding DDoS Attacks in NDN}
+
+\title{Interest Flooding Attack and Countermeasures in Named Data Networking}%:\\ Cache/Content Poisoning}
 
@@
     \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
-    \\\{alex, ilya, lixia\}@ucla.edu}
+    \\\{afanasev, iliamo, lixia\}@cs.ucla.edu}
     \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
@@
 Distributed Denial of Service attack is an ongoing problem in today's Internet, where packets from large numbers of compromised hosts thwart the paths to the victim site and/or overload the victim machines.
-In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network forwards Data packets upon request only, effectively eliminating many existing DDoS attacks.
+In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network delivers Data packets upon request only, effectively eliminating many existing DDoS attacks.
 However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  

### 2013-01-15 08-conclusion.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@933 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 % Main take out from the paper:  could be a problem, but problem is solvable.  
-
-% one may think that
-
 % One of the key components in the Named Data Networking architecture is its stateful data delivery model, which potentially can be abused by new types of denial of service attacks.
@@
 %However, the granularity of the NDN state---per each Interest packet---is what giving NDN an opportunity to stand against existing and new forms of attacks.
+%
+%NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution.
 
-NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution.
-However, the resilience of this new architecture to DoS and DDoS attacks has been relatively poorly understood.
-As a first step in this unexplored space, we describe a special instance of DDoS attacks in NDN called Interest flooding and the severe service degradation such an attack can cause to legitimate users.
-We leverage and exploit key features of the NDN architecture to design, develop and evaluate three Interest flooding mitigation strategies and perform detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.
-%Our first strategy---Token bucket with per interface fairness---while easy to implement and deploy was ineffective at ensuring an acceptable %quality of service for legitimate users.  
-Our most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers and resulted in minimal to no service impact for legitimate users. 
-Beyond our success with mitigating Interest flooding attacks in NDN, lessons from our experience with these mitigation algorithms as well as the metrics that we used to evaluate the effectiveness of our strategies can be applied to develop mitigation strategies for other classes of DDoS attacks in NDN.
+NDN is a newly proposed future Internet architecture, thus it is important to address its resilience in face of DDoS attacks.
+As a first step in this unexplored space, in this paper we first examined a specific instance of DDoS attacks, Interest flooding, and the severe service degradation such an attack may cause to legitimate users.
+We then leverage the key features of the NDN architecture to design, develop and evaluate three mitigation strategies.
+We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
+The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers so that they cause little or no service impact on legitimate users.
+
+NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balancing (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding}.
+Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as an evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation.
+
+%Beyond our success with mitigating Interest flooding attacks in NDN, lessons from our experience with these mitigation algorithms as well as the metrics that we used to evaluate the effectiveness of our strategies can be applied to develop mitigation strategies for other classes of DDoS attacks in NDN.
 {\color{red} Priya: Need a  strong concluding line on  how it can be used for other kinds of DDoS mitigation strategies.

### 2013-01-15 04-design.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@935 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
-We start by describing our simple strategies and use the insights and lessons learned from the deployment of these techniques to inform and design more effective mitigation techniques that can work well in a variety of attack scenarios.
+We start by describing our simple strategies and use the insights and lessons learned from the deployment of these to inform and design more effective mitigation techniques that works well in various topologies.
 
@@
 
-This {\it Token Bucket} approach might be exceptionally retrictive in forwarding Interests---not all Interests will result in a Data packet---thus, the network can be underutilized.
-However, the biggest drawback of the algorithm is that it itself can be used as an effective mechanism to carry out DDoS attacks.
+This {\it Token Bucket} approach might be exceptionally restrictive in forwarding Interests---not all Interests will result in a Data packet---and might result in underutilization of the network.
+However, the biggest drawback of this algorithm is the fact that it can nourish DDoS attacks.
 If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
-One way to get around this issue is to impose a per interface limit, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
+One way to get around the issue is to impose a per interface limit, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
 We describe this technique in greater detail below.
@@
 
-To address the lack of fairness associated with the na\"ive {\it Token Bucket} algorithm, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring nodes.
+To address the lack of fairness associated with the na\"ive {\it Token Bucket} approach, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring nodes.
 For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
@@
 %As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
-We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
-Thus, a PIT entry can be quickly updated when the Interest is actually forwarded; further the element can be quickly removed from the queue when the Interest expires.
+We note that, unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
+Thus, a PIT entry can be quickly updated when the Interest is actually forwarded and the element can be easily removed from the queue when the Interest expires.
 
@@
 We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
-By setting appropriate queue sizes we can control the amount of physical resources utilized at a router.
+By setting appropriate queue sizes, we can control the amount of physical resources utilized at a router.
  % (such as memory and computation power). 
-It is also important to set appropriate value for how long an Interest can be enqueued. 
-If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet could be dropped later due to state expiration at the downstream routers. 
-For our evaluations we chose to enqueue Interests up to 10\% of their original lifetime.
+It is also important to set a sensible value for how long an Interest can be enqueued. 
+If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet might be dropped at the downstream routers if their corresponding state expired. 
+For our evaluations, we empirically chose to enqueue Interests up to 10\% of their original lifetime.
 % We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
@@
 As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from the Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
-We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is ineffective in protecting legitimate users from malicious attackers. 
-Malicious attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of Interests.
+We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is ineffective in protecting legitimate users from malicious ones. 
+Attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of malicious Interests.
 
@@
 
-The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it admits Interests from malicious users.
-A sizeable percentage of these malicious Interests are forwarded all the way to content producers, thereby utilizing scarce network resources and reducing resources available to serve legitimate users.
-This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate Interests as well as malicious Interests.
-For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and effectively drop only malicious requests for content.
+The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits relatively large number of Interests from malicious users.
+A considerable percentage of these malicious Interests are forwarded all the way to content producers, thereby reducing resources available to serve legitimate users.
+This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate and malicious Interests.
+For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and differentiate malicious requests from legitimate ones.
 % `Good' Interests from legitimate users must be admited and forwarded appropriately. 
-The key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
+Thus, the key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
 
@@
 In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets.
-Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guaranteed to see if an Interest it forwarded resulted in a matching Data packet or times out.
+Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guaranteed to see if an Interest it forwarded resulted in a matching Data packet or timed out.
 %The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
@@
 However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest should be forwarded or dropped.
-For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout.
+For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to reasonably predict whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout if forwarded.
 Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
@@
 Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using this ratio to penalize malicious Interests.
-A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
+A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as the direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
 %Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
@@
 Parameter $\theta$ on line 5 of the Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
-This step is critical---while we want to drop Interests from attackers, we also want to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
+This step is critical to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
 
-A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop the Interest. 
+A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop an Interest. 
 As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
@@
 One way to prevent this overreaction and unfair penalization is to ensure that the decision taken at each router on whether to forward or drop the Interest is not independent of the decision taken at preceding routers.
-An explicit notification such as a gossip protocol between neighboring NDN routers that specifies the volume of Interests each router is willing to forward will likely address this issue.
-We leave the implementation and evaluation of a gossip protocol to future work.
+An explicit notification such as a gossip protocol between neighboring NDN routers might alleviate the problem, but we leave the design and evaluation of it to future work.
 %{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
@@
 The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to the appropriate level (recall Fig.~\ref{fig:ratio example}).
-At the next iteration of the satisfaction-based pushback algorithm, the legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and will return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
+At the next iteration of the satisfaction-based pushback algorithm, the legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
 

### 2013-01-15 05-evaluation.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@936 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 This metric corresponds to the quality of service experienced by legitimate users when the network is under attack.
-In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conclude that method $X$ is highly effective at mitigating the attack.
-We also ensure that all Interests expressed by legitimate users during a period of no-attack are satisfied.
+In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conclude that method $X$ is highly effective at mitigating the attack.% We also ensure that all Interests expressed by legitimate users during a period of no-attack are satisfied.
 
@@
 We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
-To quantify the behavior of our mitigation strategies under a worse case attack scenario, we ensure that all the attackers send junk Interests as fast as they can.
+To quantify the behavior of our mitigation strategies under a worse case attack scenario, we assume all the attackers send junk Interests as fast as they can, no Interest --including legitimate ones-- can be satisfied from caches, routers are configured for single-path routing and there is only one, single-homed producer for the prefix under attack.
 %(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
@@
 % Fixed parameters
-We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation to a fixed value for every node in the simulated topology.
+We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation to an initial %fixed 
+value for every node in the simulated topology.
 In particular, for the small-scale binary tree topology, we set delay to 80~ms, while for the large-scale ISP topology we set it to 330~ms (the order of the largest RTT).
 The data size is 1100~bytes for all simulation runs and topologies.
+% THIS IS BULLSHIT!
+There is absolutely no logic to set the delay to the same value on all nodes in the network.
+We discussed multiple times that you should fix it so that the delays are realistic and gets smaller as the nodes gets closer to the producer...
 
@@
 Contrary to expectations, the 60\% legitimate users do not receive at least 60\% of network resources.
-As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers, a good percentage of which traverse all the way to the data producer.
-Significantly reducing the number of accepted malicious Interests is fundamental for improving the effectiveness of any mitigation algorithm.
+As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers and causes congestion and packet drops near the victim.
+%Significantly reducing the number of accepted malicious Interests is fundamental for improving the effectiveness of any mitigation algorithm.
 
@@
 
-The effectiveness of this algorithm stems from the fact that routers do not admit malicious Interests into the network, thereby ensuring availability of network resources for serving legitimate users.
+The effectiveness of this algorithm stems from the fact that routers can differentiate and limit malicious Interests into the network%, thereby ensuring availability of network resources for serving legitimate users
+.
 The observed periodic dips in the Interest satisfaction ratios of legitimate users in Fig.~\ref{fig:small-scale attack progress} is a direct result of Interest satisfaction rate statistics decaying with time.
@@
 %The primary reason that such minimum peaks exist is the fact that 
-When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe traffic mix from legitimate and malicious users).
+When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe mixed traffic from legitimate and malicious users).
 Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' to the edge.
@@
 
-This mitigation algorithm is able to effectively shut down attackers and ensure that almost all of the Interests from legitimate users are satisfied. 
+In our simulations, this mitigation algorithm was able to effectively shut down attackers and ensure almost all the Interests from legitimate users are satisfied. 
 %The only potential problem with the satisfaction-based pushback algorithm is that it features 
-We observe a  sharp dip in the satisfaction ratio curve at the start of the attack.
-It takes a few seconds for all routers to be fully aware of the attack, which happens when malicious Interests start to time out and explicit Interest limit announcements succeed in containing malicious Interests close to the attacker.
-Till then, the network for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
+We observe a  sharp dip in the satisfaction ratio curve at the start of the attack as it takes a few seconds for all routers to be fully aware of the attack.
+Recovery quickly happens as malicious Interests start to time out and explicit Interest limit announcements start to succeed in containing malicious Interests close to the attacker.
+Till then, the network, for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
 Once the malicious Interests are effectively shut down, all Interests from legitimate users are satisfied.
-Unlike the satisfaction-based Interest acceptance scenario, we do not observe any periodic dips in the satisfaction curve, as the pushback algorithm effectively guarantees that once an Interest is admitted, it will almost certainly be routed to the data producer.
+Unlike the satisfaction-based Interest acceptance scenario, we do not observe any periodic dips in the satisfaction curve, as the pushback algorithm effectively guarantees that once an Interest is admitted, it will likely be routed all the way to the data producer.
 
-\subsubsection{Network reaction with to varying number of attackers}
+\subsubsection{Network reaction to varying number of attackers}
 
@@
 Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
-All other parameters and experimental set-up are similar to the previous experiment.
+All other parameters and experimental set-up is the same with the previous experiment.
 As before, for each mitigation algorithm, we perform 10 independent simulation runs.
@@
 In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.
-While both intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
-In the case of satisfaction-based pushback algorithm, over 90\% of Interests from legitimate users are satisfied even when over 50\% of the users are malicious.
+While the two intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
+In the case of satisfaction-based pushback algorithm, over 90\% of Interests from legitimate users are satisfied even if the 50\% of end nodes are malicious.
 
@@
 
-Next, our goal is to understand the behavior of our mitigation strategies when deployed on a large-scale real network topology.
-Our ISP topology is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
+In this section, we investigate the behavior of our mitigation strategies under a more realistic, large-scale network topology.
+The ISP topology we employed is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
 %In order to approximate the general structure of the Internet,
@@
 We observe similar results for the data producer placed at the backbone node as well.
-As in the case of the binary-tree topology experiments, token bucket with per interface fairness is the most ineffective algorithm and satisfaction-based pushback is the most effective one.
-Interest satisfaction percentage for legitimate users are approximately 25\% and almost 100\% respectively for these two mitigation methodologies.
+As in the case of the binary-tree topology experiments, we observe that the token bucket with per interface fairness is the most ineffective algorithm and satisfaction-based pushback is the most effective one.
+Interest satisfaction percentage for legitimate users are approximately 25\% and close to 100\% respectively for these two mitigation methodologies.
 
@@
 
-Satisfaction-based Interest acceptance algorithm, which was very effective for binary-tree topology, is completely ineffective when deployed in a larger realistic topology.
+Satisfaction-based Interest acceptance algorithm, which was very effective for binary-tree topology, is completely ineffective when deployed in a larger and more realistic topology.
 For the duration of the attack, legitimate users experience poor quality of service with only 25\% of their Interests being satisfied and continue to experience degraded service long after the attack has stopped.
-This poor performance, as detailed in  in Section~\ref{sec:probabilistic}, is due to the fact that each router in the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
+This poor performance, as detailed in Section~\ref{sec:probabilistic}, is due to the fact that each router in the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
 In the case of the larger-topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics, which in turn leads to further penalization of new Interests from them.
 
-To summarize, in all of our simulations, the satisfaction-based pushback algorithm is the most effective technique as it restricts malicious Interests from even entering the network. 
+All our evaluations leaves us with the conclusion that, among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most effective one in mitigating interest flooding attacks.% and it restricts malicious Interests from even entering the network.
 %The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
@@
 While designing our mitigation algorithms, we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
-We test the efficacy of our algorithms by simulating them on both a binary-tree topology designed to test the worst-case effectiveness of our algorithms as well as on a realizing ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network.
+We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
+as well as a more realistic ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network. 
 While our results are promising and show a great potential in mitigating Interest flooding DDoS attacks, there are certain limitations which should be addressed in future research.
@@
 First, in our evaluations we used a simple and static attacker model---attackers send junk Interests as fast as possible. 
-In the future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and junk Interest sending patterns based on the network reaction.
+In the future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and Interest sending patterns based on the network reaction.
 Second, we made an assumption that Interests are not satisfied by an intermediate router's cache and always forwarded all the way to the producer.  
-The future work needs to study impact of Interest flooding attack in more realistic scenarios, including investigation effects of multi-path routing and presence of in network caches.
+The future work needs to study impact of Interest flooding attack in more realistic scenarios, including investigation effects of multi-path routing, more realistic traffic patterns, and presence of in network caches.
 % We also ignored NDN's strategy layer that routes around failure and congestion in the network. 
 % In future work, we plan to study the impact of turning on these features. 
-Finally, we also plan to perform more extensive simulations on other realistic Internet-like topologies and traffic patterns.
+%Finally, we also plan to perform more extensive simulations on other realistic Internet-like topologies and traffic patterns.
 

### 2013-01-15 08-conclusion.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@934 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@937 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-\section{Conclusion{\color{red}-needs a pass}}
+\section{Conclusion}
 \label{sec:conclusion}
@@
 NDN is a newly proposed future Internet architecture, thus it is important to address its resilience in face of DDoS attacks.
-As a first step in this unexplored space, in this paper we first examined a specific instance of DDoS attacks, Interest flooding, and the severe service degradation such an attack may cause to legitimate users.
+As a first step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks, Interest flooding, and the severe service degradation such an attack may cause to legitimate users.
 We then leverage the key features of the NDN architecture to design, develop and evaluate three mitigation strategies.
@@
 NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balancing (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding}.
-Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as an evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation.
+Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as an evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.
+
+%<<<<<<< .mine
+%NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution.
+However, the resilience of this new architecture to DoS and DDoS attacks has been relatively poorly understood.
+As a first step in understanding the DDoS threats in NDN, we describe one instance of DDoS attacks called Interest flooding and demonstrate the severe service degradation such an attack can cause to legitimate users.
+By leveraging and exploiting key features of the NDN architecture design, we also develop and evaluate three mitigation techniques, and perform detailed simulations on a range of topologies to quantify their effectiveness in mitigating interest flooding in NDN .
+%Our first strategy---Token bucket with per interface fairness---while easy to implement and deploy was ineffective at ensuring an acceptable %quality of service for legitimate users.  
+%Our most effective algorithm---satisfaction-based pushback---was successful in almost completely eliminating the adverse effects of the attack over the network and resulted in minimal to no service impact for legitimate users.
+%Beyond our success with mitigating the particular attack in NDN, we strongly believe that the lessons from our experience with these mitigation algorithms as well as the metrics that we used to evaluate the effectiveness of our strategies can be applied to develop mitigation strategies for other classes of DDoS attacks in NDN as well.
+%=======
+%>>>>>>> .r936
 

### 2013-01-15 04-design.tex
Typo
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@938 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 %As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
-We note that, unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
-Thus, a PIT entry can be quickly updated when the Interest is actually forwarded and the element can be easily removed from the queue when the Interest expires.
+We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
+Thus, a PIT entry can be quickly updated when the Interest is actually forwarded, and the element can be easily removed from the queue when the Interest expires.
 
@@
 
-The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits relatively large number of Interests from malicious users.
+The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits a relatively large number of Interests from malicious users.
 A considerable percentage of these malicious Interests are forwarded all the way to content producers, thereby reducing resources available to serve legitimate users.

### 2013-01-15 05-evaluation.tex
typos
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@939 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 % Traffic pattern
-In our experiments, we assume that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution.
+In our experiments, we assumed that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution.
 We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
-To quantify the behavior of our mitigation strategies under a worse case attack scenario, we assume all the attackers send junk Interests as fast as they can, no Interest --including legitimate ones-- can be satisfied from caches, routers are configured for single-path routing and there is only one, single-homed producer for the prefix under attack.
+To quantify the behavior of our mitigation strategies under a worse case attack scenario, we assumed that all the attackers send junk Interests as fast as they can, no Interest---including legitimate ones---can be satisfied from caches.
+Also, we configured routers for single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
 %(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
@@
 Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
-All other parameters and experimental set-up is the same with the previous experiment.
+All other parameters and experimental setup is the same with the previous experiment.
 As before, for each mitigation algorithm, we perform 10 independent simulation runs.
@@
   \vspace{-.1cm}\includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
+  \vspace{-0.3cm}
   \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}\vspace{-.2cm}
@@
 \caption{Large-scale topology link bandwidth and delay ranges}
+\vspace{-0.3cm}
 \label{tab:large-scale}
@@
   \hline
-
 \end{tabular}
+\vspace{-0.3cm}
 \end{table}
@@
  \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
- \vspace{-.3cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.4cm}
+ \vspace{-.3cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.3cm}
  % producer on a gateway node
@@
 
-All our evaluations leaves us with the conclusion that, among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most effective one in mitigating interest flooding attacks.% and it restricts malicious Interests from even entering the network.
+All our evaluations leaves us with the conclusion that, among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most effective one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
 %The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
@@
 While designing our mitigation algorithms, we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
-We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
+We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology, % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
 as well as a more realistic ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network. 

### 2013-01-15 03-interest-flooding.tex
Final pass
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@941 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 However, an adversary can target a specific namespace.
-For example in Fig.~\ref{fig:flooding example}, if the Data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the Data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
-\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{/foo/bar} prefix to make them effective.
+For example in Fig.~\ref{fig:flooding example}, if the data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
+\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{\small /foo/bar} prefix to make them effective.
 It also assumes the producer is single-homed and the data is not replicated elsewhere.
@@
 An effective Interest flooding attack is non-trivial to create.
-To target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the Data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
+To target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
 %In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and 

### 2013-01-15 04-design.tex
Final pass
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@941 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \begin{equation}
+\label{eq:interest limit}
 \small \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
@@
 Prior to start of the attack, the percentage of unsatisfied Interests is zero.
-The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.%\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
+The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.
+%\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
 For the duration of the attack (10--70~seconds), the percentage of unsatisfied Interests is close to 100\%: 
@@
 
-Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using this ratio to penalize malicious Interests.
+Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using these ratios to penalize malicious Interests.
 A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as the direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).

### 2013-01-15 05-evaluation.tex
Final pass
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@941 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
-To quantify the behavior of our mitigation strategies under a worse case attack scenario, we assumed that all the attackers send junk Interests as fast as they can, no Interest---including legitimate ones---can be satisfied from caches.
-Also, we configured routers for single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
+To quantify the behavior of our mitigation strategies under a worst-case attack scenario, we assumed that all the attackers send junk Interests as fast as they can, no Interest---including legitimate ones---can be satisfied from caches.
+Also, we configured routers for the single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
 %(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
@@
 % Fixed parameters
-We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation to an initial %fixed 
+We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation (\ref{eq:interest limit}) to a fixed 
 value for every node in the simulated topology.
@@
 In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we used for our initial experiments.
-Legitimate users as well as attackers were placed on leaf nodes (red nodes) as show in the figure.
-There are 16 end users (both legitimate and attackers) in this topology, each expressing Interests that are routed towards a single data producer placed at the root of the tree.
+Legitimate users as well as attackers were placed on leaf nodes (top row of red nodes) as shown in the figure.
+There are 16 end users (both legitimate and attackers) in this topology, each expressing Interests that are routed towards a single data producer, placed at the root of the tree.
 Each link in this topology is assigned a bandwidth of 10~Mbps and a randomized propagation delay ranging from 1 to 10 ms.
@@
 The observed periodic dips in the Interest satisfaction ratios of legitimate users in Fig.~\ref{fig:small-scale attack progress} is a direct result of Interest satisfaction rate statistics decaying with time.
-The 50-second period approximately corresponds to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value that ranges from 30~seconds to 50~seconds.
+The 50-second period approximately corresponds to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx$20\% within 50~seconds.
+ % that ranges from 30~seconds to 50~seconds. 
 %The primary reason that such minimum peaks exist is the fact that 
 When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe mixed traffic from legitimate and malicious users).
-Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' to the edge.
+Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' again to the edge.
 
@@
 Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
-All other parameters and experimental setup is the same with the previous experiment.
+All other parameters and experimental setup are consistent with the previous experiment.
 As before, for each mitigation algorithm, we perform 10 independent simulation runs.
@@
 While the two intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
-In the case of satisfaction-based pushback algorithm, over 90\% of Interests from legitimate users are satisfied even if the 50\% of end nodes are malicious.
+In the case of satisfaction-based pushback algorithm, during the first minute of the attack over 90\% of Interests from legitimate users are satisfied even if the 50\% of end nodes are malicious.
 
@@
 
-In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over 10 simulations runs for each mitigation algorithm for the scenario, where the data producer is placed at a gateway node.
+In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over all simulations runs for each mitigation algorithm for the scenario, where the data producer is placed at a gateway node.
 We observe similar results for the data producer placed at the backbone node as well.
-As in the case of the binary-tree topology experiments, we observe that the token bucket with per interface fairness is the most ineffective algorithm and satisfaction-based pushback is the most effective one.
-Interest satisfaction percentage for legitimate users are approximately 25\% and close to 100\% respectively for these two mitigation methodologies.
+Unlike the binary-tree topology experiments, we observe that the satisfaction-based pushback is the most effective algorithm, while both the token bucket with per interface fairness and satisfaction-based Interest accept have poor performance.
+Interest satisfaction percentage for legitimate users are close to 100\% and approximately 30\% and 25\% respectively for these mitigation methodologies.
 
@@
 For the duration of the attack, legitimate users experience poor quality of service with only 25\% of their Interests being satisfied and continue to experience degraded service long after the attack has stopped.
-This poor performance, as detailed in Section~\ref{sec:probabilistic}, is due to the fact that each router in the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
+This poor performance, as detailed in Section~\ref{sec:probabilistic}, is due to the fact that each router on the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
 In the case of the larger-topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics, which in turn leads to further penalization of new Interests from them.
 
-All our evaluations leaves us with the conclusion that, among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most effective one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
+All our evaluations leaves us with the conclusion that, among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most promising one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
 %The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).

### 2013-01-15 08-conclusion.tex
Small typo
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@940 df1a90cd-247b-4364-bdaf-287a704eb499
Final pass
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@941 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 NDN is a newly proposed future Internet architecture, thus it is important to address its resilience in face of DDoS attacks.
-As a first step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks, Interest flooding, and the severe service degradation such an attack may cause to legitimate users.
-We then leverage the key features of the NDN architecture to design, develop and evaluate three mitigation strategies.
+As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks, Interest flooding, and the severe service degradation such an attack may cause to legitimate users.
+We then leveraged the key features of the NDN architecture to design, develop, and evaluate three mitigation strategies.
 We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
-The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers so that they cause little or no service impact on legitimate users.
+The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers, so that they cause little or no service impact on legitimate users.
 

### 2013-03-25 paper.tex
Final pass
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@941 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@944 df1a90cd-247b-4364-bdaf-287a704eb499

@@
-% \documentclass[10pt, conference, compsocconf]{IEEEtran}
-\documentclass[conference]{IEEEtran}
+\documentclass[10pt,conference]{IEEEtran}
 % http://networking2013.poly.edu/call-for-papers/paper-submission/
@@
 
+\hyphenation{incoming}
+
 \pagestyle{headings}
 
-%\title{Mitigating Interest Flooding DDoS Attacks in NDN}
-
-\title{Interest Flooding Attack and Countermeasures in Named Data Networking}%:\\ Cache/Content Poisoning}
-
-%I don't think submission is anonymous...
-% I PUT AUTHOR NAMES IN ALPHEBETICAL ORDER. It is the common practice in security and I always list authors alphebetically in my publications. -Ersin 
-\author{
-    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
-    \\\{afanasev, iliamo, lixia\}@cs.ucla.edu}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
-    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
-}
-
-\newfont{\nicettfont}{cmtt10}
-\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
-\renewcommand{\texttt}[1]{{\nicettfont #1}}
-
-\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \marginpar{\textsc{ToDo}}
-\framebox{\begin{minipage}[c]{0.95 \columnwidth}
-\tt #1 \end{minipage}}\vspace{5 mm}\par}
-
+\usepackage[top=.75in, bottom=1in, left=.625in, right=.625in]{geometry}
 \usepackage{graphicx}
-% \usepackage[colorlinks]{hyperref}
 \usepackage[]{hyperref}
@@
 
+\newfont{\nicettfont}{cmtt10}
+\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
+\renewcommand{\texttt}[1]{{\nicettfont #1}}
+
+\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \marginpar{\textsc{ToDo}}
+\framebox{\begin{minipage}[c]{0.95 \columnwidth}
+\tt #1 \end{minipage}}\vspace{5 mm}\par}
 \graphicspath{{figures/}}
@@
 \begin{document}
+
+\title{Interest Flooding Attack and Countermeasures in Named Data Networking}
+
+% I PUT AUTHOR NAMES IN ALPHEBETICAL ORDER. It is the common practice in security and I always list authors alphebetically in my publications. -Ersin 
+\author{
+    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
+    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
+    \\\{afanasev, iliamo, lixia\}@cs.ucla.edu}
+    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
+    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
+}
 
@@
 
-\input{01-intro}
+\section{Introduction}
+\label{sec:intro}
 
-\input{02-ndn-background}
+Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an ongoing research effort that aims to move the Internet into the future with a content-centric design that is capable of efficient content distribution and seamless mobility support.
+In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in packets.
+However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against distributed denial of service (DDoS) attacks?
+Especially since various forms of DDoS attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial to ensure that the new design is free of similar vulnerabilities.
 
-\input{03-interest-flooding}
+NDN eliminates host-based addressing and makes data the first-class network entity.
+Instead of sending packets to a given IP address, NDN nodes request desired data by sending Interest packets carrying application-level data names, and the network returns the requested Data packets following the path of Interests.
+Such a shift automatically eliminates several long-standing DDoS attacks, including direct flooding and reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
+%
+However, malicious users can attack the network by sending an excessive number of Interests. 
+Because each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can congest the network and exhaust routers' memory resources. 
+We coin the term {\it Interest flooding} to refer to such attack and
+this paper exclusively investigates the problem and the solution space for it.
 
-\input{04-design}
+Our effort is an important first step towards a complete investigation of DDoS attacks in NDN.
+We experiment with three algorithms that allow routers to exploit their state information to thwart these attacks.
+Through extensive simulations, we show how one of our mitigation methodologies effectively shuts down malicious users while preventing legitimate users from service degradation.
+The rest of the paper is organized as follows.
+We give an overview of NDN architecture in Section~\ref{sec:ccn-intro} and explain interest flooding attacks in Section~\ref{sec:interest-flooding}.
+In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
+We summarize related work in Section~\ref{sec:related-work} and finalize the paper with conclusions and future work in Section~\ref{sec:conclusion}.
 
-\input{05-evaluation}
+\section{NDN Overview\label{sec:ccn-intro}}
 
-\input{06-related}
+In this section we briefly introduce NDN with a focus on its stateful forwarding plane (refer to \cite{ndn-conext, ndn-tr, adaptive-forwarding} for more details).
+NDN is a receiver-driven, data-centric communication protocol.
+All communication in NDN is performed using two distinct types of packets: \textit{Interest} and \textit{Data}.
+Both types of packets carry a \textit{name}, which uniquely identifies a piece of data that can be carried in one Data packet.
+Data names in NDN are hierarchically structured and an example name for the first segment of a youtube video would look like: \ndnName{/youtube/videos/0F8YdlkKO9A/0}.
 
-\input{08-conclusion}
+To retrieve data, a consumer requests it by sending an Interest packet with the name of the desired content in it.
+Routers use this name to route the Interest towards data sources, and a Data packet whose name matches the name in the Interest is returned to the consumer by following the reverse path of the Interest.
+Similar to IP, Interest forwarding is based on longest name prefix match, but, unlike IP, an Interest packet and its matching Data packet always take symmetric paths.
+%% An Interest is ``satisfied'' when it is matched with a Data packet.
+
+Each NDN router maintains three major data structures:
+\begin{itemize}
+\item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards potential data sources.
+Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicates the same Interest is forwarded along multiple paths.
+\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, defining allowed directions to where Interests can be forwarded. 
+% Having one-to-many relationship in this table allows multipath forwarding of Interests.}
+\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this node, allowing efficient data retrieval by different consumers.
+\end{itemize}
+
+When a router receives an Interest packet, it first checks whether there is a matching data in its CS.
+If a match is found, the Data packet is sent back to the incoming interface of the Interest packet.
+If not, the Interest name is checked against the entries in the PIT. 
+If the name already exists in the PIT, then it can be a duplicate Interest (identified by a random number each Interest carries) that should be dropped,
+or an Interest from another consumer asking for the same Data, which requires the incoming interface of this Interest to be added to the existing PIT entry.
+If the name does not exist in the PIT, the Interest is added into the PIT and forwarded to the interface chosen by the strategy module, which uses FIB as input for its decisions.
+
+When a Data packet is received, its name is used to look up the PIT.
+If a matching PIT entry is found,
+the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the CS, and removes the PIT entry.
+Otherwise, the Data packet is deemed unsolicited and is discarded.
+Each Interest also has an associated lifetime; the PIT entry is removed when the lifetime expires.
+Although the maximum lifetime is specified by users, it is ultimately a router's decision on how long it is willing to keep a PIT entry.  
+For simplicity, we assume routers keep Interests in PIT for one second in our simulations.
+
+\section{Interest Flooding Attacks in NDN}
+\label{sec:interest-flooding}
+
+As we explained earlier, Interest packets in NDN are routed through the network based on content name prefixes and consume memory resources at intermediate routers.
+This makes them a potential tool to launch DDoS attacks in NDN.
+An attacker or a set of distributed attackers can inject excessive amounts of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.39]{attack-definition}
+  \vspace{-0.4cm}
+  \caption{Example of the Interest flooding attack}
+  \label{fig:flooding example}
+\end{figure}
+
+Since an NDN network fetches data by its name, an adversary cannot easily target specific routers or end-hosts.
+However, an adversary can target a specific namespace.
+For example in Fig.~\ref{fig:flooding example}, if the data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.
+\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{\small /foo/bar} prefix to make them effective.
+It also assumes the producer is single-homed and the data is not replicated elsewhere.
+With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding} support.}
+A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
+
+Similar to packets in traditional networks, Interest packets in NDN consume a portion of network capacity.
+A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
+In particular, a coordinated DDoS attack could target one specific namespace and concentrate attack traffic in certain segments of the network as routing in NDN is based on name prefixes.
+
+As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a router's memory, making the router unable to create new PIT entries for incoming Interests and disrupting service for legitimate users.
+
+Nevertheless, creating an effective Interest flooding attack in NDN is non-trivial.
+To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2) new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
+The former is achieved when interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers --an interest is not forwarded upstream if a router can satisfy it from its content store.
+The latter requires every single malicious Interest to ask for a unique content --all Interests requesting the same content are collapsed to one PIT entry in routers.
+Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content at each interest.
+Among the two options of an adversary, the first one is quite problematic due to the difficulties around indexing content names in a particular namespace, coordinating large number of bots to send unique interests and sustaining the attack while the network is continuously caching the requested content objects.
+However, the second option, requesting unique non-existing content at each interest, is easy to achieve and sustain.
+An adversary can construct such interests by concatenating a random name component to the victim namespace (e.g.,\ndnName{/newyorktimes/fgb...3rf3}) and can increase the memory usage at each router by lengthening the random component.
+In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
+% other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
+
+In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
+
+%\paragraph{Assumptions} 
+%E: These are assumptions for the simulations on hand and particulary to test for the worst case scenario in many aspects.
+They are not the paper's assumption and in fact the paper first should be more general on describing all possibilities.
+Then it should explain the assumptions for the simulations and discuss why they make sense and do NOT favor positive results in some way.
+
+% - assumptions about attacker position
+% - assumptions about the producer / producer namespace
+% - assumptions about the attack traffic / attack pattern
+
+%In this paper we are making the following assumptions about the Interest flooding attack:
+%\begin{itemize}
+%\item only client nodes can be compromised and become attack bots;
+%\item there are no colluding attackers inside the Data producer's network;
+%\item the attack is carried only using unique junk Interests; and
+%\item there is only one Data producer for the attacked prefix.
+%\end{itemize}
+
+%We also assume that NDN forwarding strategy uses only single-path Interest forwarding, always choosing the best-metric route advertised by the routing protocol.
+%This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
+
+%In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
+
+\section{Interest flooding mitigation methods}
+\label{sec:design}
+
+% Points what should be here:
+% - What can be done (in general) to mitigate flooding attack
+% - Which building blocks NDN architecture gives to mitigate Interest flooding attacks: Interest limits, ability to measure Interest satisfaction performance (Interest satisfaction stats)
+% - Methods to set these limits: static/dynamic
+% - Methods how limits can be applied: best-effort (fifo), "fair" queuing, probabilistic
+% - Reference to caching: we don't consider it here, but caching provides additional level of protection, especially for certain types of attacks
+
+% Our definition of attack mitigation is that good clients are still able to access data on the producer.
+
+In this section we present several algorithms to mitigate Interest flooding attacks in NDN.
+Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
+We start by describing our simple strategies and use the insights and lessons learned from the deployment of these to inform and design more effective mitigation techniques that work well in various topologies.
+
+%   - Naive approach to Interest Limits (that is called physical limits everywhere else)
+%     Example how this can be implemented in a simple way
+%     Baseline solution
+%   - Interest limits with "fair" queuing
+%     Improving problem of simple limits (no single face can dominate), but doesn't solve the proble
+
+% - Attack mitigation
+%   - Per-incoming interface Interest statistics
+
+%   - Dynamic Interests limit adjustments
+
+%   - Probabilistic Interest accept
+
+%The fact that each Data packet takes the reverse path of the corresponding Interest packet allows intermediate routers to match a received Data packet to the corresponding Interest packet and %thus determine which Interest packets were satisfied.
+As we describe in the rest of this section,  NDN routers can exploit this information to make informed decisions on which Interest packets to %forward, how many Interest packets to forward, and thus effectively defend against DDoS attacks.
+
+%Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
+%Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
+%Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
+%At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
+
+%\subsection{Na\"{i}ve attack mitigation}
+
+%We start with a couple of naive strategies that can be used to migitate attacks in an NDN network and describe the pitfalls associated with these strategies.
+
+% In a normal network operation, the size of Interests packets is supposed to be significantly smaller than the size of the requested Data.
+
+% All communication in NDN network is host-to-host and receiver-driven.
+
+An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests that are forwarded in the network. To this end, we exploit a 
+ fundamental principle of NDN architecture---flow balance between Interest and Data packets.
+The flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
+This principle allows intermediate routers to control the inbound data traffic by controlling the number of outstanding Interests in the network.
+One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding interface.
+This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet-switched networks.
+Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
+Ideally, the number of tokens (the pending \emph{Interests Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
+We can formalize this value as follows:
+% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
+%
+\begin{equation}
+\label{eq:interest limit}
+\small \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
+\end{equation}
+
+In the above equation, \emph{Delay} is the expected time of Interest being satisfied and \emph{Data packet size} is the size of the returned Data packet.
+Although both these values are not known a priori, it is not really necessary to use their exact values.
+One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as the network buffers can smooth out most of the network fluctuations.
+
+This {\it Token Bucket} approach might be exceptionally restrictive in forwarding Interests---not all Interests will result in a Data packet---and might result in underutilization of the network.
+However, the biggest drawback of this algorithm is the fact that it can nourish DDoS attacks.
+If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
+One way to get around the issue is to impose a per interface limit, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
+We describe this technique in greater detail below.
+
+%That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
+%For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
+%In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
+%
+%\subsubsection{\textbf{Interest limits (physical limits)}}
+%\label{sec:physical limits}
+%
+%\input{algos/physical-limits.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{\textbf{Token bucket with per interface fairness}}
+\label{sec:queuing}
+
+To address the lack of fairness associated with the na\"ive {\it Token Bucket} approach, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring nodes.
+For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
+%Due to the expected small volume of Interests, we cannot merely rely on network buffers to perform statistical multiplexing of Interests, as they would almost never be %buffered.
+%At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests %will arrive in the future.
+In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring nodes, 
+%, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
+we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded and implement hierarchical queues for each interface (see Fig.~\ref{fig:queueing}). 
+This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing and incoming interface.
+%As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
+We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
+Thus, a PIT entry can be quickly updated when the Interest is actually forwarded, and the element can be easily removed from the queue when the Interest expires.
+
+%For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}).
+%As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
+
+\begin{figure}[thb]
+  \centering
+  \includegraphics[scale=0.65]{queue}
+  \vspace{-0.7cm}
+  \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
+  \label{fig:queueing}
+\end{figure}
+
+We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
+By setting appropriate queue sizes, we can control the amount of physical resources utilized at a router.
+ % (such as memory and computation power). 
+It is also important to set a sensible value for how long an Interest can be enqueued. 
+If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet might be dropped at the downstream routers if their corresponding state expired. 
+For our evaluations, we empirically chose to enqueue Interests up to 10\% of their original lifetime.
+% We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
+% Alex: I don't believe there is a need for separate discussion about "freshness", as we already introduced concept of lifetime
+% {\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
+
+%It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
+%Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
+%Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
+
+%The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
+%At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
+
+\floatname{algorithm}{\small Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Token bucket with per interface fairness}
+\label{alg:queuing}
+\begin{algorithmic}[1]
+\For{\textbf{each} interface \textbf{if}}
+    \State{$L_{if} \leftarrow$ Interest Limit according to (1)}
+    \State{$O_{if} \leftarrow 0$} \Comment{Outstanding Interests on interface \textbf{if}}
+\EndFor
+
+\vspace{0.1cm}
+
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
+    \If{$L_{out} - O_{out} > 0$} \Comment{\textbf{out} is under limit cap}
+        \State $O_{out} \leftarrow O_{out} + 1$  \Comment{``borrow'' a token from the bucket}
+        \State add \textbf{out} to PIT entry and forward \textbf{i} to \textbf{out}
+    \Else
+        \State Queue $q \leftarrow out$.GetSubQueue($in$)
+        \If{$Size(q) < L_{out}$}
+           \State $q$.PushInterest($i$)
+           \State add \textbf{out} to PIT entry, and link PIT entry with the queue
+        \Else
+           \State drop Interest
+        \EndIf
+    \EndIf
+\EndFunction
+
+\vspace{0.1cm}
+
+\State{} \Comment{\textit{Whenever $L_{out} - O_{out}$ becomes larger than zero}}
+\Function{TokenBecomesAvailable}{}
+    \State Queue $q \leftarrow$ $out$.GetRoundRobinSubQueue 
+    \State Interest $i \leftarrow$ $q$.PopInterest
+    \State update PIT entry and Forward($i$, $out$)
+\EndFunction
+
+\vspace{0.1cm}
+
+\Function{InData}{Data \textbf{d}}
+   \State lookup PIT entry \textbf{p} for data \textbf{d}
+   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
+        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
+   \EndFor
+\EndFunction
+
+\vspace{0.1cm}
+
+\Function{Timeout}{PIT entry $p$}
+   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
+        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
+   \EndFor
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from the Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
+We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is ineffective in protecting legitimate users from malicious ones. 
+Attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of malicious Interests.
+
+%At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
+%Therefore, to successfully solve the problem, we need a fundamentally different, more intelligent approach, allowing localization of the attack traffic as close as possible to the attack origin.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
+The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits a relatively large number of Interests from malicious users.
+A considerable percentage of these malicious Interests are forwarded all the way to content producers, thereby reducing resources available to serve legitimate users.
+This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate and malicious Interests.
+For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and differentiate malicious requests from legitimate ones.
+% `Good' Interests from legitimate users must be admited and forwarded appropriately. 
+Thus, the key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
+
+%One can try a black- or whitelisting approach.
+However, besides the fact that source black- and whitelisting cannot work in %NDN as it does not feature source addresses, it requires extraneous knowledge to classify the incoming Interests.
+
+%Priya: I have added the below point specifically to point out that a router cannot determine from the prefix name alone whether /parc is good  or bad...
+
+%{\color{red} \textbf{Alex: This paragraph is confusing to me.
+I would remove it.} In NDN one cannot easily distinguish a `good' prefix from a `bad' one.
+Content producers must be able to support %dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded %to the producer for possible dynamic Data packet generation.
+%Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the prefix name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain %namespaces  will be inefficient and likely ineffective.
+}
+
+% Alex: I'm not sure that this part is relevant... The point I see is that blacklisting and whitelisting is not 100% effective, but it can be used in both worlds
+
+% In today's host-based Internet architecture where DDoS mitigation techniques rely on blacklisting of ``dark'' IP prefixes or whitelisting of good IP prefixes.
+% Unlike IP, in NDN one cannot easily distinguish a `good' prefix from a `bad' one. 
+% Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
+% Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
+
+\subsection{Intelligent attack mitigation}
+\label{sec:intelligent mitigating}
+
+%While the Interest limit is the key building block to suppress mechanisms of the Interest flooding attack, legitimate Interests need to be somehow prioritized and malicious Interests need to be somehow penalized in order to completely suppress the attack.
+%That is, instead of processing Interests always based on the first-in-first-serve rule, NDN routers need some basis to treat the incoming Interests differently.
+%Thus, the primary task in bringing intelligence to the Interest flooding attack mitigation is to proactively distinguish between legitimate and malicious Interests.
+
+In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets.
+Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guaranteed to see if an Interest it forwarded resulted in a matching Data packet or timed out.
+%The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
+Since malicious Interests are not likely to bring data back (as discussed in Section~\ref{sec:interest-flooding}), this information can be utilized by routers in differentiating attack and legitimate traffic.
+%Therefore, intermediate routers can classify the ones that brings data back as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}
+%Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
+
+This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
+However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest should be forwarded or dropped.
+For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to reasonably predict whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout if forwarded.
+Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
+that can further improve the estimates.
+A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but don't generate a Data stream in return.
+In order to allow negative statistics to build up fast and positive statistics deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.
+
+%Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
+%{\color{red} \it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong %here.}
+
+%The devil is always in the details.
+%From the one hand, such statistics needs to start penalizing adversaries as soon as possible (i.e., negative stats should build up fast).
+%On the other hand, the positive statistics should not deteriorate too fast (i.e., positive stats should be relatively long-term).
+%Our preliminary experiments showed that the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window, provides a good balance between the two contradictory requirements.
+
+% \subsubsection{\textbf{Data plane performance tracking}}
+% \label{sec:stats}
+
+% Note that there is a condition (line 6 in Pseudocode~\ref{alg:probabilistic model}) to check if there is a valid statistics point.
+% This condition is extremely important, because it first provides a basis to distinguish between known facts (i.e., good or bad satisfaction ratio for the incoming interface) and unknown facts (e.g., the first time an Interests arrives on the interfaces).
+% Second, it gives an opportunity to recover from a bad history (history of unsatisfied Interests) after malicious Interests are ceased to flow in.
+% Essentially, this recovery relies on statistics module to perform time-based invalidation of historical data (timely, but not too quickly\footnote{Otherwise, attackers may send short bursts of malicious Interests, successfully avoiding differential Interest treatment}).
+
+Pseudocode~\ref{algo:interest stats} formally defines how statistics can be generated for  each incoming interface.
+Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interest), only unsatisfied statistics needs to be exponentially smoothed (lines 23--26).
+
+\floatname{algorithm}{\small Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Interest satisfaction statistics}
+\label{algo:interest stats}
+\begin{algorithmic}[1]
+
+\For{\textbf{each} interface \textbf{if}}
+    \State $F_{if} \leftarrow 0$ \Comment{forwarded Interests from interface \textbf{if}}
+    \State $\hat F_{if} \leftarrow 0$ \Comment{averaged value of $F_{if}$}
+
+    \State $U_{if} \leftarrow 0$ \Comment{unsatisfied Interests from interface \textbf{if}}
+    \State $\hat U_{if} \leftarrow 0$ \Comment{averaged value of $U_{if}$}
+\EndFor
+
+\vspace{0.1cm}
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}}
+  \State $F_{in} \leftarrow F_{in} + 1$
+  \State record \textbf{\emph{in}} in the list of incoming interfaces for \textbf{\emph{i}}
+\EndFunction
+
+\vspace{0.1cm}
+\Function{InterestTimeout}{Interest \textbf{i}}
+    \State lookup the list of incoming interfaces for \textbf{\emph{i}}
+
+    \For{\textbf{each} interface \textbf{if} in the list}
+        \State $U_{if} \leftarrow U_{if} + 1$
+    \EndFor
+\EndFunction
+
+\vspace{0.1cm}
+
+\State {} \Comment{\textit{Exponentially weighted moving average smoothing}}
+\Function{EWMA}{} \Comment{Every second}
+\State $\alpha \leftarrow e^{-1.0/30.0}$  %\Comment{$\approx$ 30~sec average}
+
+\For{\textbf{each} interface \textbf{if}}
+    \State $\hat U_{if} \leftarrow \alpha \cdot \hat U_{if} + (1 - \alpha) \cdot U_{if}$ 
+    \State $U_{if} \leftarrow 0$
+
+    \If{$F_{if} > 0$} \Comment{To ensure decaying of ratio $U_{if}/F_{if}$}
+        \State $\hat F_{if} \leftarrow \alpha \cdot \hat F_{if} + (1 - \alpha) \cdot I_{if}$ 
+        \State $F_{if} \leftarrow 0$ \Comment{Reset counters}
+    \EndIf
+\EndFor
+
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+Fig.~\ref{fig:ratio example} illustrates the resulting dynamics of the statistic during and after an Interest flooding attack.
+The attack duration is from 10 to 70~seconds.
+Prior to start of the attack, the percentage of unsatisfied Interests is zero.
+The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.
+%\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
+For the duration of the attack (10--70~seconds), the percentage of unsatisfied Interests is close to 100\%: 
+when the ratio is close to 100\%, routers drop all incoming Interests, resulting in decaying of the statistics until a new Interest is admitted, which eventually brings statistics back near 100\% point.
+Finally, the ratio exponentially decays after the attack ceases.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.8]{limits}
+  \vspace{-0.3cm}
+  \caption{Dynamics of the unsatisfied Interests statistics on gateway's interface towards the attacker}
+  \label{fig:ratio example}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{\textbf{Satisfaction-based Interest acceptance}}
+\label{sec:probabilistic}
+
+Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using these ratios to penalize malicious Interests.
+A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as the direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
+%Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
+
+\floatname{algorithm}{\small Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Satisfaction-based Interest acceptance}
+\label{alg:probabilistic model}
+\begin{algorithmic}[1]
+\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+
+\vspace{0.1cm}
+\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
+
+    \State{} \Comment{Use uniform probability distribution model $P(X)$}
+    \State{} \Comment{$P(X) : \forall x \in [0,1] \Rightarrow P(x) = x$}
+
+    \If{$F_{in} > \theta $} \Comment{At least some Interests were forwarded before}
+        \State $s \leftarrow (1 - U_{in} / F_{in})$
+        \State Drop interest with probability $P(s)$
+    \EndIf
+
+    \State{forward the Interest, subjecting to token bucket limits}
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+Parameter $\theta$ on line 5 of the Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
+This step is critical to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
+
+A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop an Interest. 
+As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
+In example on Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
+At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
+Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the data producer.
+With each increasing hop in the network, the probability of being forwarded to the next hop decreases significantly.
+One way to prevent this overreaction and unfair penalization is to ensure that the decision taken at each router on whether to forward or drop the Interest is not independent of the decision taken at preceding routers.
+An explicit notification such as a gossip protocol between neighboring NDN routers might alleviate the problem, but we leave the design and evaluation of it to future work.
+%{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{\textbf{Satisfaction-based pushback}}
+\label{sec:dynamic limits}
+
+% Differential treatment of Interests received from different interfaces can be achieved in a more elegant way, without reverting to probabilistic methods.
+
+The previous algorithm---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
+% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
+An alternate algorithm for proportional token distribution without overreaction is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
+Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.
+
+The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm will work in our example in Fig.~\ref{fig:flooding example}.
+Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node will set and announce the following  incoming interface limit $L'$:
+\begin{enumerate}
+\item router B will set and announce the incoming interface limit $L'=3$;
+\item router A, after receiving announcement from B will readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
+\item both legitimate users and adversaries may either obey or ignore the announced limit, which will be in any case enforced by router A.
+\end{enumerate}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.3]{dynamic-limits}
+  \vspace{-0.3cm}
+  \caption{Satisfaction-based pushback example
+%: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer%
+}
+  \label{fig:dynamic limits example}
+\end{figure}
+
+\floatname{algorithm}{\small Pseudocode}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{ 
+\begin{algorithm}[h]
+\footnotesize
+\caption{\small Satisfaction-based pushback}
+\label{alg:dynamic limits}
+\begin{algorithmic}[1]
+% \State{}\Comment{Same initialization, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
+\vspace{0.1cm}
+\State{$\forall f \in \mathrm{interfaces} : L'_{f} \leftarrow L_{f}$} \Comment{Per-incoming interface Interest limit}
+
+\vspace{0.1cm}
+
+\State{} \Comment{\textit{Announcement from the neighbor}}
+\Function{InLimits}{InInterface $in$, Limit $L'$}
+    \State $L_{in} \leftarrow L'$
+\EndFunction
+
+\vspace{0.1cm}
+
+\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
+\For{\textbf{each} outgoing interface $out$}
+
+   \For{\textbf{each} incoming interface $in$}
+        \State $L'_{in}= {L_{out}} \times (1 - U_{in}/F_{in})$
+        \State AnnounceLimit($in$, $L'_{in}$)
+   \EndFor
+
+\EndFor
+\EndFunction
+
+\end{algorithmic}
+\end{algorithm}
+
+The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to the appropriate level (recall Fig.~\ref{fig:ratio example}).
+At the next iteration of the satisfaction-based pushback algorithm, the legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
+
+We note that while in the description of the satisfaction-based pushback algorithm we explicitly used ``outgoing'' and ``incoming'' interfaces,  all interfaces can be both incoming and outgoing.
+Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
+To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
+That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
+
+Both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, but with several core differences. 
+First, we are suppressing (pushing back) unwanted requests for data, not actual data itself.
+Second, differentiating between good and bad Interests is based on the traffic symmetry principle of NDN.
+% Alex: I'm not entirely sure about this point... 
+Finally, both intelligent attack mitigation algorithms can be deployed at all times without degrading network performance even when there are no active attackers.
+
+\section{Evaluation of Interest flooding mitigation methods}
+\label{sec:evaluation}
+
+% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
+
+% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers,
+
+% alex: what's a point of latency?  it would matter only for queueing method and we not really pushing this method
+% Latency for good clients, good versus bad interests as a function of time
+
+In this section, we present an in-depth evaluation study, aiming to quantify the effectiveness of all our Interest flooding attack mitigation methods.
+We used the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator (\url{http://www.nsnam.org/}), to run simulations for a variety of network topologies and scenarios.
+We extended ndnSIM with our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback---and evaluated effectiveness of each algorithm independently.
+
+% For evaluating the effectiveness of each mitigation algorithm, every router in the simulated topology runs the mitigation algorithm under study.
+
+% why we chose small scale topology
+% what point we wanted to show we small scale
+% what points we wanted to verify with larger-scale internet like topology
+
+% Metrics
+% not sure if i already explained that. our essential qualitative metric is .  
+% To quantify the effectiveness of the mitigation mechanism this  metric we use satisfaction percentages of user Interests.
+
+The metric we choose to quantify the effectiveness of our algorithms is the {\it percentage of satisfied Interests for legitimate users}.
+This metric corresponds to the quality of service experienced by legitimate users when the network is under attack.
+In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conclude that method $X$ is highly effective at mitigating the attack.% We also ensure that all Interests expressed by legitimate users during a period of no-attack are satisfied.
+
+%Quality of the attack mitigation methods directly corresponds to the quality of service for the legitimate users during an ongoing attack, which in NDN network can be quantified through percentage of satisfied Interest.
+%For example, if the network implements a mitigation method $X$ and under the attack majority of user-expressed Interests are getting satisfied, then the method $X$ can be seen as highly effective.
+%At the same time, if only a small percentage of the expressed Interest are getting satisfied during the attack, the method $X$ can be called ineffective.
+
+% Traffic pattern
+In our experiments, we assumed that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution.
+We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
+To quantify the behavior of our mitigation strategies under a worst-case attack scenario, we assumed that all the attackers send junk Interests as fast as they can, no Interest---including legitimate ones---can be satisfied from caches.
+Also, we configured routers for the single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
+%(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
+
+% Alex: not sure how to argue about the traffic pattern
+%Although this pattern may seem not truly realistic, it approximates a good statistical mix of traffic from all network users without excessive network buffering.
+
+%In addition to that, in each run of the simulation we ensure that all Interests expressed by the legitimate users during a no-attack period are satisfied.
+%For simplicity, we also equalized the average rates with which the legitimate users express Interests.
+%At the same time, the attackers are sending junk Interests as much as they can get through (remember, that Interest limits will not allow real f%looding of Intersests in all of the designed mitigation algorithms).
+
+We ran our simulations on two different network topologies---a smaller binary tree topology and a much larger ISP-like topology.
+We use a binary tree topology as it represents one of the worst cases to defend against Interest flooding DDoS attacks.
+The larger ISP topology reflects how our mitigation methods would perform when deployed on the real Internet.
+Again, to study the performance of our mitigation strategies under a range of conditions, we also varied the percentage of attackers in the network---the values ranged from 6\% attackers to over 50\% attackers in the network.
+
+% Fixed parameters
+We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation (\ref{eq:interest limit}) to a fixed 
+value for every node in the simulated topology.
+In particular, for the small-scale binary tree topology, we set delay to 80~ms, while for the large-scale ISP topology we set it to 330~ms (the order of the largest RTT).
+The data size is 1100~bytes for all simulation runs and topologies.
+% THIS IS BULLSHIT!
+There is absolutely no logic to set the delay to the same value on all nodes in the network.
+We discussed multiple times that you should fix it so that the delays are realistic and gets smaller as the nodes gets closer to the producer...
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Small-scale evaluations}
+\label{sec:small-scale}
+
+% Topology description
+%To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a %simplistic small-scale binary tree topology 
+In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we used for our initial experiments.
+Legitimate users as well as attackers were placed on leaf nodes (top row of red nodes) as shown in the figure.
+There are 16 end users (both legitimate and attackers) in this topology, each expressing Interests that are routed towards a single data producer, placed at the root of the tree.
+Each link in this topology is assigned a bandwidth of 10~Mbps and a randomized propagation delay ranging from 1 to 10 ms.
+
+% Alex: should we mention that?
+%The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS %attacks.
+%That is, sharing of the network links exponentially increases as decreasing level of the binary tree.
+
+\begin{figure}[]
+  \centering
+  \includegraphics[scale=0.2]{topo-tree-evil-5-good-0-producer-gw}
+  \caption{Small-scale binary tree topology}
+  \label{fig:small-scale}
+\end{figure}
+
+% in 10 independent runs of each simulation, where we randomized position of the adversaries along the legitimate users.
+In all runs, the total number of legitimate and malicious uses were fixed, meaning that when we increase number of attackers, we decrease the number of legitimate users.
+
+\subsubsection{Effectiveness of the three mitigation algorithms}
+
+%The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
+%For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).
+
+Our goal is to compare the effectiveness of each mitigation method and quantify the percentage of Interests satisfied for all legitimate users while the network is under attack.
+For each mitigation algorithm, we perform 10 independent simulation runs, where we randomly choose 7 client nodes to represent adversaries while the remaining 9 client nodes represent legitimate users.
+In each run we simulate a 10-minute attack window (total simulation time was 30 minutes, with attack starting at the 10-minute mark).
+We plot the minimum and maximum range for observed Interest satisfaction percentages for all legitimate users aggregated across the 10 simulation runs as a function of time for each mitigation algorithm in Fig.~\ref{fig:small-scale attack progress}.
+Token bucket with per-interface fair queuing performs the worst, while satisfaction-based pushback performs the best, with almost a 100\%  satisfied Interests for all legitimate users.
+
+%A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
+
+\begin{figure}[]
+  \centering
+  \hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
+  \vspace{-.3cm}
+  \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
+  \label{fig:small-scale attack progress}
+  \vspace{-.4cm}
+\end{figure}
+
+%\paragraph{\textbf{Simple token bucket}}
+
+%{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}
+
+%Let us take a deeper look on what is happening with the simple token bucket algorithm.
+%Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as token bucket restricts the number of forwarded Intersets!).
+%This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
+%In this example we assume that both the legitimate user and the adversary send Interests in about the same time.
+%
+%\begin{figure}[t]
+%  \centering
+%  \includegraphics[scale=0.3]{physical-limits-sync-problem}
+%  \caption{Three-router topology, with one legitimate and one malicious user}
+%  \label{fig:three router example}
+%\end{figure}
+%
+%Both router L and router X will forward the Interests, as both of them have a free token available.
+%At router A, two cases are possible, either of Interests can arrive first, resulting in a quite different effects.
+%When legitimate Interest arrives first, then there are no problem. 
+%Router A will capture the token, forward the Interest, which will be quickly satisfied, releasing the token for future uses.
+%In the mean time, malicious Interest will be dropped at router A, and router X will release the hold for the token in one second (i.e., after the maximum time Interests are admitted), enabling a new round of competition for router A's resources.
+%
+%In the case when malicious Interest is sent a little bit earlier, then router A will forward malicious Interests, dropping a legitimate one, and causing ``lock out'' for one second.
+%In the instant when the token gets released at router X, an adversary is able to push new Interest towards router A, which may arrive in the exact time A's token gets released (assuming an idealistic environment).
+%As a result, the adversary recaptures router A's token and extends the ``lock out'' for another second, denying service to the legitimate user without sending any massive numbers of Interests.
+
+\paragraph{\textbf{Token bucket with per interface fairness}}
+
+We observe a successful DDoS attack, where 40\% attackers succeed in significantly shutting down the remaining 60\% legitimate users---a mere 15\% of their Interests are satisfied by Data from the producer.
+Contrary to expectations, the 60\% legitimate users do not receive at least 60\% of network resources.
+As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers and causes congestion and packet drops near the victim.
+%Significantly reducing the number of accepted malicious Interests is fundamental for improving the effectiveness of any mitigation algorithm.
+
+%The described problem arises from the clocking effect and can be solved in a number different ways.
+%Augmenting token bucket algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
+%That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
+%However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
+%Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
+%We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.
+
+\paragraph{\textbf{Satisfaction-based Interest acceptance}}
+
+The effectiveness of this algorithm stems from the fact that routers can differentiate and limit malicious Interests into the network%, thereby ensuring availability of network resources for serving legitimate users
+.
+The observed periodic dips in the Interest satisfaction ratios of legitimate users in Fig.~\ref{fig:small-scale attack progress} is a direct result of Interest satisfaction rate statistics decaying with time.
+The 50-second period approximately corresponds to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx$20\% within 50~seconds.
+ % that ranges from 30~seconds to 50~seconds. 
+%The primary reason that such minimum peaks exist is the fact that 
+When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe mixed traffic from legitimate and malicious users).
+Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' again to the edge.
+
+%When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
+%That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
+
+\paragraph{\textbf{Satisfaction-based pushback}}
+
+In our simulations, this mitigation algorithm was able to effectively shut down attackers and ensure almost all the Interests from legitimate users are satisfied. 
+%The only potential problem with the satisfaction-based pushback algorithm is that it features 
+We observe a  sharp dip in the satisfaction ratio curve at the start of the attack as it takes a few seconds for all routers to be fully aware of the attack.
+Recovery quickly happens as malicious Interests start to time out and explicit Interest limit announcements start to succeed in containing malicious Interests close to the attacker.
+Till then, the network, for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
+Once the malicious Interests are effectively shut down, all Interests from legitimate users are satisfied.
+Unlike the satisfaction-based Interest acceptance scenario, we do not observe any periodic dips in the satisfaction curve, as the pushback algorithm effectively guarantees that once an Interest is admitted, it will likely be routed all the way to the data producer.
+
+\subsubsection{Network reaction to varying number of attackers}
+
+Our next goal is to study the effectiveness of our mitigation algorithms as a function of increasing adversaries in the network.
+To this end, we vary the percentage of attackers in the topology from 6\% to over 50\%.
+Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
+All other parameters and experimental setup are consistent with the previous experiment.
+As before, for each mitigation algorithm, we perform 10 independent simulation runs.
+%The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
+%To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.
+
+%Since at this point the overall attack dynamics of all the attack mitigation algorithms is relatively clear, 
+% In other words, each point captured in the box plot graph corresponds to 1-second averaged satisfaction ratio for a user in an individual simulation run.
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
+  \vspace{-.3cm}
+  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}\vspace{-.1cm}
+  \label{fig:small-scale-topo boxplot}
+\end{figure}
+
+In Fig.\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
+The results are as expected---for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
+In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.
+While the two intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
+In the case of satisfaction-based pushback algorithm, during the first minute of the attack over 90\% of Interests from legitimate users are satisfied even if the 50\% of end nodes are malicious.
+
+% \begin{figure}[htbp]
+%   \centering
+%   \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min-after-1-min}
+%   \caption{Average consumer Interest satisfaction ratios (second minute)}
+%   \label{fig:small-scale-topo 2}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Large scale simulations}
+\label{sec:largescale}
+
+%To check validity of the small-scale experiment results, we performed a larger-scale evaluation based on a modified version of
+
+In this section, we investigate the behavior of our mitigation strategies under a more realistic, large-scale network topology.
+The ISP topology we employed is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
+%In order to approximate the general structure of the Internet,
+% (scale-free structure, customer-provider, and peer-to-peer relations)
+We extract the largest connected component comprising of 562 nodes from this original topology and separate the nodes into three categories: clients, gateways, and backbones.
+Nodes having degree less than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes as classified as backbones (109 blue nodes).
+%(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
+We assign bandwidth and  delay values to links based on their type---both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
+We experiment with placing the data producer at both a gateway node as well as backbone node, which we randomly pick for each simulation run.
+Similar to the binary tree topology experiments, we fix the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly pick these nodes for each simulation run.
+We conduct 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5-minute interval.
+
+\begin{figure}[htbp]
+  \centering
+  \vspace{-.1cm}\includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
+  \vspace{-0.3cm}
+  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}\vspace{-.2cm}
+  \label{fig:large-scale-topo}
+\end{figure}
+
+\begin{table}[htbp]
+\centering
+\caption{Large-scale topology link bandwidth and delay ranges}
+\vspace{-0.3cm}
+\label{tab:large-scale}
+\begin{tabular}{|l||c|c||c|c|}
+  \hline
+  \multirow{2}{*}{\bf Link type} &  \multicolumn{2}{|c||}{\bf Delay} &  \multicolumn{2}{|c|}{\bf Bandwidth} \tabularnewline
+  \cline{2-5}
+                        &  Min & Max                       &  Min & Max \tabularnewline
+  \hline \hline
+  Backbone--Backbone    & 5~ms & 10~ms   & 40~Mbps & 100~Mbps \tabularnewline
+  \hline
+  Gateway--Backbone,    & \multirow{2}{*}{5~ms} & \multirow{2}{*}{10~ms}   
+                        & \multirow{2}{*}{10~Mbps} & \multirow{2}{*}{20~Mbps} \tabularnewline
+  Gateway--Gateway      & & & & \\
+  \hline
+  Client--Gateway       & 10~ms & 70~ms   & 1~Mbps  & 3~Mbps \\
+  \hline
+\end{tabular}
+\vspace{-0.3cm}
+\end{table}
+
+%Priya: Leaving out this in the interest of space...
+%Topological location of the data producer plays a key role in its resilience to Interest flooding attacks.
+For a data producer that %is connected to a client node via a low-bandwidth link, even a small number of junk Interests can impact services for legitimate %users.
+For a producer located at the backbone with rich connectivity through many high-bandwidth links, an attack might not %be as severe as a majority of legitimate users might not be on the attack path.
+
+% The results for all attack mitigation algorithms and all runs are aggregated in Fig.~\ref{fig:small-scale attack progress}, where Y-axis represents a minimum and maximum range for observed Interest satisfaction percentages among all nodes and all simulation runs.
+% A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
+
+In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over all simulations runs for each mitigation algorithm for the scenario, where the data producer is placed at a gateway node.
+We observe similar results for the data producer placed at the backbone node as well.
+Unlike the binary-tree topology experiments, we observe that the satisfaction-based pushback is the most effective algorithm, while both the token bucket with per interface fairness and satisfaction-based Interest accept have poor performance.
+Interest satisfaction percentage for legitimate users are close to 100\% and approximately 30\% and 25\% respectively for these mitigation methodologies.
+
+%
+%The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
+
+\begin{figure}[tbh]
+ \centering
+ \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
+ \vspace{-.3cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.3cm}
+ % producer on a gateway node
+ \label{fig:large-scale}
+\end{figure}
+
+Satisfaction-based Interest acceptance algorithm, which was very effective for binary-tree topology, is completely ineffective when deployed in a larger and more realistic topology.
+For the duration of the attack, legitimate users experience poor quality of service with only 25\% of their Interests being satisfied and continue to experience degraded service long after the attack has stopped.
+This poor performance, as detailed in Section~\ref{sec:probabilistic}, is due to the fact that each router on the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
+In the case of the larger-topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics and further penalization of new Interests from them.
+
+All our evaluations leaves us with the conclusion that, among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most promising one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
+%The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
+As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.
+
+% Alex: Anything else here?
+
+% Alex: I also experimented with placing producer at the backbone, getting slightly better results for all algorithms.  Though I'm not sure there is any value to put those results in the paper
+
+% \input{simulation-emulation.tex}
+
+\subsection{Limitations}
+%{\color{red} I gave up the idea of seperate discussion section after trying for some time, as given the space limitation, there is no way to write a reasonably comprehensive and  broad discussion section that justifies a separate section.
+Instead, I decided to have a scoped down version here that confesses upon the limiations of our evaluations only.
+Whoever has time (I need to sleep few hours), please go ahead and write 1-2 paragraphs as I outlined below.
+-Ersin}
+
+%This section should roughly say: Our results show that the two features, namely the symmetric traffic and stateful routing, give NDN routers the ability to observe and characterize traffic in real time.
+Through our evaluations, we demonstrated that a mitigation algorithm that leverages such ability has great potential in mitigating various DDoS attacks that could otherwise have grave effect on the network.
+However, as the first step in exploring the problem and the solution space, this paper has obvious limitations: (1) We assume a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations.
+Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step is evaluating the above described solutions with more sophisticated and adaptive attackers.
+(2)   Although most (such as single-path routing, no-caches in the network, single homed victim, etc) are aimed to test the proposed solutions under worst-case scenario, we made many assumptions in simulations/evaluations about the configurations, topology and the traffic that maybe poor-representative of realistic conditions.
+(3) As NDN being an ongoing research effort itself, our evaluations fully depend on simulations and done over a snapshot of its codebase.
+
+% The main contribution of the paper and this section in particular is a proof that two inherent properties of NDN architecture, namely the symmetric traffic and stateful forwarding, give NDN routers the ability to characterize traffic and react in real time.
+% We demonstrated that satisfaction-based pushback algorithm, leveraging this ability, has great potential in mitigating various DDoS attacks that could otherwise have a grave effect on the network. 
+% However, as the first step in exploring the problem and the solution space, our paper has obvious limitations.
+% First, we assumed a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations. 
+% Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step that we are leaving out for future work is evaluating the above described solutions with more sophisticated and adaptive attackers.
+% Second, while aiming to test the designed algorithms under worst-case conditions, the future work needs to address behavior in more realistic scenarios, including investigation of multi-path routing, in network caches, as well as multi-homed victims.
+
+This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space. 
+While designing our mitigation algorithms, we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
+We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology, % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
+as well as a more realistic ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network. 
+While our results are promising and show a great potential in mitigating Interest flooding DDoS attacks, there are certain limitations which should be addressed in future research.
+
+First, in our evaluations we used a simple and static attacker model---attackers send junk Interests as fast as possible. 
+In the future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and Interest sending patterns based on the network reaction.
+Second, we made an assumption that Interests are not satisfied by an intermediate router's cache and always forwarded all the way to the producer.  
+The future work needs to study impact of Interest flooding attack in more realistic scenarios with multi-path routing, more realistic traffic patterns, and presence of in network caches.
+% We also ignored NDN's strategy layer that routes around failure and congestion in the network. 
+% In future work, we plan to study the impact of turning on these features. 
+%Finally, we also plan to perform more extensive simulations on other realistic Internet-like topologies and traffic patterns.
+
+\section{Related work}
+\label{sec:related-work}
+
+As a new Internet architecture proposal, the Named Data Networking has attracted attention from the security community. 
+Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
+W\"ahlisch et al.~\cite{Wahlisch:2012:Backscatter-from} explore security and stability threats in the general area of information-centric networks (ICN), using CCNx software as an example.  
+While this work aims to generalize findings for all ICNs, it largely does not go beyond the current design choices of CCNx.
+% (which is an example, but not the final word in NDN) 
+% Gasti et al.~\cite{gasti2012ddos} identified several NDN architecture-specific attacks (Interest flooding and content/cache poisoning) and proposed potential solutions, without devising particular algorithms.
+In this paper we follow the suggestions by Gasti et al.~\cite{gasti2012ddos} and utilize the properties provided by the NDN architecture to mitigate DDoS attacks, and tackle the Interest flooding problem as a first step in this direction.
+More specifically our attack mitigation design relies on NDN's stateful forwarding plane 
+which provides statistics on unsatisfied Interests.  
+Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
+
+The general area of mitigating denial of service attacks is among the hottest topics in recent years.
+% Among all the body of work, 
+The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushbacking malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
+overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
+various ticketing systems with conditional admission of traffic to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
+and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
+Identifying malicious traffic requires establishing certain state at routers, and the above mentioned solutions differ in the specifics on what state to use and how to establish it.
+By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions.
+Therefore, one can simply take full advantage of this state to develop desired solutions.
+
+% Our design for the Interest flooding attack mitigation borrows
+
+% This paper talks about attacks on content centric infrastructure (not specifically to NDN).
+% \cite{Wahlisch:2012:Backscatter-from}
+
+% % Collaborative detection of DDoS attacks over multiple network domains
+% \cite{Chen:2007:Collaborative-detection} distributed change-point detection
+
+% % DDoS flooding attack detection through a step-by-step investigation
+% \cite{Jun:2011:DDoS-flooding}
+
+% % A practical method to counteract denial of service attacks
+% \cite{Tupakula:2003:A-practical-method}
+
+% Alex: We should not include this reference for the review, but afterwards
+% Previous work on DDoS and DoS~\cite{gasti2012ddos}
+
+% Network level (Flooding)
+% % 2002
+% Pushback~\cite{Pushback} (hop-by-hop push back) aggregate- based congestion control/congestion signatures (e.g., per-destination), rate-limiting, explicit notification
+% AITF~\cite{Argyraki:2005:Active-internet} (active filtering requests; path recording, last-point of trust detecting)?
+% DefCOM \cite{Oikonomou:2006:A-framework-for-a-collaborative} Communication between src, core, and dst to provide collaborative defense.
+Dst raises alerts, src differentiate bad/good, packet tagging.
+Core rate-limit, congestion-aware re-tag.
+Traffic prioritization.
+% StopIt \cite{Liu:2008:To-filter-or-to-authorize:} (filtering) tagging with passports, tagged prioritization, dst- invoked filter instantiation
+% NetFence \cite{Liu:2010:NetFence:-preventing} congestion policing: fair queuing (one leaky bucket per {src,L}, L- bottleneck), secure "ticketing" with signals for AIMD to increase/decrease bandwidth allowance
+% PSP \cite{Chou:2009:Proactive-surge} topology as origin-destination pairs, packet tagging, OD traffic isolation, sharing based on historic bandwidth demand
+
+% SIFF~\cite{Yaar:2004:SIFF:-A-stateless} (time-based tickets, capabilities)
+% TVA \cite{Yang:2005:A-DoS-limiting-network} like SIFF, traffic- based tickets, hierarchical per- AS, per-source fair queuing
+% FastPass \cite{Wendlandt:2006:Fastpass:-Providing} (tokens: various puzzles, other methods) traffic authorization, routers verify and filter.
+% \cite{Natu:2007:Fine-grained-capabilities} based on TVA/SIFF: specifies previously unspecified mechanisms to grant "tickets" for requesters, extends capabilities to include priorities, changing tickets to be only destination- dependent, not path dependent
+% % LazySusan \cite{Crowcroft:2007:Lazy-Susan:} TR (latency-based proof of work--- computational puzzles)
+% Portcullis \cite{Portcullis} Protecting connection setup with computational proof of work, tickets and traffic prioritization for the rest, per- computational fairness; DNS to disseminate puzzles
+% There are many other puzzle- based schemes, on which Portcullis is based or which problems it solves
+
+% PacketSymmetry \cite{Kreibich:2005:Using-packet} (leverages packet symmetry to detect and remove bad traffic) packet asymmetry - number of transmitted packets (tx) to received packets (rx); negative values when rx outweighs tx, positive values when tx outweighs rx, and zero in the case of perfectly balanced traffic)
+% % Detecting SYN flooding attacks
+% \cite{Wang:2002:Detecting-SYN-flooding} based on the protocol behavior of TCP SYN-FIN (RST) pairs, and is an instance of the Seqnential Change Point Detection
+% dFence \cite{Mahimkar:2007:dFence:-Transparent} (middleboxes) TCP connection proxying, rate estimation and TCP/ACK modification
+
+% Overlays:
+% CenterTrack \cite{Stone:2000:CenterTrack:-An-IP-overlay} (overlay) reroute suspicious traffic to a special routers with diagnostic capabilities using an overlay
+% SOS \cite{Keromytis:2004:SOS:-An-architecture}
+% Shield \cite{Kline:2011:Shield:-DoS-filtering}
+
+% NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
+In this section we will overview generic directions of DDoS mitigation designs and try to think about which tricks could be used in NDN.
+
+% Capability-based systems allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
+Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
+This implies that each client must pass through an authentication process prior to using any bandwidth~\cite{Capabilities}.
+We believe that for NDN this method doesn't fit really well for the following reasons.
+First, this method is very questionable in terms of scalability and mobility support since it requires tight trust connections between routers and hosts.
+Thus, it neglects one of the main advantages (mobility) of NDN.
+Second, the design of trust infrastructure for NDN is not well defined yet, which means that we cannot really make assumptions in our design of mitigation techniques.
+
+% Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
+Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients.
+One of the main difficulties in such systems is the question of puzzle dessimination.
+In ~\cite{Portcullis} authors suggested to propagate puzzles using DNS system.
+In NDN since routers have caching abilities, we can propagate puzzles just like a normal data packets, using Interest-Data exchange.
+Overall, this method looks interesting and deserves being investigated in a future work.
+
+% Congestion control systems do per flow traffic analysis and drop of packets belonging to misbehaving flows.
+For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
+Such techniques, if largely deployed, could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
+Since NDN routers maintain a richer per-packet state, which translates into a better per-flow statistics, these techniques can become much more effective when applied to NDN.
+
+% Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
+This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines~\cite{Pushback}.
+In general this technique can be applied to NDN architecture thanks to its decentralized coordination of downrating bad traffic flows.
+Moreover, NDN provides better capabilities for accurate flow detection.
+
+%were looking for getting accustomed
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+% Main take out from the paper:  could be a problem, but problem is solvable.  
+% One of the key components in the Named Data Networking architecture is its stateful data delivery model, which potentially can be abused by new types of denial of service attacks.
+% However, one should not forget that the same stateful data delivery provides effective mechanisms to fight back against such attacks.
+
+%In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
+%The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data path symmetry and full receiver-based traffic control.
+%In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Interests can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
+%
+%Other forms of attack may require different mitigation mechanisms.  
+%However, the granularity of the NDN state---per each Interest packet---is what giving NDN an opportunity to stand against existing and new forms of attacks.
+%
+%NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution.
+
+NDN is a newly proposed future Internet architecture, thus it is important to address its resilience in face of DDoS attacks.
+As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks, Interest flooding, and the severe service degradation such an attack may cause to legitimate users.
+We then leveraged the key features of the NDN architecture to design, develop, and evaluate three mitigation strategies.
+We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
+The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers, so that they cause little or no service impact on legitimate users.
+
+NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balancing (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding}.
+Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as an evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.
 

### 2013-03-25 paper.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@946 df1a90cd-247b-4364-bdaf-287a704eb499
Done till section IV
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@947 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \usepackage{graphicx}
-\usepackage[]{hyperref}
+%\usepackage[]{hyperref} %IEEE does not like hyperrefs...
 \usepackage{breakurl}
@@
 \begin{abstract}
-Distributed Denial of Service attack is an ongoing problem in today's Internet, where packets from large numbers of compromised hosts thwart the paths to the victim site and/or overload the victim machines.
+Distributed Denial of Service (DDoS) attacks are an ongoing problem in today's Internet, where packets from a large number of compromised hosts thwart the paths to the victim site and/or overload the victim machines.
 In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network delivers Data packets upon request only, effectively eliminating many existing DDoS attacks.
@@
 In this paper we investigate effective solutions to mitigate Interest flooding.
-We show that NDN's inherent properties to keep per packet state on each router and flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
+We show that NDN's inherent properties of storing per packet state on each router and maintaining flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
 Our evaluation through simulations shows that the solution can quickly and effectively respond and mitigate Interest flooding.
@@
 Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an ongoing research effort that aims to move the Internet into the future with a content-centric design that is capable of efficient content distribution and seamless mobility support.
-In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in packets.
-However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against distributed denial of service (DDoS) attacks?
+In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in the packets.
+However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against DDoS attacks?
 Especially since various forms of DDoS attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial to ensure that the new design is free of similar vulnerabilities.
@@
 However, malicious users can attack the network by sending an excessive number of Interests. 
-Because each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can congest the network and exhaust routers' memory resources. 
+Since each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can congest the network and exhaust a router's memory. 
 We coin the term {\it Interest flooding} to refer to such attack and
@@
 The rest of the paper is organized as follows.
-We give an overview of NDN architecture in Section~\ref{sec:ccn-intro} and explain interest flooding attacks in Section~\ref{sec:interest-flooding}.
+We provide an overview of NDN architecture in Section~\ref{sec:ccn-intro} and describe Interest flooding attacks in Section~\ref{sec:interest-flooding}.
 In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
-We summarize related work in Section~\ref{sec:related-work} and finalize the paper with conclusions and future work in Section~\ref{sec:conclusion}.
+We summarize related work in Section~\ref{sec:related-work} .
+We discuss future work and conclude in Section~\ref{sec:conclusion}.
 
@@
 NDN is a receiver-driven, data-centric communication protocol.
-All communication in NDN is performed using two distinct types of packets: \textit{Interest} and \textit{Data}.
-Both types of packets carry a \textit{name}, which uniquely identifies a piece of data that can be carried in one Data packet.
+All communications in NDN are performed using two distinct types of packets: \textit{Interest} and \textit{Data}.
+Both types of packets carry a \textit{name}, which uniquely identifies a piece of content that can be carried in one Data packet.
 Data names in NDN are hierarchically structured and an example name for the first segment of a youtube video would look like: \ndnName{/youtube/videos/0F8YdlkKO9A/0}.
@@
 Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicates the same Interest is forwarded along multiple paths.
-\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, defining allowed directions to where Interests can be forwarded. 
+\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, specifying directions where Interests can be forwarded. 
 % Having one-to-many relationship in this table allows multipath forwarding of Interests.}
@@
 or an Interest from another consumer asking for the same Data, which requires the incoming interface of this Interest to be added to the existing PIT entry.
-If the name does not exist in the PIT, the Interest is added into the PIT and forwarded to the interface chosen by the strategy module, which uses FIB as input for its decisions.
+If the name does not exist in the PIT, the Interest is added into the PIT and forwarded along the interface chosen by the strategy module, which uses FIB as input for its decisions.
 
@@
 This makes them a potential tool to launch DDoS attacks in NDN.
-An attacker or a set of distributed attackers can inject excessive amounts of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
+An attacker or a set of distributed attackers can inject excessive number of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
 
@@
 To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2) new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
-The former is achieved when interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers --an interest is not forwarded upstream if a router can satisfy it from its content store.
-The latter requires every single malicious Interest to ask for a unique content --all Interests requesting the same content are collapsed to one PIT entry in routers.
-Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content at each interest.
-Among the two options of an adversary, the first one is quite problematic due to the difficulties around indexing content names in a particular namespace, coordinating large number of bots to send unique interests and sustaining the attack while the network is continuously caching the requested content objects.
-However, the second option, requesting unique non-existing content at each interest, is easy to achieve and sustain.
-An adversary can construct such interests by concatenating a random name component to the victim namespace (e.g.,\ndnName{/newyorktimes/fgb...3rf3}) and can increase the memory usage at each router by lengthening the random component.
+The former is achieved when interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers -- an interest is not forwarded upstream if a router can satisfy it from its content store.
+The latter requires every single malicious Interest to ask for a unique content -- all Interests requesting the same content are collapsed to one PIT entry in routers.
+Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content with each Interest.
+Of the two options available to an adversary, the first one is challenging due to the difficulties around indexing content names in a particular namespace, coordinating a large number of bots to send unique Interests and sustaining the attack while the network is continuously caching the requested content objects.
+However, the second option {\it i.e.} requesting unique non-existing content with each Interest, is easy to achieve and sustain.
+An adversary can construct such Interests by concatenating a random name component to the victim namespace (e.g.,\ndnName{/newyorktimes/fgb...3rf3}) and can increase the memory usage at each router by lengthening the random component.
 In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
@@
 
-In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
+In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
 

### 2013-03-25 paper.tex
Done with my pass
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@948 df1a90cd-247b-4364-bdaf-287a704eb499

@@
   \includegraphics[scale=0.39]{attack-definition}
-  \vspace{-0.4cm}
-  \caption{Example of the Interest flooding attack}
+  \vspace{-0.6cm}
+  \caption{Example of Interest flooding attack}
   \label{fig:flooding example}
@@
 To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2) new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
-The former is achieved when interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers -- an interest is not forwarded upstream if a router can satisfy it from its content store.
-The latter requires every single malicious Interest to ask for a unique content -- all Interests requesting the same content are collapsed to one PIT entry in routers.
+The former is achieved when interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers---an interest is not forwarded upstream if a router can satisfy it from its content store.
+The latter requires every single malicious Interest to ask for a unique content---all Interests requesting the same content are collapsed to one PIT entry in routers.
 Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content with each Interest.
@@
 
-An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests that are forwarded in the network. To this end, we exploit a 
+An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests forwarded through the network. To this end, we exploit a 
  fundamental principle of NDN architecture---flow balance between Interest and Data packets.
-The flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
+Flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
 This principle allows intermediate routers to control the inbound data traffic by controlling the number of outstanding Interests in the network.
@@
 Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
-Ideally, the number of tokens (the pending \emph{Interests Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
+Ideally, the number of tokens (the pending \emph{Interest Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
 We can formalize this value as follows:
@@
 
-In the above equation, \emph{Delay} is the expected time of Interest being satisfied and \emph{Data packet size} is the size of the returned Data packet.
+In the above equation, \emph{Delay} is the expected time for the Interest to be satisfied and \emph{Data packet size} is the size of the returning Data packet.
 Although both these values are not known a priori, it is not really necessary to use their exact values.
-One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as the network buffers can smooth out most of the network fluctuations.
+One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as network buffers can smooth out most of the network fluctuations.
 
@@
 If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
-One way to get around the issue is to impose a per interface limit, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
+One way to get around this issue is to impose a per interface limit, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
 We describe this technique in greater detail below.
@@
   \centering
-  \includegraphics[scale=0.65]{queue}
-  \vspace{-0.7cm}
+  \includegraphics[scale=0.6]{queue}
+  \vspace{-0.4cm}
   \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
@@
 
-As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from the Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
+As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
 We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is ineffective in protecting legitimate users from malicious ones. 
@@
 that can further improve the estimates.
-A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but don't generate a Data stream in return.
-In order to allow negative statistics to build up fast and positive statistics deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.
+A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but don't result in a returning Data packet.
+In order to allow negative statistics to build up fast and positive statistics to  deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.
 
@@
 Pseudocode~\ref{algo:interest stats} formally defines how statistics can be generated for  each incoming interface.
-Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interest), only unsatisfied statistics needs to be exponentially smoothed (lines 23--26).
+Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interests), only unsatisfied statistics needs to be exponentially smoothed (lines 23--26).
 
@@
   \vspace{-0.3cm}
-  \caption{Dynamics of the unsatisfied Interests statistics on gateway's interface towards the attacker}
+  \caption{Dynamics of  unsatisfied Interests statistics on a gateway's interface towards the attacker}
   \label{fig:ratio example}
@@
 Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using these ratios to penalize malicious Interests.
-A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as the direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
+A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
 %Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
@@
 
-Parameter $\theta$ on line 5 of the Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
+Parameter $\theta$ on line 5 of Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
 This step is critical to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
@@
 As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
-In example on Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
+In our example in Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
 At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
@@
 \item router A, after receiving announcement from B will readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
-\item both legitimate users and adversaries may either obey or ignore the announced limit, which will be in any case enforced by router A.
+\item both legitimate users and adversaries may either obey or ignore the announced limit, which will in any case be enforced by router A.
 \end{enumerate}
@@
 
-The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to the appropriate level (recall Fig.~\ref{fig:ratio example}).
-At the next iteration of the satisfaction-based pushback algorithm, the legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
+The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to an appropriate level (recall Fig.~\ref{fig:ratio example}).
+At the next iteration of the satisfaction-based pushback algorithm, a legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
 
@@
 To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
-That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
+That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on the sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
 
@@
 We used the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator (\url{http://www.nsnam.org/}), to run simulations for a variety of network topologies and scenarios.
-We extended ndnSIM with our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback---and evaluated effectiveness of each algorithm independently.
+We extended ndnSIM with our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, and satisfaction-based pushback---and evaluated the effectiveness of each algorithm independently.
 
@@
 We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
-To quantify the behavior of our mitigation strategies under a worst-case attack scenario, we assumed that all the attackers send junk Interests as fast as they can, no Interest---including legitimate ones---can be satisfied from caches.
-Also, we configured routers for the single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
+To quantify the behavior of our mitigation strategies under a worst-case attack scenario, we assumed that all the attackers send junk Interests as fast as they can.
+Further, no Interest---including legitimate ones---can be satisfied from caches.
+We also configured routers for single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
 %(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
@@
 The larger ISP topology reflects how our mitigation methods would perform when deployed on the real Internet.
-Again, to study the performance of our mitigation strategies under a range of conditions, we also varied the percentage of attackers in the network---the values ranged from 6\% attackers to over 50\% attackers in the network.
-
+Again, to study the performance of our mitigation strategies under a range of conditions, we varied the percentage of attackers in the network---the values ranged from 6\% attackers to over 50\% attackers in the network.
 % Fixed parameters
-We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation (\ref{eq:interest limit}) to a fixed 
+We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation (formula \ref{eq:interest limit}) to a fixed 
 value for every node in the simulated topology.
@@
 We observe a  sharp dip in the satisfaction ratio curve at the start of the attack as it takes a few seconds for all routers to be fully aware of the attack.
-Recovery quickly happens as malicious Interests start to time out and explicit Interest limit announcements start to succeed in containing malicious Interests close to the attacker.
+However, recovery is quick as malicious Interests start to time out and explicit Interest limit announcements start to succeed in containing malicious Interests close to the attacker.
 Till then, the network, for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
@@
 While the two intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
-In the case of satisfaction-based pushback algorithm, during the first minute of the attack over 90\% of Interests from legitimate users are satisfied even if the 50\% of end nodes are malicious.
+In the case of satisfaction-based pushback algorithm, during the first minute of the attack over 90\% of Interests from legitimate users are satisfied even if 50\% of end nodes are malicious.
 
@@
 In this section, we investigate the behavior of our mitigation strategies under a more realistic, large-scale network topology.
-The ISP topology we employed is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
+The ISP topology we used is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
 %In order to approximate the general structure of the Internet,
@@
 We extract the largest connected component comprising of 562 nodes from this original topology and separate the nodes into three categories: clients, gateways, and backbones.
-Nodes having degree less than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes as classified as backbones (109 blue nodes).
+Nodes having degree less than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes are classified as backbones (109 blue nodes).
 %(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
@@
 
-In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over all simulations runs for each mitigation algorithm for the scenario, where the data producer is placed at a gateway node.
-We observe similar results for the data producer placed at the backbone node as well.
-Unlike the binary-tree topology experiments, we observe that the satisfaction-based pushback is the most effective algorithm, while both the token bucket with per interface fairness and satisfaction-based Interest accept have poor performance.
+In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over all simulations runs for each mitigation algorithm for the scenario where the data producer is placed at a gateway node.
+We observe similar results for the data producer placed at a backbone node as well.
+Unlike the binary-tree topology experiments, we observe that the satisfaction-based pushback is the most effective algorithm, while both the token bucket with per interface fairness and satisfaction-based Interest acceptance have poor performance.
 Interest satisfaction percentage for legitimate users are close to 100\% and approximately 30\% and 25\% respectively for these mitigation methodologies.
@@
 
-All our evaluations leaves us with the conclusion that, among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most promising one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
+All our evaluations leave us to conclude that among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most promising one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
 %The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
@@
 First, in our evaluations we used a simple and static attacker model---attackers send junk Interests as fast as possible. 
-In the future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and Interest sending patterns based on the network reaction.
-Second, we made an assumption that Interests are not satisfied by an intermediate router's cache and always forwarded all the way to the producer.  
-The future work needs to study impact of Interest flooding attack in more realistic scenarios with multi-path routing, more realistic traffic patterns, and presence of in network caches.
+In future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and Interest sending patterns based on the network reaction. 
+Second, we assumed that Interests are not satisfied by an intermediate router's cache and always forwarded all the way to the producer.  
+In future, we plan to study the impact of Interest flooding attacks in more realistic scenarios with multi-path routing enabled, more realistic traffic patterns, and the presence of in-network caches.
 % We also ignored NDN's strategy layer that routes around failure and congestion in the network. 
@@
 
-As a new Internet architecture proposal, the Named Data Networking has attracted attention from the security community. 
+As a new Internet architecture proposal, Named Data Networking has attracted attention from the security community. 
 Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
@@
 In this paper we follow the suggestions by Gasti et al.~\cite{gasti2012ddos} and utilize the properties provided by the NDN architecture to mitigate DDoS attacks, and tackle the Interest flooding problem as a first step in this direction.
-More specifically our attack mitigation design relies on NDN's stateful forwarding plane 
-which provides statistics on unsatisfied Interests.  
+More specifically our attack mitigation design relies on NDN's stateful forwarding plane that allows us to
+maintain statistics on unsatisfied Interests.  
 Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
 
-The general area of mitigating denial of service attacks is among the hottest topics in recent years.
+The general area of mitigating denial of service attacks is amongst the hottest topics in recent years.
 % Among all the body of work, 
-The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushbacking malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
+The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushing back malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
 overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
-various ticketing systems with conditional admission of traffic to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
+various ticketing systems with conditional admission of traffic in to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
 and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
 Identifying malicious traffic requires establishing certain state at routers, and the above mentioned solutions differ in the specifics on what state to use and how to establish it.
-By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions.
-Therefore, one can simply take full advantage of this state to develop desired solutions.
+By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions---we simply take full advantage of this state to develop desired solutions.
 
@@
 
-NDN is a newly proposed future Internet architecture, thus it is important to address its resilience in face of DDoS attacks.
-As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks, Interest flooding, and the severe service degradation such an attack may cause to legitimate users.
+NDN being a newly proposed future Internet architecture, it is important to address its resilience in face of DDoS attacks.
+As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks namely Interest flooding and the severe service degradation such an attack may cause to legitimate users.
 We then leveraged the key features of the NDN architecture to design, develop, and evaluate three mitigation strategies.
 We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
-The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers, so that they cause little or no service impact on legitimate users.
-
-NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balancing (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding}.
-Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as an evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.
+The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers, so that they cause little or no service impact to legitimate users.
+
+NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balance (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding}.
+Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.
 

### 2013-03-26 paper.tex
Spacing updates
Moving all figures and tables to the top of the page.  Compressing
algorithms.

git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@949 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 
-\usepackage[top=.75in, bottom=1in, left=.625in, right=.625in]{geometry}
+% \usepackage[top=.75in, bottom=1in, left=.625in, right=.625in]{geometry}
 \usepackage{graphicx}
-%\usepackage[]{hyperref} %IEEE does not like hyperrefs...
+\usepackage[]{hyperref}
 \usepackage{breakurl}
@@
 % \usepackage{algpseudocode}
-\usepackage{algpseudocode,algorithm}
+\usepackage[noend]{algpseudocode,algorithm}
 % More customizeable version. Probably it would be better to convert pseudocode to 2e format
@@
 
-\newfont{\nicettfont}{cmtt10}
+\newfont{\nicettfont}{cmtt9}
 \newcommand{\ndnName}[1]{``{\nicettfont #1}''}
@@
 
-\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \marginpar{\textsc{ToDo}}
-\framebox{\begin{minipage}[c]{0.95 \columnwidth}
-\tt #1 \end{minipage}}\vspace{5 mm}\par}
 \graphicspath{{figures/}}
@@
 
-% I PUT AUTHOR NAMES IN ALPHEBETICAL ORDER. It is the common practice in security and I always list authors alphebetically in my publications. -Ersin 
 \author{
@@
 In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
-We summarize related work in Section~\ref{sec:related-work} .
+We summarize related work in Section~\ref{sec:related-work}.
 We discuss future work and conclude in Section~\ref{sec:conclusion}.
@@
 
-\begin{figure}[htbp]
+\begin{figure}[t]
   \centering
-  \includegraphics[scale=0.39]{attack-definition}
-  \vspace{-0.6cm}
+  \includegraphics[scale=0.3]{attack-definition}
   \caption{Example of Interest flooding attack}
   \label{fig:flooding example}
+  \vspace{-0.3cm}
 \end{figure}
@@
 However, an adversary can target a specific namespace.
-For example in Fig.~\ref{fig:flooding example}, if the data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.
+For example in Fig.~\ref{fig:flooding example}, if the data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
 \footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{\small /foo/bar} prefix to make them effective.
@@
 
-\begin{figure}[thb]
+\begin{figure}[t]
   \centering
   \includegraphics[scale=0.6]{queue}
-  \vspace{-0.4cm}
   \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
   \label{fig:queueing}
+  \vspace{-0.3cm}
 \end{figure}
@@
 \end{algorithmic}
+
 \end{algorithm}
@@
 
-\begin{algorithm}[h]
+\begin{algorithm}[t]
 \footnotesize
@@
 
-\begin{figure}[htbp]
+\begin{figure}[t]
   \centering
   \includegraphics[scale=0.8]{limits}
-  \vspace{-0.3cm}
+  % \vspace{-0.3cm}
   \caption{Dynamics of  unsatisfied Interests statistics on a gateway's interface towards the attacker}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[t]
   \centering
   \includegraphics[scale=0.3]{dynamic-limits}
-  \vspace{-0.3cm}
   \caption{Satisfaction-based pushback example
@@
 { 
-\begin{algorithm}[h]
+\begin{algorithm}[t]
 \footnotesize
@@
 
-\begin{figure}[]
+\begin{figure}[t]
   \centering
@@
   \label{fig:small-scale}
+  \vspace{-0.3cm}
 \end{figure}
@@
   \hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
-  \vspace{-.3cm}
+  % \vspace{-.3cm}
   \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
   \label{fig:small-scale attack progress}
-  \vspace{-.4cm}
+  % \vspace{-.4cm}
 \end{figure}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[t]
   \centering
   \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
-  \vspace{-.3cm}
-  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}\vspace{-.1cm}
+  % \vspace{-.3cm}
+  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}
   \label{fig:small-scale-topo boxplot}
+  % \vspace{-0.5cm}
 \end{figure}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[t]
   \centering
-  \vspace{-.1cm}\includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
-  \vspace{-0.3cm}
-  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}\vspace{-.2cm}
+  % \vspace{-.1cm}
+  \includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
+  % \vspace{-0.3cm}
+  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
   \label{fig:large-scale-topo}
@@
 
-\begin{table}[htbp]
+\begin{table}[t]
 \centering
 \caption{Large-scale topology link bandwidth and delay ranges}
-\vspace{-0.3cm}
+% \vspace{-0.3cm}
 \label{tab:large-scale}
@@
 \end{tabular}
-\vspace{-0.3cm}
+% \vspace{-0.3cm}
 \end{table}
@@
 
-\begin{figure}[tbh]
+\begin{figure}[t]
  \centering
  \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
- \vspace{-.3cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.3cm}
+ % \vspace{-.3cm}
+ \caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}
  % producer on a gateway node
  \label{fig:large-scale}
+ % \vspace{-.7cm}
 \end{figure}

### 2013-03-26 paper.tex
Final check
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@950 df1a90cd-247b-4364-bdaf-287a704eb499

@@
 \hyphenation{incoming}
+\hyphenation{na-me-spa-ce}
+\hyphenation{sa-tis-fac-tion}
+\hyphenation{sa-tis-fied}
 
@@
 \usepackage{graphicx}
-\usepackage[]{hyperref}
+% \usepackage[]{hyperref}
 \usepackage{breakurl}
@@
 
-In this section we briefly introduce NDN with a focus on its stateful forwarding plane (refer to \cite{ndn-conext, ndn-tr, adaptive-forwarding} for more details).
+In this section we briefly introduce NDN with a focus on its stateful forwarding plane (refer to \cite{ndn-conext, ndn-tr, adaptive-forwarding, Yi:2013:A-Case-for-Stateful} for more details).
 NDN is a receiver-driven, data-centric communication protocol.
@@
 \item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards potential data sources.
-Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicates the same Interest is forwarded along multiple paths.
+Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicate the same Interest is forwarded along multiple paths.
 \item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, specifying directions where Interests can be forwarded. 
 % Having one-to-many relationship in this table allows multipath forwarding of Interests.}
-\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this node, allowing efficient data retrieval by different consumers.
+\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this router, allowing efficient data retrieval by different consumers.
 \end{itemize}
@@
 It also assumes the producer is single-homed and the data is not replicated elsewhere.
-With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding} support.}
+With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding, Yi:2013:A-Case-for-Stateful} support.}
 A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
@@
 A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
-In particular, a coordinated DDoS attack could target one specific namespace and concentrate attack traffic in certain segments of the network as routing in NDN is based on name prefixes.
+In particular, a coordinated DDoS attack could target one specific namespace and concentrate attack traffic in certain segments of the network, as routing in NDN is based on name prefixes.
 
@@
 Nevertheless, creating an effective Interest flooding attack in NDN is non-trivial.
-To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2) new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
-The former is achieved when interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers---an interest is not forwarded upstream if a router can satisfy it from its content store.
-The latter requires every single malicious Interest to ask for a unique content---all Interests requesting the same content are collapsed to one PIT entry in routers.
+To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1)~the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2)~new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
+The former is achieved when Interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers---an Interest is not forwarded upstream if a router can satisfy it from its content store.
+The latter requires every single malicious Interest to ask for unique content---all Interests requesting the same content are combined into one PIT entry in routers.
 Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content with each Interest.
-Of the two options available to an adversary, the first one is challenging due to the difficulties around indexing content names in a particular namespace, coordinating a large number of bots to send unique Interests and sustaining the attack while the network is continuously caching the requested content objects.
-However, the second option {\it i.e.} requesting unique non-existing content with each Interest, is easy to achieve and sustain.
-An adversary can construct such Interests by concatenating a random name component to the victim namespace (e.g.,\ndnName{/newyorktimes/fgb...3rf3}) and can increase the memory usage at each router by lengthening the random component.
-In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
+Of the two options available to an adversary, the first one is challenging due to the difficulties around indexing content names in a particular namespace, coordinating a large number of bots to send unique Interests, and sustaining the attack while the network is continuously caching the requested content objects.
+However, the second option---requesting a unique non-existing content with each Interest---is easy to achieve and sustain.
+For example, an adversary can construct such Interests by concatenating a variable-length random name component to the victim namespace (e.g., \ndnName{/newyorktimes/3rf3...}).
+In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest, but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
 % other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
@@
 This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet-switched networks.
-Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
+Analogous to the {\it Token Bucket} algorithm, NDN routers can keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
 Ideally, the number of tokens (the pending \emph{Interest Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
@@
 If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
-One way to get around this issue is to impose a per interface limit, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
+One way to get around this issue is to impose a per interface fairness, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
 We describe this technique in greater detail below.
@@
 If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet might be dropped at the downstream routers if their corresponding state expired. 
-For our evaluations, we empirically chose to enqueue Interests up to 10\% of their original lifetime.
+For our evaluations, we empirically chose to enqueue Interests up to 10\% of their original lifetime (100~ms).
 % We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
@@
 
-As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
-We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is ineffective in protecting legitimate users from malicious ones. 
+As we show in Section~\ref{sec:evaluation}, this algorithm provides a partial relief from Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
+We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is largely ineffective in protecting legitimate users from malicious ones. 
 Attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of malicious Interests.
@@
 This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate and malicious Interests.
-For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and differentiate malicious requests from legitimate ones.
+For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and differentiate to some extent malicious requests from legitimate ones.
 % `Good' Interests from legitimate users must be admited and forwarded appropriately. 
@@
 This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
-However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest should be forwarded or dropped.
-For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to reasonably predict whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout if forwarded.
+However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use these statistics to determine whether an incoming Interest should be forwarded or dropped.
+For example, maintaining Interest satisfaction ratio statistics for each incoming interface is sufficient to reasonably predict whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout if forwarded.
 Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
 that can further improve the estimates.
-A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but don't result in a returning Data packet.
+A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but do not result in a returning Data packet.
 In order to allow negative statistics to build up fast and positive statistics to  deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.
@@
 Pseudocode~\ref{algo:interest stats} formally defines how statistics can be generated for  each incoming interface.
-Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interests), only unsatisfied statistics needs to be exponentially smoothed (lines 23--26).
+Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interests), only unsatisfied statistics needs to be exponentially smoothed (lines 19--21).
 
@@
 
-Fig.~\ref{fig:ratio example} illustrates the resulting dynamics of the statistic during and after an Interest flooding attack.
+Fig.~\ref{fig:ratio example} illustrates the resulting dynamics of the statistics during and after an Interest flooding attack.
 The attack duration is from 10 to 70~seconds.
@@
 We note that while in the description of the satisfaction-based pushback algorithm we explicitly used ``outgoing'' and ``incoming'' interfaces,  all interfaces can be both incoming and outgoing.
-Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
+Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 9 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
 To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
@@
 
-In our simulations, this mitigation algorithm was able to effectively shut down attackers and ensure almost all the Interests from legitimate users are satisfied. 
+In our simulations, this mitigation algorithm was able to effectively shut down attackers and ensure that almost all the Interests from legitimate users are satisfied. 
 %The only potential problem with the satisfaction-based pushback algorithm is that it features 
@@
 
-In Fig.\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
+In Fig.~\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
 The results are as expected---for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
@@
 In this section, we investigate the behavior of our mitigation strategies under a more realistic, large-scale network topology.
-The ISP topology we used is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
+The ISP-like topology we used is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
 %In order to approximate the general structure of the Internet,
 % (scale-free structure, customer-provider, and peer-to-peer relations)
-We extract the largest connected component comprising of 562 nodes from this original topology and separate the nodes into three categories: clients, gateways, and backbones.
-Nodes having degree less than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes are classified as backbones (109 blue nodes).
+We extracted the largest connected component comprising of 562 nodes from this original topology and separated the nodes into three categories: clients, gateways, and backbones.
+Nodes having degree less than four were classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients were classified as gateways (109 green nodes), and the remaining nodes were classified as backbones (109 blue nodes).
 %(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
-We assign bandwidth and  delay values to links based on their type---both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
-We experiment with placing the data producer at both a gateway node as well as backbone node, which we randomly pick for each simulation run.
-Similar to the binary tree topology experiments, we fix the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly pick these nodes for each simulation run.
-We conduct 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5-minute interval.
+We assigned bandwidth and delay values to links based on their type---both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
+We experimented with placing the data producer at both a gateway node as well as backbone node, which we randomly picked for each simulation run.
+Similar to the binary tree topology experiments, we fixed the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly picked these nodes for each simulation run.
+We conducted 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5-minute interval.
 
@@
 We observe similar results for the data producer placed at a backbone node as well.
-Unlike the binary-tree topology experiments, we observe that the satisfaction-based pushback is the most effective algorithm, while both the token bucket with per interface fairness and satisfaction-based Interest acceptance have poor performance.
-Interest satisfaction percentage for legitimate users are close to 100\% and approximately 30\% and 25\% respectively for these mitigation methodologies.
+Unlike the binary-tree topology experiments, we observe that
+both the token bucket with per interface fairness and satisfaction-based Interest acceptance have poor performance, while the satisfaction-based pushback is still the most effective algorithm.
+Interest satisfaction percentage for legitimate users are close to 30\%, 25\%, and 100\% respectively for these mitigation methodologies.
 
@@
 This poor performance, as detailed in Section~\ref{sec:probabilistic}, is due to the fact that each router on the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
-In the case of the larger-topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics and further penalization of new Interests from them.
+In the case of a large topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics and further penalization of new Interests from them.
 
@@
 This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space. 
-While designing our mitigation algorithms, we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
+To design our mitigation algorithms we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
 We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology, % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
@@
 
-As a new Internet architecture proposal, Named Data Networking has attracted attention from the security community. 
+As a new Internet architecture proposal, Named Data Networking has attracted a limited attention from the security community. 
 Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
@@
 maintain statistics on unsatisfied Interests.  
-Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
+Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr,Yi:2013:A-Case-for-Stateful} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
 
@@
 NDN being a newly proposed future Internet architecture, it is important to address its resilience in face of DDoS attacks.
-As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks namely Interest flooding and the severe service degradation such an attack may cause to legitimate users.
+As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks---namely, Interest flooding---and the severe service degradation such an attack may cause to legitimate users.
 We then leveraged the key features of the NDN architecture to design, develop, and evaluate three mitigation strategies.
@@
 
-NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balance (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding}.
+NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balance (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding,Yi:2013:A-Case-for-Stateful}.
 Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.

### 2013-05-13 00-abstract.tex
Splitting paper back to its normal organization

--- 2013-03-26 paper.tex
@@
-\documentclass[10pt,conference]{IEEEtran}
-% http://networking2013.poly.edu/call-for-papers/paper-submission/
-% Page limit 9 pages
-
-\makeatletter
-\def\ps@headings{%
-\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
-\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
-\def\@oddfoot{}%
-\def\@evenfoot{}}
-\makeatother
-
-\hyphenation{incoming}
-
-\pagestyle{headings}
-
-% \usepackage[top=.75in, bottom=1in, left=.625in, right=.625in]{geometry}
-\usepackage{graphicx}
-\usepackage[]{hyperref}
-\usepackage{breakurl}
-\usepackage{url}
-\usepackage[nocompress]{cite}
-% \usepackage{verbatim}
-% \usepackage{algpseudocode}
-\usepackage[noend]{algpseudocode,algorithm}
-% More customizeable version. Probably it would be better to convert pseudocode to 2e format
-% \usepackage{algorithm2e} 
-\usepackage{multirow}
-\usepackage{times}
-\usepackage{color}
-
-\newfont{\nicettfont}{cmtt9}
-\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
-\renewcommand{\texttt}[1]{{\nicettfont #1}}
-
-\graphicspath{{figures/}}
-
-\begin{document}
-
-\title{Interest Flooding Attack and Countermeasures in Named Data Networking}
-
-\author{
-    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
-    \\\{afanasev, iliamo, lixia\}@cs.ucla.edu}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
-    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
-}
-
-\maketitle
-
 \begin{abstract}
@@
 \end{IEEEkeywords}
-
-\section{Introduction}
-\label{sec:intro}
-
-Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an ongoing research effort that aims to move the Internet into the future with a content-centric design that is capable of efficient content distribution and seamless mobility support.
-In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in the packets.
-However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against DDoS attacks?
-Especially since various forms of DDoS attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial to ensure that the new design is free of similar vulnerabilities.
-
-NDN eliminates host-based addressing and makes data the first-class network entity.
-Instead of sending packets to a given IP address, NDN nodes request desired data by sending Interest packets carrying application-level data names, and the network returns the requested Data packets following the path of Interests.
-Such a shift automatically eliminates several long-standing DDoS attacks, including direct flooding and reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
-%
-However, malicious users can attack the network by sending an excessive number of Interests. 
-Since each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can congest the network and exhaust a router's memory. 
-We coin the term {\it Interest flooding} to refer to such attack and
-this paper exclusively investigates the problem and the solution space for it.
-
-Our effort is an important first step towards a complete investigation of DDoS attacks in NDN.
-We experiment with three algorithms that allow routers to exploit their state information to thwart these attacks.
-Through extensive simulations, we show how one of our mitigation methodologies effectively shuts down malicious users while preventing legitimate users from service degradation.
-The rest of the paper is organized as follows.
-We provide an overview of NDN architecture in Section~\ref{sec:ccn-intro} and describe Interest flooding attacks in Section~\ref{sec:interest-flooding}.
-In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
-We summarize related work in Section~\ref{sec:related-work}.
-We discuss future work and conclude in Section~\ref{sec:conclusion}.
-
-\section{NDN Overview\label{sec:ccn-intro}}
-
-In this section we briefly introduce NDN with a focus on its stateful forwarding plane (refer to \cite{ndn-conext, ndn-tr, adaptive-forwarding} for more details).
-NDN is a receiver-driven, data-centric communication protocol.
-All communications in NDN are performed using two distinct types of packets: \textit{Interest} and \textit{Data}.
-Both types of packets carry a \textit{name}, which uniquely identifies a piece of content that can be carried in one Data packet.
-Data names in NDN are hierarchically structured and an example name for the first segment of a youtube video would look like: \ndnName{/youtube/videos/0F8YdlkKO9A/0}.
-
-To retrieve data, a consumer requests it by sending an Interest packet with the name of the desired content in it.
-Routers use this name to route the Interest towards data sources, and a Data packet whose name matches the name in the Interest is returned to the consumer by following the reverse path of the Interest.
-Similar to IP, Interest forwarding is based on longest name prefix match, but, unlike IP, an Interest packet and its matching Data packet always take symmetric paths.
-%% An Interest is ``satisfied'' when it is matched with a Data packet.
-
-Each NDN router maintains three major data structures:
-\begin{itemize}
-\item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards potential data sources.
-Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicates the same Interest is forwarded along multiple paths.
-\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, specifying directions where Interests can be forwarded. 
-% Having one-to-many relationship in this table allows multipath forwarding of Interests.}
-\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this node, allowing efficient data retrieval by different consumers.
-\end{itemize}
-
-When a router receives an Interest packet, it first checks whether there is a matching data in its CS.
-If a match is found, the Data packet is sent back to the incoming interface of the Interest packet.
-If not, the Interest name is checked against the entries in the PIT. 
-If the name already exists in the PIT, then it can be a duplicate Interest (identified by a random number each Interest carries) that should be dropped,
-or an Interest from another consumer asking for the same Data, which requires the incoming interface of this Interest to be added to the existing PIT entry.
-If the name does not exist in the PIT, the Interest is added into the PIT and forwarded along the interface chosen by the strategy module, which uses FIB as input for its decisions.
-
-When a Data packet is received, its name is used to look up the PIT.
-If a matching PIT entry is found,
-the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the CS, and removes the PIT entry.
-Otherwise, the Data packet is deemed unsolicited and is discarded.
-Each Interest also has an associated lifetime; the PIT entry is removed when the lifetime expires.
-Although the maximum lifetime is specified by users, it is ultimately a router's decision on how long it is willing to keep a PIT entry.  
-For simplicity, we assume routers keep Interests in PIT for one second in our simulations.
-
-\section{Interest Flooding Attacks in NDN}
-\label{sec:interest-flooding}
-
-As we explained earlier, Interest packets in NDN are routed through the network based on content name prefixes and consume memory resources at intermediate routers.
-This makes them a potential tool to launch DDoS attacks in NDN.
-An attacker or a set of distributed attackers can inject excessive number of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{attack-definition}
-  \caption{Example of Interest flooding attack}
-  \label{fig:flooding example}
-  \vspace{-0.3cm}
-\end{figure}
-
-Since an NDN network fetches data by its name, an adversary cannot easily target specific routers or end-hosts.
-However, an adversary can target a specific namespace.
-For example in Fig.~\ref{fig:flooding example}, if the data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
-\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{\small /foo/bar} prefix to make them effective.
-It also assumes the producer is single-homed and the data is not replicated elsewhere.
-With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding} support.}
-A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
-
-Similar to packets in traditional networks, Interest packets in NDN consume a portion of network capacity.
-A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
-In particular, a coordinated DDoS attack could target one specific namespace and concentrate attack traffic in certain segments of the network as routing in NDN is based on name prefixes.
-
-As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a router's memory, making the router unable to create new PIT entries for incoming Interests and disrupting service for legitimate users.
-
-Nevertheless, creating an effective Interest flooding attack in NDN is non-trivial.
-To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2) new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
-The former is achieved when interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers---an interest is not forwarded upstream if a router can satisfy it from its content store.
-The latter requires every single malicious Interest to ask for a unique content---all Interests requesting the same content are collapsed to one PIT entry in routers.
-Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content with each Interest.
-Of the two options available to an adversary, the first one is challenging due to the difficulties around indexing content names in a particular namespace, coordinating a large number of bots to send unique Interests and sustaining the attack while the network is continuously caching the requested content objects.
-However, the second option {\it i.e.} requesting unique non-existing content with each Interest, is easy to achieve and sustain.
-An adversary can construct such Interests by concatenating a random name component to the victim namespace (e.g.,\ndnName{/newyorktimes/fgb...3rf3}) and can increase the memory usage at each router by lengthening the random component.
-In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
-% other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
-
-In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
-
-%\paragraph{Assumptions} 
-%E: These are assumptions for the simulations on hand and particulary to test for the worst case scenario in many aspects.
-They are not the paper's assumption and in fact the paper first should be more general on describing all possibilities.
-Then it should explain the assumptions for the simulations and discuss why they make sense and do NOT favor positive results in some way.
-
-% - assumptions about attacker position
-% - assumptions about the producer / producer namespace
-% - assumptions about the attack traffic / attack pattern
-
-%In this paper we are making the following assumptions about the Interest flooding attack:
-%\begin{itemize}
-%\item only client nodes can be compromised and become attack bots;
-%\item there are no colluding attackers inside the Data producer's network;
-%\item the attack is carried only using unique junk Interests; and
-%\item there is only one Data producer for the attacked prefix.
-%\end{itemize}
-
-%We also assume that NDN forwarding strategy uses only single-path Interest forwarding, always choosing the best-metric route advertised by the routing protocol.
-%This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
-
-%In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
-
-\section{Interest flooding mitigation methods}
-\label{sec:design}
-
-% Points what should be here:
-% - What can be done (in general) to mitigate flooding attack
-% - Which building blocks NDN architecture gives to mitigate Interest flooding attacks: Interest limits, ability to measure Interest satisfaction performance (Interest satisfaction stats)
-% - Methods to set these limits: static/dynamic
-% - Methods how limits can be applied: best-effort (fifo), "fair" queuing, probabilistic
-% - Reference to caching: we don't consider it here, but caching provides additional level of protection, especially for certain types of attacks
-
-% Our definition of attack mitigation is that good clients are still able to access data on the producer.
-
-In this section we present several algorithms to mitigate Interest flooding attacks in NDN.
-Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
-We start by describing our simple strategies and use the insights and lessons learned from the deployment of these to inform and design more effective mitigation techniques that work well in various topologies.
-
-%   - Naive approach to Interest Limits (that is called physical limits everywhere else)
-%     Example how this can be implemented in a simple way
-%     Baseline solution
-%   - Interest limits with "fair" queuing
-%     Improving problem of simple limits (no single face can dominate), but doesn't solve the proble
-
-% - Attack mitigation
-%   - Per-incoming interface Interest statistics
-
-%   - Dynamic Interests limit adjustments
-
-%   - Probabilistic Interest accept
-
-%The fact that each Data packet takes the reverse path of the corresponding Interest packet allows intermediate routers to match a received Data packet to the corresponding Interest packet and %thus determine which Interest packets were satisfied.
-As we describe in the rest of this section,  NDN routers can exploit this information to make informed decisions on which Interest packets to %forward, how many Interest packets to forward, and thus effectively defend against DDoS attacks.
-
-%Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
-%Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
-%Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
-%At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
-
-%\subsection{Na\"{i}ve attack mitigation}
-
-%We start with a couple of naive strategies that can be used to migitate attacks in an NDN network and describe the pitfalls associated with these strategies.
-
-% In a normal network operation, the size of Interests packets is supposed to be significantly smaller than the size of the requested Data.
-
-% All communication in NDN network is host-to-host and receiver-driven.
-
-An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests forwarded through the network. To this end, we exploit a 
- fundamental principle of NDN architecture---flow balance between Interest and Data packets.
-Flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
-This principle allows intermediate routers to control the inbound data traffic by controlling the number of outstanding Interests in the network.
-One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding interface.
-This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet-switched networks.
-Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
-Ideally, the number of tokens (the pending \emph{Interest Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
-We can formalize this value as follows:
-% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
-%
-\begin{equation}
-\label{eq:interest limit}
-\small \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
-\end{equation}
-
-In the above equation, \emph{Delay} is the expected time for the Interest to be satisfied and \emph{Data packet size} is the size of the returning Data packet.
-Although both these values are not known a priori, it is not really necessary to use their exact values.
-One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as network buffers can smooth out most of the network fluctuations.
-
-This {\it Token Bucket} approach might be exceptionally restrictive in forwarding Interests---not all Interests will result in a Data packet---and might result in underutilization of the network.
-However, the biggest drawback of this algorithm is the fact that it can nourish DDoS attacks.
-If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
-One way to get around this issue is to impose a per interface limit, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
-We describe this technique in greater detail below.
-
-%That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
-%For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
-%In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
-%
-%\subsubsection{\textbf{Interest limits (physical limits)}}
-%\label{sec:physical limits}
-%
-%\input{algos/physical-limits.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Token bucket with per interface fairness}}
-\label{sec:queuing}
-
-To address the lack of fairness associated with the na\"ive {\it Token Bucket} approach, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring nodes.
-For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
-%Due to the expected small volume of Interests, we cannot merely rely on network buffers to perform statistical multiplexing of Interests, as they would almost never be %buffered.
-%At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests %will arrive in the future.
-In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring nodes, 
-%, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
-we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded and implement hierarchical queues for each interface (see Fig.~\ref{fig:queueing}). 
-This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing and incoming interface.
-%As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
-We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
-Thus, a PIT entry can be quickly updated when the Interest is actually forwarded, and the element can be easily removed from the queue when the Interest expires.
-
-%For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}).
-%As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.6]{queue}
-  \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
-  \label{fig:queueing}
-  \vspace{-0.3cm}
-\end{figure}
-
-We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
-By setting appropriate queue sizes, we can control the amount of physical resources utilized at a router.
- % (such as memory and computation power). 
-It is also important to set a sensible value for how long an Interest can be enqueued. 
-If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet might be dropped at the downstream routers if their corresponding state expired. 
-For our evaluations, we empirically chose to enqueue Interests up to 10\% of their original lifetime.
-% We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
-% Alex: I don't believe there is a need for separate discussion about "freshness", as we already introduced concept of lifetime
-% {\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
-
-%It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
-%Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
-%Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
-
-%The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
-%At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[h]
-\footnotesize
-\caption{\small Token bucket with per interface fairness}
-\label{alg:queuing}
-\begin{algorithmic}[1]
-\For{\textbf{each} interface \textbf{if}}
-    \State{$L_{if} \leftarrow$ Interest Limit according to (1)}
-    \State{$O_{if} \leftarrow 0$} \Comment{Outstanding Interests on interface \textbf{if}}
-\EndFor
-
-\vspace{0.1cm}
-
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
-    \If{$L_{out} - O_{out} > 0$} \Comment{\textbf{out} is under limit cap}
-        \State $O_{out} \leftarrow O_{out} + 1$  \Comment{``borrow'' a token from the bucket}
-        \State add \textbf{out} to PIT entry and forward \textbf{i} to \textbf{out}
-    \Else
-        \State Queue $q \leftarrow out$.GetSubQueue($in$)
-        \If{$Size(q) < L_{out}$}
-           \State $q$.PushInterest($i$)
-           \State add \textbf{out} to PIT entry, and link PIT entry with the queue
-        \Else
-           \State drop Interest
-        \EndIf
-    \EndIf
-\EndFunction
-
-\vspace{0.1cm}
-
-\State{} \Comment{\textit{Whenever $L_{out} - O_{out}$ becomes larger than zero}}
-\Function{TokenBecomesAvailable}{}
-    \State Queue $q \leftarrow$ $out$.GetRoundRobinSubQueue 
-    \State Interest $i \leftarrow$ $q$.PopInterest
-    \State update PIT entry and Forward($i$, $out$)
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{InData}{Data \textbf{d}}
-   \State lookup PIT entry \textbf{p} for data \textbf{d}
-   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
-        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
-   \EndFor
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{Timeout}{PIT entry $p$}
-   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
-        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
-   \EndFor
-\EndFunction
-
-\end{algorithmic}
-
-\end{algorithm}
-
-As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
-We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is ineffective in protecting legitimate users from malicious ones. 
-Attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of malicious Interests.
-
-%At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
-%Therefore, to successfully solve the problem, we need a fundamentally different, more intelligent approach, allowing localization of the attack traffic as close as possible to the attack origin.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits a relatively large number of Interests from malicious users.
-A considerable percentage of these malicious Interests are forwarded all the way to content producers, thereby reducing resources available to serve legitimate users.
-This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate and malicious Interests.
-For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and differentiate malicious requests from legitimate ones.
-% `Good' Interests from legitimate users must be admited and forwarded appropriately. 
-Thus, the key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
-
-%One can try a black- or whitelisting approach.
-However, besides the fact that source black- and whitelisting cannot work in %NDN as it does not feature source addresses, it requires extraneous knowledge to classify the incoming Interests.
-
-%Priya: I have added the below point specifically to point out that a router cannot determine from the prefix name alone whether /parc is good  or bad...
-
-%{\color{red} \textbf{Alex: This paragraph is confusing to me.
-I would remove it.} In NDN one cannot easily distinguish a `good' prefix from a `bad' one.
-Content producers must be able to support %dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded %to the producer for possible dynamic Data packet generation.
-%Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the prefix name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain %namespaces  will be inefficient and likely ineffective.
-}
-
-% Alex: I'm not sure that this part is relevant... The point I see is that blacklisting and whitelisting is not 100% effective, but it can be used in both worlds
-
-% In today's host-based Internet architecture where DDoS mitigation techniques rely on blacklisting of ``dark'' IP prefixes or whitelisting of good IP prefixes.
-% Unlike IP, in NDN one cannot easily distinguish a `good' prefix from a `bad' one. 
-% Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
-% Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
-
-\subsection{Intelligent attack mitigation}
-\label{sec:intelligent mitigating}
-
-%While the Interest limit is the key building block to suppress mechanisms of the Interest flooding attack, legitimate Interests need to be somehow prioritized and malicious Interests need to be somehow penalized in order to completely suppress the attack.
-%That is, instead of processing Interests always based on the first-in-first-serve rule, NDN routers need some basis to treat the incoming Interests differently.
-%Thus, the primary task in bringing intelligence to the Interest flooding attack mitigation is to proactively distinguish between legitimate and malicious Interests.
-
-In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets.
-Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guaranteed to see if an Interest it forwarded resulted in a matching Data packet or timed out.
-%The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
-Since malicious Interests are not likely to bring data back (as discussed in Section~\ref{sec:interest-flooding}), this information can be utilized by routers in differentiating attack and legitimate traffic.
-%Therefore, intermediate routers can classify the ones that brings data back as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}
-%Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
-
-This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
-However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest should be forwarded or dropped.
-For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to reasonably predict whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout if forwarded.
-Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
-that can further improve the estimates.
-A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but don't result in a returning Data packet.
-In order to allow negative statistics to build up fast and positive statistics to  deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.
-
-%Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
-%{\color{red} \it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong %here.}
-
-%The devil is always in the details.
-%From the one hand, such statistics needs to start penalizing adversaries as soon as possible (i.e., negative stats should build up fast).
-%On the other hand, the positive statistics should not deteriorate too fast (i.e., positive stats should be relatively long-term).
-%Our preliminary experiments showed that the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window, provides a good balance between the two contradictory requirements.
-
-% \subsubsection{\textbf{Data plane performance tracking}}
-% \label{sec:stats}
-
-% Note that there is a condition (line 6 in Pseudocode~\ref{alg:probabilistic model}) to check if there is a valid statistics point.
-% This condition is extremely important, because it first provides a basis to distinguish between known facts (i.e., good or bad satisfaction ratio for the incoming interface) and unknown facts (e.g., the first time an Interests arrives on the interfaces).
-% Second, it gives an opportunity to recover from a bad history (history of unsatisfied Interests) after malicious Interests are ceased to flow in.
-% Essentially, this recovery relies on statistics module to perform time-based invalidation of historical data (timely, but not too quickly\footnote{Otherwise, attackers may send short bursts of malicious Interests, successfully avoiding differential Interest treatment}).
-
-Pseudocode~\ref{algo:interest stats} formally defines how statistics can be generated for  each incoming interface.
-Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interests), only unsatisfied statistics needs to be exponentially smoothed (lines 23--26).
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Interest satisfaction statistics}
-\label{algo:interest stats}
-\begin{algorithmic}[1]
-
-\For{\textbf{each} interface \textbf{if}}
-    \State $F_{if} \leftarrow 0$ \Comment{forwarded Interests from interface \textbf{if}}
-    \State $\hat F_{if} \leftarrow 0$ \Comment{averaged value of $F_{if}$}
-
-    \State $U_{if} \leftarrow 0$ \Comment{unsatisfied Interests from interface \textbf{if}}
-    \State $\hat U_{if} \leftarrow 0$ \Comment{averaged value of $U_{if}$}
-\EndFor
-
-\vspace{0.1cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}}
-  \State $F_{in} \leftarrow F_{in} + 1$
-  \State record \textbf{\emph{in}} in the list of incoming interfaces for \textbf{\emph{i}}
-\EndFunction
-
-\vspace{0.1cm}
-\Function{InterestTimeout}{Interest \textbf{i}}
-    \State lookup the list of incoming interfaces for \textbf{\emph{i}}
-
-    \For{\textbf{each} interface \textbf{if} in the list}
-        \State $U_{if} \leftarrow U_{if} + 1$
-    \EndFor
-\EndFunction
-
-\vspace{0.1cm}
-
-\State {} \Comment{\textit{Exponentially weighted moving average smoothing}}
-\Function{EWMA}{} \Comment{Every second}
-\State $\alpha \leftarrow e^{-1.0/30.0}$  %\Comment{$\approx$ 30~sec average}
-
-\For{\textbf{each} interface \textbf{if}}
-    \State $\hat U_{if} \leftarrow \alpha \cdot \hat U_{if} + (1 - \alpha) \cdot U_{if}$ 
-    \State $U_{if} \leftarrow 0$
-
-    \If{$F_{if} > 0$} \Comment{To ensure decaying of ratio $U_{if}/F_{if}$}
-        \State $\hat F_{if} \leftarrow \alpha \cdot \hat F_{if} + (1 - \alpha) \cdot I_{if}$ 
-        \State $F_{if} \leftarrow 0$ \Comment{Reset counters}
-    \EndIf
-\EndFor
-
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-Fig.~\ref{fig:ratio example} illustrates the resulting dynamics of the statistic during and after an Interest flooding attack.
-The attack duration is from 10 to 70~seconds.
-Prior to start of the attack, the percentage of unsatisfied Interests is zero.
-The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.
-%\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
-For the duration of the attack (10--70~seconds), the percentage of unsatisfied Interests is close to 100\%: 
-when the ratio is close to 100\%, routers drop all incoming Interests, resulting in decaying of the statistics until a new Interest is admitted, which eventually brings statistics back near 100\% point.
-Finally, the ratio exponentially decays after the attack ceases.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.8]{limits}
-  % \vspace{-0.3cm}
-  \caption{Dynamics of  unsatisfied Interests statistics on a gateway's interface towards the attacker}
-  \label{fig:ratio example}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Satisfaction-based Interest acceptance}}
-\label{sec:probabilistic}
-
-Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using these ratios to penalize malicious Interests.
-A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
-%Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Satisfaction-based Interest acceptance}
-\label{alg:probabilistic model}
-\begin{algorithmic}[1]
-\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-
-\vspace{0.1cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
-
-    \State{} \Comment{Use uniform probability distribution model $P(X)$}
-    \State{} \Comment{$P(X) : \forall x \in [0,1] \Rightarrow P(x) = x$}
-
-    \If{$F_{in} > \theta $} \Comment{At least some Interests were forwarded before}
-        \State $s \leftarrow (1 - U_{in} / F_{in})$
-        \State Drop interest with probability $P(s)$
-    \EndIf
-
-    \State{forward the Interest, subjecting to token bucket limits}
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-Parameter $\theta$ on line 5 of Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
-This step is critical to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
-
-A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop an Interest. 
-As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
-In our example in Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
-At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
-Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the data producer.
-With each increasing hop in the network, the probability of being forwarded to the next hop decreases significantly.
-One way to prevent this overreaction and unfair penalization is to ensure that the decision taken at each router on whether to forward or drop the Interest is not independent of the decision taken at preceding routers.
-An explicit notification such as a gossip protocol between neighboring NDN routers might alleviate the problem, but we leave the design and evaluation of it to future work.
-%{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Satisfaction-based pushback}}
-\label{sec:dynamic limits}
-
-% Differential treatment of Interests received from different interfaces can be achieved in a more elegant way, without reverting to probabilistic methods.
-
-The previous algorithm---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
-% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
-An alternate algorithm for proportional token distribution without overreaction is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
-Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.
-
-The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm will work in our example in Fig.~\ref{fig:flooding example}.
-Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node will set and announce the following  incoming interface limit $L'$:
-\begin{enumerate}
-\item router B will set and announce the incoming interface limit $L'=3$;
-\item router A, after receiving announcement from B will readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
-\item both legitimate users and adversaries may either obey or ignore the announced limit, which will in any case be enforced by router A.
-\end{enumerate}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{dynamic-limits}
-  \caption{Satisfaction-based pushback example
-%: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer%
-}
-  \label{fig:dynamic limits example}
-\end{figure}
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{ 
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Satisfaction-based pushback}
-\label{alg:dynamic limits}
-\begin{algorithmic}[1]
-% \State{}\Comment{Same initialization, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-\vspace{0.1cm}
-\State{$\forall f \in \mathrm{interfaces} : L'_{f} \leftarrow L_{f}$} \Comment{Per-incoming interface Interest limit}
-
-\vspace{0.1cm}
-
-\State{} \Comment{\textit{Announcement from the neighbor}}
-\Function{InLimits}{InInterface $in$, Limit $L'$}
-    \State $L_{in} \leftarrow L'$
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
-\For{\textbf{each} outgoing interface $out$}
-
-   \For{\textbf{each} incoming interface $in$}
-        \State $L'_{in}= {L_{out}} \times (1 - U_{in}/F_{in})$
-        \State AnnounceLimit($in$, $L'_{in}$)
-   \EndFor
-
-\EndFor
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to an appropriate level (recall Fig.~\ref{fig:ratio example}).
-At the next iteration of the satisfaction-based pushback algorithm, a legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
-
-We note that while in the description of the satisfaction-based pushback algorithm we explicitly used ``outgoing'' and ``incoming'' interfaces,  all interfaces can be both incoming and outgoing.
-Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
-To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
-That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on the sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
-
-Both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, but with several core differences. 
-First, we are suppressing (pushing back) unwanted requests for data, not actual data itself.
-Second, differentiating between good and bad Interests is based on the traffic symmetry principle of NDN.
-% Alex: I'm not entirely sure about this point... 
-Finally, both intelligent attack mitigation algorithms can be deployed at all times without degrading network performance even when there are no active attackers.
-
-\section{Evaluation of Interest flooding mitigation methods}
-\label{sec:evaluation}
-
-% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
-
-% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers,
-
-% alex: what's a point of latency?  it would matter only for queueing method and we not really pushing this method
-% Latency for good clients, good versus bad interests as a function of time
-
-In this section, we present an in-depth evaluation study, aiming to quantify the effectiveness of all our Interest flooding attack mitigation methods.
-We used the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator (\url{http://www.nsnam.org/}), to run simulations for a variety of network topologies and scenarios.
-We extended ndnSIM with our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, and satisfaction-based pushback---and evaluated the effectiveness of each algorithm independently.
-
-% For evaluating the effectiveness of each mitigation algorithm, every router in the simulated topology runs the mitigation algorithm under study.
-
-% why we chose small scale topology
-% what point we wanted to show we small scale
-% what points we wanted to verify with larger-scale internet like topology
-
-% Metrics
-% not sure if i already explained that. our essential qualitative metric is .  
-% To quantify the effectiveness of the mitigation mechanism this  metric we use satisfaction percentages of user Interests.
-
-The metric we choose to quantify the effectiveness of our algorithms is the {\it percentage of satisfied Interests for legitimate users}.
-This metric corresponds to the quality of service experienced by legitimate users when the network is under attack.
-In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conclude that method $X$ is highly effective at mitigating the attack.% We also ensure that all Interests expressed by legitimate users during a period of no-attack are satisfied.
-
-%Quality of the attack mitigation methods directly corresponds to the quality of service for the legitimate users during an ongoing attack, which in NDN network can be quantified through percentage of satisfied Interest.
-%For example, if the network implements a mitigation method $X$ and under the attack majority of user-expressed Interests are getting satisfied, then the method $X$ can be seen as highly effective.
-%At the same time, if only a small percentage of the expressed Interest are getting satisfied during the attack, the method $X$ can be called ineffective.
-
-% Traffic pattern
-In our experiments, we assumed that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution.
-We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
-To quantify the behavior of our mitigation strategies under a worst-case attack scenario, we assumed that all the attackers send junk Interests as fast as they can.
-Further, no Interest---including legitimate ones---can be satisfied from caches.
-We also configured routers for single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
-%(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
-
-% Alex: not sure how to argue about the traffic pattern
-%Although this pattern may seem not truly realistic, it approximates a good statistical mix of traffic from all network users without excessive network buffering.
-
-%In addition to that, in each run of the simulation we ensure that all Interests expressed by the legitimate users during a no-attack period are satisfied.
-%For simplicity, we also equalized the average rates with which the legitimate users express Interests.
-%At the same time, the attackers are sending junk Interests as much as they can get through (remember, that Interest limits will not allow real f%looding of Intersests in all of the designed mitigation algorithms).
-
-We ran our simulations on two different network topologies---a smaller binary tree topology and a much larger ISP-like topology.
-We use a binary tree topology as it represents one of the worst cases to defend against Interest flooding DDoS attacks.
-The larger ISP topology reflects how our mitigation methods would perform when deployed on the real Internet.
-Again, to study the performance of our mitigation strategies under a range of conditions, we varied the percentage of attackers in the network---the values ranged from 6\% attackers to over 50\% attackers in the network.
-% Fixed parameters
-We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation (formula \ref{eq:interest limit}) to a fixed 
-value for every node in the simulated topology.
-In particular, for the small-scale binary tree topology, we set delay to 80~ms, while for the large-scale ISP topology we set it to 330~ms (the order of the largest RTT).
-The data size is 1100~bytes for all simulation runs and topologies.
-% THIS IS BULLSHIT!
-There is absolutely no logic to set the delay to the same value on all nodes in the network.
-We discussed multiple times that you should fix it so that the delays are realistic and gets smaller as the nodes gets closer to the producer...
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Small-scale evaluations}
-\label{sec:small-scale}
-
-% Topology description
-%To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a %simplistic small-scale binary tree topology 
-In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we used for our initial experiments.
-Legitimate users as well as attackers were placed on leaf nodes (top row of red nodes) as shown in the figure.
-There are 16 end users (both legitimate and attackers) in this topology, each expressing Interests that are routed towards a single data producer, placed at the root of the tree.
-Each link in this topology is assigned a bandwidth of 10~Mbps and a randomized propagation delay ranging from 1 to 10 ms.
-
-% Alex: should we mention that?
-%The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS %attacks.
-%That is, sharing of the network links exponentially increases as decreasing level of the binary tree.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.2]{topo-tree-evil-5-good-0-producer-gw}
-  \caption{Small-scale binary tree topology}
-  \label{fig:small-scale}
-  \vspace{-0.3cm}
-\end{figure}
-
-% in 10 independent runs of each simulation, where we randomized position of the adversaries along the legitimate users.
-In all runs, the total number of legitimate and malicious uses were fixed, meaning that when we increase number of attackers, we decrease the number of legitimate users.
-
-\subsubsection{Effectiveness of the three mitigation algorithms}
-
-%The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
-%For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).
-
-Our goal is to compare the effectiveness of each mitigation method and quantify the percentage of Interests satisfied for all legitimate users while the network is under attack.
-For each mitigation algorithm, we perform 10 independent simulation runs, where we randomly choose 7 client nodes to represent adversaries while the remaining 9 client nodes represent legitimate users.
-In each run we simulate a 10-minute attack window (total simulation time was 30 minutes, with attack starting at the 10-minute mark).
-We plot the minimum and maximum range for observed Interest satisfaction percentages for all legitimate users aggregated across the 10 simulation runs as a function of time for each mitigation algorithm in Fig.~\ref{fig:small-scale attack progress}.
-Token bucket with per-interface fair queuing performs the worst, while satisfaction-based pushback performs the best, with almost a 100\%  satisfied Interests for all legitimate users.
-
-%A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
-
-\begin{figure}[]
-  \centering
-  \hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
-  % \vspace{-.3cm}
-  \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
-  \label{fig:small-scale attack progress}
-  % \vspace{-.4cm}
-\end{figure}
-
-%\paragraph{\textbf{Simple token bucket}}
-
-%{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}
-
-%Let us take a deeper look on what is happening with the simple token bucket algorithm.
-%Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as token bucket restricts the number of forwarded Intersets!).
-%This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
-%In this example we assume that both the legitimate user and the adversary send Interests in about the same time.
-%
-%\begin{figure}[t]
-%  \centering
-%  \includegraphics[scale=0.3]{physical-limits-sync-problem}
-%  \caption{Three-router topology, with one legitimate and one malicious user}
-%  \label{fig:three router example}
-%\end{figure}
-%
-%Both router L and router X will forward the Interests, as both of them have a free token available.
-%At router A, two cases are possible, either of Interests can arrive first, resulting in a quite different effects.
-%When legitimate Interest arrives first, then there are no problem. 
-%Router A will capture the token, forward the Interest, which will be quickly satisfied, releasing the token for future uses.
-%In the mean time, malicious Interest will be dropped at router A, and router X will release the hold for the token in one second (i.e., after the maximum time Interests are admitted), enabling a new round of competition for router A's resources.
-%
-%In the case when malicious Interest is sent a little bit earlier, then router A will forward malicious Interests, dropping a legitimate one, and causing ``lock out'' for one second.
-%In the instant when the token gets released at router X, an adversary is able to push new Interest towards router A, which may arrive in the exact time A's token gets released (assuming an idealistic environment).
-%As a result, the adversary recaptures router A's token and extends the ``lock out'' for another second, denying service to the legitimate user without sending any massive numbers of Interests.
-
-\paragraph{\textbf{Token bucket with per interface fairness}}
-
-We observe a successful DDoS attack, where 40\% attackers succeed in significantly shutting down the remaining 60\% legitimate users---a mere 15\% of their Interests are satisfied by Data from the producer.
-Contrary to expectations, the 60\% legitimate users do not receive at least 60\% of network resources.
-As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers and causes congestion and packet drops near the victim.
-%Significantly reducing the number of accepted malicious Interests is fundamental for improving the effectiveness of any mitigation algorithm.
-
-%The described problem arises from the clocking effect and can be solved in a number different ways.
-%Augmenting token bucket algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
-%That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
-%However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
-%Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
-%We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.
-
-\paragraph{\textbf{Satisfaction-based Interest acceptance}}
-
-The effectiveness of this algorithm stems from the fact that routers can differentiate and limit malicious Interests into the network%, thereby ensuring availability of network resources for serving legitimate users
-.
-The observed periodic dips in the Interest satisfaction ratios of legitimate users in Fig.~\ref{fig:small-scale attack progress} is a direct result of Interest satisfaction rate statistics decaying with time.
-The 50-second period approximately corresponds to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx$20\% within 50~seconds.
- % that ranges from 30~seconds to 50~seconds. 
-%The primary reason that such minimum peaks exist is the fact that 
-When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe mixed traffic from legitimate and malicious users).
-Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' again to the edge.
-
-%When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
-%That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
-
-\paragraph{\textbf{Satisfaction-based pushback}}
-
-In our simulations, this mitigation algorithm was able to effectively shut down attackers and ensure almost all the Interests from legitimate users are satisfied. 
-%The only potential problem with the satisfaction-based pushback algorithm is that it features 
-We observe a  sharp dip in the satisfaction ratio curve at the start of the attack as it takes a few seconds for all routers to be fully aware of the attack.
-However, recovery is quick as malicious Interests start to time out and explicit Interest limit announcements start to succeed in containing malicious Interests close to the attacker.
-Till then, the network, for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
-Once the malicious Interests are effectively shut down, all Interests from legitimate users are satisfied.
-Unlike the satisfaction-based Interest acceptance scenario, we do not observe any periodic dips in the satisfaction curve, as the pushback algorithm effectively guarantees that once an Interest is admitted, it will likely be routed all the way to the data producer.
-
-\subsubsection{Network reaction to varying number of attackers}
-
-Our next goal is to study the effectiveness of our mitigation algorithms as a function of increasing adversaries in the network.
-To this end, we vary the percentage of attackers in the topology from 6\% to over 50\%.
-Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
-All other parameters and experimental setup are consistent with the previous experiment.
-As before, for each mitigation algorithm, we perform 10 independent simulation runs.
-%The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
-%To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.
-
-%Since at this point the overall attack dynamics of all the attack mitigation algorithms is relatively clear, 
-% In other words, each point captured in the box plot graph corresponds to 1-second averaged satisfaction ratio for a user in an individual simulation run.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
-  % \vspace{-.3cm}
-  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}
-  \label{fig:small-scale-topo boxplot}
-  % \vspace{-0.5cm}
-\end{figure}
-
-In Fig.\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
-The results are as expected---for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
-In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.
-While the two intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
-In the case of satisfaction-based pushback algorithm, during the first minute of the attack over 90\% of Interests from legitimate users are satisfied even if 50\% of end nodes are malicious.
-
-% \begin{figure}[htbp]
-%   \centering
-%   \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min-after-1-min}
-%   \caption{Average consumer Interest satisfaction ratios (second minute)}
-%   \label{fig:small-scale-topo 2}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Large scale simulations}
-\label{sec:largescale}
-
-%To check validity of the small-scale experiment results, we performed a larger-scale evaluation based on a modified version of
-
-In this section, we investigate the behavior of our mitigation strategies under a more realistic, large-scale network topology.
-The ISP topology we used is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
-%In order to approximate the general structure of the Internet,
-% (scale-free structure, customer-provider, and peer-to-peer relations)
-We extract the largest connected component comprising of 562 nodes from this original topology and separate the nodes into three categories: clients, gateways, and backbones.
-Nodes having degree less than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes are classified as backbones (109 blue nodes).
-%(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
-We assign bandwidth and  delay values to links based on their type---both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
-We experiment with placing the data producer at both a gateway node as well as backbone node, which we randomly pick for each simulation run.
-Similar to the binary tree topology experiments, we fix the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly pick these nodes for each simulation run.
-We conduct 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5-minute interval.
-
-\begin{figure}[t]
-  \centering
-  % \vspace{-.1cm}
-  \includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
-  % \vspace{-0.3cm}
-  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
-  \label{fig:large-scale-topo}
-\end{figure}
-
-\begin{table}[t]
-\centering
-\caption{Large-scale topology link bandwidth and delay ranges}
-% \vspace{-0.3cm}
-\label{tab:large-scale}
-\begin{tabular}{|l||c|c||c|c|}
-  \hline
-  \multirow{2}{*}{\bf Link type} &  \multicolumn{2}{|c||}{\bf Delay} &  \multicolumn{2}{|c|}{\bf Bandwidth} \tabularnewline
-  \cline{2-5}
-                        &  Min & Max                       &  Min & Max \tabularnewline
-  \hline \hline
-  Backbone--Backbone    & 5~ms & 10~ms   & 40~Mbps & 100~Mbps \tabularnewline
-  \hline
-  Gateway--Backbone,    & \multirow{2}{*}{5~ms} & \multirow{2}{*}{10~ms}   
-                        & \multirow{2}{*}{10~Mbps} & \multirow{2}{*}{20~Mbps} \tabularnewline
-  Gateway--Gateway      & & & & \\
-  \hline
-  Client--Gateway       & 10~ms & 70~ms   & 1~Mbps  & 3~Mbps \\
-  \hline
-\end{tabular}
-% \vspace{-0.3cm}
-\end{table}
-
-%Priya: Leaving out this in the interest of space...
-%Topological location of the data producer plays a key role in its resilience to Interest flooding attacks.
-For a data producer that %is connected to a client node via a low-bandwidth link, even a small number of junk Interests can impact services for legitimate %users.
-For a producer located at the backbone with rich connectivity through many high-bandwidth links, an attack might not %be as severe as a majority of legitimate users might not be on the attack path.
-
-% The results for all attack mitigation algorithms and all runs are aggregated in Fig.~\ref{fig:small-scale attack progress}, where Y-axis represents a minimum and maximum range for observed Interest satisfaction percentages among all nodes and all simulation runs.
-% A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
-
-In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over all simulations runs for each mitigation algorithm for the scenario where the data producer is placed at a gateway node.
-We observe similar results for the data producer placed at a backbone node as well.
-Unlike the binary-tree topology experiments, we observe that the satisfaction-based pushback is the most effective algorithm, while both the token bucket with per interface fairness and satisfaction-based Interest acceptance have poor performance.
-Interest satisfaction percentage for legitimate users are close to 100\% and approximately 30\% and 25\% respectively for these mitigation methodologies.
-
-%
-%The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
-
-\begin{figure}[t]
- \centering
- \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
- % \vspace{-.3cm}
- \caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}
- % producer on a gateway node
- \label{fig:large-scale}
- % \vspace{-.7cm}
-\end{figure}
-
-Satisfaction-based Interest acceptance algorithm, which was very effective for binary-tree topology, is completely ineffective when deployed in a larger and more realistic topology.
-For the duration of the attack, legitimate users experience poor quality of service with only 25\% of their Interests being satisfied and continue to experience degraded service long after the attack has stopped.
-This poor performance, as detailed in Section~\ref{sec:probabilistic}, is due to the fact that each router on the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
-In the case of the larger-topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics and further penalization of new Interests from them.
-
-All our evaluations leave us to conclude that among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most promising one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
-%The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
-As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.
-
-% Alex: Anything else here?
-
-% Alex: I also experimented with placing producer at the backbone, getting slightly better results for all algorithms.  Though I'm not sure there is any value to put those results in the paper
-
-% \input{simulation-emulation.tex}
-
-\subsection{Limitations}
-%{\color{red} I gave up the idea of seperate discussion section after trying for some time, as given the space limitation, there is no way to write a reasonably comprehensive and  broad discussion section that justifies a separate section.
-Instead, I decided to have a scoped down version here that confesses upon the limiations of our evaluations only.
-Whoever has time (I need to sleep few hours), please go ahead and write 1-2 paragraphs as I outlined below.
--Ersin}
-
-%This section should roughly say: Our results show that the two features, namely the symmetric traffic and stateful routing, give NDN routers the ability to observe and characterize traffic in real time.
-Through our evaluations, we demonstrated that a mitigation algorithm that leverages such ability has great potential in mitigating various DDoS attacks that could otherwise have grave effect on the network.
-However, as the first step in exploring the problem and the solution space, this paper has obvious limitations: (1) We assume a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations.
-Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step is evaluating the above described solutions with more sophisticated and adaptive attackers.
-(2)   Although most (such as single-path routing, no-caches in the network, single homed victim, etc) are aimed to test the proposed solutions under worst-case scenario, we made many assumptions in simulations/evaluations about the configurations, topology and the traffic that maybe poor-representative of realistic conditions.
-(3) As NDN being an ongoing research effort itself, our evaluations fully depend on simulations and done over a snapshot of its codebase.
-
-% The main contribution of the paper and this section in particular is a proof that two inherent properties of NDN architecture, namely the symmetric traffic and stateful forwarding, give NDN routers the ability to characterize traffic and react in real time.
-% We demonstrated that satisfaction-based pushback algorithm, leveraging this ability, has great potential in mitigating various DDoS attacks that could otherwise have a grave effect on the network. 
-% However, as the first step in exploring the problem and the solution space, our paper has obvious limitations.
-% First, we assumed a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations. 
-% Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step that we are leaving out for future work is evaluating the above described solutions with more sophisticated and adaptive attackers.
-% Second, while aiming to test the designed algorithms under worst-case conditions, the future work needs to address behavior in more realistic scenarios, including investigation of multi-path routing, in network caches, as well as multi-homed victims.
-
-This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space. 
-While designing our mitigation algorithms, we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
-We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology, % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
-as well as a more realistic ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network. 
-While our results are promising and show a great potential in mitigating Interest flooding DDoS attacks, there are certain limitations which should be addressed in future research.
-
-First, in our evaluations we used a simple and static attacker model---attackers send junk Interests as fast as possible. 
-In future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and Interest sending patterns based on the network reaction. 
-Second, we assumed that Interests are not satisfied by an intermediate router's cache and always forwarded all the way to the producer.  
-In future, we plan to study the impact of Interest flooding attacks in more realistic scenarios with multi-path routing enabled, more realistic traffic patterns, and the presence of in-network caches.
-% We also ignored NDN's strategy layer that routes around failure and congestion in the network. 
-% In future work, we plan to study the impact of turning on these features. 
-%Finally, we also plan to perform more extensive simulations on other realistic Internet-like topologies and traffic patterns.
-
-\section{Related work}
-\label{sec:related-work}
-
-As a new Internet architecture proposal, Named Data Networking has attracted attention from the security community. 
-Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
-W\"ahlisch et al.~\cite{Wahlisch:2012:Backscatter-from} explore security and stability threats in the general area of information-centric networks (ICN), using CCNx software as an example.  
-While this work aims to generalize findings for all ICNs, it largely does not go beyond the current design choices of CCNx.
-% (which is an example, but not the final word in NDN) 
-% Gasti et al.~\cite{gasti2012ddos} identified several NDN architecture-specific attacks (Interest flooding and content/cache poisoning) and proposed potential solutions, without devising particular algorithms.
-In this paper we follow the suggestions by Gasti et al.~\cite{gasti2012ddos} and utilize the properties provided by the NDN architecture to mitigate DDoS attacks, and tackle the Interest flooding problem as a first step in this direction.
-More specifically our attack mitigation design relies on NDN's stateful forwarding plane that allows us to
-maintain statistics on unsatisfied Interests.  
-Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
-
-The general area of mitigating denial of service attacks is amongst the hottest topics in recent years.
-% Among all the body of work, 
-The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushing back malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
-overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
-various ticketing systems with conditional admission of traffic in to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
-and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
-Identifying malicious traffic requires establishing certain state at routers, and the above mentioned solutions differ in the specifics on what state to use and how to establish it.
-By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions---we simply take full advantage of this state to develop desired solutions.
-
-% Our design for the Interest flooding attack mitigation borrows
-
-% This paper talks about attacks on content centric infrastructure (not specifically to NDN).
-% \cite{Wahlisch:2012:Backscatter-from}
-
-% % Collaborative detection of DDoS attacks over multiple network domains
-% \cite{Chen:2007:Collaborative-detection} distributed change-point detection
-
-% % DDoS flooding attack detection through a step-by-step investigation
-% \cite{Jun:2011:DDoS-flooding}
-
-% % A practical method to counteract denial of service attacks
-% \cite{Tupakula:2003:A-practical-method}
-
-% Alex: We should not include this reference for the review, but afterwards
-% Previous work on DDoS and DoS~\cite{gasti2012ddos}
-
-% Network level (Flooding)
-% % 2002
-% Pushback~\cite{Pushback} (hop-by-hop push back) aggregate- based congestion control/congestion signatures (e.g., per-destination), rate-limiting, explicit notification
-% AITF~\cite{Argyraki:2005:Active-internet} (active filtering requests; path recording, last-point of trust detecting)?
-% DefCOM \cite{Oikonomou:2006:A-framework-for-a-collaborative} Communication between src, core, and dst to provide collaborative defense.
-Dst raises alerts, src differentiate bad/good, packet tagging.
-Core rate-limit, congestion-aware re-tag.
-Traffic prioritization.
-% StopIt \cite{Liu:2008:To-filter-or-to-authorize:} (filtering) tagging with passports, tagged prioritization, dst- invoked filter instantiation
-% NetFence \cite{Liu:2010:NetFence:-preventing} congestion policing: fair queuing (one leaky bucket per {src,L}, L- bottleneck), secure "ticketing" with signals for AIMD to increase/decrease bandwidth allowance
-% PSP \cite{Chou:2009:Proactive-surge} topology as origin-destination pairs, packet tagging, OD traffic isolation, sharing based on historic bandwidth demand
-
-% SIFF~\cite{Yaar:2004:SIFF:-A-stateless} (time-based tickets, capabilities)
-% TVA \cite{Yang:2005:A-DoS-limiting-network} like SIFF, traffic- based tickets, hierarchical per- AS, per-source fair queuing
-% FastPass \cite{Wendlandt:2006:Fastpass:-Providing} (tokens: various puzzles, other methods) traffic authorization, routers verify and filter.
-% \cite{Natu:2007:Fine-grained-capabilities} based on TVA/SIFF: specifies previously unspecified mechanisms to grant "tickets" for requesters, extends capabilities to include priorities, changing tickets to be only destination- dependent, not path dependent
-% % LazySusan \cite{Crowcroft:2007:Lazy-Susan:} TR (latency-based proof of work--- computational puzzles)
-% Portcullis \cite{Portcullis} Protecting connection setup with computational proof of work, tickets and traffic prioritization for the rest, per- computational fairness; DNS to disseminate puzzles
-% There are many other puzzle- based schemes, on which Portcullis is based or which problems it solves
-
-% PacketSymmetry \cite{Kreibich:2005:Using-packet} (leverages packet symmetry to detect and remove bad traffic) packet asymmetry - number of transmitted packets (tx) to received packets (rx); negative values when rx outweighs tx, positive values when tx outweighs rx, and zero in the case of perfectly balanced traffic)
-% % Detecting SYN flooding attacks
-% \cite{Wang:2002:Detecting-SYN-flooding} based on the protocol behavior of TCP SYN-FIN (RST) pairs, and is an instance of the Seqnential Change Point Detection
-% dFence \cite{Mahimkar:2007:dFence:-Transparent} (middleboxes) TCP connection proxying, rate estimation and TCP/ACK modification
-
-% Overlays:
-% CenterTrack \cite{Stone:2000:CenterTrack:-An-IP-overlay} (overlay) reroute suspicious traffic to a special routers with diagnostic capabilities using an overlay
-% SOS \cite{Keromytis:2004:SOS:-An-architecture}
-% Shield \cite{Kline:2011:Shield:-DoS-filtering}
-
-% NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
-In this section we will overview generic directions of DDoS mitigation designs and try to think about which tricks could be used in NDN.
-
-% Capability-based systems allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
-Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
-This implies that each client must pass through an authentication process prior to using any bandwidth~\cite{Capabilities}.
-We believe that for NDN this method doesn't fit really well for the following reasons.
-First, this method is very questionable in terms of scalability and mobility support since it requires tight trust connections between routers and hosts.
-Thus, it neglects one of the main advantages (mobility) of NDN.
-Second, the design of trust infrastructure for NDN is not well defined yet, which means that we cannot really make assumptions in our design of mitigation techniques.
-
-% Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
-Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients.
-One of the main difficulties in such systems is the question of puzzle dessimination.
-In ~\cite{Portcullis} authors suggested to propagate puzzles using DNS system.
-In NDN since routers have caching abilities, we can propagate puzzles just like a normal data packets, using Interest-Data exchange.
-Overall, this method looks interesting and deserves being investigated in a future work.
-
-% Congestion control systems do per flow traffic analysis and drop of packets belonging to misbehaving flows.
-For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
-Such techniques, if largely deployed, could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
-Since NDN routers maintain a richer per-packet state, which translates into a better per-flow statistics, these techniques can become much more effective when applied to NDN.
-
-% Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
-This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines~\cite{Pushback}.
-In general this technique can be applied to NDN architecture thanks to its decentralized coordination of downrating bad traffic flows.
-Moreover, NDN provides better capabilities for accurate flow detection.
-
-%were looking for getting accustomed
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-% Main take out from the paper:  could be a problem, but problem is solvable.  
-% One of the key components in the Named Data Networking architecture is its stateful data delivery model, which potentially can be abused by new types of denial of service attacks.
-% However, one should not forget that the same stateful data delivery provides effective mechanisms to fight back against such attacks.
-
-%In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
-%The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data path symmetry and full receiver-based traffic control.
-%In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Interests can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
-%
-%Other forms of attack may require different mitigation mechanisms.  
-%However, the granularity of the NDN state---per each Interest packet---is what giving NDN an opportunity to stand against existing and new forms of attacks.
-%
-%NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution.
-
-NDN being a newly proposed future Internet architecture, it is important to address its resilience in face of DDoS attacks.
-As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks namely Interest flooding and the severe service degradation such an attack may cause to legitimate users.
-We then leveraged the key features of the NDN architecture to design, develop, and evaluate three mitigation strategies.
-We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
-The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers, so that they cause little or no service impact to legitimate users.
-
-NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balance (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding}.
-Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.
-
-\bibliographystyle{IEEEtran}
-\bibliography{references}
-
-\end{document}

### 2013-05-13 01-intro.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@932 df1a90cd-247b-4364-bdaf-287a704eb499
Splitting paper back to its normal organization

@@
 
-% Introduction / Motivation
-% Brief introduction about attacks in NDN
-% Contributions of the paper
-
-% Introduction to the problem: ndn, solves many problems, but has potential to introduce new problems.
-% in this paer we are studing a number of remedies to Interest floodig attack, as well as trying to doscover ptential of tjese dolutions and their shortcomings
-
-% Structure. Hopefully around three paragraps. 
-% - what is happening with ndn and what is interest floodog
-% - what are the general approaches we are taking, ranging from naïve to more intelligent
-% - basic summary of the results
-
-% move disclaimer from section 3 to the intro.
-
-% The Internet is a unique global success story that earmarked the information age. 
-% However, the design that fostered its success and wide-adaptation over the last three decades is now aged and limited in accommodating the changing demands of today's users. 
 Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an ongoing research effort that aims to move the Internet into the future with a content-centric design that is capable of efficient content distribution and seamless mobility support.
-In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in packets.
-However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against distributed denial of service (DDoS) attacks?
+In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in the packets.
+However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against DDoS attacks?
 Especially since various forms of DDoS attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial to ensure that the new design is free of similar vulnerabilities.
@@
 NDN eliminates host-based addressing and makes data the first-class network entity.
-Instead of sending packets to a given IP address, in NDN end hosts request desired data by sending Interest packets carrying application-level data names, and the network returns the requested Data packets following the path of Interests.
+Instead of sending packets to a given IP address, NDN nodes request desired data by sending Interest packets carrying application-level data names, and the network returns the requested Data packets following the path of Interests.
 Such a shift automatically eliminates several long-standing DDoS attacks, including direct flooding and reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
@@
 However, malicious users can attack the network by sending an excessive number of Interests. 
-Because each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can potentially congest the network and exhaust routers' memory. 
+Since each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can congest the network and exhaust a router's memory. 
 We coin the term {\it Interest flooding} to refer to such attack and
-%One can also attack an NDN network by hijacking Interest packets and then injecting false data replies into the network.
 this paper exclusively investigates the problem and the solution space for it.
@@
 Through extensive simulations, we show how one of our mitigation methodologies effectively shuts down malicious users while preventing legitimate users from service degradation.
-%We use extensive simulations to show the devastating effect of Interest flooding on vanilla NDN and how a router can effectively exploit its state information to effectively mitigate them. 
- %(Section~\ref{sec:design}).
-%We base our solutions on the following two insights.
-%First, instead of creating state for all incoming Interests, an NDN router should only needs to accept enough Interest packets to fully utilize downstream link capacity.
-%Second, because Data packets traverse the path taken by the Interests, an NDN router can observe whether an Interest retrieves Data (good %Interest) or not (bad Interest).
-% Alex: Not sure whether it should be mentioned in intro or not.  If it should, then I don't really like it...
-
-% Alex: I generally don't like this section as it is does not bring anything valuable. 
-% My first candidate to be cut
 The rest of the paper is organized as follows.
-We give an overview of NDN architecture in Section~\ref{sec:ccn-intro} and explain interest flooding attacks in Section~\ref{sec:interest-flooding}.
+We provide an overview of NDN architecture in Section~\ref{sec:ccn-intro} and describe Interest flooding attacks in Section~\ref{sec:interest-flooding}.
 In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
-We summarize related work in Section~\ref{sec:related-work} and finalize the paper with conclusions and future work in Section~\ref{sec:conclusion}.
-
-%We conduct simulation-based evaluations to quantify the effectiveness of our proposed attack mitigation algorithms %(Section~\ref{sec:evaluation}).
-%% based on trivial small-scale and Internet-like larger-scale topologies.
-%The results show a great potential of one of the designed algorithms (satisfaction-based pushback, Section~\ref{sec:dynamic limits}), where %the attack traffic can be effectively localized near the attacker himself.
-%\todo{LZ: I did not modify this last paragraph; need to see the rest of the paper first.}
-
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: "paper"
-%%% End:
+We summarize related work in Section~\ref{sec:related-work}.
+We discuss future work and conclude in Section~\ref{sec:conclusion}.

### 2013-05-13 02-ndn-overview.tex
Splitting paper back to its normal organization

--- 2013-03-26 paper.tex
@@
-\documentclass[10pt,conference]{IEEEtran}
-% http://networking2013.poly.edu/call-for-papers/paper-submission/
-% Page limit 9 pages
-
-\makeatletter
-\def\ps@headings{%
-\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
-\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
-\def\@oddfoot{}%
-\def\@evenfoot{}}
-\makeatother
-
-\hyphenation{incoming}
-\hyphenation{na-me-spa-ce}
-\hyphenation{sa-tis-fac-tion}
-\hyphenation{sa-tis-fied}
-
-\pagestyle{headings}
-
-% \usepackage[top=.75in, bottom=1in, left=.625in, right=.625in]{geometry}
-\usepackage{graphicx}
-% \usepackage[]{hyperref}
-\usepackage{breakurl}
-\usepackage{url}
-\usepackage[nocompress]{cite}
-% \usepackage{verbatim}
-% \usepackage{algpseudocode}
-\usepackage[noend]{algpseudocode,algorithm}
-% More customizeable version. Probably it would be better to convert pseudocode to 2e format
-% \usepackage{algorithm2e} 
-\usepackage{multirow}
-\usepackage{times}
-\usepackage{color}
-
-\newfont{\nicettfont}{cmtt9}
-\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
-\renewcommand{\texttt}[1]{{\nicettfont #1}}
-
-\graphicspath{{figures/}}
-
-\begin{document}
-
-\title{Interest Flooding Attack and Countermeasures in Named Data Networking}
-
-\author{
-    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
-    \\\{afanasev, iliamo, lixia\}@cs.ucla.edu}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
-    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
-}
-
-\maketitle
-
-\begin{abstract}
-Distributed Denial of Service (DDoS) attacks are an ongoing problem in today's Internet, where packets from a large number of compromised hosts thwart the paths to the victim site and/or overload the victim machines.
-In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network delivers Data packets upon request only, effectively eliminating many existing DDoS attacks.
-However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  
-In this paper we investigate effective solutions to mitigate Interest flooding.
-We show that NDN's inherent properties of storing per packet state on each router and maintaining flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
-Our evaluation through simulations shows that the solution can quickly and effectively respond and mitigate Interest flooding.
-\end{abstract}
-
-\begin{IEEEkeywords}
-Information-centric networks, named-data networking, denial-of-service
-\end{IEEEkeywords}
-
-\section{Introduction}
-\label{sec:intro}
-
-Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an ongoing research effort that aims to move the Internet into the future with a content-centric design that is capable of efficient content distribution and seamless mobility support.
-In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in the packets.
-However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against DDoS attacks?
-Especially since various forms of DDoS attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial to ensure that the new design is free of similar vulnerabilities.
-
-NDN eliminates host-based addressing and makes data the first-class network entity.
-Instead of sending packets to a given IP address, NDN nodes request desired data by sending Interest packets carrying application-level data names, and the network returns the requested Data packets following the path of Interests.
-Such a shift automatically eliminates several long-standing DDoS attacks, including direct flooding and reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
-%
-However, malicious users can attack the network by sending an excessive number of Interests. 
-Since each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can congest the network and exhaust a router's memory. 
-We coin the term {\it Interest flooding} to refer to such attack and
-this paper exclusively investigates the problem and the solution space for it.
-
-Our effort is an important first step towards a complete investigation of DDoS attacks in NDN.
-We experiment with three algorithms that allow routers to exploit their state information to thwart these attacks.
-Through extensive simulations, we show how one of our mitigation methodologies effectively shuts down malicious users while preventing legitimate users from service degradation.
-The rest of the paper is organized as follows.
-We provide an overview of NDN architecture in Section~\ref{sec:ccn-intro} and describe Interest flooding attacks in Section~\ref{sec:interest-flooding}.
-In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
-We summarize related work in Section~\ref{sec:related-work}.
-We discuss future work and conclude in Section~\ref{sec:conclusion}.
-
 \section{NDN Overview\label{sec:ccn-intro}}
@@
 For simplicity, we assume routers keep Interests in PIT for one second in our simulations.
-
-\section{Interest Flooding Attacks in NDN}
-\label{sec:interest-flooding}
-
-As we explained earlier, Interest packets in NDN are routed through the network based on content name prefixes and consume memory resources at intermediate routers.
-This makes them a potential tool to launch DDoS attacks in NDN.
-An attacker or a set of distributed attackers can inject excessive number of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{attack-definition}
-  \caption{Example of Interest flooding attack}
-  \label{fig:flooding example}
-  \vspace{-0.3cm}
-\end{figure}
-
-Since an NDN network fetches data by its name, an adversary cannot easily target specific routers or end-hosts.
-However, an adversary can target a specific namespace.
-For example in Fig.~\ref{fig:flooding example}, if the data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
-\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{\small /foo/bar} prefix to make them effective.
-It also assumes the producer is single-homed and the data is not replicated elsewhere.
-With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding, Yi:2013:A-Case-for-Stateful} support.}
-A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
-
-Similar to packets in traditional networks, Interest packets in NDN consume a portion of network capacity.
-A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
-In particular, a coordinated DDoS attack could target one specific namespace and concentrate attack traffic in certain segments of the network, as routing in NDN is based on name prefixes.
-
-As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a router's memory, making the router unable to create new PIT entries for incoming Interests and disrupting service for legitimate users.
-
-Nevertheless, creating an effective Interest flooding attack in NDN is non-trivial.
-To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1)~the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2)~new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
-The former is achieved when Interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers---an Interest is not forwarded upstream if a router can satisfy it from its content store.
-The latter requires every single malicious Interest to ask for unique content---all Interests requesting the same content are combined into one PIT entry in routers.
-Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content with each Interest.
-Of the two options available to an adversary, the first one is challenging due to the difficulties around indexing content names in a particular namespace, coordinating a large number of bots to send unique Interests, and sustaining the attack while the network is continuously caching the requested content objects.
-However, the second option---requesting a unique non-existing content with each Interest---is easy to achieve and sustain.
-For example, an adversary can construct such Interests by concatenating a variable-length random name component to the victim namespace (e.g., \ndnName{/newyorktimes/3rf3...}).
-In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest, but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
-% other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
-
-In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
-
-%\paragraph{Assumptions} 
-%E: These are assumptions for the simulations on hand and particulary to test for the worst case scenario in many aspects.
-They are not the paper's assumption and in fact the paper first should be more general on describing all possibilities.
-Then it should explain the assumptions for the simulations and discuss why they make sense and do NOT favor positive results in some way.
-
-% - assumptions about attacker position
-% - assumptions about the producer / producer namespace
-% - assumptions about the attack traffic / attack pattern
-
-%In this paper we are making the following assumptions about the Interest flooding attack:
-%\begin{itemize}
-%\item only client nodes can be compromised and become attack bots;
-%\item there are no colluding attackers inside the Data producer's network;
-%\item the attack is carried only using unique junk Interests; and
-%\item there is only one Data producer for the attacked prefix.
-%\end{itemize}
-
-%We also assume that NDN forwarding strategy uses only single-path Interest forwarding, always choosing the best-metric route advertised by the routing protocol.
-%This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
-
-%In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
-
-\section{Interest flooding mitigation methods}
-\label{sec:design}
-
-% Points what should be here:
-% - What can be done (in general) to mitigate flooding attack
-% - Which building blocks NDN architecture gives to mitigate Interest flooding attacks: Interest limits, ability to measure Interest satisfaction performance (Interest satisfaction stats)
-% - Methods to set these limits: static/dynamic
-% - Methods how limits can be applied: best-effort (fifo), "fair" queuing, probabilistic
-% - Reference to caching: we don't consider it here, but caching provides additional level of protection, especially for certain types of attacks
-
-% Our definition of attack mitigation is that good clients are still able to access data on the producer.
-
-In this section we present several algorithms to mitigate Interest flooding attacks in NDN.
-Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
-We start by describing our simple strategies and use the insights and lessons learned from the deployment of these to inform and design more effective mitigation techniques that work well in various topologies.
-
-%   - Naive approach to Interest Limits (that is called physical limits everywhere else)
-%     Example how this can be implemented in a simple way
-%     Baseline solution
-%   - Interest limits with "fair" queuing
-%     Improving problem of simple limits (no single face can dominate), but doesn't solve the proble
-
-% - Attack mitigation
-%   - Per-incoming interface Interest statistics
-
-%   - Dynamic Interests limit adjustments
-
-%   - Probabilistic Interest accept
-
-%The fact that each Data packet takes the reverse path of the corresponding Interest packet allows intermediate routers to match a received Data packet to the corresponding Interest packet and %thus determine which Interest packets were satisfied.
-As we describe in the rest of this section,  NDN routers can exploit this information to make informed decisions on which Interest packets to %forward, how many Interest packets to forward, and thus effectively defend against DDoS attacks.
-
-%Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
-%Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
-%Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
-%At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
-
-%\subsection{Na\"{i}ve attack mitigation}
-
-%We start with a couple of naive strategies that can be used to migitate attacks in an NDN network and describe the pitfalls associated with these strategies.
-
-% In a normal network operation, the size of Interests packets is supposed to be significantly smaller than the size of the requested Data.
-
-% All communication in NDN network is host-to-host and receiver-driven.
-
-An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests forwarded through the network. To this end, we exploit a 
- fundamental principle of NDN architecture---flow balance between Interest and Data packets.
-Flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
-This principle allows intermediate routers to control the inbound data traffic by controlling the number of outstanding Interests in the network.
-One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding interface.
-This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet-switched networks.
-Analogous to the {\it Token Bucket} algorithm, NDN routers can keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
-Ideally, the number of tokens (the pending \emph{Interest Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
-We can formalize this value as follows:
-% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
-%
-\begin{equation}
-\label{eq:interest limit}
-\small \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
-\end{equation}
-
-In the above equation, \emph{Delay} is the expected time for the Interest to be satisfied and \emph{Data packet size} is the size of the returning Data packet.
-Although both these values are not known a priori, it is not really necessary to use their exact values.
-One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as network buffers can smooth out most of the network fluctuations.
-
-This {\it Token Bucket} approach might be exceptionally restrictive in forwarding Interests---not all Interests will result in a Data packet---and might result in underutilization of the network.
-However, the biggest drawback of this algorithm is the fact that it can nourish DDoS attacks.
-If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
-One way to get around this issue is to impose a per interface fairness, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
-We describe this technique in greater detail below.
-
-%That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
-%For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
-%In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
-%
-%\subsubsection{\textbf{Interest limits (physical limits)}}
-%\label{sec:physical limits}
-%
-%\input{algos/physical-limits.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Token bucket with per interface fairness}}
-\label{sec:queuing}
-
-To address the lack of fairness associated with the na\"ive {\it Token Bucket} approach, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring nodes.
-For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
-%Due to the expected small volume of Interests, we cannot merely rely on network buffers to perform statistical multiplexing of Interests, as they would almost never be %buffered.
-%At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests %will arrive in the future.
-In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring nodes, 
-%, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
-we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded and implement hierarchical queues for each interface (see Fig.~\ref{fig:queueing}). 
-This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing and incoming interface.
-%As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
-We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
-Thus, a PIT entry can be quickly updated when the Interest is actually forwarded, and the element can be easily removed from the queue when the Interest expires.
-
-%For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}).
-%As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.6]{queue}
-  \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
-  \label{fig:queueing}
-  \vspace{-0.3cm}
-\end{figure}
-
-We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
-By setting appropriate queue sizes, we can control the amount of physical resources utilized at a router.
- % (such as memory and computation power). 
-It is also important to set a sensible value for how long an Interest can be enqueued. 
-If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet might be dropped at the downstream routers if their corresponding state expired. 
-For our evaluations, we empirically chose to enqueue Interests up to 10\% of their original lifetime (100~ms).
-% We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
-% Alex: I don't believe there is a need for separate discussion about "freshness", as we already introduced concept of lifetime
-% {\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
-
-%It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
-%Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
-%Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
-
-%The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
-%At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[h]
-\footnotesize
-\caption{\small Token bucket with per interface fairness}
-\label{alg:queuing}
-\begin{algorithmic}[1]
-\For{\textbf{each} interface \textbf{if}}
-    \State{$L_{if} \leftarrow$ Interest Limit according to (1)}
-    \State{$O_{if} \leftarrow 0$} \Comment{Outstanding Interests on interface \textbf{if}}
-\EndFor
-
-\vspace{0.1cm}
-
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
-    \If{$L_{out} - O_{out} > 0$} \Comment{\textbf{out} is under limit cap}
-        \State $O_{out} \leftarrow O_{out} + 1$  \Comment{``borrow'' a token from the bucket}
-        \State add \textbf{out} to PIT entry and forward \textbf{i} to \textbf{out}
-    \Else
-        \State Queue $q \leftarrow out$.GetSubQueue($in$)
-        \If{$Size(q) < L_{out}$}
-           \State $q$.PushInterest($i$)
-           \State add \textbf{out} to PIT entry, and link PIT entry with the queue
-        \Else
-           \State drop Interest
-        \EndIf
-    \EndIf
-\EndFunction
-
-\vspace{0.1cm}
-
-\State{} \Comment{\textit{Whenever $L_{out} - O_{out}$ becomes larger than zero}}
-\Function{TokenBecomesAvailable}{}
-    \State Queue $q \leftarrow$ $out$.GetRoundRobinSubQueue 
-    \State Interest $i \leftarrow$ $q$.PopInterest
-    \State update PIT entry and Forward($i$, $out$)
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{InData}{Data \textbf{d}}
-   \State lookup PIT entry \textbf{p} for data \textbf{d}
-   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
-        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
-   \EndFor
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{Timeout}{PIT entry $p$}
-   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
-        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
-   \EndFor
-\EndFunction
-
-\end{algorithmic}
-
-\end{algorithm}
-
-As we show in Section~\ref{sec:evaluation}, this algorithm provides a partial relief from Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
-We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is largely ineffective in protecting legitimate users from malicious ones. 
-Attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of malicious Interests.
-
-%At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
-%Therefore, to successfully solve the problem, we need a fundamentally different, more intelligent approach, allowing localization of the attack traffic as close as possible to the attack origin.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits a relatively large number of Interests from malicious users.
-A considerable percentage of these malicious Interests are forwarded all the way to content producers, thereby reducing resources available to serve legitimate users.
-This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate and malicious Interests.
-For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and differentiate to some extent malicious requests from legitimate ones.
-% `Good' Interests from legitimate users must be admited and forwarded appropriately. 
-Thus, the key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
-
-%One can try a black- or whitelisting approach.
-However, besides the fact that source black- and whitelisting cannot work in %NDN as it does not feature source addresses, it requires extraneous knowledge to classify the incoming Interests.
-
-%Priya: I have added the below point specifically to point out that a router cannot determine from the prefix name alone whether /parc is good  or bad...
-
-%{\color{red} \textbf{Alex: This paragraph is confusing to me.
-I would remove it.} In NDN one cannot easily distinguish a `good' prefix from a `bad' one.
-Content producers must be able to support %dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded %to the producer for possible dynamic Data packet generation.
-%Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the prefix name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain %namespaces  will be inefficient and likely ineffective.
-}
-
-% Alex: I'm not sure that this part is relevant... The point I see is that blacklisting and whitelisting is not 100% effective, but it can be used in both worlds
-
-% In today's host-based Internet architecture where DDoS mitigation techniques rely on blacklisting of ``dark'' IP prefixes or whitelisting of good IP prefixes.
-% Unlike IP, in NDN one cannot easily distinguish a `good' prefix from a `bad' one. 
-% Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
-% Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
-
-\subsection{Intelligent attack mitigation}
-\label{sec:intelligent mitigating}
-
-%While the Interest limit is the key building block to suppress mechanisms of the Interest flooding attack, legitimate Interests need to be somehow prioritized and malicious Interests need to be somehow penalized in order to completely suppress the attack.
-%That is, instead of processing Interests always based on the first-in-first-serve rule, NDN routers need some basis to treat the incoming Interests differently.
-%Thus, the primary task in bringing intelligence to the Interest flooding attack mitigation is to proactively distinguish between legitimate and malicious Interests.
-
-In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets.
-Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guaranteed to see if an Interest it forwarded resulted in a matching Data packet or timed out.
-%The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
-Since malicious Interests are not likely to bring data back (as discussed in Section~\ref{sec:interest-flooding}), this information can be utilized by routers in differentiating attack and legitimate traffic.
-%Therefore, intermediate routers can classify the ones that brings data back as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}
-%Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
-
-This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
-However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use these statistics to determine whether an incoming Interest should be forwarded or dropped.
-For example, maintaining Interest satisfaction ratio statistics for each incoming interface is sufficient to reasonably predict whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout if forwarded.
-Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
-that can further improve the estimates.
-A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but do not result in a returning Data packet.
-In order to allow negative statistics to build up fast and positive statistics to  deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.
-
-%Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
-%{\color{red} \it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong %here.}
-
-%The devil is always in the details.
-%From the one hand, such statistics needs to start penalizing adversaries as soon as possible (i.e., negative stats should build up fast).
-%On the other hand, the positive statistics should not deteriorate too fast (i.e., positive stats should be relatively long-term).
-%Our preliminary experiments showed that the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window, provides a good balance between the two contradictory requirements.
-
-% \subsubsection{\textbf{Data plane performance tracking}}
-% \label{sec:stats}
-
-% Note that there is a condition (line 6 in Pseudocode~\ref{alg:probabilistic model}) to check if there is a valid statistics point.
-% This condition is extremely important, because it first provides a basis to distinguish between known facts (i.e., good or bad satisfaction ratio for the incoming interface) and unknown facts (e.g., the first time an Interests arrives on the interfaces).
-% Second, it gives an opportunity to recover from a bad history (history of unsatisfied Interests) after malicious Interests are ceased to flow in.
-% Essentially, this recovery relies on statistics module to perform time-based invalidation of historical data (timely, but not too quickly\footnote{Otherwise, attackers may send short bursts of malicious Interests, successfully avoiding differential Interest treatment}).
-
-Pseudocode~\ref{algo:interest stats} formally defines how statistics can be generated for  each incoming interface.
-Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interests), only unsatisfied statistics needs to be exponentially smoothed (lines 19--21).
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Interest satisfaction statistics}
-\label{algo:interest stats}
-\begin{algorithmic}[1]
-
-\For{\textbf{each} interface \textbf{if}}
-    \State $F_{if} \leftarrow 0$ \Comment{forwarded Interests from interface \textbf{if}}
-    \State $\hat F_{if} \leftarrow 0$ \Comment{averaged value of $F_{if}$}
-
-    \State $U_{if} \leftarrow 0$ \Comment{unsatisfied Interests from interface \textbf{if}}
-    \State $\hat U_{if} \leftarrow 0$ \Comment{averaged value of $U_{if}$}
-\EndFor
-
-\vspace{0.1cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}}
-  \State $F_{in} \leftarrow F_{in} + 1$
-  \State record \textbf{\emph{in}} in the list of incoming interfaces for \textbf{\emph{i}}
-\EndFunction
-
-\vspace{0.1cm}
-\Function{InterestTimeout}{Interest \textbf{i}}
-    \State lookup the list of incoming interfaces for \textbf{\emph{i}}
-
-    \For{\textbf{each} interface \textbf{if} in the list}
-        \State $U_{if} \leftarrow U_{if} + 1$
-    \EndFor
-\EndFunction
-
-\vspace{0.1cm}
-
-\State {} \Comment{\textit{Exponentially weighted moving average smoothing}}
-\Function{EWMA}{} \Comment{Every second}
-\State $\alpha \leftarrow e^{-1.0/30.0}$  %\Comment{$\approx$ 30~sec average}
-
-\For{\textbf{each} interface \textbf{if}}
-    \State $\hat U_{if} \leftarrow \alpha \cdot \hat U_{if} + (1 - \alpha) \cdot U_{if}$ 
-    \State $U_{if} \leftarrow 0$
-
-    \If{$F_{if} > 0$} \Comment{To ensure decaying of ratio $U_{if}/F_{if}$}
-        \State $\hat F_{if} \leftarrow \alpha \cdot \hat F_{if} + (1 - \alpha) \cdot I_{if}$ 
-        \State $F_{if} \leftarrow 0$ \Comment{Reset counters}
-    \EndIf
-\EndFor
-
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-Fig.~\ref{fig:ratio example} illustrates the resulting dynamics of the statistics during and after an Interest flooding attack.
-The attack duration is from 10 to 70~seconds.
-Prior to start of the attack, the percentage of unsatisfied Interests is zero.
-The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.
-%\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
-For the duration of the attack (10--70~seconds), the percentage of unsatisfied Interests is close to 100\%: 
-when the ratio is close to 100\%, routers drop all incoming Interests, resulting in decaying of the statistics until a new Interest is admitted, which eventually brings statistics back near 100\% point.
-Finally, the ratio exponentially decays after the attack ceases.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.8]{limits}
-  % \vspace{-0.3cm}
-  \caption{Dynamics of  unsatisfied Interests statistics on a gateway's interface towards the attacker}
-  \label{fig:ratio example}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Satisfaction-based Interest acceptance}}
-\label{sec:probabilistic}
-
-Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using these ratios to penalize malicious Interests.
-A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
-%Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Satisfaction-based Interest acceptance}
-\label{alg:probabilistic model}
-\begin{algorithmic}[1]
-\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-
-\vspace{0.1cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
-
-    \State{} \Comment{Use uniform probability distribution model $P(X)$}
-    \State{} \Comment{$P(X) : \forall x \in [0,1] \Rightarrow P(x) = x$}
-
-    \If{$F_{in} > \theta $} \Comment{At least some Interests were forwarded before}
-        \State $s \leftarrow (1 - U_{in} / F_{in})$
-        \State Drop interest with probability $P(s)$
-    \EndIf
-
-    \State{forward the Interest, subjecting to token bucket limits}
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-Parameter $\theta$ on line 5 of Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
-This step is critical to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
-
-A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop an Interest. 
-As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
-In our example in Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
-At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
-Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the data producer.
-With each increasing hop in the network, the probability of being forwarded to the next hop decreases significantly.
-One way to prevent this overreaction and unfair penalization is to ensure that the decision taken at each router on whether to forward or drop the Interest is not independent of the decision taken at preceding routers.
-An explicit notification such as a gossip protocol between neighboring NDN routers might alleviate the problem, but we leave the design and evaluation of it to future work.
-%{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Satisfaction-based pushback}}
-\label{sec:dynamic limits}
-
-% Differential treatment of Interests received from different interfaces can be achieved in a more elegant way, without reverting to probabilistic methods.
-
-The previous algorithm---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
-% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
-An alternate algorithm for proportional token distribution without overreaction is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
-Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.
-
-The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm will work in our example in Fig.~\ref{fig:flooding example}.
-Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node will set and announce the following  incoming interface limit $L'$:
-\begin{enumerate}
-\item router B will set and announce the incoming interface limit $L'=3$;
-\item router A, after receiving announcement from B will readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
-\item both legitimate users and adversaries may either obey or ignore the announced limit, which will in any case be enforced by router A.
-\end{enumerate}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{dynamic-limits}
-  \caption{Satisfaction-based pushback example
-%: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer%
-}
-  \label{fig:dynamic limits example}
-\end{figure}
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{ 
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Satisfaction-based pushback}
-\label{alg:dynamic limits}
-\begin{algorithmic}[1]
-% \State{}\Comment{Same initialization, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-\vspace{0.1cm}
-\State{$\forall f \in \mathrm{interfaces} : L'_{f} \leftarrow L_{f}$} \Comment{Per-incoming interface Interest limit}
-
-\vspace{0.1cm}
-
-\State{} \Comment{\textit{Announcement from the neighbor}}
-\Function{InLimits}{InInterface $in$, Limit $L'$}
-    \State $L_{in} \leftarrow L'$
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
-\For{\textbf{each} outgoing interface $out$}
-
-   \For{\textbf{each} incoming interface $in$}
-        \State $L'_{in}= {L_{out}} \times (1 - U_{in}/F_{in})$
-        \State AnnounceLimit($in$, $L'_{in}$)
-   \EndFor
-
-\EndFor
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to an appropriate level (recall Fig.~\ref{fig:ratio example}).
-At the next iteration of the satisfaction-based pushback algorithm, a legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
-
-We note that while in the description of the satisfaction-based pushback algorithm we explicitly used ``outgoing'' and ``incoming'' interfaces,  all interfaces can be both incoming and outgoing.
-Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 9 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
-To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
-That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on the sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
-
-Both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, but with several core differences. 
-First, we are suppressing (pushing back) unwanted requests for data, not actual data itself.
-Second, differentiating between good and bad Interests is based on the traffic symmetry principle of NDN.
-% Alex: I'm not entirely sure about this point... 
-Finally, both intelligent attack mitigation algorithms can be deployed at all times without degrading network performance even when there are no active attackers.
-
-\section{Evaluation of Interest flooding mitigation methods}
-\label{sec:evaluation}
-
-% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
-
-% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers,
-
-% alex: what's a point of latency?  it would matter only for queueing method and we not really pushing this method
-% Latency for good clients, good versus bad interests as a function of time
-
-In this section, we present an in-depth evaluation study, aiming to quantify the effectiveness of all our Interest flooding attack mitigation methods.
-We used the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator (\url{http://www.nsnam.org/}), to run simulations for a variety of network topologies and scenarios.
-We extended ndnSIM with our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, and satisfaction-based pushback---and evaluated the effectiveness of each algorithm independently.
-
-% For evaluating the effectiveness of each mitigation algorithm, every router in the simulated topology runs the mitigation algorithm under study.
-
-% why we chose small scale topology
-% what point we wanted to show we small scale
-% what points we wanted to verify with larger-scale internet like topology
-
-% Metrics
-% not sure if i already explained that. our essential qualitative metric is .  
-% To quantify the effectiveness of the mitigation mechanism this  metric we use satisfaction percentages of user Interests.
-
-The metric we choose to quantify the effectiveness of our algorithms is the {\it percentage of satisfied Interests for legitimate users}.
-This metric corresponds to the quality of service experienced by legitimate users when the network is under attack.
-In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conclude that method $X$ is highly effective at mitigating the attack.% We also ensure that all Interests expressed by legitimate users during a period of no-attack are satisfied.
-
-%Quality of the attack mitigation methods directly corresponds to the quality of service for the legitimate users during an ongoing attack, which in NDN network can be quantified through percentage of satisfied Interest.
-%For example, if the network implements a mitigation method $X$ and under the attack majority of user-expressed Interests are getting satisfied, then the method $X$ can be seen as highly effective.
-%At the same time, if only a small percentage of the expressed Interest are getting satisfied during the attack, the method $X$ can be called ineffective.
-
-% Traffic pattern
-In our experiments, we assumed that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution.
-We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
-To quantify the behavior of our mitigation strategies under a worst-case attack scenario, we assumed that all the attackers send junk Interests as fast as they can.
-Further, no Interest---including legitimate ones---can be satisfied from caches.
-We also configured routers for single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
-%(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
-
-% Alex: not sure how to argue about the traffic pattern
-%Although this pattern may seem not truly realistic, it approximates a good statistical mix of traffic from all network users without excessive network buffering.
-
-%In addition to that, in each run of the simulation we ensure that all Interests expressed by the legitimate users during a no-attack period are satisfied.
-%For simplicity, we also equalized the average rates with which the legitimate users express Interests.
-%At the same time, the attackers are sending junk Interests as much as they can get through (remember, that Interest limits will not allow real f%looding of Intersests in all of the designed mitigation algorithms).
-
-We ran our simulations on two different network topologies---a smaller binary tree topology and a much larger ISP-like topology.
-We use a binary tree topology as it represents one of the worst cases to defend against Interest flooding DDoS attacks.
-The larger ISP topology reflects how our mitigation methods would perform when deployed on the real Internet.
-Again, to study the performance of our mitigation strategies under a range of conditions, we varied the percentage of attackers in the network---the values ranged from 6\% attackers to over 50\% attackers in the network.
-% Fixed parameters
-We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation (formula \ref{eq:interest limit}) to a fixed 
-value for every node in the simulated topology.
-In particular, for the small-scale binary tree topology, we set delay to 80~ms, while for the large-scale ISP topology we set it to 330~ms (the order of the largest RTT).
-The data size is 1100~bytes for all simulation runs and topologies.
-% THIS IS BULLSHIT!
-There is absolutely no logic to set the delay to the same value on all nodes in the network.
-We discussed multiple times that you should fix it so that the delays are realistic and gets smaller as the nodes gets closer to the producer...
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Small-scale evaluations}
-\label{sec:small-scale}
-
-% Topology description
-%To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a %simplistic small-scale binary tree topology 
-In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we used for our initial experiments.
-Legitimate users as well as attackers were placed on leaf nodes (top row of red nodes) as shown in the figure.
-There are 16 end users (both legitimate and attackers) in this topology, each expressing Interests that are routed towards a single data producer, placed at the root of the tree.
-Each link in this topology is assigned a bandwidth of 10~Mbps and a randomized propagation delay ranging from 1 to 10 ms.
-
-% Alex: should we mention that?
-%The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS %attacks.
-%That is, sharing of the network links exponentially increases as decreasing level of the binary tree.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.2]{topo-tree-evil-5-good-0-producer-gw}
-  \caption{Small-scale binary tree topology}
-  \label{fig:small-scale}
-  \vspace{-0.3cm}
-\end{figure}
-
-% in 10 independent runs of each simulation, where we randomized position of the adversaries along the legitimate users.
-In all runs, the total number of legitimate and malicious uses were fixed, meaning that when we increase number of attackers, we decrease the number of legitimate users.
-
-\subsubsection{Effectiveness of the three mitigation algorithms}
-
-%The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
-%For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).
-
-Our goal is to compare the effectiveness of each mitigation method and quantify the percentage of Interests satisfied for all legitimate users while the network is under attack.
-For each mitigation algorithm, we perform 10 independent simulation runs, where we randomly choose 7 client nodes to represent adversaries while the remaining 9 client nodes represent legitimate users.
-In each run we simulate a 10-minute attack window (total simulation time was 30 minutes, with attack starting at the 10-minute mark).
-We plot the minimum and maximum range for observed Interest satisfaction percentages for all legitimate users aggregated across the 10 simulation runs as a function of time for each mitigation algorithm in Fig.~\ref{fig:small-scale attack progress}.
-Token bucket with per-interface fair queuing performs the worst, while satisfaction-based pushback performs the best, with almost a 100\%  satisfied Interests for all legitimate users.
-
-%A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
-
-\begin{figure}[]
-  \centering
-  \hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
-  % \vspace{-.3cm}
-  \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
-  \label{fig:small-scale attack progress}
-  % \vspace{-.4cm}
-\end{figure}
-
-%\paragraph{\textbf{Simple token bucket}}
-
-%{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}
-
-%Let us take a deeper look on what is happening with the simple token bucket algorithm.
-%Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as token bucket restricts the number of forwarded Intersets!).
-%This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
-%In this example we assume that both the legitimate user and the adversary send Interests in about the same time.
-%
-%\begin{figure}[t]
-%  \centering
-%  \includegraphics[scale=0.3]{physical-limits-sync-problem}
-%  \caption{Three-router topology, with one legitimate and one malicious user}
-%  \label{fig:three router example}
-%\end{figure}
-%
-%Both router L and router X will forward the Interests, as both of them have a free token available.
-%At router A, two cases are possible, either of Interests can arrive first, resulting in a quite different effects.
-%When legitimate Interest arrives first, then there are no problem. 
-%Router A will capture the token, forward the Interest, which will be quickly satisfied, releasing the token for future uses.
-%In the mean time, malicious Interest will be dropped at router A, and router X will release the hold for the token in one second (i.e., after the maximum time Interests are admitted), enabling a new round of competition for router A's resources.
-%
-%In the case when malicious Interest is sent a little bit earlier, then router A will forward malicious Interests, dropping a legitimate one, and causing ``lock out'' for one second.
-%In the instant when the token gets released at router X, an adversary is able to push new Interest towards router A, which may arrive in the exact time A's token gets released (assuming an idealistic environment).
-%As a result, the adversary recaptures router A's token and extends the ``lock out'' for another second, denying service to the legitimate user without sending any massive numbers of Interests.
-
-\paragraph{\textbf{Token bucket with per interface fairness}}
-
-We observe a successful DDoS attack, where 40\% attackers succeed in significantly shutting down the remaining 60\% legitimate users---a mere 15\% of their Interests are satisfied by Data from the producer.
-Contrary to expectations, the 60\% legitimate users do not receive at least 60\% of network resources.
-As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers and causes congestion and packet drops near the victim.
-%Significantly reducing the number of accepted malicious Interests is fundamental for improving the effectiveness of any mitigation algorithm.
-
-%The described problem arises from the clocking effect and can be solved in a number different ways.
-%Augmenting token bucket algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
-%That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
-%However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
-%Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
-%We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.
-
-\paragraph{\textbf{Satisfaction-based Interest acceptance}}
-
-The effectiveness of this algorithm stems from the fact that routers can differentiate and limit malicious Interests into the network%, thereby ensuring availability of network resources for serving legitimate users
-.
-The observed periodic dips in the Interest satisfaction ratios of legitimate users in Fig.~\ref{fig:small-scale attack progress} is a direct result of Interest satisfaction rate statistics decaying with time.
-The 50-second period approximately corresponds to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx$20\% within 50~seconds.
- % that ranges from 30~seconds to 50~seconds. 
-%The primary reason that such minimum peaks exist is the fact that 
-When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe mixed traffic from legitimate and malicious users).
-Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' again to the edge.
-
-%When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
-%That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
-
-\paragraph{\textbf{Satisfaction-based pushback}}
-
-In our simulations, this mitigation algorithm was able to effectively shut down attackers and ensure that almost all the Interests from legitimate users are satisfied. 
-%The only potential problem with the satisfaction-based pushback algorithm is that it features 
-We observe a  sharp dip in the satisfaction ratio curve at the start of the attack as it takes a few seconds for all routers to be fully aware of the attack.
-However, recovery is quick as malicious Interests start to time out and explicit Interest limit announcements start to succeed in containing malicious Interests close to the attacker.
-Till then, the network, for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
-Once the malicious Interests are effectively shut down, all Interests from legitimate users are satisfied.
-Unlike the satisfaction-based Interest acceptance scenario, we do not observe any periodic dips in the satisfaction curve, as the pushback algorithm effectively guarantees that once an Interest is admitted, it will likely be routed all the way to the data producer.
-
-\subsubsection{Network reaction to varying number of attackers}
-
-Our next goal is to study the effectiveness of our mitigation algorithms as a function of increasing adversaries in the network.
-To this end, we vary the percentage of attackers in the topology from 6\% to over 50\%.
-Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
-All other parameters and experimental setup are consistent with the previous experiment.
-As before, for each mitigation algorithm, we perform 10 independent simulation runs.
-%The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
-%To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.
-
-%Since at this point the overall attack dynamics of all the attack mitigation algorithms is relatively clear, 
-% In other words, each point captured in the box plot graph corresponds to 1-second averaged satisfaction ratio for a user in an individual simulation run.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
-  % \vspace{-.3cm}
-  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}
-  \label{fig:small-scale-topo boxplot}
-  % \vspace{-0.5cm}
-\end{figure}
-
-In Fig.~\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
-The results are as expected---for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
-In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.
-While the two intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
-In the case of satisfaction-based pushback algorithm, during the first minute of the attack over 90\% of Interests from legitimate users are satisfied even if 50\% of end nodes are malicious.
-
-% \begin{figure}[htbp]
-%   \centering
-%   \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min-after-1-min}
-%   \caption{Average consumer Interest satisfaction ratios (second minute)}
-%   \label{fig:small-scale-topo 2}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Large scale simulations}
-\label{sec:largescale}
-
-%To check validity of the small-scale experiment results, we performed a larger-scale evaluation based on a modified version of
-
-In this section, we investigate the behavior of our mitigation strategies under a more realistic, large-scale network topology.
-The ISP-like topology we used is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
-%In order to approximate the general structure of the Internet,
-% (scale-free structure, customer-provider, and peer-to-peer relations)
-We extracted the largest connected component comprising of 562 nodes from this original topology and separated the nodes into three categories: clients, gateways, and backbones.
-Nodes having degree less than four were classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients were classified as gateways (109 green nodes), and the remaining nodes were classified as backbones (109 blue nodes).
-%(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
-We assigned bandwidth and delay values to links based on their type---both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
-We experimented with placing the data producer at both a gateway node as well as backbone node, which we randomly picked for each simulation run.
-Similar to the binary tree topology experiments, we fixed the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly picked these nodes for each simulation run.
-We conducted 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5-minute interval.
-
-\begin{figure}[t]
-  \centering
-  % \vspace{-.1cm}
-  \includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
-  % \vspace{-0.3cm}
-  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
-  \label{fig:large-scale-topo}
-\end{figure}
-
-\begin{table}[t]
-\centering
-\caption{Large-scale topology link bandwidth and delay ranges}
-% \vspace{-0.3cm}
-\label{tab:large-scale}
-\begin{tabular}{|l||c|c||c|c|}
-  \hline
-  \multirow{2}{*}{\bf Link type} &  \multicolumn{2}{|c||}{\bf Delay} &  \multicolumn{2}{|c|}{\bf Bandwidth} \tabularnewline
-  \cline{2-5}
-                        &  Min & Max                       &  Min & Max \tabularnewline
-  \hline \hline
-  Backbone--Backbone    & 5~ms & 10~ms   & 40~Mbps & 100~Mbps \tabularnewline
-  \hline
-  Gateway--Backbone,    & \multirow{2}{*}{5~ms} & \multirow{2}{*}{10~ms}   
-                        & \multirow{2}{*}{10~Mbps} & \multirow{2}{*}{20~Mbps} \tabularnewline
-  Gateway--Gateway      & & & & \\
-  \hline
-  Client--Gateway       & 10~ms & 70~ms   & 1~Mbps  & 3~Mbps \\
-  \hline
-\end{tabular}
-% \vspace{-0.3cm}
-\end{table}
-
-%Priya: Leaving out this in the interest of space...
-%Topological location of the data producer plays a key role in its resilience to Interest flooding attacks.
-For a data producer that %is connected to a client node via a low-bandwidth link, even a small number of junk Interests can impact services for legitimate %users.
-For a producer located at the backbone with rich connectivity through many high-bandwidth links, an attack might not %be as severe as a majority of legitimate users might not be on the attack path.
-
-% The results for all attack mitigation algorithms and all runs are aggregated in Fig.~\ref{fig:small-scale attack progress}, where Y-axis represents a minimum and maximum range for observed Interest satisfaction percentages among all nodes and all simulation runs.
-% A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
-
-In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over all simulations runs for each mitigation algorithm for the scenario where the data producer is placed at a gateway node.
-We observe similar results for the data producer placed at a backbone node as well.
-Unlike the binary-tree topology experiments, we observe that
-both the token bucket with per interface fairness and satisfaction-based Interest acceptance have poor performance, while the satisfaction-based pushback is still the most effective algorithm.
-Interest satisfaction percentage for legitimate users are close to 30\%, 25\%, and 100\% respectively for these mitigation methodologies.
-
-%
-%The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
-
-\begin{figure}[t]
- \centering
- \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
- % \vspace{-.3cm}
- \caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}
- % producer on a gateway node
- \label{fig:large-scale}
- % \vspace{-.7cm}
-\end{figure}
-
-Satisfaction-based Interest acceptance algorithm, which was very effective for binary-tree topology, is completely ineffective when deployed in a larger and more realistic topology.
-For the duration of the attack, legitimate users experience poor quality of service with only 25\% of their Interests being satisfied and continue to experience degraded service long after the attack has stopped.
-This poor performance, as detailed in Section~\ref{sec:probabilistic}, is due to the fact that each router on the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
-In the case of a large topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics and further penalization of new Interests from them.
-
-All our evaluations leave us to conclude that among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most promising one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
-%The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
-As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.
-
-% Alex: Anything else here?
-
-% Alex: I also experimented with placing producer at the backbone, getting slightly better results for all algorithms.  Though I'm not sure there is any value to put those results in the paper
-
-% \input{simulation-emulation.tex}
-
-\subsection{Limitations}
-%{\color{red} I gave up the idea of seperate discussion section after trying for some time, as given the space limitation, there is no way to write a reasonably comprehensive and  broad discussion section that justifies a separate section.
-Instead, I decided to have a scoped down version here that confesses upon the limiations of our evaluations only.
-Whoever has time (I need to sleep few hours), please go ahead and write 1-2 paragraphs as I outlined below.
--Ersin}
-
-%This section should roughly say: Our results show that the two features, namely the symmetric traffic and stateful routing, give NDN routers the ability to observe and characterize traffic in real time.
-Through our evaluations, we demonstrated that a mitigation algorithm that leverages such ability has great potential in mitigating various DDoS attacks that could otherwise have grave effect on the network.
-However, as the first step in exploring the problem and the solution space, this paper has obvious limitations: (1) We assume a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations.
-Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step is evaluating the above described solutions with more sophisticated and adaptive attackers.
-(2)   Although most (such as single-path routing, no-caches in the network, single homed victim, etc) are aimed to test the proposed solutions under worst-case scenario, we made many assumptions in simulations/evaluations about the configurations, topology and the traffic that maybe poor-representative of realistic conditions.
-(3) As NDN being an ongoing research effort itself, our evaluations fully depend on simulations and done over a snapshot of its codebase.
-
-% The main contribution of the paper and this section in particular is a proof that two inherent properties of NDN architecture, namely the symmetric traffic and stateful forwarding, give NDN routers the ability to characterize traffic and react in real time.
-% We demonstrated that satisfaction-based pushback algorithm, leveraging this ability, has great potential in mitigating various DDoS attacks that could otherwise have a grave effect on the network. 
-% However, as the first step in exploring the problem and the solution space, our paper has obvious limitations.
-% First, we assumed a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations. 
-% Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step that we are leaving out for future work is evaluating the above described solutions with more sophisticated and adaptive attackers.
-% Second, while aiming to test the designed algorithms under worst-case conditions, the future work needs to address behavior in more realistic scenarios, including investigation of multi-path routing, in network caches, as well as multi-homed victims.
-
-This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space. 
-To design our mitigation algorithms we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
-We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology, % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
-as well as a more realistic ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network. 
-While our results are promising and show a great potential in mitigating Interest flooding DDoS attacks, there are certain limitations which should be addressed in future research.
-
-First, in our evaluations we used a simple and static attacker model---attackers send junk Interests as fast as possible. 
-In future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and Interest sending patterns based on the network reaction. 
-Second, we assumed that Interests are not satisfied by an intermediate router's cache and always forwarded all the way to the producer.  
-In future, we plan to study the impact of Interest flooding attacks in more realistic scenarios with multi-path routing enabled, more realistic traffic patterns, and the presence of in-network caches.
-% We also ignored NDN's strategy layer that routes around failure and congestion in the network. 
-% In future work, we plan to study the impact of turning on these features. 
-%Finally, we also plan to perform more extensive simulations on other realistic Internet-like topologies and traffic patterns.
-
-\section{Related work}
-\label{sec:related-work}
-
-As a new Internet architecture proposal, Named Data Networking has attracted a limited attention from the security community. 
-Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
-W\"ahlisch et al.~\cite{Wahlisch:2012:Backscatter-from} explore security and stability threats in the general area of information-centric networks (ICN), using CCNx software as an example.  
-While this work aims to generalize findings for all ICNs, it largely does not go beyond the current design choices of CCNx.
-% (which is an example, but not the final word in NDN) 
-% Gasti et al.~\cite{gasti2012ddos} identified several NDN architecture-specific attacks (Interest flooding and content/cache poisoning) and proposed potential solutions, without devising particular algorithms.
-In this paper we follow the suggestions by Gasti et al.~\cite{gasti2012ddos} and utilize the properties provided by the NDN architecture to mitigate DDoS attacks, and tackle the Interest flooding problem as a first step in this direction.
-More specifically our attack mitigation design relies on NDN's stateful forwarding plane that allows us to
-maintain statistics on unsatisfied Interests.  
-Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr,Yi:2013:A-Case-for-Stateful} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
-
-The general area of mitigating denial of service attacks is amongst the hottest topics in recent years.
-% Among all the body of work, 
-The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushing back malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
-overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
-various ticketing systems with conditional admission of traffic in to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
-and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
-Identifying malicious traffic requires establishing certain state at routers, and the above mentioned solutions differ in the specifics on what state to use and how to establish it.
-By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions---we simply take full advantage of this state to develop desired solutions.
-
-% Our design for the Interest flooding attack mitigation borrows
-
-% This paper talks about attacks on content centric infrastructure (not specifically to NDN).
-% \cite{Wahlisch:2012:Backscatter-from}
-
-% % Collaborative detection of DDoS attacks over multiple network domains
-% \cite{Chen:2007:Collaborative-detection} distributed change-point detection
-
-% % DDoS flooding attack detection through a step-by-step investigation
-% \cite{Jun:2011:DDoS-flooding}
-
-% % A practical method to counteract denial of service attacks
-% \cite{Tupakula:2003:A-practical-method}
-
-% Alex: We should not include this reference for the review, but afterwards
-% Previous work on DDoS and DoS~\cite{gasti2012ddos}
-
-% Network level (Flooding)
-% % 2002
-% Pushback~\cite{Pushback} (hop-by-hop push back) aggregate- based congestion control/congestion signatures (e.g., per-destination), rate-limiting, explicit notification
-% AITF~\cite{Argyraki:2005:Active-internet} (active filtering requests; path recording, last-point of trust detecting)?
-% DefCOM \cite{Oikonomou:2006:A-framework-for-a-collaborative} Communication between src, core, and dst to provide collaborative defense.
-Dst raises alerts, src differentiate bad/good, packet tagging.
-Core rate-limit, congestion-aware re-tag.
-Traffic prioritization.
-% StopIt \cite{Liu:2008:To-filter-or-to-authorize:} (filtering) tagging with passports, tagged prioritization, dst- invoked filter instantiation
-% NetFence \cite{Liu:2010:NetFence:-preventing} congestion policing: fair queuing (one leaky bucket per {src,L}, L- bottleneck), secure "ticketing" with signals for AIMD to increase/decrease bandwidth allowance
-% PSP \cite{Chou:2009:Proactive-surge} topology as origin-destination pairs, packet tagging, OD traffic isolation, sharing based on historic bandwidth demand
-
-% SIFF~\cite{Yaar:2004:SIFF:-A-stateless} (time-based tickets, capabilities)
-% TVA \cite{Yang:2005:A-DoS-limiting-network} like SIFF, traffic- based tickets, hierarchical per- AS, per-source fair queuing
-% FastPass \cite{Wendlandt:2006:Fastpass:-Providing} (tokens: various puzzles, other methods) traffic authorization, routers verify and filter.
-% \cite{Natu:2007:Fine-grained-capabilities} based on TVA/SIFF: specifies previously unspecified mechanisms to grant "tickets" for requesters, extends capabilities to include priorities, changing tickets to be only destination- dependent, not path dependent
-% % LazySusan \cite{Crowcroft:2007:Lazy-Susan:} TR (latency-based proof of work--- computational puzzles)
-% Portcullis \cite{Portcullis} Protecting connection setup with computational proof of work, tickets and traffic prioritization for the rest, per- computational fairness; DNS to disseminate puzzles
-% There are many other puzzle- based schemes, on which Portcullis is based or which problems it solves
-
-% PacketSymmetry \cite{Kreibich:2005:Using-packet} (leverages packet symmetry to detect and remove bad traffic) packet asymmetry - number of transmitted packets (tx) to received packets (rx); negative values when rx outweighs tx, positive values when tx outweighs rx, and zero in the case of perfectly balanced traffic)
-% % Detecting SYN flooding attacks
-% \cite{Wang:2002:Detecting-SYN-flooding} based on the protocol behavior of TCP SYN-FIN (RST) pairs, and is an instance of the Seqnential Change Point Detection
-% dFence \cite{Mahimkar:2007:dFence:-Transparent} (middleboxes) TCP connection proxying, rate estimation and TCP/ACK modification
-
-% Overlays:
-% CenterTrack \cite{Stone:2000:CenterTrack:-An-IP-overlay} (overlay) reroute suspicious traffic to a special routers with diagnostic capabilities using an overlay
-% SOS \cite{Keromytis:2004:SOS:-An-architecture}
-% Shield \cite{Kline:2011:Shield:-DoS-filtering}
-
-% NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
-In this section we will overview generic directions of DDoS mitigation designs and try to think about which tricks could be used in NDN.
-
-% Capability-based systems allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
-Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
-This implies that each client must pass through an authentication process prior to using any bandwidth~\cite{Capabilities}.
-We believe that for NDN this method doesn't fit really well for the following reasons.
-First, this method is very questionable in terms of scalability and mobility support since it requires tight trust connections between routers and hosts.
-Thus, it neglects one of the main advantages (mobility) of NDN.
-Second, the design of trust infrastructure for NDN is not well defined yet, which means that we cannot really make assumptions in our design of mitigation techniques.
-
-% Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
-Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients.
-One of the main difficulties in such systems is the question of puzzle dessimination.
-In ~\cite{Portcullis} authors suggested to propagate puzzles using DNS system.
-In NDN since routers have caching abilities, we can propagate puzzles just like a normal data packets, using Interest-Data exchange.
-Overall, this method looks interesting and deserves being investigated in a future work.
-
-% Congestion control systems do per flow traffic analysis and drop of packets belonging to misbehaving flows.
-For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
-Such techniques, if largely deployed, could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
-Since NDN routers maintain a richer per-packet state, which translates into a better per-flow statistics, these techniques can become much more effective when applied to NDN.
-
-% Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
-This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines~\cite{Pushback}.
-In general this technique can be applied to NDN architecture thanks to its decentralized coordination of downrating bad traffic flows.
-Moreover, NDN provides better capabilities for accurate flow detection.
-
-%were looking for getting accustomed
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-% Main take out from the paper:  could be a problem, but problem is solvable.  
-% One of the key components in the Named Data Networking architecture is its stateful data delivery model, which potentially can be abused by new types of denial of service attacks.
-% However, one should not forget that the same stateful data delivery provides effective mechanisms to fight back against such attacks.
-
-%In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
-%The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data path symmetry and full receiver-based traffic control.
-%In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Interests can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
-%
-%Other forms of attack may require different mitigation mechanisms.  
-%However, the granularity of the NDN state---per each Interest packet---is what giving NDN an opportunity to stand against existing and new forms of attacks.
-%
-%NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution.
-
-NDN being a newly proposed future Internet architecture, it is important to address its resilience in face of DDoS attacks.
-As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks---namely, Interest flooding---and the severe service degradation such an attack may cause to legitimate users.
-We then leveraged the key features of the NDN architecture to design, develop, and evaluate three mitigation strategies.
-We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
-The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers, so that they cause little or no service impact to legitimate users.
-
-NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balance (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding,Yi:2013:A-Case-for-Stateful}.
-Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.
-
-\bibliographystyle{IEEEtran}
-\bibliography{references}
-
-\end{document}

### 2013-05-13 03-interest-flooding.tex
Splitting paper back to its normal organization

@@
 
-% Points here:
-% - Classification
-% - Mechanisms: congestion and memory exhaustion
-% - Target
-% - Effectiveness: random names, non-existing content
-% - Assumptions: the network, attackers, attack traffic, and legitimate consumers
+As we explained earlier, Interest packets in NDN are routed through the network based on content name prefixes and consume memory resources at intermediate routers.
+This makes them a potential tool to launch DDoS attacks in NDN.
+An attacker or a set of distributed attackers can inject excessive number of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
 
-%???
-- References to the discussion about other types of attacks (ordifferent attack assumptions) about other attacks and explicitly stating that this work aims to build a baseline for general Interest Flooding mitigation problem, with other attack profiles and malicious gateways.
-
-%\paragraph{What is it?}
-
-As we explained earlier, Interest packets in NDN are routed through the network based on their content name prefixes and consume memory resources at intermediate routers.
-This makes them a potential tool to launch DDoS attacks in an NDN network.
-An attacker or a set of distributed attackers can inject excessive amounts of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-%%% Alex %%% We have (almost) exactly the same sentence in the intro.
-I think here is kind of redundant, as it is obvious how we call the attack from the section title.
-Also, we are referring to the term again in the last paragraph of the section.
-% We coin the term \emph{Interest flooding} to refer to these network-level flooding attacks.
-
-\begin{figure}[htbp]
+\begin{figure}[t]
   \centering
-  \includegraphics[scale=0.39]{attack-definition}
-  \vspace{-0.4cm}
-  \caption{Example of the Interest flooding attack}
+  \includegraphics[scale=0.3]{attack-definition}
+  \caption{Example of Interest flooding attack}
   \label{fig:flooding example}
+  \vspace{-0.3cm}
 \end{figure}
 
-%\paragraph{How does it work?}
-
-Since an NDN network fetches data by its name, an adversary cannot target specific routers or end-hosts.
-%% as neither is required to have a globally routable network identity/address.
+Since an NDN network fetches data by its name, an adversary cannot easily target specific routers or end-hosts.
 However, an adversary can target a specific namespace.
@@
 It also assumes the producer is single-homed and the data is not replicated elsewhere.
-With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding}.}
+With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding, Yi:2013:A-Case-for-Stateful} support.}
 A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
@@
 A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
-In particular a coordinated DDoS attack could target one specific namespace to concentrate attack traffic in certain segments of the network, typically closest to the publisher serving that namespace.
-%% since name prefixes in NDN loosely correspond to a network location or sets of network locations.
+In particular, a coordinated DDoS attack could target one specific namespace and concentrate attack traffic in certain segments of the network, as routing in NDN is based on name prefixes.
 
-As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a router's memory, making the router unable to create new PIT entries for incoming Interests, thus disrupting service for legitimate users.
-% there is no point in forwarding the Interest further.
-% Otherwise, if Data comes back, it would be considered unsolicited and dropped anyways.
-%Therefore, service for legitimate users can be disrupted due to limited memory resources in routers without saturating communication links to their limits.
+As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a router's memory, making the router unable to create new PIT entries for incoming Interests and disrupting service for legitimate users.
 
-%\paragraph{Target}
+Nevertheless, creating an effective Interest flooding attack in NDN is non-trivial.
+To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1)~the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2)~new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
+The former is achieved when Interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers---an Interest is not forwarded upstream if a router can satisfy it from its content store.
+The latter requires every single malicious Interest to ask for unique content---all Interests requesting the same content are combined into one PIT entry in routers.
+Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content with each Interest.
+Of the two options available to an adversary, the first one is challenging due to the difficulties around indexing content names in a particular namespace, coordinating a large number of bots to send unique Interests, and sustaining the attack while the network is continuously caching the requested content objects.
+However, the second option---requesting a unique non-existing content with each Interest---is easy to achieve and sustain.
+For example, an adversary can construct such Interests by concatenating a variable-length random name component to the victim namespace (e.g., \ndnName{/newyorktimes/3rf3...}).
+In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest, but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
+% other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
 
-% \paragraph{Countermeasures}?
-
-%\paragraph{Effectiveness}
-
-An effective Interest flooding attack is non-trivial to create.
-To target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed as close to the data producer as possible, and (2) the corresponding PIT entries are stored at intermediate NDN routers for as long as possible.
-%In order to achieve both requirements effectively, malicious Interests should avoid Interest collapsing and 
-To avoid an Interest being served from caches of intermediate routers, every single malicious Interest has to request an unpopular or non-existing content, e.g., content with a unique name (\emph{unique junk Interests}).
-In this paper, we exclusively focus on this particular attack strategy as it maximizes the damage from each malicious Interest in the network.
-However, other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
-
-In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker that is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
+In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
 
@@
 %In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
-
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: "paper"
-%%% End:

### 2013-05-13 04-flooding-mitigation.tex
Splitting paper back to its normal organization

--- 2013-03-26 paper.tex
@@
-\documentclass[10pt,conference]{IEEEtran}
-% http://networking2013.poly.edu/call-for-papers/paper-submission/
-% Page limit 9 pages
-
-\makeatletter
-\def\ps@headings{%
-\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
-\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
-\def\@oddfoot{}%
-\def\@evenfoot{}}
-\makeatother
-
-\hyphenation{incoming}
-\hyphenation{na-me-spa-ce}
-\hyphenation{sa-tis-fac-tion}
-\hyphenation{sa-tis-fied}
-
-\pagestyle{headings}
-
-% \usepackage[top=.75in, bottom=1in, left=.625in, right=.625in]{geometry}
-\usepackage{graphicx}
-% \usepackage[]{hyperref}
-\usepackage{breakurl}
-\usepackage{url}
-\usepackage[nocompress]{cite}
-% \usepackage{verbatim}
-% \usepackage{algpseudocode}
-\usepackage[noend]{algpseudocode,algorithm}
-% More customizeable version. Probably it would be better to convert pseudocode to 2e format
-% \usepackage{algorithm2e} 
-\usepackage{multirow}
-\usepackage{times}
-\usepackage{color}
-
-\newfont{\nicettfont}{cmtt9}
-\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
-\renewcommand{\texttt}[1]{{\nicettfont #1}}
-
-\graphicspath{{figures/}}
-
-\begin{document}
-
-\title{Interest Flooding Attack and Countermeasures in Named Data Networking}
-
-\author{
-    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
-    \\\{afanasev, iliamo, lixia\}@cs.ucla.edu}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
-    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
-}
-
-\maketitle
-
-\begin{abstract}
-Distributed Denial of Service (DDoS) attacks are an ongoing problem in today's Internet, where packets from a large number of compromised hosts thwart the paths to the victim site and/or overload the victim machines.
-In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network delivers Data packets upon request only, effectively eliminating many existing DDoS attacks.
-However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  
-In this paper we investigate effective solutions to mitigate Interest flooding.
-We show that NDN's inherent properties of storing per packet state on each router and maintaining flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
-Our evaluation through simulations shows that the solution can quickly and effectively respond and mitigate Interest flooding.
-\end{abstract}
-
-\begin{IEEEkeywords}
-Information-centric networks, named-data networking, denial-of-service
-\end{IEEEkeywords}
-
-\section{Introduction}
-\label{sec:intro}
-
-Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an ongoing research effort that aims to move the Internet into the future with a content-centric design that is capable of efficient content distribution and seamless mobility support.
-In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in the packets.
-However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against DDoS attacks?
-Especially since various forms of DDoS attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial to ensure that the new design is free of similar vulnerabilities.
-
-NDN eliminates host-based addressing and makes data the first-class network entity.
-Instead of sending packets to a given IP address, NDN nodes request desired data by sending Interest packets carrying application-level data names, and the network returns the requested Data packets following the path of Interests.
-Such a shift automatically eliminates several long-standing DDoS attacks, including direct flooding and reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
-%
-However, malicious users can attack the network by sending an excessive number of Interests. 
-Since each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can congest the network and exhaust a router's memory. 
-We coin the term {\it Interest flooding} to refer to such attack and
-this paper exclusively investigates the problem and the solution space for it.
-
-Our effort is an important first step towards a complete investigation of DDoS attacks in NDN.
-We experiment with three algorithms that allow routers to exploit their state information to thwart these attacks.
-Through extensive simulations, we show how one of our mitigation methodologies effectively shuts down malicious users while preventing legitimate users from service degradation.
-The rest of the paper is organized as follows.
-We provide an overview of NDN architecture in Section~\ref{sec:ccn-intro} and describe Interest flooding attacks in Section~\ref{sec:interest-flooding}.
-In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
-We summarize related work in Section~\ref{sec:related-work}.
-We discuss future work and conclude in Section~\ref{sec:conclusion}.
-
-\section{NDN Overview\label{sec:ccn-intro}}
-
-In this section we briefly introduce NDN with a focus on its stateful forwarding plane (refer to \cite{ndn-conext, ndn-tr, adaptive-forwarding, Yi:2013:A-Case-for-Stateful} for more details).
-NDN is a receiver-driven, data-centric communication protocol.
-All communications in NDN are performed using two distinct types of packets: \textit{Interest} and \textit{Data}.
-Both types of packets carry a \textit{name}, which uniquely identifies a piece of content that can be carried in one Data packet.
-Data names in NDN are hierarchically structured and an example name for the first segment of a youtube video would look like: \ndnName{/youtube/videos/0F8YdlkKO9A/0}.
-
-To retrieve data, a consumer requests it by sending an Interest packet with the name of the desired content in it.
-Routers use this name to route the Interest towards data sources, and a Data packet whose name matches the name in the Interest is returned to the consumer by following the reverse path of the Interest.
-Similar to IP, Interest forwarding is based on longest name prefix match, but, unlike IP, an Interest packet and its matching Data packet always take symmetric paths.
-%% An Interest is ``satisfied'' when it is matched with a Data packet.
-
-Each NDN router maintains three major data structures:
-\begin{itemize}
-\item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards potential data sources.
-Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicate the same Interest is forwarded along multiple paths.
-\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, specifying directions where Interests can be forwarded. 
-% Having one-to-many relationship in this table allows multipath forwarding of Interests.}
-\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this router, allowing efficient data retrieval by different consumers.
-\end{itemize}
-
-When a router receives an Interest packet, it first checks whether there is a matching data in its CS.
-If a match is found, the Data packet is sent back to the incoming interface of the Interest packet.
-If not, the Interest name is checked against the entries in the PIT. 
-If the name already exists in the PIT, then it can be a duplicate Interest (identified by a random number each Interest carries) that should be dropped,
-or an Interest from another consumer asking for the same Data, which requires the incoming interface of this Interest to be added to the existing PIT entry.
-If the name does not exist in the PIT, the Interest is added into the PIT and forwarded along the interface chosen by the strategy module, which uses FIB as input for its decisions.
-
-When a Data packet is received, its name is used to look up the PIT.
-If a matching PIT entry is found,
-the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the CS, and removes the PIT entry.
-Otherwise, the Data packet is deemed unsolicited and is discarded.
-Each Interest also has an associated lifetime; the PIT entry is removed when the lifetime expires.
-Although the maximum lifetime is specified by users, it is ultimately a router's decision on how long it is willing to keep a PIT entry.  
-For simplicity, we assume routers keep Interests in PIT for one second in our simulations.
-
-\section{Interest Flooding Attacks in NDN}
-\label{sec:interest-flooding}
-
-As we explained earlier, Interest packets in NDN are routed through the network based on content name prefixes and consume memory resources at intermediate routers.
-This makes them a potential tool to launch DDoS attacks in NDN.
-An attacker or a set of distributed attackers can inject excessive number of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{attack-definition}
-  \caption{Example of Interest flooding attack}
-  \label{fig:flooding example}
-  \vspace{-0.3cm}
-\end{figure}
-
-Since an NDN network fetches data by its name, an adversary cannot easily target specific routers or end-hosts.
-However, an adversary can target a specific namespace.
-For example in Fig.~\ref{fig:flooding example}, if the data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
-\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{\small /foo/bar} prefix to make them effective.
-It also assumes the producer is single-homed and the data is not replicated elsewhere.
-With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding, Yi:2013:A-Case-for-Stateful} support.}
-A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
-
-Similar to packets in traditional networks, Interest packets in NDN consume a portion of network capacity.
-A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
-In particular, a coordinated DDoS attack could target one specific namespace and concentrate attack traffic in certain segments of the network, as routing in NDN is based on name prefixes.
-
-As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a router's memory, making the router unable to create new PIT entries for incoming Interests and disrupting service for legitimate users.
-
-Nevertheless, creating an effective Interest flooding attack in NDN is non-trivial.
-To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1)~the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2)~new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
-The former is achieved when Interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers---an Interest is not forwarded upstream if a router can satisfy it from its content store.
-The latter requires every single malicious Interest to ask for unique content---all Interests requesting the same content are combined into one PIT entry in routers.
-Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content with each Interest.
-Of the two options available to an adversary, the first one is challenging due to the difficulties around indexing content names in a particular namespace, coordinating a large number of bots to send unique Interests, and sustaining the attack while the network is continuously caching the requested content objects.
-However, the second option---requesting a unique non-existing content with each Interest---is easy to achieve and sustain.
-For example, an adversary can construct such Interests by concatenating a variable-length random name component to the victim namespace (e.g., \ndnName{/newyorktimes/3rf3...}).
-In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest, but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
-% other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
-
-In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
-
-%\paragraph{Assumptions} 
-%E: These are assumptions for the simulations on hand and particulary to test for the worst case scenario in many aspects.
-They are not the paper's assumption and in fact the paper first should be more general on describing all possibilities.
-Then it should explain the assumptions for the simulations and discuss why they make sense and do NOT favor positive results in some way.
-
-% - assumptions about attacker position
-% - assumptions about the producer / producer namespace
-% - assumptions about the attack traffic / attack pattern
-
-%In this paper we are making the following assumptions about the Interest flooding attack:
-%\begin{itemize}
-%\item only client nodes can be compromised and become attack bots;
-%\item there are no colluding attackers inside the Data producer's network;
-%\item the attack is carried only using unique junk Interests; and
-%\item there is only one Data producer for the attacked prefix.
-%\end{itemize}
-
-%We also assume that NDN forwarding strategy uses only single-path Interest forwarding, always choosing the best-metric route advertised by the routing protocol.
-%This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
-
-%In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
-
 \section{Interest flooding mitigation methods}
@@
 Finally, both intelligent attack mitigation algorithms can be deployed at all times without degrading network performance even when there are no active attackers.
-
-\section{Evaluation of Interest flooding mitigation methods}
-\label{sec:evaluation}
-
-% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
-
-% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers,
-
-% alex: what's a point of latency?  it would matter only for queueing method and we not really pushing this method
-% Latency for good clients, good versus bad interests as a function of time
-
-In this section, we present an in-depth evaluation study, aiming to quantify the effectiveness of all our Interest flooding attack mitigation methods.
-We used the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator (\url{http://www.nsnam.org/}), to run simulations for a variety of network topologies and scenarios.
-We extended ndnSIM with our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, and satisfaction-based pushback---and evaluated the effectiveness of each algorithm independently.
-
-% For evaluating the effectiveness of each mitigation algorithm, every router in the simulated topology runs the mitigation algorithm under study.
-
-% why we chose small scale topology
-% what point we wanted to show we small scale
-% what points we wanted to verify with larger-scale internet like topology
-
-% Metrics
-% not sure if i already explained that. our essential qualitative metric is .  
-% To quantify the effectiveness of the mitigation mechanism this  metric we use satisfaction percentages of user Interests.
-
-The metric we choose to quantify the effectiveness of our algorithms is the {\it percentage of satisfied Interests for legitimate users}.
-This metric corresponds to the quality of service experienced by legitimate users when the network is under attack.
-In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conclude that method $X$ is highly effective at mitigating the attack.% We also ensure that all Interests expressed by legitimate users during a period of no-attack are satisfied.
-
-%Quality of the attack mitigation methods directly corresponds to the quality of service for the legitimate users during an ongoing attack, which in NDN network can be quantified through percentage of satisfied Interest.
-%For example, if the network implements a mitigation method $X$ and under the attack majority of user-expressed Interests are getting satisfied, then the method $X$ can be seen as highly effective.
-%At the same time, if only a small percentage of the expressed Interest are getting satisfied during the attack, the method $X$ can be called ineffective.
-
-% Traffic pattern
-In our experiments, we assumed that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution.
-We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
-To quantify the behavior of our mitigation strategies under a worst-case attack scenario, we assumed that all the attackers send junk Interests as fast as they can.
-Further, no Interest---including legitimate ones---can be satisfied from caches.
-We also configured routers for single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
-%(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
-
-% Alex: not sure how to argue about the traffic pattern
-%Although this pattern may seem not truly realistic, it approximates a good statistical mix of traffic from all network users without excessive network buffering.
-
-%In addition to that, in each run of the simulation we ensure that all Interests expressed by the legitimate users during a no-attack period are satisfied.
-%For simplicity, we also equalized the average rates with which the legitimate users express Interests.
-%At the same time, the attackers are sending junk Interests as much as they can get through (remember, that Interest limits will not allow real f%looding of Intersests in all of the designed mitigation algorithms).
-
-We ran our simulations on two different network topologies---a smaller binary tree topology and a much larger ISP-like topology.
-We use a binary tree topology as it represents one of the worst cases to defend against Interest flooding DDoS attacks.
-The larger ISP topology reflects how our mitigation methods would perform when deployed on the real Internet.
-Again, to study the performance of our mitigation strategies under a range of conditions, we varied the percentage of attackers in the network---the values ranged from 6\% attackers to over 50\% attackers in the network.
-% Fixed parameters
-We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation (formula \ref{eq:interest limit}) to a fixed 
-value for every node in the simulated topology.
-In particular, for the small-scale binary tree topology, we set delay to 80~ms, while for the large-scale ISP topology we set it to 330~ms (the order of the largest RTT).
-The data size is 1100~bytes for all simulation runs and topologies.
-% THIS IS BULLSHIT!
-There is absolutely no logic to set the delay to the same value on all nodes in the network.
-We discussed multiple times that you should fix it so that the delays are realistic and gets smaller as the nodes gets closer to the producer...
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Small-scale evaluations}
-\label{sec:small-scale}
-
-% Topology description
-%To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a %simplistic small-scale binary tree topology 
-In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we used for our initial experiments.
-Legitimate users as well as attackers were placed on leaf nodes (top row of red nodes) as shown in the figure.
-There are 16 end users (both legitimate and attackers) in this topology, each expressing Interests that are routed towards a single data producer, placed at the root of the tree.
-Each link in this topology is assigned a bandwidth of 10~Mbps and a randomized propagation delay ranging from 1 to 10 ms.
-
-% Alex: should we mention that?
-%The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS %attacks.
-%That is, sharing of the network links exponentially increases as decreasing level of the binary tree.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.2]{topo-tree-evil-5-good-0-producer-gw}
-  \caption{Small-scale binary tree topology}
-  \label{fig:small-scale}
-  \vspace{-0.3cm}
-\end{figure}
-
-% in 10 independent runs of each simulation, where we randomized position of the adversaries along the legitimate users.
-In all runs, the total number of legitimate and malicious uses were fixed, meaning that when we increase number of attackers, we decrease the number of legitimate users.
-
-\subsubsection{Effectiveness of the three mitigation algorithms}
-
-%The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
-%For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).
-
-Our goal is to compare the effectiveness of each mitigation method and quantify the percentage of Interests satisfied for all legitimate users while the network is under attack.
-For each mitigation algorithm, we perform 10 independent simulation runs, where we randomly choose 7 client nodes to represent adversaries while the remaining 9 client nodes represent legitimate users.
-In each run we simulate a 10-minute attack window (total simulation time was 30 minutes, with attack starting at the 10-minute mark).
-We plot the minimum and maximum range for observed Interest satisfaction percentages for all legitimate users aggregated across the 10 simulation runs as a function of time for each mitigation algorithm in Fig.~\ref{fig:small-scale attack progress}.
-Token bucket with per-interface fair queuing performs the worst, while satisfaction-based pushback performs the best, with almost a 100\%  satisfied Interests for all legitimate users.
-
-%A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
-
-\begin{figure}[]
-  \centering
-  \hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
-  % \vspace{-.3cm}
-  \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
-  \label{fig:small-scale attack progress}
-  % \vspace{-.4cm}
-\end{figure}
-
-%\paragraph{\textbf{Simple token bucket}}
-
-%{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}
-
-%Let us take a deeper look on what is happening with the simple token bucket algorithm.
-%Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as token bucket restricts the number of forwarded Intersets!).
-%This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
-%In this example we assume that both the legitimate user and the adversary send Interests in about the same time.
-%
-%\begin{figure}[t]
-%  \centering
-%  \includegraphics[scale=0.3]{physical-limits-sync-problem}
-%  \caption{Three-router topology, with one legitimate and one malicious user}
-%  \label{fig:three router example}
-%\end{figure}
-%
-%Both router L and router X will forward the Interests, as both of them have a free token available.
-%At router A, two cases are possible, either of Interests can arrive first, resulting in a quite different effects.
-%When legitimate Interest arrives first, then there are no problem. 
-%Router A will capture the token, forward the Interest, which will be quickly satisfied, releasing the token for future uses.
-%In the mean time, malicious Interest will be dropped at router A, and router X will release the hold for the token in one second (i.e., after the maximum time Interests are admitted), enabling a new round of competition for router A's resources.
-%
-%In the case when malicious Interest is sent a little bit earlier, then router A will forward malicious Interests, dropping a legitimate one, and causing ``lock out'' for one second.
-%In the instant when the token gets released at router X, an adversary is able to push new Interest towards router A, which may arrive in the exact time A's token gets released (assuming an idealistic environment).
-%As a result, the adversary recaptures router A's token and extends the ``lock out'' for another second, denying service to the legitimate user without sending any massive numbers of Interests.
-
-\paragraph{\textbf{Token bucket with per interface fairness}}
-
-We observe a successful DDoS attack, where 40\% attackers succeed in significantly shutting down the remaining 60\% legitimate users---a mere 15\% of their Interests are satisfied by Data from the producer.
-Contrary to expectations, the 60\% legitimate users do not receive at least 60\% of network resources.
-As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers and causes congestion and packet drops near the victim.
-%Significantly reducing the number of accepted malicious Interests is fundamental for improving the effectiveness of any mitigation algorithm.
-
-%The described problem arises from the clocking effect and can be solved in a number different ways.
-%Augmenting token bucket algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
-%That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
-%However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
-%Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
-%We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.
-
-\paragraph{\textbf{Satisfaction-based Interest acceptance}}
-
-The effectiveness of this algorithm stems from the fact that routers can differentiate and limit malicious Interests into the network%, thereby ensuring availability of network resources for serving legitimate users
-.
-The observed periodic dips in the Interest satisfaction ratios of legitimate users in Fig.~\ref{fig:small-scale attack progress} is a direct result of Interest satisfaction rate statistics decaying with time.
-The 50-second period approximately corresponds to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx$20\% within 50~seconds.
- % that ranges from 30~seconds to 50~seconds. 
-%The primary reason that such minimum peaks exist is the fact that 
-When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe mixed traffic from legitimate and malicious users).
-Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' again to the edge.
-
-%When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
-%That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
-
-\paragraph{\textbf{Satisfaction-based pushback}}
-
-In our simulations, this mitigation algorithm was able to effectively shut down attackers and ensure that almost all the Interests from legitimate users are satisfied. 
-%The only potential problem with the satisfaction-based pushback algorithm is that it features 
-We observe a  sharp dip in the satisfaction ratio curve at the start of the attack as it takes a few seconds for all routers to be fully aware of the attack.
-However, recovery is quick as malicious Interests start to time out and explicit Interest limit announcements start to succeed in containing malicious Interests close to the attacker.
-Till then, the network, for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
-Once the malicious Interests are effectively shut down, all Interests from legitimate users are satisfied.
-Unlike the satisfaction-based Interest acceptance scenario, we do not observe any periodic dips in the satisfaction curve, as the pushback algorithm effectively guarantees that once an Interest is admitted, it will likely be routed all the way to the data producer.
-
-\subsubsection{Network reaction to varying number of attackers}
-
-Our next goal is to study the effectiveness of our mitigation algorithms as a function of increasing adversaries in the network.
-To this end, we vary the percentage of attackers in the topology from 6\% to over 50\%.
-Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
-All other parameters and experimental setup are consistent with the previous experiment.
-As before, for each mitigation algorithm, we perform 10 independent simulation runs.
-%The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
-%To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.
-
-%Since at this point the overall attack dynamics of all the attack mitigation algorithms is relatively clear, 
-% In other words, each point captured in the box plot graph corresponds to 1-second averaged satisfaction ratio for a user in an individual simulation run.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
-  % \vspace{-.3cm}
-  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}
-  \label{fig:small-scale-topo boxplot}
-  % \vspace{-0.5cm}
-\end{figure}
-
-In Fig.~\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
-The results are as expected---for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
-In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.
-While the two intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
-In the case of satisfaction-based pushback algorithm, during the first minute of the attack over 90\% of Interests from legitimate users are satisfied even if 50\% of end nodes are malicious.
-
-% \begin{figure}[htbp]
-%   \centering
-%   \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min-after-1-min}
-%   \caption{Average consumer Interest satisfaction ratios (second minute)}
-%   \label{fig:small-scale-topo 2}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Large scale simulations}
-\label{sec:largescale}
-
-%To check validity of the small-scale experiment results, we performed a larger-scale evaluation based on a modified version of
-
-In this section, we investigate the behavior of our mitigation strategies under a more realistic, large-scale network topology.
-The ISP-like topology we used is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
-%In order to approximate the general structure of the Internet,
-% (scale-free structure, customer-provider, and peer-to-peer relations)
-We extracted the largest connected component comprising of 562 nodes from this original topology and separated the nodes into three categories: clients, gateways, and backbones.
-Nodes having degree less than four were classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients were classified as gateways (109 green nodes), and the remaining nodes were classified as backbones (109 blue nodes).
-%(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
-We assigned bandwidth and delay values to links based on their type---both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
-We experimented with placing the data producer at both a gateway node as well as backbone node, which we randomly picked for each simulation run.
-Similar to the binary tree topology experiments, we fixed the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly picked these nodes for each simulation run.
-We conducted 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5-minute interval.
-
-\begin{figure}[t]
-  \centering
-  % \vspace{-.1cm}
-  \includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
-  % \vspace{-0.3cm}
-  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
-  \label{fig:large-scale-topo}
-\end{figure}
-
-\begin{table}[t]
-\centering
-\caption{Large-scale topology link bandwidth and delay ranges}
-% \vspace{-0.3cm}
-\label{tab:large-scale}
-\begin{tabular}{|l||c|c||c|c|}
-  \hline
-  \multirow{2}{*}{\bf Link type} &  \multicolumn{2}{|c||}{\bf Delay} &  \multicolumn{2}{|c|}{\bf Bandwidth} \tabularnewline
-  \cline{2-5}
-                        &  Min & Max                       &  Min & Max \tabularnewline
-  \hline \hline
-  Backbone--Backbone    & 5~ms & 10~ms   & 40~Mbps & 100~Mbps \tabularnewline
-  \hline
-  Gateway--Backbone,    & \multirow{2}{*}{5~ms} & \multirow{2}{*}{10~ms}   
-                        & \multirow{2}{*}{10~Mbps} & \multirow{2}{*}{20~Mbps} \tabularnewline
-  Gateway--Gateway      & & & & \\
-  \hline
-  Client--Gateway       & 10~ms & 70~ms   & 1~Mbps  & 3~Mbps \\
-  \hline
-\end{tabular}
-% \vspace{-0.3cm}
-\end{table}
-
-%Priya: Leaving out this in the interest of space...
-%Topological location of the data producer plays a key role in its resilience to Interest flooding attacks.
-For a data producer that %is connected to a client node via a low-bandwidth link, even a small number of junk Interests can impact services for legitimate %users.
-For a producer located at the backbone with rich connectivity through many high-bandwidth links, an attack might not %be as severe as a majority of legitimate users might not be on the attack path.
-
-% The results for all attack mitigation algorithms and all runs are aggregated in Fig.~\ref{fig:small-scale attack progress}, where Y-axis represents a minimum and maximum range for observed Interest satisfaction percentages among all nodes and all simulation runs.
-% A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
-
-In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over all simulations runs for each mitigation algorithm for the scenario where the data producer is placed at a gateway node.
-We observe similar results for the data producer placed at a backbone node as well.
-Unlike the binary-tree topology experiments, we observe that
-both the token bucket with per interface fairness and satisfaction-based Interest acceptance have poor performance, while the satisfaction-based pushback is still the most effective algorithm.
-Interest satisfaction percentage for legitimate users are close to 30\%, 25\%, and 100\% respectively for these mitigation methodologies.
-
-%
-%The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
-
-\begin{figure}[t]
- \centering
- \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
- % \vspace{-.3cm}
- \caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}
- % producer on a gateway node
- \label{fig:large-scale}
- % \vspace{-.7cm}
-\end{figure}
-
-Satisfaction-based Interest acceptance algorithm, which was very effective for binary-tree topology, is completely ineffective when deployed in a larger and more realistic topology.
-For the duration of the attack, legitimate users experience poor quality of service with only 25\% of their Interests being satisfied and continue to experience degraded service long after the attack has stopped.
-This poor performance, as detailed in Section~\ref{sec:probabilistic}, is due to the fact that each router on the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
-In the case of a large topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics and further penalization of new Interests from them.
-
-All our evaluations leave us to conclude that among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most promising one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
-%The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
-As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.
-
-% Alex: Anything else here?
-
-% Alex: I also experimented with placing producer at the backbone, getting slightly better results for all algorithms.  Though I'm not sure there is any value to put those results in the paper
-
-% \input{simulation-emulation.tex}
-
-\subsection{Limitations}
-%{\color{red} I gave up the idea of seperate discussion section after trying for some time, as given the space limitation, there is no way to write a reasonably comprehensive and  broad discussion section that justifies a separate section.
-Instead, I decided to have a scoped down version here that confesses upon the limiations of our evaluations only.
-Whoever has time (I need to sleep few hours), please go ahead and write 1-2 paragraphs as I outlined below.
--Ersin}
-
-%This section should roughly say: Our results show that the two features, namely the symmetric traffic and stateful routing, give NDN routers the ability to observe and characterize traffic in real time.
-Through our evaluations, we demonstrated that a mitigation algorithm that leverages such ability has great potential in mitigating various DDoS attacks that could otherwise have grave effect on the network.
-However, as the first step in exploring the problem and the solution space, this paper has obvious limitations: (1) We assume a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations.
-Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step is evaluating the above described solutions with more sophisticated and adaptive attackers.
-(2)   Although most (such as single-path routing, no-caches in the network, single homed victim, etc) are aimed to test the proposed solutions under worst-case scenario, we made many assumptions in simulations/evaluations about the configurations, topology and the traffic that maybe poor-representative of realistic conditions.
-(3) As NDN being an ongoing research effort itself, our evaluations fully depend on simulations and done over a snapshot of its codebase.
-
-% The main contribution of the paper and this section in particular is a proof that two inherent properties of NDN architecture, namely the symmetric traffic and stateful forwarding, give NDN routers the ability to characterize traffic and react in real time.
-% We demonstrated that satisfaction-based pushback algorithm, leveraging this ability, has great potential in mitigating various DDoS attacks that could otherwise have a grave effect on the network. 
-% However, as the first step in exploring the problem and the solution space, our paper has obvious limitations.
-% First, we assumed a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations. 
-% Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step that we are leaving out for future work is evaluating the above described solutions with more sophisticated and adaptive attackers.
-% Second, while aiming to test the designed algorithms under worst-case conditions, the future work needs to address behavior in more realistic scenarios, including investigation of multi-path routing, in network caches, as well as multi-homed victims.
-
-This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space. 
-To design our mitigation algorithms we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
-We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology, % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
-as well as a more realistic ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network. 
-While our results are promising and show a great potential in mitigating Interest flooding DDoS attacks, there are certain limitations which should be addressed in future research.
-
-First, in our evaluations we used a simple and static attacker model---attackers send junk Interests as fast as possible. 
-In future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and Interest sending patterns based on the network reaction. 
-Second, we assumed that Interests are not satisfied by an intermediate router's cache and always forwarded all the way to the producer.  
-In future, we plan to study the impact of Interest flooding attacks in more realistic scenarios with multi-path routing enabled, more realistic traffic patterns, and the presence of in-network caches.
-% We also ignored NDN's strategy layer that routes around failure and congestion in the network. 
-% In future work, we plan to study the impact of turning on these features. 
-%Finally, we also plan to perform more extensive simulations on other realistic Internet-like topologies and traffic patterns.
-
-\section{Related work}
-\label{sec:related-work}
-
-As a new Internet architecture proposal, Named Data Networking has attracted a limited attention from the security community. 
-Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
-W\"ahlisch et al.~\cite{Wahlisch:2012:Backscatter-from} explore security and stability threats in the general area of information-centric networks (ICN), using CCNx software as an example.  
-While this work aims to generalize findings for all ICNs, it largely does not go beyond the current design choices of CCNx.
-% (which is an example, but not the final word in NDN) 
-% Gasti et al.~\cite{gasti2012ddos} identified several NDN architecture-specific attacks (Interest flooding and content/cache poisoning) and proposed potential solutions, without devising particular algorithms.
-In this paper we follow the suggestions by Gasti et al.~\cite{gasti2012ddos} and utilize the properties provided by the NDN architecture to mitigate DDoS attacks, and tackle the Interest flooding problem as a first step in this direction.
-More specifically our attack mitigation design relies on NDN's stateful forwarding plane that allows us to
-maintain statistics on unsatisfied Interests.  
-Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr,Yi:2013:A-Case-for-Stateful} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
-
-The general area of mitigating denial of service attacks is amongst the hottest topics in recent years.
-% Among all the body of work, 
-The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushing back malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
-overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
-various ticketing systems with conditional admission of traffic in to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
-and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
-Identifying malicious traffic requires establishing certain state at routers, and the above mentioned solutions differ in the specifics on what state to use and how to establish it.
-By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions---we simply take full advantage of this state to develop desired solutions.
-
-% Our design for the Interest flooding attack mitigation borrows
-
-% This paper talks about attacks on content centric infrastructure (not specifically to NDN).
-% \cite{Wahlisch:2012:Backscatter-from}
-
-% % Collaborative detection of DDoS attacks over multiple network domains
-% \cite{Chen:2007:Collaborative-detection} distributed change-point detection
-
-% % DDoS flooding attack detection through a step-by-step investigation
-% \cite{Jun:2011:DDoS-flooding}
-
-% % A practical method to counteract denial of service attacks
-% \cite{Tupakula:2003:A-practical-method}
-
-% Alex: We should not include this reference for the review, but afterwards
-% Previous work on DDoS and DoS~\cite{gasti2012ddos}
-
-% Network level (Flooding)
-% % 2002
-% Pushback~\cite{Pushback} (hop-by-hop push back) aggregate- based congestion control/congestion signatures (e.g., per-destination), rate-limiting, explicit notification
-% AITF~\cite{Argyraki:2005:Active-internet} (active filtering requests; path recording, last-point of trust detecting)?
-% DefCOM \cite{Oikonomou:2006:A-framework-for-a-collaborative} Communication between src, core, and dst to provide collaborative defense.
-Dst raises alerts, src differentiate bad/good, packet tagging.
-Core rate-limit, congestion-aware re-tag.
-Traffic prioritization.
-% StopIt \cite{Liu:2008:To-filter-or-to-authorize:} (filtering) tagging with passports, tagged prioritization, dst- invoked filter instantiation
-% NetFence \cite{Liu:2010:NetFence:-preventing} congestion policing: fair queuing (one leaky bucket per {src,L}, L- bottleneck), secure "ticketing" with signals for AIMD to increase/decrease bandwidth allowance
-% PSP \cite{Chou:2009:Proactive-surge} topology as origin-destination pairs, packet tagging, OD traffic isolation, sharing based on historic bandwidth demand
-
-% SIFF~\cite{Yaar:2004:SIFF:-A-stateless} (time-based tickets, capabilities)
-% TVA \cite{Yang:2005:A-DoS-limiting-network} like SIFF, traffic- based tickets, hierarchical per- AS, per-source fair queuing
-% FastPass \cite{Wendlandt:2006:Fastpass:-Providing} (tokens: various puzzles, other methods) traffic authorization, routers verify and filter.
-% \cite{Natu:2007:Fine-grained-capabilities} based on TVA/SIFF: specifies previously unspecified mechanisms to grant "tickets" for requesters, extends capabilities to include priorities, changing tickets to be only destination- dependent, not path dependent
-% % LazySusan \cite{Crowcroft:2007:Lazy-Susan:} TR (latency-based proof of work--- computational puzzles)
-% Portcullis \cite{Portcullis} Protecting connection setup with computational proof of work, tickets and traffic prioritization for the rest, per- computational fairness; DNS to disseminate puzzles
-% There are many other puzzle- based schemes, on which Portcullis is based or which problems it solves
-
-% PacketSymmetry \cite{Kreibich:2005:Using-packet} (leverages packet symmetry to detect and remove bad traffic) packet asymmetry - number of transmitted packets (tx) to received packets (rx); negative values when rx outweighs tx, positive values when tx outweighs rx, and zero in the case of perfectly balanced traffic)
-% % Detecting SYN flooding attacks
-% \cite{Wang:2002:Detecting-SYN-flooding} based on the protocol behavior of TCP SYN-FIN (RST) pairs, and is an instance of the Seqnential Change Point Detection
-% dFence \cite{Mahimkar:2007:dFence:-Transparent} (middleboxes) TCP connection proxying, rate estimation and TCP/ACK modification
-
-% Overlays:
-% CenterTrack \cite{Stone:2000:CenterTrack:-An-IP-overlay} (overlay) reroute suspicious traffic to a special routers with diagnostic capabilities using an overlay
-% SOS \cite{Keromytis:2004:SOS:-An-architecture}
-% Shield \cite{Kline:2011:Shield:-DoS-filtering}
-
-% NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
-In this section we will overview generic directions of DDoS mitigation designs and try to think about which tricks could be used in NDN.
-
-% Capability-based systems allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
-Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
-This implies that each client must pass through an authentication process prior to using any bandwidth~\cite{Capabilities}.
-We believe that for NDN this method doesn't fit really well for the following reasons.
-First, this method is very questionable in terms of scalability and mobility support since it requires tight trust connections between routers and hosts.
-Thus, it neglects one of the main advantages (mobility) of NDN.
-Second, the design of trust infrastructure for NDN is not well defined yet, which means that we cannot really make assumptions in our design of mitigation techniques.
-
-% Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
-Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients.
-One of the main difficulties in such systems is the question of puzzle dessimination.
-In ~\cite{Portcullis} authors suggested to propagate puzzles using DNS system.
-In NDN since routers have caching abilities, we can propagate puzzles just like a normal data packets, using Interest-Data exchange.
-Overall, this method looks interesting and deserves being investigated in a future work.
-
-% Congestion control systems do per flow traffic analysis and drop of packets belonging to misbehaving flows.
-For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
-Such techniques, if largely deployed, could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
-Since NDN routers maintain a richer per-packet state, which translates into a better per-flow statistics, these techniques can become much more effective when applied to NDN.
-
-% Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
-This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines~\cite{Pushback}.
-In general this technique can be applied to NDN architecture thanks to its decentralized coordination of downrating bad traffic flows.
-Moreover, NDN provides better capabilities for accurate flow detection.
-
-%were looking for getting accustomed
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-% Main take out from the paper:  could be a problem, but problem is solvable.  
-% One of the key components in the Named Data Networking architecture is its stateful data delivery model, which potentially can be abused by new types of denial of service attacks.
-% However, one should not forget that the same stateful data delivery provides effective mechanisms to fight back against such attacks.
-
-%In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
-%The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data path symmetry and full receiver-based traffic control.
-%In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Interests can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
-%
-%Other forms of attack may require different mitigation mechanisms.  
-%However, the granularity of the NDN state---per each Interest packet---is what giving NDN an opportunity to stand against existing and new forms of attacks.
-%
-%NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution.
-
-NDN being a newly proposed future Internet architecture, it is important to address its resilience in face of DDoS attacks.
-As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks---namely, Interest flooding---and the severe service degradation such an attack may cause to legitimate users.
-We then leveraged the key features of the NDN architecture to design, develop, and evaluate three mitigation strategies.
-We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
-The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers, so that they cause little or no service impact to legitimate users.
-
-NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balance (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding,Yi:2013:A-Case-for-Stateful}.
-Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.
-
-\bibliographystyle{IEEEtran}
-\bibliography{references}
-
-\end{document}

### 2013-05-13 05-evals.tex
Splitting paper back to its normal organization

--- 2013-03-26 paper.tex
@@
-\documentclass[10pt,conference]{IEEEtran}
-% http://networking2013.poly.edu/call-for-papers/paper-submission/
-% Page limit 9 pages
-
-\makeatletter
-\def\ps@headings{%
-\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
-\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
-\def\@oddfoot{}%
-\def\@evenfoot{}}
-\makeatother
-
-\hyphenation{incoming}
-\hyphenation{na-me-spa-ce}
-\hyphenation{sa-tis-fac-tion}
-\hyphenation{sa-tis-fied}
-
-\pagestyle{headings}
-
-% \usepackage[top=.75in, bottom=1in, left=.625in, right=.625in]{geometry}
-\usepackage{graphicx}
-% \usepackage[]{hyperref}
-\usepackage{breakurl}
-\usepackage{url}
-\usepackage[nocompress]{cite}
-% \usepackage{verbatim}
-% \usepackage{algpseudocode}
-\usepackage[noend]{algpseudocode,algorithm}
-% More customizeable version. Probably it would be better to convert pseudocode to 2e format
-% \usepackage{algorithm2e} 
-\usepackage{multirow}
-\usepackage{times}
-\usepackage{color}
-
-\newfont{\nicettfont}{cmtt9}
-\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
-\renewcommand{\texttt}[1]{{\nicettfont #1}}
-
-\graphicspath{{figures/}}
-
-\begin{document}
-
-\title{Interest Flooding Attack and Countermeasures in Named Data Networking}
-
-\author{
-    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
-    \\\{afanasev, iliamo, lixia\}@cs.ucla.edu}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
-    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
-}
-
-\maketitle
-
-\begin{abstract}
-Distributed Denial of Service (DDoS) attacks are an ongoing problem in today's Internet, where packets from a large number of compromised hosts thwart the paths to the victim site and/or overload the victim machines.
-In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network delivers Data packets upon request only, effectively eliminating many existing DDoS attacks.
-However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  
-In this paper we investigate effective solutions to mitigate Interest flooding.
-We show that NDN's inherent properties of storing per packet state on each router and maintaining flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
-Our evaluation through simulations shows that the solution can quickly and effectively respond and mitigate Interest flooding.
-\end{abstract}
-
-\begin{IEEEkeywords}
-Information-centric networks, named-data networking, denial-of-service
-\end{IEEEkeywords}
-
-\section{Introduction}
-\label{sec:intro}
-
-Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an ongoing research effort that aims to move the Internet into the future with a content-centric design that is capable of efficient content distribution and seamless mobility support.
-In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in the packets.
-However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against DDoS attacks?
-Especially since various forms of DDoS attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial to ensure that the new design is free of similar vulnerabilities.
-
-NDN eliminates host-based addressing and makes data the first-class network entity.
-Instead of sending packets to a given IP address, NDN nodes request desired data by sending Interest packets carrying application-level data names, and the network returns the requested Data packets following the path of Interests.
-Such a shift automatically eliminates several long-standing DDoS attacks, including direct flooding and reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
-%
-However, malicious users can attack the network by sending an excessive number of Interests. 
-Since each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can congest the network and exhaust a router's memory. 
-We coin the term {\it Interest flooding} to refer to such attack and
-this paper exclusively investigates the problem and the solution space for it.
-
-Our effort is an important first step towards a complete investigation of DDoS attacks in NDN.
-We experiment with three algorithms that allow routers to exploit their state information to thwart these attacks.
-Through extensive simulations, we show how one of our mitigation methodologies effectively shuts down malicious users while preventing legitimate users from service degradation.
-The rest of the paper is organized as follows.
-We provide an overview of NDN architecture in Section~\ref{sec:ccn-intro} and describe Interest flooding attacks in Section~\ref{sec:interest-flooding}.
-In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
-We summarize related work in Section~\ref{sec:related-work}.
-We discuss future work and conclude in Section~\ref{sec:conclusion}.
-
-\section{NDN Overview\label{sec:ccn-intro}}
-
-In this section we briefly introduce NDN with a focus on its stateful forwarding plane (refer to \cite{ndn-conext, ndn-tr, adaptive-forwarding, Yi:2013:A-Case-for-Stateful} for more details).
-NDN is a receiver-driven, data-centric communication protocol.
-All communications in NDN are performed using two distinct types of packets: \textit{Interest} and \textit{Data}.
-Both types of packets carry a \textit{name}, which uniquely identifies a piece of content that can be carried in one Data packet.
-Data names in NDN are hierarchically structured and an example name for the first segment of a youtube video would look like: \ndnName{/youtube/videos/0F8YdlkKO9A/0}.
-
-To retrieve data, a consumer requests it by sending an Interest packet with the name of the desired content in it.
-Routers use this name to route the Interest towards data sources, and a Data packet whose name matches the name in the Interest is returned to the consumer by following the reverse path of the Interest.
-Similar to IP, Interest forwarding is based on longest name prefix match, but, unlike IP, an Interest packet and its matching Data packet always take symmetric paths.
-%% An Interest is ``satisfied'' when it is matched with a Data packet.
-
-Each NDN router maintains three major data structures:
-\begin{itemize}
-\item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards potential data sources.
-Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicate the same Interest is forwarded along multiple paths.
-\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, specifying directions where Interests can be forwarded. 
-% Having one-to-many relationship in this table allows multipath forwarding of Interests.}
-\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this router, allowing efficient data retrieval by different consumers.
-\end{itemize}
-
-When a router receives an Interest packet, it first checks whether there is a matching data in its CS.
-If a match is found, the Data packet is sent back to the incoming interface of the Interest packet.
-If not, the Interest name is checked against the entries in the PIT. 
-If the name already exists in the PIT, then it can be a duplicate Interest (identified by a random number each Interest carries) that should be dropped,
-or an Interest from another consumer asking for the same Data, which requires the incoming interface of this Interest to be added to the existing PIT entry.
-If the name does not exist in the PIT, the Interest is added into the PIT and forwarded along the interface chosen by the strategy module, which uses FIB as input for its decisions.
-
-When a Data packet is received, its name is used to look up the PIT.
-If a matching PIT entry is found,
-the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the CS, and removes the PIT entry.
-Otherwise, the Data packet is deemed unsolicited and is discarded.
-Each Interest also has an associated lifetime; the PIT entry is removed when the lifetime expires.
-Although the maximum lifetime is specified by users, it is ultimately a router's decision on how long it is willing to keep a PIT entry.  
-For simplicity, we assume routers keep Interests in PIT for one second in our simulations.
-
-\section{Interest Flooding Attacks in NDN}
-\label{sec:interest-flooding}
-
-As we explained earlier, Interest packets in NDN are routed through the network based on content name prefixes and consume memory resources at intermediate routers.
-This makes them a potential tool to launch DDoS attacks in NDN.
-An attacker or a set of distributed attackers can inject excessive number of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{attack-definition}
-  \caption{Example of Interest flooding attack}
-  \label{fig:flooding example}
-  \vspace{-0.3cm}
-\end{figure}
-
-Since an NDN network fetches data by its name, an adversary cannot easily target specific routers or end-hosts.
-However, an adversary can target a specific namespace.
-For example in Fig.~\ref{fig:flooding example}, if the data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
-\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{\small /foo/bar} prefix to make them effective.
-It also assumes the producer is single-homed and the data is not replicated elsewhere.
-With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding, Yi:2013:A-Case-for-Stateful} support.}
-A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
-
-Similar to packets in traditional networks, Interest packets in NDN consume a portion of network capacity.
-A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
-In particular, a coordinated DDoS attack could target one specific namespace and concentrate attack traffic in certain segments of the network, as routing in NDN is based on name prefixes.
-
-As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a router's memory, making the router unable to create new PIT entries for incoming Interests and disrupting service for legitimate users.
-
-Nevertheless, creating an effective Interest flooding attack in NDN is non-trivial.
-To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1)~the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2)~new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
-The former is achieved when Interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers---an Interest is not forwarded upstream if a router can satisfy it from its content store.
-The latter requires every single malicious Interest to ask for unique content---all Interests requesting the same content are combined into one PIT entry in routers.
-Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content with each Interest.
-Of the two options available to an adversary, the first one is challenging due to the difficulties around indexing content names in a particular namespace, coordinating a large number of bots to send unique Interests, and sustaining the attack while the network is continuously caching the requested content objects.
-However, the second option---requesting a unique non-existing content with each Interest---is easy to achieve and sustain.
-For example, an adversary can construct such Interests by concatenating a variable-length random name component to the victim namespace (e.g., \ndnName{/newyorktimes/3rf3...}).
-In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest, but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
-% other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
-
-In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
-
-%\paragraph{Assumptions} 
-%E: These are assumptions for the simulations on hand and particulary to test for the worst case scenario in many aspects.
-They are not the paper's assumption and in fact the paper first should be more general on describing all possibilities.
-Then it should explain the assumptions for the simulations and discuss why they make sense and do NOT favor positive results in some way.
-
-% - assumptions about attacker position
-% - assumptions about the producer / producer namespace
-% - assumptions about the attack traffic / attack pattern
-
-%In this paper we are making the following assumptions about the Interest flooding attack:
-%\begin{itemize}
-%\item only client nodes can be compromised and become attack bots;
-%\item there are no colluding attackers inside the Data producer's network;
-%\item the attack is carried only using unique junk Interests; and
-%\item there is only one Data producer for the attacked prefix.
-%\end{itemize}
-
-%We also assume that NDN forwarding strategy uses only single-path Interest forwarding, always choosing the best-metric route advertised by the routing protocol.
-%This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
-
-%In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
-
-\section{Interest flooding mitigation methods}
-\label{sec:design}
-
-% Points what should be here:
-% - What can be done (in general) to mitigate flooding attack
-% - Which building blocks NDN architecture gives to mitigate Interest flooding attacks: Interest limits, ability to measure Interest satisfaction performance (Interest satisfaction stats)
-% - Methods to set these limits: static/dynamic
-% - Methods how limits can be applied: best-effort (fifo), "fair" queuing, probabilistic
-% - Reference to caching: we don't consider it here, but caching provides additional level of protection, especially for certain types of attacks
-
-% Our definition of attack mitigation is that good clients are still able to access data on the producer.
-
-In this section we present several algorithms to mitigate Interest flooding attacks in NDN.
-Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
-We start by describing our simple strategies and use the insights and lessons learned from the deployment of these to inform and design more effective mitigation techniques that work well in various topologies.
-
-%   - Naive approach to Interest Limits (that is called physical limits everywhere else)
-%     Example how this can be implemented in a simple way
-%     Baseline solution
-%   - Interest limits with "fair" queuing
-%     Improving problem of simple limits (no single face can dominate), but doesn't solve the proble
-
-% - Attack mitigation
-%   - Per-incoming interface Interest statistics
-
-%   - Dynamic Interests limit adjustments
-
-%   - Probabilistic Interest accept
-
-%The fact that each Data packet takes the reverse path of the corresponding Interest packet allows intermediate routers to match a received Data packet to the corresponding Interest packet and %thus determine which Interest packets were satisfied.
-As we describe in the rest of this section,  NDN routers can exploit this information to make informed decisions on which Interest packets to %forward, how many Interest packets to forward, and thus effectively defend against DDoS attacks.
-
-%Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
-%Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
-%Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
-%At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
-
-%\subsection{Na\"{i}ve attack mitigation}
-
-%We start with a couple of naive strategies that can be used to migitate attacks in an NDN network and describe the pitfalls associated with these strategies.
-
-% In a normal network operation, the size of Interests packets is supposed to be significantly smaller than the size of the requested Data.
-
-% All communication in NDN network is host-to-host and receiver-driven.
-
-An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests forwarded through the network. To this end, we exploit a 
- fundamental principle of NDN architecture---flow balance between Interest and Data packets.
-Flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
-This principle allows intermediate routers to control the inbound data traffic by controlling the number of outstanding Interests in the network.
-One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding interface.
-This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet-switched networks.
-Analogous to the {\it Token Bucket} algorithm, NDN routers can keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
-Ideally, the number of tokens (the pending \emph{Interest Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
-We can formalize this value as follows:
-% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
-%
-\begin{equation}
-\label{eq:interest limit}
-\small \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
-\end{equation}
-
-In the above equation, \emph{Delay} is the expected time for the Interest to be satisfied and \emph{Data packet size} is the size of the returning Data packet.
-Although both these values are not known a priori, it is not really necessary to use their exact values.
-One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as network buffers can smooth out most of the network fluctuations.
-
-This {\it Token Bucket} approach might be exceptionally restrictive in forwarding Interests---not all Interests will result in a Data packet---and might result in underutilization of the network.
-However, the biggest drawback of this algorithm is the fact that it can nourish DDoS attacks.
-If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
-One way to get around this issue is to impose a per interface fairness, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
-We describe this technique in greater detail below.
-
-%That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
-%For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
-%In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
-%
-%\subsubsection{\textbf{Interest limits (physical limits)}}
-%\label{sec:physical limits}
-%
-%\input{algos/physical-limits.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Token bucket with per interface fairness}}
-\label{sec:queuing}
-
-To address the lack of fairness associated with the na\"ive {\it Token Bucket} approach, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring nodes.
-For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
-%Due to the expected small volume of Interests, we cannot merely rely on network buffers to perform statistical multiplexing of Interests, as they would almost never be %buffered.
-%At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests %will arrive in the future.
-In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring nodes, 
-%, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
-we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded and implement hierarchical queues for each interface (see Fig.~\ref{fig:queueing}). 
-This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing and incoming interface.
-%As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
-We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
-Thus, a PIT entry can be quickly updated when the Interest is actually forwarded, and the element can be easily removed from the queue when the Interest expires.
-
-%For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}).
-%As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.6]{queue}
-  \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
-  \label{fig:queueing}
-  \vspace{-0.3cm}
-\end{figure}
-
-We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
-By setting appropriate queue sizes, we can control the amount of physical resources utilized at a router.
- % (such as memory and computation power). 
-It is also important to set a sensible value for how long an Interest can be enqueued. 
-If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet might be dropped at the downstream routers if their corresponding state expired. 
-For our evaluations, we empirically chose to enqueue Interests up to 10\% of their original lifetime (100~ms).
-% We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
-% Alex: I don't believe there is a need for separate discussion about "freshness", as we already introduced concept of lifetime
-% {\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
-
-%It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
-%Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
-%Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
-
-%The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
-%At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[h]
-\footnotesize
-\caption{\small Token bucket with per interface fairness}
-\label{alg:queuing}
-\begin{algorithmic}[1]
-\For{\textbf{each} interface \textbf{if}}
-    \State{$L_{if} \leftarrow$ Interest Limit according to (1)}
-    \State{$O_{if} \leftarrow 0$} \Comment{Outstanding Interests on interface \textbf{if}}
-\EndFor
-
-\vspace{0.1cm}
-
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
-    \If{$L_{out} - O_{out} > 0$} \Comment{\textbf{out} is under limit cap}
-        \State $O_{out} \leftarrow O_{out} + 1$  \Comment{``borrow'' a token from the bucket}
-        \State add \textbf{out} to PIT entry and forward \textbf{i} to \textbf{out}
-    \Else
-        \State Queue $q \leftarrow out$.GetSubQueue($in$)
-        \If{$Size(q) < L_{out}$}
-           \State $q$.PushInterest($i$)
-           \State add \textbf{out} to PIT entry, and link PIT entry with the queue
-        \Else
-           \State drop Interest
-        \EndIf
-    \EndIf
-\EndFunction
-
-\vspace{0.1cm}
-
-\State{} \Comment{\textit{Whenever $L_{out} - O_{out}$ becomes larger than zero}}
-\Function{TokenBecomesAvailable}{}
-    \State Queue $q \leftarrow$ $out$.GetRoundRobinSubQueue 
-    \State Interest $i \leftarrow$ $q$.PopInterest
-    \State update PIT entry and Forward($i$, $out$)
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{InData}{Data \textbf{d}}
-   \State lookup PIT entry \textbf{p} for data \textbf{d}
-   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
-        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
-   \EndFor
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{Timeout}{PIT entry $p$}
-   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
-        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
-   \EndFor
-\EndFunction
-
-\end{algorithmic}
-
-\end{algorithm}
-
-As we show in Section~\ref{sec:evaluation}, this algorithm provides a partial relief from Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
-We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is largely ineffective in protecting legitimate users from malicious ones. 
-Attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of malicious Interests.
-
-%At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
-%Therefore, to successfully solve the problem, we need a fundamentally different, more intelligent approach, allowing localization of the attack traffic as close as possible to the attack origin.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits a relatively large number of Interests from malicious users.
-A considerable percentage of these malicious Interests are forwarded all the way to content producers, thereby reducing resources available to serve legitimate users.
-This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate and malicious Interests.
-For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and differentiate to some extent malicious requests from legitimate ones.
-% `Good' Interests from legitimate users must be admited and forwarded appropriately. 
-Thus, the key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
-
-%One can try a black- or whitelisting approach.
-However, besides the fact that source black- and whitelisting cannot work in %NDN as it does not feature source addresses, it requires extraneous knowledge to classify the incoming Interests.
-
-%Priya: I have added the below point specifically to point out that a router cannot determine from the prefix name alone whether /parc is good  or bad...
-
-%{\color{red} \textbf{Alex: This paragraph is confusing to me.
-I would remove it.} In NDN one cannot easily distinguish a `good' prefix from a `bad' one.
-Content producers must be able to support %dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded %to the producer for possible dynamic Data packet generation.
-%Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the prefix name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain %namespaces  will be inefficient and likely ineffective.
-}
-
-% Alex: I'm not sure that this part is relevant... The point I see is that blacklisting and whitelisting is not 100% effective, but it can be used in both worlds
-
-% In today's host-based Internet architecture where DDoS mitigation techniques rely on blacklisting of ``dark'' IP prefixes or whitelisting of good IP prefixes.
-% Unlike IP, in NDN one cannot easily distinguish a `good' prefix from a `bad' one. 
-% Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
-% Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
-
-\subsection{Intelligent attack mitigation}
-\label{sec:intelligent mitigating}
-
-%While the Interest limit is the key building block to suppress mechanisms of the Interest flooding attack, legitimate Interests need to be somehow prioritized and malicious Interests need to be somehow penalized in order to completely suppress the attack.
-%That is, instead of processing Interests always based on the first-in-first-serve rule, NDN routers need some basis to treat the incoming Interests differently.
-%Thus, the primary task in bringing intelligence to the Interest flooding attack mitigation is to proactively distinguish between legitimate and malicious Interests.
-
-In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets.
-Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guaranteed to see if an Interest it forwarded resulted in a matching Data packet or timed out.
-%The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
-Since malicious Interests are not likely to bring data back (as discussed in Section~\ref{sec:interest-flooding}), this information can be utilized by routers in differentiating attack and legitimate traffic.
-%Therefore, intermediate routers can classify the ones that brings data back as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}
-%Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
-
-This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
-However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use these statistics to determine whether an incoming Interest should be forwarded or dropped.
-For example, maintaining Interest satisfaction ratio statistics for each incoming interface is sufficient to reasonably predict whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout if forwarded.
-Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
-that can further improve the estimates.
-A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but do not result in a returning Data packet.
-In order to allow negative statistics to build up fast and positive statistics to  deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.
-
-%Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
-%{\color{red} \it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong %here.}
-
-%The devil is always in the details.
-%From the one hand, such statistics needs to start penalizing adversaries as soon as possible (i.e., negative stats should build up fast).
-%On the other hand, the positive statistics should not deteriorate too fast (i.e., positive stats should be relatively long-term).
-%Our preliminary experiments showed that the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window, provides a good balance between the two contradictory requirements.
-
-% \subsubsection{\textbf{Data plane performance tracking}}
-% \label{sec:stats}
-
-% Note that there is a condition (line 6 in Pseudocode~\ref{alg:probabilistic model}) to check if there is a valid statistics point.
-% This condition is extremely important, because it first provides a basis to distinguish between known facts (i.e., good or bad satisfaction ratio for the incoming interface) and unknown facts (e.g., the first time an Interests arrives on the interfaces).
-% Second, it gives an opportunity to recover from a bad history (history of unsatisfied Interests) after malicious Interests are ceased to flow in.
-% Essentially, this recovery relies on statistics module to perform time-based invalidation of historical data (timely, but not too quickly\footnote{Otherwise, attackers may send short bursts of malicious Interests, successfully avoiding differential Interest treatment}).
-
-Pseudocode~\ref{algo:interest stats} formally defines how statistics can be generated for  each incoming interface.
-Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interests), only unsatisfied statistics needs to be exponentially smoothed (lines 19--21).
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Interest satisfaction statistics}
-\label{algo:interest stats}
-\begin{algorithmic}[1]
-
-\For{\textbf{each} interface \textbf{if}}
-    \State $F_{if} \leftarrow 0$ \Comment{forwarded Interests from interface \textbf{if}}
-    \State $\hat F_{if} \leftarrow 0$ \Comment{averaged value of $F_{if}$}
-
-    \State $U_{if} \leftarrow 0$ \Comment{unsatisfied Interests from interface \textbf{if}}
-    \State $\hat U_{if} \leftarrow 0$ \Comment{averaged value of $U_{if}$}
-\EndFor
-
-\vspace{0.1cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}}
-  \State $F_{in} \leftarrow F_{in} + 1$
-  \State record \textbf{\emph{in}} in the list of incoming interfaces for \textbf{\emph{i}}
-\EndFunction
-
-\vspace{0.1cm}
-\Function{InterestTimeout}{Interest \textbf{i}}
-    \State lookup the list of incoming interfaces for \textbf{\emph{i}}
-
-    \For{\textbf{each} interface \textbf{if} in the list}
-        \State $U_{if} \leftarrow U_{if} + 1$
-    \EndFor
-\EndFunction
-
-\vspace{0.1cm}
-
-\State {} \Comment{\textit{Exponentially weighted moving average smoothing}}
-\Function{EWMA}{} \Comment{Every second}
-\State $\alpha \leftarrow e^{-1.0/30.0}$  %\Comment{$\approx$ 30~sec average}
-
-\For{\textbf{each} interface \textbf{if}}
-    \State $\hat U_{if} \leftarrow \alpha \cdot \hat U_{if} + (1 - \alpha) \cdot U_{if}$ 
-    \State $U_{if} \leftarrow 0$
-
-    \If{$F_{if} > 0$} \Comment{To ensure decaying of ratio $U_{if}/F_{if}$}
-        \State $\hat F_{if} \leftarrow \alpha \cdot \hat F_{if} + (1 - \alpha) \cdot I_{if}$ 
-        \State $F_{if} \leftarrow 0$ \Comment{Reset counters}
-    \EndIf
-\EndFor
-
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-Fig.~\ref{fig:ratio example} illustrates the resulting dynamics of the statistics during and after an Interest flooding attack.
-The attack duration is from 10 to 70~seconds.
-Prior to start of the attack, the percentage of unsatisfied Interests is zero.
-The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.
-%\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
-For the duration of the attack (10--70~seconds), the percentage of unsatisfied Interests is close to 100\%: 
-when the ratio is close to 100\%, routers drop all incoming Interests, resulting in decaying of the statistics until a new Interest is admitted, which eventually brings statistics back near 100\% point.
-Finally, the ratio exponentially decays after the attack ceases.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.8]{limits}
-  % \vspace{-0.3cm}
-  \caption{Dynamics of  unsatisfied Interests statistics on a gateway's interface towards the attacker}
-  \label{fig:ratio example}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Satisfaction-based Interest acceptance}}
-\label{sec:probabilistic}
-
-Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using these ratios to penalize malicious Interests.
-A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
-%Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Satisfaction-based Interest acceptance}
-\label{alg:probabilistic model}
-\begin{algorithmic}[1]
-\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-
-\vspace{0.1cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
-
-    \State{} \Comment{Use uniform probability distribution model $P(X)$}
-    \State{} \Comment{$P(X) : \forall x \in [0,1] \Rightarrow P(x) = x$}
-
-    \If{$F_{in} > \theta $} \Comment{At least some Interests were forwarded before}
-        \State $s \leftarrow (1 - U_{in} / F_{in})$
-        \State Drop interest with probability $P(s)$
-    \EndIf
-
-    \State{forward the Interest, subjecting to token bucket limits}
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-Parameter $\theta$ on line 5 of Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
-This step is critical to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
-
-A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop an Interest. 
-As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
-In our example in Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
-At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
-Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the data producer.
-With each increasing hop in the network, the probability of being forwarded to the next hop decreases significantly.
-One way to prevent this overreaction and unfair penalization is to ensure that the decision taken at each router on whether to forward or drop the Interest is not independent of the decision taken at preceding routers.
-An explicit notification such as a gossip protocol between neighboring NDN routers might alleviate the problem, but we leave the design and evaluation of it to future work.
-%{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Satisfaction-based pushback}}
-\label{sec:dynamic limits}
-
-% Differential treatment of Interests received from different interfaces can be achieved in a more elegant way, without reverting to probabilistic methods.
-
-The previous algorithm---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
-% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
-An alternate algorithm for proportional token distribution without overreaction is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
-Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.
-
-The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm will work in our example in Fig.~\ref{fig:flooding example}.
-Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node will set and announce the following  incoming interface limit $L'$:
-\begin{enumerate}
-\item router B will set and announce the incoming interface limit $L'=3$;
-\item router A, after receiving announcement from B will readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
-\item both legitimate users and adversaries may either obey or ignore the announced limit, which will in any case be enforced by router A.
-\end{enumerate}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{dynamic-limits}
-  \caption{Satisfaction-based pushback example
-%: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer%
-}
-  \label{fig:dynamic limits example}
-\end{figure}
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{ 
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Satisfaction-based pushback}
-\label{alg:dynamic limits}
-\begin{algorithmic}[1]
-% \State{}\Comment{Same initialization, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-\vspace{0.1cm}
-\State{$\forall f \in \mathrm{interfaces} : L'_{f} \leftarrow L_{f}$} \Comment{Per-incoming interface Interest limit}
-
-\vspace{0.1cm}
-
-\State{} \Comment{\textit{Announcement from the neighbor}}
-\Function{InLimits}{InInterface $in$, Limit $L'$}
-    \State $L_{in} \leftarrow L'$
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
-\For{\textbf{each} outgoing interface $out$}
-
-   \For{\textbf{each} incoming interface $in$}
-        \State $L'_{in}= {L_{out}} \times (1 - U_{in}/F_{in})$
-        \State AnnounceLimit($in$, $L'_{in}$)
-   \EndFor
-
-\EndFor
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to an appropriate level (recall Fig.~\ref{fig:ratio example}).
-At the next iteration of the satisfaction-based pushback algorithm, a legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
-
-We note that while in the description of the satisfaction-based pushback algorithm we explicitly used ``outgoing'' and ``incoming'' interfaces,  all interfaces can be both incoming and outgoing.
-Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 9 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
-To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
-That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on the sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
-
-Both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, but with several core differences. 
-First, we are suppressing (pushing back) unwanted requests for data, not actual data itself.
-Second, differentiating between good and bad Interests is based on the traffic symmetry principle of NDN.
-% Alex: I'm not entirely sure about this point... 
-Finally, both intelligent attack mitigation algorithms can be deployed at all times without degrading network performance even when there are no active attackers.
-
 \section{Evaluation of Interest flooding mitigation methods}
@@
 %Finally, we also plan to perform more extensive simulations on other realistic Internet-like topologies and traffic patterns.
-
-\section{Related work}
-\label{sec:related-work}
-
-As a new Internet architecture proposal, Named Data Networking has attracted a limited attention from the security community. 
-Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
-W\"ahlisch et al.~\cite{Wahlisch:2012:Backscatter-from} explore security and stability threats in the general area of information-centric networks (ICN), using CCNx software as an example.  
-While this work aims to generalize findings for all ICNs, it largely does not go beyond the current design choices of CCNx.
-% (which is an example, but not the final word in NDN) 
-% Gasti et al.~\cite{gasti2012ddos} identified several NDN architecture-specific attacks (Interest flooding and content/cache poisoning) and proposed potential solutions, without devising particular algorithms.
-In this paper we follow the suggestions by Gasti et al.~\cite{gasti2012ddos} and utilize the properties provided by the NDN architecture to mitigate DDoS attacks, and tackle the Interest flooding problem as a first step in this direction.
-More specifically our attack mitigation design relies on NDN's stateful forwarding plane that allows us to
-maintain statistics on unsatisfied Interests.  
-Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr,Yi:2013:A-Case-for-Stateful} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
-
-The general area of mitigating denial of service attacks is amongst the hottest topics in recent years.
-% Among all the body of work, 
-The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushing back malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
-overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
-various ticketing systems with conditional admission of traffic in to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
-and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
-Identifying malicious traffic requires establishing certain state at routers, and the above mentioned solutions differ in the specifics on what state to use and how to establish it.
-By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions---we simply take full advantage of this state to develop desired solutions.
-
-% Our design for the Interest flooding attack mitigation borrows
-
-% This paper talks about attacks on content centric infrastructure (not specifically to NDN).
-% \cite{Wahlisch:2012:Backscatter-from}
-
-% % Collaborative detection of DDoS attacks over multiple network domains
-% \cite{Chen:2007:Collaborative-detection} distributed change-point detection
-
-% % DDoS flooding attack detection through a step-by-step investigation
-% \cite{Jun:2011:DDoS-flooding}
-
-% % A practical method to counteract denial of service attacks
-% \cite{Tupakula:2003:A-practical-method}
-
-% Alex: We should not include this reference for the review, but afterwards
-% Previous work on DDoS and DoS~\cite{gasti2012ddos}
-
-% Network level (Flooding)
-% % 2002
-% Pushback~\cite{Pushback} (hop-by-hop push back) aggregate- based congestion control/congestion signatures (e.g., per-destination), rate-limiting, explicit notification
-% AITF~\cite{Argyraki:2005:Active-internet} (active filtering requests; path recording, last-point of trust detecting)?
-% DefCOM \cite{Oikonomou:2006:A-framework-for-a-collaborative} Communication between src, core, and dst to provide collaborative defense.
-Dst raises alerts, src differentiate bad/good, packet tagging.
-Core rate-limit, congestion-aware re-tag.
-Traffic prioritization.
-% StopIt \cite{Liu:2008:To-filter-or-to-authorize:} (filtering) tagging with passports, tagged prioritization, dst- invoked filter instantiation
-% NetFence \cite{Liu:2010:NetFence:-preventing} congestion policing: fair queuing (one leaky bucket per {src,L}, L- bottleneck), secure "ticketing" with signals for AIMD to increase/decrease bandwidth allowance
-% PSP \cite{Chou:2009:Proactive-surge} topology as origin-destination pairs, packet tagging, OD traffic isolation, sharing based on historic bandwidth demand
-
-% SIFF~\cite{Yaar:2004:SIFF:-A-stateless} (time-based tickets, capabilities)
-% TVA \cite{Yang:2005:A-DoS-limiting-network} like SIFF, traffic- based tickets, hierarchical per- AS, per-source fair queuing
-% FastPass \cite{Wendlandt:2006:Fastpass:-Providing} (tokens: various puzzles, other methods) traffic authorization, routers verify and filter.
-% \cite{Natu:2007:Fine-grained-capabilities} based on TVA/SIFF: specifies previously unspecified mechanisms to grant "tickets" for requesters, extends capabilities to include priorities, changing tickets to be only destination- dependent, not path dependent
-% % LazySusan \cite{Crowcroft:2007:Lazy-Susan:} TR (latency-based proof of work--- computational puzzles)
-% Portcullis \cite{Portcullis} Protecting connection setup with computational proof of work, tickets and traffic prioritization for the rest, per- computational fairness; DNS to disseminate puzzles
-% There are many other puzzle- based schemes, on which Portcullis is based or which problems it solves
-
-% PacketSymmetry \cite{Kreibich:2005:Using-packet} (leverages packet symmetry to detect and remove bad traffic) packet asymmetry - number of transmitted packets (tx) to received packets (rx); negative values when rx outweighs tx, positive values when tx outweighs rx, and zero in the case of perfectly balanced traffic)
-% % Detecting SYN flooding attacks
-% \cite{Wang:2002:Detecting-SYN-flooding} based on the protocol behavior of TCP SYN-FIN (RST) pairs, and is an instance of the Seqnential Change Point Detection
-% dFence \cite{Mahimkar:2007:dFence:-Transparent} (middleboxes) TCP connection proxying, rate estimation and TCP/ACK modification
-
-% Overlays:
-% CenterTrack \cite{Stone:2000:CenterTrack:-An-IP-overlay} (overlay) reroute suspicious traffic to a special routers with diagnostic capabilities using an overlay
-% SOS \cite{Keromytis:2004:SOS:-An-architecture}
-% Shield \cite{Kline:2011:Shield:-DoS-filtering}
-
-% NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
-In this section we will overview generic directions of DDoS mitigation designs and try to think about which tricks could be used in NDN.
-
-% Capability-based systems allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
-Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
-This implies that each client must pass through an authentication process prior to using any bandwidth~\cite{Capabilities}.
-We believe that for NDN this method doesn't fit really well for the following reasons.
-First, this method is very questionable in terms of scalability and mobility support since it requires tight trust connections between routers and hosts.
-Thus, it neglects one of the main advantages (mobility) of NDN.
-Second, the design of trust infrastructure for NDN is not well defined yet, which means that we cannot really make assumptions in our design of mitigation techniques.
-
-% Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
-Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients.
-One of the main difficulties in such systems is the question of puzzle dessimination.
-In ~\cite{Portcullis} authors suggested to propagate puzzles using DNS system.
-In NDN since routers have caching abilities, we can propagate puzzles just like a normal data packets, using Interest-Data exchange.
-Overall, this method looks interesting and deserves being investigated in a future work.
-
-% Congestion control systems do per flow traffic analysis and drop of packets belonging to misbehaving flows.
-For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
-Such techniques, if largely deployed, could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
-Since NDN routers maintain a richer per-packet state, which translates into a better per-flow statistics, these techniques can become much more effective when applied to NDN.
-
-% Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
-This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines~\cite{Pushback}.
-In general this technique can be applied to NDN architecture thanks to its decentralized coordination of downrating bad traffic flows.
-Moreover, NDN provides better capabilities for accurate flow detection.
-
-%were looking for getting accustomed
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-% Main take out from the paper:  could be a problem, but problem is solvable.  
-% One of the key components in the Named Data Networking architecture is its stateful data delivery model, which potentially can be abused by new types of denial of service attacks.
-% However, one should not forget that the same stateful data delivery provides effective mechanisms to fight back against such attacks.
-
-%In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
-%The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data path symmetry and full receiver-based traffic control.
-%In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Interests can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
-%
-%Other forms of attack may require different mitigation mechanisms.  
-%However, the granularity of the NDN state---per each Interest packet---is what giving NDN an opportunity to stand against existing and new forms of attacks.
-%
-%NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution.
-
-NDN being a newly proposed future Internet architecture, it is important to address its resilience in face of DDoS attacks.
-As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks---namely, Interest flooding---and the severe service degradation such an attack may cause to legitimate users.
-We then leveraged the key features of the NDN architecture to design, develop, and evaluate three mitigation strategies.
-We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
-The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers, so that they cause little or no service impact to legitimate users.
-
-NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balance (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding,Yi:2013:A-Case-for-Stateful}.
-Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.
-
-\bibliographystyle{IEEEtran}
-\bibliography{references}
-
-\end{document}

### 2013-05-13 06-related.tex
Final pass
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@941 df1a90cd-247b-4364-bdaf-287a704eb499
Splitting paper back to its normal organization

@@
 
-As a new Internet architecture proposal, the Named Data Networking has attracted attention from the security community. 
+As a new Internet architecture proposal, Named Data Networking has attracted a limited attention from the security community. 
 Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
@@
 In this paper we follow the suggestions by Gasti et al.~\cite{gasti2012ddos} and utilize the properties provided by the NDN architecture to mitigate DDoS attacks, and tackle the Interest flooding problem as a first step in this direction.
-More specifically our attack mitigation design relies on NDN's stateful forwarding plane 
-which provides statistics on unsatisfied Interests.  
-Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
+More specifically our attack mitigation design relies on NDN's stateful forwarding plane that allows us to
+maintain statistics on unsatisfied Interests.  
+Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr,Yi:2013:A-Case-for-Stateful} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
 
-The general area of mitigating denial of service attacks is among the hottest topics in recent years.
+The general area of mitigating denial of service attacks is amongst the hottest topics in recent years.
 % Among all the body of work, 
-The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushbacking malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
+The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushing back malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
 overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
-various ticketing systems with conditional admission of traffic to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
+various ticketing systems with conditional admission of traffic in to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
 and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
 Identifying malicious traffic requires establishing certain state at routers, and the above mentioned solutions differ in the specifics on what state to use and how to establish it.
-By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions.
-Therefore one can simply take full advantage of this state to develop desired solutions.
+By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions---we simply take full advantage of this state to develop desired solutions.
 
@@
 %were looking for getting accustomed
-
-%%% Local Variables: 
-%%% mode: latex
-%%% TeX-master: "paper"
-%%% End:

### 2013-05-13 07-conclusion.tex
Splitting paper back to its normal organization

--- 2013-03-26 paper.tex
@@
-\documentclass[10pt,conference]{IEEEtran}
-% http://networking2013.poly.edu/call-for-papers/paper-submission/
-% Page limit 9 pages
-
-\makeatletter
-\def\ps@headings{%
-\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
-\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
-\def\@oddfoot{}%
-\def\@evenfoot{}}
-\makeatother
-
-\hyphenation{incoming}
-\hyphenation{na-me-spa-ce}
-\hyphenation{sa-tis-fac-tion}
-\hyphenation{sa-tis-fied}
-
-\pagestyle{headings}
-
-% \usepackage[top=.75in, bottom=1in, left=.625in, right=.625in]{geometry}
-\usepackage{graphicx}
-% \usepackage[]{hyperref}
-\usepackage{breakurl}
-\usepackage{url}
-\usepackage[nocompress]{cite}
-% \usepackage{verbatim}
-% \usepackage{algpseudocode}
-\usepackage[noend]{algpseudocode,algorithm}
-% More customizeable version. Probably it would be better to convert pseudocode to 2e format
-% \usepackage{algorithm2e} 
-\usepackage{multirow}
-\usepackage{times}
-\usepackage{color}
-
-\newfont{\nicettfont}{cmtt9}
-\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
-\renewcommand{\texttt}[1]{{\nicettfont #1}}
-
-\graphicspath{{figures/}}
-
-\begin{document}
-
-\title{Interest Flooding Attack and Countermeasures in Named Data Networking}
-
-\author{
-    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
-    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
-    \\\{afanasev, iliamo, lixia\}@cs.ucla.edu}
-    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
-    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
-}
-
-\maketitle
-
-\begin{abstract}
-Distributed Denial of Service (DDoS) attacks are an ongoing problem in today's Internet, where packets from a large number of compromised hosts thwart the paths to the victim site and/or overload the victim machines.
-In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network delivers Data packets upon request only, effectively eliminating many existing DDoS attacks.
-However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  
-In this paper we investigate effective solutions to mitigate Interest flooding.
-We show that NDN's inherent properties of storing per packet state on each router and maintaining flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
-Our evaluation through simulations shows that the solution can quickly and effectively respond and mitigate Interest flooding.
-\end{abstract}
-
-\begin{IEEEkeywords}
-Information-centric networks, named-data networking, denial-of-service
-\end{IEEEkeywords}
-
-\section{Introduction}
-\label{sec:intro}
-
-Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an ongoing research effort that aims to move the Internet into the future with a content-centric design that is capable of efficient content distribution and seamless mobility support.
-In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in the packets.
-However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against DDoS attacks?
-Especially since various forms of DDoS attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial to ensure that the new design is free of similar vulnerabilities.
-
-NDN eliminates host-based addressing and makes data the first-class network entity.
-Instead of sending packets to a given IP address, NDN nodes request desired data by sending Interest packets carrying application-level data names, and the network returns the requested Data packets following the path of Interests.
-Such a shift automatically eliminates several long-standing DDoS attacks, including direct flooding and reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
-%
-However, malicious users can attack the network by sending an excessive number of Interests. 
-Since each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can congest the network and exhaust a router's memory. 
-We coin the term {\it Interest flooding} to refer to such attack and
-this paper exclusively investigates the problem and the solution space for it.
-
-Our effort is an important first step towards a complete investigation of DDoS attacks in NDN.
-We experiment with three algorithms that allow routers to exploit their state information to thwart these attacks.
-Through extensive simulations, we show how one of our mitigation methodologies effectively shuts down malicious users while preventing legitimate users from service degradation.
-The rest of the paper is organized as follows.
-We provide an overview of NDN architecture in Section~\ref{sec:ccn-intro} and describe Interest flooding attacks in Section~\ref{sec:interest-flooding}.
-In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
-We summarize related work in Section~\ref{sec:related-work}.
-We discuss future work and conclude in Section~\ref{sec:conclusion}.
-
-\section{NDN Overview\label{sec:ccn-intro}}
-
-In this section we briefly introduce NDN with a focus on its stateful forwarding plane (refer to \cite{ndn-conext, ndn-tr, adaptive-forwarding, Yi:2013:A-Case-for-Stateful} for more details).
-NDN is a receiver-driven, data-centric communication protocol.
-All communications in NDN are performed using two distinct types of packets: \textit{Interest} and \textit{Data}.
-Both types of packets carry a \textit{name}, which uniquely identifies a piece of content that can be carried in one Data packet.
-Data names in NDN are hierarchically structured and an example name for the first segment of a youtube video would look like: \ndnName{/youtube/videos/0F8YdlkKO9A/0}.
-
-To retrieve data, a consumer requests it by sending an Interest packet with the name of the desired content in it.
-Routers use this name to route the Interest towards data sources, and a Data packet whose name matches the name in the Interest is returned to the consumer by following the reverse path of the Interest.
-Similar to IP, Interest forwarding is based on longest name prefix match, but, unlike IP, an Interest packet and its matching Data packet always take symmetric paths.
-%% An Interest is ``satisfied'' when it is matched with a Data packet.
-
-Each NDN router maintains three major data structures:
-\begin{itemize}
-\item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards potential data sources.
-Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicate the same Interest is forwarded along multiple paths.
-\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, specifying directions where Interests can be forwarded. 
-% Having one-to-many relationship in this table allows multipath forwarding of Interests.}
-\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this router, allowing efficient data retrieval by different consumers.
-\end{itemize}
-
-When a router receives an Interest packet, it first checks whether there is a matching data in its CS.
-If a match is found, the Data packet is sent back to the incoming interface of the Interest packet.
-If not, the Interest name is checked against the entries in the PIT. 
-If the name already exists in the PIT, then it can be a duplicate Interest (identified by a random number each Interest carries) that should be dropped,
-or an Interest from another consumer asking for the same Data, which requires the incoming interface of this Interest to be added to the existing PIT entry.
-If the name does not exist in the PIT, the Interest is added into the PIT and forwarded along the interface chosen by the strategy module, which uses FIB as input for its decisions.
-
-When a Data packet is received, its name is used to look up the PIT.
-If a matching PIT entry is found,
-the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the CS, and removes the PIT entry.
-Otherwise, the Data packet is deemed unsolicited and is discarded.
-Each Interest also has an associated lifetime; the PIT entry is removed when the lifetime expires.
-Although the maximum lifetime is specified by users, it is ultimately a router's decision on how long it is willing to keep a PIT entry.  
-For simplicity, we assume routers keep Interests in PIT for one second in our simulations.
-
-\section{Interest Flooding Attacks in NDN}
-\label{sec:interest-flooding}
-
-As we explained earlier, Interest packets in NDN are routed through the network based on content name prefixes and consume memory resources at intermediate routers.
-This makes them a potential tool to launch DDoS attacks in NDN.
-An attacker or a set of distributed attackers can inject excessive number of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{attack-definition}
-  \caption{Example of Interest flooding attack}
-  \label{fig:flooding example}
-  \vspace{-0.3cm}
-\end{figure}
-
-Since an NDN network fetches data by its name, an adversary cannot easily target specific routers or end-hosts.
-However, an adversary can target a specific namespace.
-For example in Fig.~\ref{fig:flooding example}, if the data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
-\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{\small /foo/bar} prefix to make them effective.
-It also assumes the producer is single-homed and the data is not replicated elsewhere.
-With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding, Yi:2013:A-Case-for-Stateful} support.}
-A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
-
-Similar to packets in traditional networks, Interest packets in NDN consume a portion of network capacity.
-A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
-In particular, a coordinated DDoS attack could target one specific namespace and concentrate attack traffic in certain segments of the network, as routing in NDN is based on name prefixes.
-
-As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a router's memory, making the router unable to create new PIT entries for incoming Interests and disrupting service for legitimate users.
-
-Nevertheless, creating an effective Interest flooding attack in NDN is non-trivial.
-To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1)~the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2)~new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
-The former is achieved when Interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers---an Interest is not forwarded upstream if a router can satisfy it from its content store.
-The latter requires every single malicious Interest to ask for unique content---all Interests requesting the same content are combined into one PIT entry in routers.
-Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content with each Interest.
-Of the two options available to an adversary, the first one is challenging due to the difficulties around indexing content names in a particular namespace, coordinating a large number of bots to send unique Interests, and sustaining the attack while the network is continuously caching the requested content objects.
-However, the second option---requesting a unique non-existing content with each Interest---is easy to achieve and sustain.
-For example, an adversary can construct such Interests by concatenating a variable-length random name component to the victim namespace (e.g., \ndnName{/newyorktimes/3rf3...}).
-In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest, but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
-% other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
-
-In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
-
-%\paragraph{Assumptions} 
-%E: These are assumptions for the simulations on hand and particulary to test for the worst case scenario in many aspects.
-They are not the paper's assumption and in fact the paper first should be more general on describing all possibilities.
-Then it should explain the assumptions for the simulations and discuss why they make sense and do NOT favor positive results in some way.
-
-% - assumptions about attacker position
-% - assumptions about the producer / producer namespace
-% - assumptions about the attack traffic / attack pattern
-
-%In this paper we are making the following assumptions about the Interest flooding attack:
-%\begin{itemize}
-%\item only client nodes can be compromised and become attack bots;
-%\item there are no colluding attackers inside the Data producer's network;
-%\item the attack is carried only using unique junk Interests; and
-%\item there is only one Data producer for the attacked prefix.
-%\end{itemize}
-
-%We also assume that NDN forwarding strategy uses only single-path Interest forwarding, always choosing the best-metric route advertised by the routing protocol.
-%This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
-
-%In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
-
-\section{Interest flooding mitigation methods}
-\label{sec:design}
-
-% Points what should be here:
-% - What can be done (in general) to mitigate flooding attack
-% - Which building blocks NDN architecture gives to mitigate Interest flooding attacks: Interest limits, ability to measure Interest satisfaction performance (Interest satisfaction stats)
-% - Methods to set these limits: static/dynamic
-% - Methods how limits can be applied: best-effort (fifo), "fair" queuing, probabilistic
-% - Reference to caching: we don't consider it here, but caching provides additional level of protection, especially for certain types of attacks
-
-% Our definition of attack mitigation is that good clients are still able to access data on the producer.
-
-In this section we present several algorithms to mitigate Interest flooding attacks in NDN.
-Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
-We start by describing our simple strategies and use the insights and lessons learned from the deployment of these to inform and design more effective mitigation techniques that work well in various topologies.
-
-%   - Naive approach to Interest Limits (that is called physical limits everywhere else)
-%     Example how this can be implemented in a simple way
-%     Baseline solution
-%   - Interest limits with "fair" queuing
-%     Improving problem of simple limits (no single face can dominate), but doesn't solve the proble
-
-% - Attack mitigation
-%   - Per-incoming interface Interest statistics
-
-%   - Dynamic Interests limit adjustments
-
-%   - Probabilistic Interest accept
-
-%The fact that each Data packet takes the reverse path of the corresponding Interest packet allows intermediate routers to match a received Data packet to the corresponding Interest packet and %thus determine which Interest packets were satisfied.
-As we describe in the rest of this section,  NDN routers can exploit this information to make informed decisions on which Interest packets to %forward, how many Interest packets to forward, and thus effectively defend against DDoS attacks.
-
-%Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
-%Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
-%Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
-%At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
-
-%\subsection{Na\"{i}ve attack mitigation}
-
-%We start with a couple of naive strategies that can be used to migitate attacks in an NDN network and describe the pitfalls associated with these strategies.
-
-% In a normal network operation, the size of Interests packets is supposed to be significantly smaller than the size of the requested Data.
-
-% All communication in NDN network is host-to-host and receiver-driven.
-
-An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests forwarded through the network. To this end, we exploit a 
- fundamental principle of NDN architecture---flow balance between Interest and Data packets.
-Flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
-This principle allows intermediate routers to control the inbound data traffic by controlling the number of outstanding Interests in the network.
-One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding interface.
-This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet-switched networks.
-Analogous to the {\it Token Bucket} algorithm, NDN routers can keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
-Ideally, the number of tokens (the pending \emph{Interest Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
-We can formalize this value as follows:
-% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
-%
-\begin{equation}
-\label{eq:interest limit}
-\small \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
-\end{equation}
-
-In the above equation, \emph{Delay} is the expected time for the Interest to be satisfied and \emph{Data packet size} is the size of the returning Data packet.
-Although both these values are not known a priori, it is not really necessary to use their exact values.
-One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as network buffers can smooth out most of the network fluctuations.
-
-This {\it Token Bucket} approach might be exceptionally restrictive in forwarding Interests---not all Interests will result in a Data packet---and might result in underutilization of the network.
-However, the biggest drawback of this algorithm is the fact that it can nourish DDoS attacks.
-If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
-One way to get around this issue is to impose a per interface fairness, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
-We describe this technique in greater detail below.
-
-%That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
-%For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
-%In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
-%
-%\subsubsection{\textbf{Interest limits (physical limits)}}
-%\label{sec:physical limits}
-%
-%\input{algos/physical-limits.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Token bucket with per interface fairness}}
-\label{sec:queuing}
-
-To address the lack of fairness associated with the na\"ive {\it Token Bucket} approach, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring nodes.
-For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
-%Due to the expected small volume of Interests, we cannot merely rely on network buffers to perform statistical multiplexing of Interests, as they would almost never be %buffered.
-%At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests %will arrive in the future.
-In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring nodes, 
-%, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
-we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded and implement hierarchical queues for each interface (see Fig.~\ref{fig:queueing}). 
-This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing and incoming interface.
-%As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
-We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
-Thus, a PIT entry can be quickly updated when the Interest is actually forwarded, and the element can be easily removed from the queue when the Interest expires.
-
-%For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}).
-%As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.6]{queue}
-  \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
-  \label{fig:queueing}
-  \vspace{-0.3cm}
-\end{figure}
-
-We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
-By setting appropriate queue sizes, we can control the amount of physical resources utilized at a router.
- % (such as memory and computation power). 
-It is also important to set a sensible value for how long an Interest can be enqueued. 
-If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet might be dropped at the downstream routers if their corresponding state expired. 
-For our evaluations, we empirically chose to enqueue Interests up to 10\% of their original lifetime (100~ms).
-% We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
-% Alex: I don't believe there is a need for separate discussion about "freshness", as we already introduced concept of lifetime
-% {\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
-
-%It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
-%Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
-%Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
-
-%The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
-%At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[h]
-\footnotesize
-\caption{\small Token bucket with per interface fairness}
-\label{alg:queuing}
-\begin{algorithmic}[1]
-\For{\textbf{each} interface \textbf{if}}
-    \State{$L_{if} \leftarrow$ Interest Limit according to (1)}
-    \State{$O_{if} \leftarrow 0$} \Comment{Outstanding Interests on interface \textbf{if}}
-\EndFor
-
-\vspace{0.1cm}
-
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
-    \If{$L_{out} - O_{out} > 0$} \Comment{\textbf{out} is under limit cap}
-        \State $O_{out} \leftarrow O_{out} + 1$  \Comment{``borrow'' a token from the bucket}
-        \State add \textbf{out} to PIT entry and forward \textbf{i} to \textbf{out}
-    \Else
-        \State Queue $q \leftarrow out$.GetSubQueue($in$)
-        \If{$Size(q) < L_{out}$}
-           \State $q$.PushInterest($i$)
-           \State add \textbf{out} to PIT entry, and link PIT entry with the queue
-        \Else
-           \State drop Interest
-        \EndIf
-    \EndIf
-\EndFunction
-
-\vspace{0.1cm}
-
-\State{} \Comment{\textit{Whenever $L_{out} - O_{out}$ becomes larger than zero}}
-\Function{TokenBecomesAvailable}{}
-    \State Queue $q \leftarrow$ $out$.GetRoundRobinSubQueue 
-    \State Interest $i \leftarrow$ $q$.PopInterest
-    \State update PIT entry and Forward($i$, $out$)
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{InData}{Data \textbf{d}}
-   \State lookup PIT entry \textbf{p} for data \textbf{d}
-   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
-        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
-   \EndFor
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{Timeout}{PIT entry $p$}
-   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
-        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
-   \EndFor
-\EndFunction
-
-\end{algorithmic}
-
-\end{algorithm}
-
-As we show in Section~\ref{sec:evaluation}, this algorithm provides a partial relief from Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
-We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is largely ineffective in protecting legitimate users from malicious ones. 
-Attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of malicious Interests.
-
-%At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
-%Therefore, to successfully solve the problem, we need a fundamentally different, more intelligent approach, allowing localization of the attack traffic as close as possible to the attack origin.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits a relatively large number of Interests from malicious users.
-A considerable percentage of these malicious Interests are forwarded all the way to content producers, thereby reducing resources available to serve legitimate users.
-This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate and malicious Interests.
-For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and differentiate to some extent malicious requests from legitimate ones.
-% `Good' Interests from legitimate users must be admited and forwarded appropriately. 
-Thus, the key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
-
-%One can try a black- or whitelisting approach.
-However, besides the fact that source black- and whitelisting cannot work in %NDN as it does not feature source addresses, it requires extraneous knowledge to classify the incoming Interests.
-
-%Priya: I have added the below point specifically to point out that a router cannot determine from the prefix name alone whether /parc is good  or bad...
-
-%{\color{red} \textbf{Alex: This paragraph is confusing to me.
-I would remove it.} In NDN one cannot easily distinguish a `good' prefix from a `bad' one.
-Content producers must be able to support %dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded %to the producer for possible dynamic Data packet generation.
-%Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the prefix name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain %namespaces  will be inefficient and likely ineffective.
-}
-
-% Alex: I'm not sure that this part is relevant... The point I see is that blacklisting and whitelisting is not 100% effective, but it can be used in both worlds
-
-% In today's host-based Internet architecture where DDoS mitigation techniques rely on blacklisting of ``dark'' IP prefixes or whitelisting of good IP prefixes.
-% Unlike IP, in NDN one cannot easily distinguish a `good' prefix from a `bad' one. 
-% Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
-% Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
-
-\subsection{Intelligent attack mitigation}
-\label{sec:intelligent mitigating}
-
-%While the Interest limit is the key building block to suppress mechanisms of the Interest flooding attack, legitimate Interests need to be somehow prioritized and malicious Interests need to be somehow penalized in order to completely suppress the attack.
-%That is, instead of processing Interests always based on the first-in-first-serve rule, NDN routers need some basis to treat the incoming Interests differently.
-%Thus, the primary task in bringing intelligence to the Interest flooding attack mitigation is to proactively distinguish between legitimate and malicious Interests.
-
-In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets.
-Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guaranteed to see if an Interest it forwarded resulted in a matching Data packet or timed out.
-%The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
-Since malicious Interests are not likely to bring data back (as discussed in Section~\ref{sec:interest-flooding}), this information can be utilized by routers in differentiating attack and legitimate traffic.
-%Therefore, intermediate routers can classify the ones that brings data back as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}
-%Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
-
-This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
-However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use these statistics to determine whether an incoming Interest should be forwarded or dropped.
-For example, maintaining Interest satisfaction ratio statistics for each incoming interface is sufficient to reasonably predict whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout if forwarded.
-Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
-that can further improve the estimates.
-A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but do not result in a returning Data packet.
-In order to allow negative statistics to build up fast and positive statistics to  deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.
-
-%Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
-%{\color{red} \it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong %here.}
-
-%The devil is always in the details.
-%From the one hand, such statistics needs to start penalizing adversaries as soon as possible (i.e., negative stats should build up fast).
-%On the other hand, the positive statistics should not deteriorate too fast (i.e., positive stats should be relatively long-term).
-%Our preliminary experiments showed that the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window, provides a good balance between the two contradictory requirements.
-
-% \subsubsection{\textbf{Data plane performance tracking}}
-% \label{sec:stats}
-
-% Note that there is a condition (line 6 in Pseudocode~\ref{alg:probabilistic model}) to check if there is a valid statistics point.
-% This condition is extremely important, because it first provides a basis to distinguish between known facts (i.e., good or bad satisfaction ratio for the incoming interface) and unknown facts (e.g., the first time an Interests arrives on the interfaces).
-% Second, it gives an opportunity to recover from a bad history (history of unsatisfied Interests) after malicious Interests are ceased to flow in.
-% Essentially, this recovery relies on statistics module to perform time-based invalidation of historical data (timely, but not too quickly\footnote{Otherwise, attackers may send short bursts of malicious Interests, successfully avoiding differential Interest treatment}).
-
-Pseudocode~\ref{algo:interest stats} formally defines how statistics can be generated for  each incoming interface.
-Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interests), only unsatisfied statistics needs to be exponentially smoothed (lines 19--21).
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Interest satisfaction statistics}
-\label{algo:interest stats}
-\begin{algorithmic}[1]
-
-\For{\textbf{each} interface \textbf{if}}
-    \State $F_{if} \leftarrow 0$ \Comment{forwarded Interests from interface \textbf{if}}
-    \State $\hat F_{if} \leftarrow 0$ \Comment{averaged value of $F_{if}$}
-
-    \State $U_{if} \leftarrow 0$ \Comment{unsatisfied Interests from interface \textbf{if}}
-    \State $\hat U_{if} \leftarrow 0$ \Comment{averaged value of $U_{if}$}
-\EndFor
-
-\vspace{0.1cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}}
-  \State $F_{in} \leftarrow F_{in} + 1$
-  \State record \textbf{\emph{in}} in the list of incoming interfaces for \textbf{\emph{i}}
-\EndFunction
-
-\vspace{0.1cm}
-\Function{InterestTimeout}{Interest \textbf{i}}
-    \State lookup the list of incoming interfaces for \textbf{\emph{i}}
-
-    \For{\textbf{each} interface \textbf{if} in the list}
-        \State $U_{if} \leftarrow U_{if} + 1$
-    \EndFor
-\EndFunction
-
-\vspace{0.1cm}
-
-\State {} \Comment{\textit{Exponentially weighted moving average smoothing}}
-\Function{EWMA}{} \Comment{Every second}
-\State $\alpha \leftarrow e^{-1.0/30.0}$  %\Comment{$\approx$ 30~sec average}
-
-\For{\textbf{each} interface \textbf{if}}
-    \State $\hat U_{if} \leftarrow \alpha \cdot \hat U_{if} + (1 - \alpha) \cdot U_{if}$ 
-    \State $U_{if} \leftarrow 0$
-
-    \If{$F_{if} > 0$} \Comment{To ensure decaying of ratio $U_{if}/F_{if}$}
-        \State $\hat F_{if} \leftarrow \alpha \cdot \hat F_{if} + (1 - \alpha) \cdot I_{if}$ 
-        \State $F_{if} \leftarrow 0$ \Comment{Reset counters}
-    \EndIf
-\EndFor
-
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-Fig.~\ref{fig:ratio example} illustrates the resulting dynamics of the statistics during and after an Interest flooding attack.
-The attack duration is from 10 to 70~seconds.
-Prior to start of the attack, the percentage of unsatisfied Interests is zero.
-The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.
-%\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
-For the duration of the attack (10--70~seconds), the percentage of unsatisfied Interests is close to 100\%: 
-when the ratio is close to 100\%, routers drop all incoming Interests, resulting in decaying of the statistics until a new Interest is admitted, which eventually brings statistics back near 100\% point.
-Finally, the ratio exponentially decays after the attack ceases.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.8]{limits}
-  % \vspace{-0.3cm}
-  \caption{Dynamics of  unsatisfied Interests statistics on a gateway's interface towards the attacker}
-  \label{fig:ratio example}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Satisfaction-based Interest acceptance}}
-\label{sec:probabilistic}
-
-Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using these ratios to penalize malicious Interests.
-A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
-%Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Satisfaction-based Interest acceptance}
-\label{alg:probabilistic model}
-\begin{algorithmic}[1]
-\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-
-\vspace{0.1cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
-
-    \State{} \Comment{Use uniform probability distribution model $P(X)$}
-    \State{} \Comment{$P(X) : \forall x \in [0,1] \Rightarrow P(x) = x$}
-
-    \If{$F_{in} > \theta $} \Comment{At least some Interests were forwarded before}
-        \State $s \leftarrow (1 - U_{in} / F_{in})$
-        \State Drop interest with probability $P(s)$
-    \EndIf
-
-    \State{forward the Interest, subjecting to token bucket limits}
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-Parameter $\theta$ on line 5 of Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
-This step is critical to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
-
-A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop an Interest. 
-As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
-In our example in Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
-At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
-Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the data producer.
-With each increasing hop in the network, the probability of being forwarded to the next hop decreases significantly.
-One way to prevent this overreaction and unfair penalization is to ensure that the decision taken at each router on whether to forward or drop the Interest is not independent of the decision taken at preceding routers.
-An explicit notification such as a gossip protocol between neighboring NDN routers might alleviate the problem, but we leave the design and evaluation of it to future work.
-%{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Satisfaction-based pushback}}
-\label{sec:dynamic limits}
-
-% Differential treatment of Interests received from different interfaces can be achieved in a more elegant way, without reverting to probabilistic methods.
-
-The previous algorithm---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
-% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
-An alternate algorithm for proportional token distribution without overreaction is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
-Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.
-
-The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm will work in our example in Fig.~\ref{fig:flooding example}.
-Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node will set and announce the following  incoming interface limit $L'$:
-\begin{enumerate}
-\item router B will set and announce the incoming interface limit $L'=3$;
-\item router A, after receiving announcement from B will readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
-\item both legitimate users and adversaries may either obey or ignore the announced limit, which will in any case be enforced by router A.
-\end{enumerate}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{dynamic-limits}
-  \caption{Satisfaction-based pushback example
-%: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer%
-}
-  \label{fig:dynamic limits example}
-\end{figure}
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{ 
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Satisfaction-based pushback}
-\label{alg:dynamic limits}
-\begin{algorithmic}[1]
-% \State{}\Comment{Same initialization, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-\vspace{0.1cm}
-\State{$\forall f \in \mathrm{interfaces} : L'_{f} \leftarrow L_{f}$} \Comment{Per-incoming interface Interest limit}
-
-\vspace{0.1cm}
-
-\State{} \Comment{\textit{Announcement from the neighbor}}
-\Function{InLimits}{InInterface $in$, Limit $L'$}
-    \State $L_{in} \leftarrow L'$
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
-\For{\textbf{each} outgoing interface $out$}
-
-   \For{\textbf{each} incoming interface $in$}
-        \State $L'_{in}= {L_{out}} \times (1 - U_{in}/F_{in})$
-        \State AnnounceLimit($in$, $L'_{in}$)
-   \EndFor
-
-\EndFor
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to an appropriate level (recall Fig.~\ref{fig:ratio example}).
-At the next iteration of the satisfaction-based pushback algorithm, a legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
-
-We note that while in the description of the satisfaction-based pushback algorithm we explicitly used ``outgoing'' and ``incoming'' interfaces,  all interfaces can be both incoming and outgoing.
-Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 9 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
-To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
-That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on the sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
-
-Both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, but with several core differences. 
-First, we are suppressing (pushing back) unwanted requests for data, not actual data itself.
-Second, differentiating between good and bad Interests is based on the traffic symmetry principle of NDN.
-% Alex: I'm not entirely sure about this point... 
-Finally, both intelligent attack mitigation algorithms can be deployed at all times without degrading network performance even when there are no active attackers.
-
-\section{Evaluation of Interest flooding mitigation methods}
-\label{sec:evaluation}
-
-% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
-
-% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers,
-
-% alex: what's a point of latency?  it would matter only for queueing method and we not really pushing this method
-% Latency for good clients, good versus bad interests as a function of time
-
-In this section, we present an in-depth evaluation study, aiming to quantify the effectiveness of all our Interest flooding attack mitigation methods.
-We used the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator (\url{http://www.nsnam.org/}), to run simulations for a variety of network topologies and scenarios.
-We extended ndnSIM with our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, and satisfaction-based pushback---and evaluated the effectiveness of each algorithm independently.
-
-% For evaluating the effectiveness of each mitigation algorithm, every router in the simulated topology runs the mitigation algorithm under study.
-
-% why we chose small scale topology
-% what point we wanted to show we small scale
-% what points we wanted to verify with larger-scale internet like topology
-
-% Metrics
-% not sure if i already explained that. our essential qualitative metric is .  
-% To quantify the effectiveness of the mitigation mechanism this  metric we use satisfaction percentages of user Interests.
-
-The metric we choose to quantify the effectiveness of our algorithms is the {\it percentage of satisfied Interests for legitimate users}.
-This metric corresponds to the quality of service experienced by legitimate users when the network is under attack.
-In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conclude that method $X$ is highly effective at mitigating the attack.% We also ensure that all Interests expressed by legitimate users during a period of no-attack are satisfied.
-
-%Quality of the attack mitigation methods directly corresponds to the quality of service for the legitimate users during an ongoing attack, which in NDN network can be quantified through percentage of satisfied Interest.
-%For example, if the network implements a mitigation method $X$ and under the attack majority of user-expressed Interests are getting satisfied, then the method $X$ can be seen as highly effective.
-%At the same time, if only a small percentage of the expressed Interest are getting satisfied during the attack, the method $X$ can be called ineffective.
-
-% Traffic pattern
-In our experiments, we assumed that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution.
-We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
-To quantify the behavior of our mitigation strategies under a worst-case attack scenario, we assumed that all the attackers send junk Interests as fast as they can.
-Further, no Interest---including legitimate ones---can be satisfied from caches.
-We also configured routers for single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
-%(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
-
-% Alex: not sure how to argue about the traffic pattern
-%Although this pattern may seem not truly realistic, it approximates a good statistical mix of traffic from all network users without excessive network buffering.
-
-%In addition to that, in each run of the simulation we ensure that all Interests expressed by the legitimate users during a no-attack period are satisfied.
-%For simplicity, we also equalized the average rates with which the legitimate users express Interests.
-%At the same time, the attackers are sending junk Interests as much as they can get through (remember, that Interest limits will not allow real f%looding of Intersests in all of the designed mitigation algorithms).
-
-We ran our simulations on two different network topologies---a smaller binary tree topology and a much larger ISP-like topology.
-We use a binary tree topology as it represents one of the worst cases to defend against Interest flooding DDoS attacks.
-The larger ISP topology reflects how our mitigation methods would perform when deployed on the real Internet.
-Again, to study the performance of our mitigation strategies under a range of conditions, we varied the percentage of attackers in the network---the values ranged from 6\% attackers to over 50\% attackers in the network.
-% Fixed parameters
-We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation (formula \ref{eq:interest limit}) to a fixed 
-value for every node in the simulated topology.
-In particular, for the small-scale binary tree topology, we set delay to 80~ms, while for the large-scale ISP topology we set it to 330~ms (the order of the largest RTT).
-The data size is 1100~bytes for all simulation runs and topologies.
-% THIS IS BULLSHIT!
-There is absolutely no logic to set the delay to the same value on all nodes in the network.
-We discussed multiple times that you should fix it so that the delays are realistic and gets smaller as the nodes gets closer to the producer...
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Small-scale evaluations}
-\label{sec:small-scale}
-
-% Topology description
-%To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a %simplistic small-scale binary tree topology 
-In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we used for our initial experiments.
-Legitimate users as well as attackers were placed on leaf nodes (top row of red nodes) as shown in the figure.
-There are 16 end users (both legitimate and attackers) in this topology, each expressing Interests that are routed towards a single data producer, placed at the root of the tree.
-Each link in this topology is assigned a bandwidth of 10~Mbps and a randomized propagation delay ranging from 1 to 10 ms.
-
-% Alex: should we mention that?
-%The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS %attacks.
-%That is, sharing of the network links exponentially increases as decreasing level of the binary tree.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.2]{topo-tree-evil-5-good-0-producer-gw}
-  \caption{Small-scale binary tree topology}
-  \label{fig:small-scale}
-  \vspace{-0.3cm}
-\end{figure}
-
-% in 10 independent runs of each simulation, where we randomized position of the adversaries along the legitimate users.
-In all runs, the total number of legitimate and malicious uses were fixed, meaning that when we increase number of attackers, we decrease the number of legitimate users.
-
-\subsubsection{Effectiveness of the three mitigation algorithms}
-
-%The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
-%For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).
-
-Our goal is to compare the effectiveness of each mitigation method and quantify the percentage of Interests satisfied for all legitimate users while the network is under attack.
-For each mitigation algorithm, we perform 10 independent simulation runs, where we randomly choose 7 client nodes to represent adversaries while the remaining 9 client nodes represent legitimate users.
-In each run we simulate a 10-minute attack window (total simulation time was 30 minutes, with attack starting at the 10-minute mark).
-We plot the minimum and maximum range for observed Interest satisfaction percentages for all legitimate users aggregated across the 10 simulation runs as a function of time for each mitigation algorithm in Fig.~\ref{fig:small-scale attack progress}.
-Token bucket with per-interface fair queuing performs the worst, while satisfaction-based pushback performs the best, with almost a 100\%  satisfied Interests for all legitimate users.
-
-%A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
-
-\begin{figure}[]
-  \centering
-  \hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
-  % \vspace{-.3cm}
-  \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
-  \label{fig:small-scale attack progress}
-  % \vspace{-.4cm}
-\end{figure}
-
-%\paragraph{\textbf{Simple token bucket}}
-
-%{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}
-
-%Let us take a deeper look on what is happening with the simple token bucket algorithm.
-%Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as token bucket restricts the number of forwarded Intersets!).
-%This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
-%In this example we assume that both the legitimate user and the adversary send Interests in about the same time.
-%
-%\begin{figure}[t]
-%  \centering
-%  \includegraphics[scale=0.3]{physical-limits-sync-problem}
-%  \caption{Three-router topology, with one legitimate and one malicious user}
-%  \label{fig:three router example}
-%\end{figure}
-%
-%Both router L and router X will forward the Interests, as both of them have a free token available.
-%At router A, two cases are possible, either of Interests can arrive first, resulting in a quite different effects.
-%When legitimate Interest arrives first, then there are no problem. 
-%Router A will capture the token, forward the Interest, which will be quickly satisfied, releasing the token for future uses.
-%In the mean time, malicious Interest will be dropped at router A, and router X will release the hold for the token in one second (i.e., after the maximum time Interests are admitted), enabling a new round of competition for router A's resources.
-%
-%In the case when malicious Interest is sent a little bit earlier, then router A will forward malicious Interests, dropping a legitimate one, and causing ``lock out'' for one second.
-%In the instant when the token gets released at router X, an adversary is able to push new Interest towards router A, which may arrive in the exact time A's token gets released (assuming an idealistic environment).
-%As a result, the adversary recaptures router A's token and extends the ``lock out'' for another second, denying service to the legitimate user without sending any massive numbers of Interests.
-
-\paragraph{\textbf{Token bucket with per interface fairness}}
-
-We observe a successful DDoS attack, where 40\% attackers succeed in significantly shutting down the remaining 60\% legitimate users---a mere 15\% of their Interests are satisfied by Data from the producer.
-Contrary to expectations, the 60\% legitimate users do not receive at least 60\% of network resources.
-As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers and causes congestion and packet drops near the victim.
-%Significantly reducing the number of accepted malicious Interests is fundamental for improving the effectiveness of any mitigation algorithm.
-
-%The described problem arises from the clocking effect and can be solved in a number different ways.
-%Augmenting token bucket algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
-%That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
-%However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
-%Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
-%We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.
-
-\paragraph{\textbf{Satisfaction-based Interest acceptance}}
-
-The effectiveness of this algorithm stems from the fact that routers can differentiate and limit malicious Interests into the network%, thereby ensuring availability of network resources for serving legitimate users
-.
-The observed periodic dips in the Interest satisfaction ratios of legitimate users in Fig.~\ref{fig:small-scale attack progress} is a direct result of Interest satisfaction rate statistics decaying with time.
-The 50-second period approximately corresponds to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx$20\% within 50~seconds.
- % that ranges from 30~seconds to 50~seconds. 
-%The primary reason that such minimum peaks exist is the fact that 
-When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe mixed traffic from legitimate and malicious users).
-Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' again to the edge.
-
-%When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
-%That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
-
-\paragraph{\textbf{Satisfaction-based pushback}}
-
-In our simulations, this mitigation algorithm was able to effectively shut down attackers and ensure that almost all the Interests from legitimate users are satisfied. 
-%The only potential problem with the satisfaction-based pushback algorithm is that it features 
-We observe a  sharp dip in the satisfaction ratio curve at the start of the attack as it takes a few seconds for all routers to be fully aware of the attack.
-However, recovery is quick as malicious Interests start to time out and explicit Interest limit announcements start to succeed in containing malicious Interests close to the attacker.
-Till then, the network, for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
-Once the malicious Interests are effectively shut down, all Interests from legitimate users are satisfied.
-Unlike the satisfaction-based Interest acceptance scenario, we do not observe any periodic dips in the satisfaction curve, as the pushback algorithm effectively guarantees that once an Interest is admitted, it will likely be routed all the way to the data producer.
-
-\subsubsection{Network reaction to varying number of attackers}
-
-Our next goal is to study the effectiveness of our mitigation algorithms as a function of increasing adversaries in the network.
-To this end, we vary the percentage of attackers in the topology from 6\% to over 50\%.
-Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
-All other parameters and experimental setup are consistent with the previous experiment.
-As before, for each mitigation algorithm, we perform 10 independent simulation runs.
-%The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
-%To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.
-
-%Since at this point the overall attack dynamics of all the attack mitigation algorithms is relatively clear, 
-% In other words, each point captured in the box plot graph corresponds to 1-second averaged satisfaction ratio for a user in an individual simulation run.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
-  % \vspace{-.3cm}
-  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}
-  \label{fig:small-scale-topo boxplot}
-  % \vspace{-0.5cm}
-\end{figure}
-
-In Fig.~\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
-The results are as expected---for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
-In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.
-While the two intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
-In the case of satisfaction-based pushback algorithm, during the first minute of the attack over 90\% of Interests from legitimate users are satisfied even if 50\% of end nodes are malicious.
-
-% \begin{figure}[htbp]
-%   \centering
-%   \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min-after-1-min}
-%   \caption{Average consumer Interest satisfaction ratios (second minute)}
-%   \label{fig:small-scale-topo 2}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Large scale simulations}
-\label{sec:largescale}
-
-%To check validity of the small-scale experiment results, we performed a larger-scale evaluation based on a modified version of
-
-In this section, we investigate the behavior of our mitigation strategies under a more realistic, large-scale network topology.
-The ISP-like topology we used is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
-%In order to approximate the general structure of the Internet,
-% (scale-free structure, customer-provider, and peer-to-peer relations)
-We extracted the largest connected component comprising of 562 nodes from this original topology and separated the nodes into three categories: clients, gateways, and backbones.
-Nodes having degree less than four were classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients were classified as gateways (109 green nodes), and the remaining nodes were classified as backbones (109 blue nodes).
-%(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
-We assigned bandwidth and delay values to links based on their type---both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
-We experimented with placing the data producer at both a gateway node as well as backbone node, which we randomly picked for each simulation run.
-Similar to the binary tree topology experiments, we fixed the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly picked these nodes for each simulation run.
-We conducted 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5-minute interval.
-
-\begin{figure}[t]
-  \centering
-  % \vspace{-.1cm}
-  \includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
-  % \vspace{-0.3cm}
-  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
-  \label{fig:large-scale-topo}
-\end{figure}
-
-\begin{table}[t]
-\centering
-\caption{Large-scale topology link bandwidth and delay ranges}
-% \vspace{-0.3cm}
-\label{tab:large-scale}
-\begin{tabular}{|l||c|c||c|c|}
-  \hline
-  \multirow{2}{*}{\bf Link type} &  \multicolumn{2}{|c||}{\bf Delay} &  \multicolumn{2}{|c|}{\bf Bandwidth} \tabularnewline
-  \cline{2-5}
-                        &  Min & Max                       &  Min & Max \tabularnewline
-  \hline \hline
-  Backbone--Backbone    & 5~ms & 10~ms   & 40~Mbps & 100~Mbps \tabularnewline
-  \hline
-  Gateway--Backbone,    & \multirow{2}{*}{5~ms} & \multirow{2}{*}{10~ms}   
-                        & \multirow{2}{*}{10~Mbps} & \multirow{2}{*}{20~Mbps} \tabularnewline
-  Gateway--Gateway      & & & & \\
-  \hline
-  Client--Gateway       & 10~ms & 70~ms   & 1~Mbps  & 3~Mbps \\
-  \hline
-\end{tabular}
-% \vspace{-0.3cm}
-\end{table}
-
-%Priya: Leaving out this in the interest of space...
-%Topological location of the data producer plays a key role in its resilience to Interest flooding attacks.
-For a data producer that %is connected to a client node via a low-bandwidth link, even a small number of junk Interests can impact services for legitimate %users.
-For a producer located at the backbone with rich connectivity through many high-bandwidth links, an attack might not %be as severe as a majority of legitimate users might not be on the attack path.
-
-% The results for all attack mitigation algorithms and all runs are aggregated in Fig.~\ref{fig:small-scale attack progress}, where Y-axis represents a minimum and maximum range for observed Interest satisfaction percentages among all nodes and all simulation runs.
-% A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
-
-In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over all simulations runs for each mitigation algorithm for the scenario where the data producer is placed at a gateway node.
-We observe similar results for the data producer placed at a backbone node as well.
-Unlike the binary-tree topology experiments, we observe that
-both the token bucket with per interface fairness and satisfaction-based Interest acceptance have poor performance, while the satisfaction-based pushback is still the most effective algorithm.
-Interest satisfaction percentage for legitimate users are close to 30\%, 25\%, and 100\% respectively for these mitigation methodologies.
-
-%
-%The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
-
-\begin{figure}[t]
- \centering
- \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
- % \vspace{-.3cm}
- \caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}
- % producer on a gateway node
- \label{fig:large-scale}
- % \vspace{-.7cm}
-\end{figure}
-
-Satisfaction-based Interest acceptance algorithm, which was very effective for binary-tree topology, is completely ineffective when deployed in a larger and more realistic topology.
-For the duration of the attack, legitimate users experience poor quality of service with only 25\% of their Interests being satisfied and continue to experience degraded service long after the attack has stopped.
-This poor performance, as detailed in Section~\ref{sec:probabilistic}, is due to the fact that each router on the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
-In the case of a large topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics and further penalization of new Interests from them.
-
-All our evaluations leave us to conclude that among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most promising one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
-%The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
-As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.
-
-% Alex: Anything else here?
-
-% Alex: I also experimented with placing producer at the backbone, getting slightly better results for all algorithms.  Though I'm not sure there is any value to put those results in the paper
-
-% \input{simulation-emulation.tex}
-
-\subsection{Limitations}
-%{\color{red} I gave up the idea of seperate discussion section after trying for some time, as given the space limitation, there is no way to write a reasonably comprehensive and  broad discussion section that justifies a separate section.
-Instead, I decided to have a scoped down version here that confesses upon the limiations of our evaluations only.
-Whoever has time (I need to sleep few hours), please go ahead and write 1-2 paragraphs as I outlined below.
--Ersin}
-
-%This section should roughly say: Our results show that the two features, namely the symmetric traffic and stateful routing, give NDN routers the ability to observe and characterize traffic in real time.
-Through our evaluations, we demonstrated that a mitigation algorithm that leverages such ability has great potential in mitigating various DDoS attacks that could otherwise have grave effect on the network.
-However, as the first step in exploring the problem and the solution space, this paper has obvious limitations: (1) We assume a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations.
-Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step is evaluating the above described solutions with more sophisticated and adaptive attackers.
-(2)   Although most (such as single-path routing, no-caches in the network, single homed victim, etc) are aimed to test the proposed solutions under worst-case scenario, we made many assumptions in simulations/evaluations about the configurations, topology and the traffic that maybe poor-representative of realistic conditions.
-(3) As NDN being an ongoing research effort itself, our evaluations fully depend on simulations and done over a snapshot of its codebase.
-
-% The main contribution of the paper and this section in particular is a proof that two inherent properties of NDN architecture, namely the symmetric traffic and stateful forwarding, give NDN routers the ability to characterize traffic and react in real time.
-% We demonstrated that satisfaction-based pushback algorithm, leveraging this ability, has great potential in mitigating various DDoS attacks that could otherwise have a grave effect on the network. 
-% However, as the first step in exploring the problem and the solution space, our paper has obvious limitations.
-% First, we assumed a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations. 
-% Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step that we are leaving out for future work is evaluating the above described solutions with more sophisticated and adaptive attackers.
-% Second, while aiming to test the designed algorithms under worst-case conditions, the future work needs to address behavior in more realistic scenarios, including investigation of multi-path routing, in network caches, as well as multi-homed victims.
-
-This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space. 
-To design our mitigation algorithms we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
-We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology, % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
-as well as a more realistic ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network. 
-While our results are promising and show a great potential in mitigating Interest flooding DDoS attacks, there are certain limitations which should be addressed in future research.
-
-First, in our evaluations we used a simple and static attacker model---attackers send junk Interests as fast as possible. 
-In future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and Interest sending patterns based on the network reaction. 
-Second, we assumed that Interests are not satisfied by an intermediate router's cache and always forwarded all the way to the producer.  
-In future, we plan to study the impact of Interest flooding attacks in more realistic scenarios with multi-path routing enabled, more realistic traffic patterns, and the presence of in-network caches.
-% We also ignored NDN's strategy layer that routes around failure and congestion in the network. 
-% In future work, we plan to study the impact of turning on these features. 
-%Finally, we also plan to perform more extensive simulations on other realistic Internet-like topologies and traffic patterns.
-
-\section{Related work}
-\label{sec:related-work}
-
-As a new Internet architecture proposal, Named Data Networking has attracted a limited attention from the security community. 
-Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
-W\"ahlisch et al.~\cite{Wahlisch:2012:Backscatter-from} explore security and stability threats in the general area of information-centric networks (ICN), using CCNx software as an example.  
-While this work aims to generalize findings for all ICNs, it largely does not go beyond the current design choices of CCNx.
-% (which is an example, but not the final word in NDN) 
-% Gasti et al.~\cite{gasti2012ddos} identified several NDN architecture-specific attacks (Interest flooding and content/cache poisoning) and proposed potential solutions, without devising particular algorithms.
-In this paper we follow the suggestions by Gasti et al.~\cite{gasti2012ddos} and utilize the properties provided by the NDN architecture to mitigate DDoS attacks, and tackle the Interest flooding problem as a first step in this direction.
-More specifically our attack mitigation design relies on NDN's stateful forwarding plane that allows us to
-maintain statistics on unsatisfied Interests.  
-Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr,Yi:2013:A-Case-for-Stateful} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
-
-The general area of mitigating denial of service attacks is amongst the hottest topics in recent years.
-% Among all the body of work, 
-The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushing back malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
-overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
-various ticketing systems with conditional admission of traffic in to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
-and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
-Identifying malicious traffic requires establishing certain state at routers, and the above mentioned solutions differ in the specifics on what state to use and how to establish it.
-By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions---we simply take full advantage of this state to develop desired solutions.
-
-% Our design for the Interest flooding attack mitigation borrows
-
-% This paper talks about attacks on content centric infrastructure (not specifically to NDN).
-% \cite{Wahlisch:2012:Backscatter-from}
-
-% % Collaborative detection of DDoS attacks over multiple network domains
-% \cite{Chen:2007:Collaborative-detection} distributed change-point detection
-
-% % DDoS flooding attack detection through a step-by-step investigation
-% \cite{Jun:2011:DDoS-flooding}
-
-% % A practical method to counteract denial of service attacks
-% \cite{Tupakula:2003:A-practical-method}
-
-% Alex: We should not include this reference for the review, but afterwards
-% Previous work on DDoS and DoS~\cite{gasti2012ddos}
-
-% Network level (Flooding)
-% % 2002
-% Pushback~\cite{Pushback} (hop-by-hop push back) aggregate- based congestion control/congestion signatures (e.g., per-destination), rate-limiting, explicit notification
-% AITF~\cite{Argyraki:2005:Active-internet} (active filtering requests; path recording, last-point of trust detecting)?
-% DefCOM \cite{Oikonomou:2006:A-framework-for-a-collaborative} Communication between src, core, and dst to provide collaborative defense.
-Dst raises alerts, src differentiate bad/good, packet tagging.
-Core rate-limit, congestion-aware re-tag.
-Traffic prioritization.
-% StopIt \cite{Liu:2008:To-filter-or-to-authorize:} (filtering) tagging with passports, tagged prioritization, dst- invoked filter instantiation
-% NetFence \cite{Liu:2010:NetFence:-preventing} congestion policing: fair queuing (one leaky bucket per {src,L}, L- bottleneck), secure "ticketing" with signals for AIMD to increase/decrease bandwidth allowance
-% PSP \cite{Chou:2009:Proactive-surge} topology as origin-destination pairs, packet tagging, OD traffic isolation, sharing based on historic bandwidth demand
-
-% SIFF~\cite{Yaar:2004:SIFF:-A-stateless} (time-based tickets, capabilities)
-% TVA \cite{Yang:2005:A-DoS-limiting-network} like SIFF, traffic- based tickets, hierarchical per- AS, per-source fair queuing
-% FastPass \cite{Wendlandt:2006:Fastpass:-Providing} (tokens: various puzzles, other methods) traffic authorization, routers verify and filter.
-% \cite{Natu:2007:Fine-grained-capabilities} based on TVA/SIFF: specifies previously unspecified mechanisms to grant "tickets" for requesters, extends capabilities to include priorities, changing tickets to be only destination- dependent, not path dependent
-% % LazySusan \cite{Crowcroft:2007:Lazy-Susan:} TR (latency-based proof of work--- computational puzzles)
-% Portcullis \cite{Portcullis} Protecting connection setup with computational proof of work, tickets and traffic prioritization for the rest, per- computational fairness; DNS to disseminate puzzles
-% There are many other puzzle- based schemes, on which Portcullis is based or which problems it solves
-
-% PacketSymmetry \cite{Kreibich:2005:Using-packet} (leverages packet symmetry to detect and remove bad traffic) packet asymmetry - number of transmitted packets (tx) to received packets (rx); negative values when rx outweighs tx, positive values when tx outweighs rx, and zero in the case of perfectly balanced traffic)
-% % Detecting SYN flooding attacks
-% \cite{Wang:2002:Detecting-SYN-flooding} based on the protocol behavior of TCP SYN-FIN (RST) pairs, and is an instance of the Seqnential Change Point Detection
-% dFence \cite{Mahimkar:2007:dFence:-Transparent} (middleboxes) TCP connection proxying, rate estimation and TCP/ACK modification
-
-% Overlays:
-% CenterTrack \cite{Stone:2000:CenterTrack:-An-IP-overlay} (overlay) reroute suspicious traffic to a special routers with diagnostic capabilities using an overlay
-% SOS \cite{Keromytis:2004:SOS:-An-architecture}
-% Shield \cite{Kline:2011:Shield:-DoS-filtering}
-
-% NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
-In this section we will overview generic directions of DDoS mitigation designs and try to think about which tricks could be used in NDN.
-
-% Capability-based systems allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
-Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
-This implies that each client must pass through an authentication process prior to using any bandwidth~\cite{Capabilities}.
-We believe that for NDN this method doesn't fit really well for the following reasons.
-First, this method is very questionable in terms of scalability and mobility support since it requires tight trust connections between routers and hosts.
-Thus, it neglects one of the main advantages (mobility) of NDN.
-Second, the design of trust infrastructure for NDN is not well defined yet, which means that we cannot really make assumptions in our design of mitigation techniques.
-
-% Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
-Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients.
-One of the main difficulties in such systems is the question of puzzle dessimination.
-In ~\cite{Portcullis} authors suggested to propagate puzzles using DNS system.
-In NDN since routers have caching abilities, we can propagate puzzles just like a normal data packets, using Interest-Data exchange.
-Overall, this method looks interesting and deserves being investigated in a future work.
-
-% Congestion control systems do per flow traffic analysis and drop of packets belonging to misbehaving flows.
-For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
-Such techniques, if largely deployed, could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
-Since NDN routers maintain a richer per-packet state, which translates into a better per-flow statistics, these techniques can become much more effective when applied to NDN.
-
-% Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
-This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines~\cite{Pushback}.
-In general this technique can be applied to NDN architecture thanks to its decentralized coordination of downrating bad traffic flows.
-Moreover, NDN provides better capabilities for accurate flow detection.
-
-%were looking for getting accustomed
-
 \section{Conclusion}
@@
 Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.
-
-\bibliographystyle{IEEEtran}
-\bibliography{references}
-
-\end{document}

### 2013-05-13 ifip-ddos.tex
Splitting paper back to its normal organization

--- 2013-03-26 paper.tex
@@
 
-% \usepackage[top=.75in, bottom=1in, left=.625in, right=.625in]{geometry}
 \usepackage{graphicx}
@@
 \usepackage[nocompress]{cite}
-% \usepackage{verbatim}
-% \usepackage{algpseudocode}
 \usepackage[noend]{algpseudocode,algorithm}
-% More customizeable version. Probably it would be better to convert pseudocode to 2e format
-% \usepackage{algorithm2e} 
 \usepackage{multirow}
@@
 
-\begin{document}
+\usepackage{eso-pic,xcolor}
+\makeatletter
+\AddToShipoutPicture*{%
+\setlength{\@tempdimb}{20pt}%
+\setlength{\@tempdimc}{\paperheight}%
+\setlength{\unitlength}{1pt}%
+\put(\strip@pt\@tempdimb,\strip@pt\@tempdimc){%
+    \put(10,-10){\parbox[t]{\textwidth}{\color{blue}%
+\copyright\ IFIP, 2013.
+This is author's version of this work.
+It is posted here by permission of IFIP for you personal use.
+Not for redistribution.
+The definitive version was published in the proceedings of IFIP Networking 2013.}}
+  }%
+\put(\strip@pt\@tempdimb,\strip@pt\@tempdimc){%
+  }%
+}
+\makeatother
 
@@
 
+\begin{document}
+
 \maketitle
 
-\begin{abstract}
-Distributed Denial of Service (DDoS) attacks are an ongoing problem in today's Internet, where packets from a large number of compromised hosts thwart the paths to the victim site and/or overload the victim machines.
-In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network delivers Data packets upon request only, effectively eliminating many existing DDoS attacks.
-However, an NDN network can be subject to a new type of DDoS attack, namely Interest packet flooding.  
-In this paper we investigate effective solutions to mitigate Interest flooding.
-We show that NDN's inherent properties of storing per packet state on each router and maintaining flow balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
-Our evaluation through simulations shows that the solution can quickly and effectively respond and mitigate Interest flooding.
-\end{abstract}
+\input{00-abstract}
 
-\begin{IEEEkeywords}
-Information-centric networks, named-data networking, denial-of-service
-\end{IEEEkeywords}
-
-\section{Introduction}
-\label{sec:intro}
-
-Named Data Networking (NDN)~\cite{ndn-conext, ndn-tr} is an ongoing research effort that aims to move the Internet into the future with a content-centric design that is capable of efficient content distribution and seamless mobility support.
-In contrast to today's Internet, a key goal of the NDN project is ``security by design." In fact, it goes a long way by guaranteeing the integrity and provenance of every Data packet with digital signatures and protecting user-privacy with no source addresses carried in the packets.
-However, one big question that is yet to be answered is: how does the NDN architecture fare in terms of its resilience against DDoS attacks?
-Especially since various forms of DDoS attacks pose a significant threat to the existing Internet infrastructure~\cite{arbor-report}, it is crucial to ensure that the new design is free of similar vulnerabilities.
-
-NDN eliminates host-based addressing and makes data the first-class network entity.
-Instead of sending packets to a given IP address, NDN nodes request desired data by sending Interest packets carrying application-level data names, and the network returns the requested Data packets following the path of Interests.
-Such a shift automatically eliminates several long-standing DDoS attacks, including direct flooding and reflector attacks through source address spoofing~\cite{mirkovic2004taxonomy}.
-%
-However, malicious users can attack the network by sending an excessive number of Interests. 
-Since each Interest consumes resources at intermediate routers as it is routed through the network, an excessive number of Interests can congest the network and exhaust a router's memory. 
-We coin the term {\it Interest flooding} to refer to such attack and
-this paper exclusively investigates the problem and the solution space for it.
-
-Our effort is an important first step towards a complete investigation of DDoS attacks in NDN.
-We experiment with three algorithms that allow routers to exploit their state information to thwart these attacks.
-Through extensive simulations, we show how one of our mitigation methodologies effectively shuts down malicious users while preventing legitimate users from service degradation.
-The rest of the paper is organized as follows.
-We provide an overview of NDN architecture in Section~\ref{sec:ccn-intro} and describe Interest flooding attacks in Section~\ref{sec:interest-flooding}.
-In Sections~\ref{sec:design} and \ref{sec:evaluation} we introduce techniques to mitigate these attacks, evaluate their effectiveness, and discuss their limitations.
-We summarize related work in Section~\ref{sec:related-work}.
-We discuss future work and conclude in Section~\ref{sec:conclusion}.
-
-\section{NDN Overview\label{sec:ccn-intro}}
-
-In this section we briefly introduce NDN with a focus on its stateful forwarding plane (refer to \cite{ndn-conext, ndn-tr, adaptive-forwarding} for more details).
-NDN is a receiver-driven, data-centric communication protocol.
-All communications in NDN are performed using two distinct types of packets: \textit{Interest} and \textit{Data}.
-Both types of packets carry a \textit{name}, which uniquely identifies a piece of content that can be carried in one Data packet.
-Data names in NDN are hierarchically structured and an example name for the first segment of a youtube video would look like: \ndnName{/youtube/videos/0F8YdlkKO9A/0}.
-
-To retrieve data, a consumer requests it by sending an Interest packet with the name of the desired content in it.
-Routers use this name to route the Interest towards data sources, and a Data packet whose name matches the name in the Interest is returned to the consumer by following the reverse path of the Interest.
-Similar to IP, Interest forwarding is based on longest name prefix match, but, unlike IP, an Interest packet and its matching Data packet always take symmetric paths.
-%% An Interest is ``satisfied'' when it is matched with a Data packet.
-
-Each NDN router maintains three major data structures:
-\begin{itemize}
-\item \textit{Pending Interest Table (PIT)} holds all ``not yet satisfied'' Interests that have been sent upstream towards potential data sources.
-Each PIT entry contains one or multiple incoming and outgoing physical interfaces; multiple incoming interfaces indicate the same data is requested from multiple downstream users; multiple outgoing interfaces indicates the same Interest is forwarded along multiple paths.
-\item \textit{Forwarding Interest Base (FIB)} maps name prefixes to one or multiple physical network interfaces, specifying directions where Interests can be forwarded. 
-% Having one-to-many relationship in this table allows multipath forwarding of Interests.}
-\item \textit{Content Store (CS)} temporarily buffers Data packets that pass through this node, allowing efficient data retrieval by different consumers.
-\end{itemize}
-
-When a router receives an Interest packet, it first checks whether there is a matching data in its CS.
-If a match is found, the Data packet is sent back to the incoming interface of the Interest packet.
-If not, the Interest name is checked against the entries in the PIT. 
-If the name already exists in the PIT, then it can be a duplicate Interest (identified by a random number each Interest carries) that should be dropped,
-or an Interest from another consumer asking for the same Data, which requires the incoming interface of this Interest to be added to the existing PIT entry.
-If the name does not exist in the PIT, the Interest is added into the PIT and forwarded along the interface chosen by the strategy module, which uses FIB as input for its decisions.
-
-When a Data packet is received, its name is used to look up the PIT.
-If a matching PIT entry is found,
-the router sends the Data packet to the interface(s) from which the Interest was received, caches the data in the CS, and removes the PIT entry.
-Otherwise, the Data packet is deemed unsolicited and is discarded.
-Each Interest also has an associated lifetime; the PIT entry is removed when the lifetime expires.
-Although the maximum lifetime is specified by users, it is ultimately a router's decision on how long it is willing to keep a PIT entry.  
-For simplicity, we assume routers keep Interests in PIT for one second in our simulations.
-
-\section{Interest Flooding Attacks in NDN}
-\label{sec:interest-flooding}
-
-As we explained earlier, Interest packets in NDN are routed through the network based on content name prefixes and consume memory resources at intermediate routers.
-This makes them a potential tool to launch DDoS attacks in NDN.
-An attacker or a set of distributed attackers can inject excessive number of Interests in an attempt to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{attack-definition}
-  \caption{Example of Interest flooding attack}
-  \label{fig:flooding example}
-  \vspace{-0.3cm}
-\end{figure}
-
-Since an NDN network fetches data by its name, an adversary cannot easily target specific routers or end-hosts.
-However, an adversary can target a specific namespace.
-For example in Fig.~\ref{fig:flooding example}, if the data producer is the exclusive owner of \ndnName{/foo/bar} namespace, both router B and the data producer would receive all Interests for \ndnName{/foo/bar/\ldots} that cannot be otherwise satisfied from in-network caches.%
-\footnote {This example assumes that the adversary floods the network with unique data names carrying \ndnName{\small /foo/bar} prefix to make them effective.
-It also assumes the producer is single-homed and the data is not replicated elsewhere.
-With multi-homed producers or replicated data, NDN would likely to cope better with DDoS attacks due its native multipath and adaptive forwarding~\cite{adaptive-forwarding} support.}
-A large volume of such malicious Interests can disrupt service quality in NDN network in two ways: \emph{create network congestion} and \emph{exhaust resources on routers}.
-
-Similar to packets in traditional networks, Interest packets in NDN consume a portion of network capacity.
-A large number of Interest packets might cause congestion and lead to legitimate packets being dropped in the network.
-In particular, a coordinated DDoS attack could target one specific namespace and concentrate attack traffic in certain segments of the network as routing in NDN is based on name prefixes.
-
-As NDN routers maintain per-packet states for each forwarded Interest (i.e., an entry in its PIT), an excessive amount of malicious Interests can lead to exhaustion of a router's memory, making the router unable to create new PIT entries for incoming Interests and disrupting service for legitimate users.
-
-Nevertheless, creating an effective Interest flooding attack in NDN is non-trivial.
-To efficaciously target a specific namespace (e.g., \ndnName{/newyorktimes/}), an adversary needs to make sure that (1) the expressed Interests are routed towards and as close to the data producer/provider as possible, and (2) new corresponding PIT entries are created for those interests and are stored at intermediate NDN routers for as long as possible.
-The former is achieved when interests share the same name prefix (e.g., \ndnName{/newyorktimes/}) and as long as they are not served from caches of intermediate routers---an interest is not forwarded upstream if a router can satisfy it from its content store.
-The latter requires every single malicious Interest to ask for a unique content---all Interests requesting the same content are collapsed to one PIT entry in routers.
-Thus, an adversary has to request either an unpopular (i.e., not cached in routers) or non-existing unique content with each Interest.
-Of the two options available to an adversary, the first one is challenging due to the difficulties around indexing content names in a particular namespace, coordinating a large number of bots to send unique Interests and sustaining the attack while the network is continuously caching the requested content objects.
-However, the second option {\it i.e.} requesting unique non-existing content with each Interest, is easy to achieve and sustain.
-An adversary can construct such Interests by concatenating a random name component to the victim namespace (e.g.,\ndnName{/newyorktimes/fgb...3rf3}) and can increase the memory usage at each router by lengthening the random component.
-In this paper, we exclusively focus on this particular attack strategy as it not only maximizes the damage from each malicious Interest but also is the one that is easy to launch and widely applicable to all namespaces (small or large).
-% other less effective strains of Interest flooding attacks can also be mitigated by applying the same or similar countermeasures described in the next section.
-
-In the rest of this paper, we use the general term \emph{Interest flooding attack} to refer to the above described attack and assume an attacker is limited to controlling a botnet of end-hosts only, i.e., we assume the routers in the network and the computers in the victim domain are not compromised.
-
-%\paragraph{Assumptions} 
-%E: These are assumptions for the simulations on hand and particulary to test for the worst case scenario in many aspects.
-They are not the paper's assumption and in fact the paper first should be more general on describing all possibilities.
-Then it should explain the assumptions for the simulations and discuss why they make sense and do NOT favor positive results in some way.
-
-% - assumptions about attacker position
-% - assumptions about the producer / producer namespace
-% - assumptions about the attack traffic / attack pattern
-
-%In this paper we are making the following assumptions about the Interest flooding attack:
-%\begin{itemize}
-%\item only client nodes can be compromised and become attack bots;
-%\item there are no colluding attackers inside the Data producer's network;
-%\item the attack is carried only using unique junk Interests; and
-%\item there is only one Data producer for the attacked prefix.
-%\end{itemize}
-
-%We also assume that NDN forwarding strategy uses only single-path Interest forwarding, always choosing the best-metric route advertised by the routing protocol.
-%This way, we are able to analyze the attack in its best environment, as enabling the multi-path forwarding would only alleviate effects of the Interest flooding attack.
-
-%In section~\ref{sec:discussion} we discuss potential of the Interest flooding attack under several other attack assumptions.
-
-\section{Interest flooding mitigation methods}
-\label{sec:design}
-
-% Points what should be here:
-% - What can be done (in general) to mitigate flooding attack
-% - Which building blocks NDN architecture gives to mitigate Interest flooding attacks: Interest limits, ability to measure Interest satisfaction performance (Interest satisfaction stats)
-% - Methods to set these limits: static/dynamic
-% - Methods how limits can be applied: best-effort (fifo), "fair" queuing, probabilistic
-% - Reference to caching: we don't consider it here, but caching provides additional level of protection, especially for certain types of attacks
-
-% Our definition of attack mitigation is that good clients are still able to access data on the producer.
-
-In this section we present several algorithms to mitigate Interest flooding attacks in NDN.
-Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks.
-We start by describing our simple strategies and use the insights and lessons learned from the deployment of these to inform and design more effective mitigation techniques that work well in various topologies.
-
-%   - Naive approach to Interest Limits (that is called physical limits everywhere else)
-%     Example how this can be implemented in a simple way
-%     Baseline solution
-%   - Interest limits with "fair" queuing
-%     Improving problem of simple limits (no single face can dominate), but doesn't solve the proble
-
-% - Attack mitigation
-%   - Per-incoming interface Interest statistics
-
-%   - Dynamic Interests limit adjustments
-
-%   - Probabilistic Interest accept
-
-%The fact that each Data packet takes the reverse path of the corresponding Interest packet allows intermediate routers to match a received Data packet to the corresponding Interest packet and %thus determine which Interest packets were satisfied.
-As we describe in the rest of this section,  NDN routers can exploit this information to make informed decisions on which Interest packets to %forward, how many Interest packets to forward, and thus effectively defend against DDoS attacks.
-
-%Our methods to mitigate Interest flooding attack rely on the fundamental principle of the NDN architecture: the flow balance between Interest and Data packets: one Interest packet (the only communication initiator) can be satisfied with at most one Data packet.
-%Because NDN is host-to-host architecture (as opposed to end-to-end in the current IP Internet), the flow balance principle allow any entity on the network, end-hosts and routers, control what and how much Data they want to receive.
-%Therefore, any node can limit the number of forwarded Interests, effectively limiting the amount of the retrieved Data.
-%At the same time, each forwarded Interest can be used to build up various data plane performance statistics, such as per-incoming interface ratios of satisfied Interests.
-
-%\subsection{Na\"{i}ve attack mitigation}
-
-%We start with a couple of naive strategies that can be used to migitate attacks in an NDN network and describe the pitfalls associated with these strategies.
-
-% In a normal network operation, the size of Interests packets is supposed to be significantly smaller than the size of the requested Data.
-
-% All communication in NDN network is host-to-host and receiver-driven.
-
-An obvious and na\"ive solution to defend against Interest flooding attacks is to restrict the number of Interests forwarded through the network. To this end, we exploit a 
- fundamental principle of NDN architecture---flow balance between Interest and Data packets.
-Flow balance refers to the fact that one Interest can be satisfied by at most one Data packet.
-This principle allows intermediate routers to control the inbound data traffic by controlling the number of outstanding Interests in the network.
-One simple implementation technique  is for an NDN router to limit the number of forwarded Interests out of each interface based on the physical capacity of the corresponding interface.
-This technique is a slight modification of the well-known {\it Token Bucket} algorithm that is currently widely used in packet-switched networks.
-Analogous to the {\it Token Bucket} algorithm, NDN routers keep track of the amount of data requested that can fully utilize the downstream link (estimated from the number of forwarded Interests) and once the link capacity limit has been reached, they no longer forward new incoming Interests.
-Ideally, the number of tokens (the pending \emph{Interest Limit}) for each link will be proportional to the link's bandwidth-delay product (BDP)~\cite{tcp-survey}.
-We can formalize this value as follows:
-% With the objective to request as many Data packets, as downstream link can pump through, we are getting the following equation for Interest limit:
-%
-\begin{equation}
-\label{eq:interest limit}
-\small \mathrm{Interest\ Limit} = Delay\ [s] \cdot \frac{\mathrm{Bandwidth\ [Bytes/s]}}{\mathrm{Data\ packet\ size\ [Bytes]}}
-\end{equation}
-
-In the above equation, \emph{Delay} is the expected time for the Interest to be satisfied and \emph{Data packet size} is the size of the returning Data packet.
-Although both these values are not known a priori, it is not really necessary to use their exact values.
-One can simply set the pending Interest limit based on the average values of round trip time and observed Data packet size, as network buffers can smooth out most of the network fluctuations.
-
-This {\it Token Bucket} approach might be exceptionally restrictive in forwarding Interests---not all Interests will result in a Data packet---and might result in underutilization of the network.
-However, the biggest drawback of this algorithm is the fact that it can nourish DDoS attacks.
-If a router has utilized all its tokens to forward malicious Interests, it can no longer forward incoming Interests from legitimate users till the pending malicious Interests start to expire.
-One way to get around this issue is to impose a per interface limit, so that malicious Interests are not allowed to entirely consume the limits of a specific interface.
-We describe this technique in greater detail below.
-
-%That is, if it is known that the amount of already requested data ($=$~amount of forwarded Interests) can fully utilize the downstream link, an NDN node---either an end-user or an NDN router---has absolutely no point in forwarding new incoming Interests and creating corresponding PIT entries.
-%For example, if a router A on Fig.~\ref{fig:flooding example} already forwarded 125 Interests requesting 1000-byte Data packets, any new incoming Interests can be almost safely dropped, provided the link capacity between A--B is 100~Mbps and delay is 10~ms.
-%In other words, 125 Data packets returned by router B will fully utilize the link ($125 \times 1000 \mathrm{~bytes} \approx 10\mathrm{~ms} \times 100\mathrm{~Mbps}$) and any excess Data would be dropped.
-%
-%\subsubsection{\textbf{Interest limits (physical limits)}}
-%\label{sec:physical limits}
-%
-%\input{algos/physical-limits.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Token bucket with per interface fairness}}
-\label{sec:queuing}
-
-To address the lack of fairness associated with the na\"ive {\it Token Bucket} approach, we modify it to ensure that the Interests forwarded by a router on each interface represent a fair mix of Interests received from neighboring nodes.
-For example, in Fig.~\ref{fig:flooding example} router A can ensure that the tokens associated with Interests sent out on interface {\texttt eth2}  are fairly distributed across incoming interfaces \texttt{eth0} and \texttt{eth1}.
-%Due to the expected small volume of Interests, we cannot merely rely on network buffers to perform statistical multiplexing of Interests, as they would almost never be %buffered.
-%At the same time, until bag of tokens is not empty, there is no reason to delay Interest forwarding, as we do not known how many and from which interfaces Interests %will arrive in the future.
-In order to achieve our goal of ensuring ``fair'' mixing of Interests from all neighboring nodes, 
-%, we implement an additional features to support buffering of Interests, if they cannot be immediately forwarded. 
-we extend the Pending Interest Table to support flagging of Interests that cannot be immediately forwarded and implement hierarchical queues for each interface (see Fig.~\ref{fig:queueing}). 
-This mechanism is essentially a class based queuing~\cite{floyd1995link}, with classes for each outgoing and incoming interface.
-%As an alternative to hierarchical queues, one can also use an approach based on virtual time. For details, please see ~\cite{zhang1990virtual}.
-We note that unlike normal queuing, Interest queues do not actually store a packet, but merely a bi-directional pointer to the existing PIT entry.
-Thus, a PIT entry can be quickly updated when the Interest is actually forwarded, and the element can be easily removed from the queue when the Interest expires.
-
-%For the buffering part, we can reuse Pending Interest Table, with a small extension to support flagging of the Interests that cannot be forwarded immediately (see example on Fig.~\ref{fig:queueing}).
-%As for the mixing part, we need an additional fair queuing mechanism, which can be implemented in a form of hierarchical queues (on Fig.~\ref{fig:queueing})\footnote{This essentially is a class based queuing, with classes for each outgoing/incoming interface.} or using virtual time approach~\cite{zhang1990virtual}.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.6]{queue}
-  \caption{Interest queuing: if tokens are unavailable, the router creates a PIT entry, but instead of forwarding, it enqueues the Interest}
-  \label{fig:queueing}
-  \vspace{-0.3cm}
-\end{figure}
-
-We present a formalized description of this algorithm in Pseudocode~\ref{alg:queuing}. 
-By setting appropriate queue sizes, we can control the amount of physical resources utilized at a router.
- % (such as memory and computation power). 
-It is also important to set a sensible value for how long an Interest can be enqueued. 
-If an Interest is enqueued for a long time, by the time it is dequeued and forwarded, the retrieved Data packet might be dropped at the downstream routers if their corresponding state expired. 
-For our evaluations, we empirically chose to enqueue Interests up to 10\% of their original lifetime.
-% We believe that implementing additional mechanisms on each pair of communicating routers to keep the Interests from getting stale would mitigate this issue, though the details are beyond the scope of this paper.
-% Alex: I don't believe there is a need for separate discussion about "freshness", as we already introduced concept of lifetime
-% {\color{red} \it Priya:  We need to  touch upon the Interest freshness issue in the NDN overview section; else we should get rid of this bit.}
-
-%It should be noted that enqueued Interests should not be kept in the queue for a prolonged period of time.
-%Otherwise, by the time the Interests reaches the Data, the state could have been long expired downstream, effectively making such an Interest useless.
-%Additional mechanisms of pair-wise agreements between NDN routers and periodic Interest refresh can solve this particular problem, but it is out of the scope of the present paper.
-
-%The algorithm extends the base Physical limits algorithm by enabling queuing when the bag of tokens is empty (lines 7--10), as well as by triggering an action (lines 16--21), when a token becomes available and enqueued Interest can be finally forwarded.
-%At the same time, the algorithm limits number of Interests allowed in a queue, constraining memory usage increase by at most a constant factor, compared to the base Physical limits algorithm (i.e., memory attack on routers are still unfeasible).
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[h]
-\footnotesize
-\caption{\small Token bucket with per interface fairness}
-\label{alg:queuing}
-\begin{algorithmic}[1]
-\For{\textbf{each} interface \textbf{if}}
-    \State{$L_{if} \leftarrow$ Interest Limit according to (1)}
-    \State{$O_{if} \leftarrow 0$} \Comment{Outstanding Interests on interface \textbf{if}}
-\EndFor
-
-\vspace{0.1cm}
-
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
-    \If{$L_{out} - O_{out} > 0$} \Comment{\textbf{out} is under limit cap}
-        \State $O_{out} \leftarrow O_{out} + 1$  \Comment{``borrow'' a token from the bucket}
-        \State add \textbf{out} to PIT entry and forward \textbf{i} to \textbf{out}
-    \Else
-        \State Queue $q \leftarrow out$.GetSubQueue($in$)
-        \If{$Size(q) < L_{out}$}
-           \State $q$.PushInterest($i$)
-           \State add \textbf{out} to PIT entry, and link PIT entry with the queue
-        \Else
-           \State drop Interest
-        \EndIf
-    \EndIf
-\EndFunction
-
-\vspace{0.1cm}
-
-\State{} \Comment{\textit{Whenever $L_{out} - O_{out}$ becomes larger than zero}}
-\Function{TokenBecomesAvailable}{}
-    \State Queue $q \leftarrow$ $out$.GetRoundRobinSubQueue 
-    \State Interest $i \leftarrow$ $q$.PopInterest
-    \State update PIT entry and Forward($i$, $out$)
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{InData}{Data \textbf{d}}
-   \State lookup PIT entry \textbf{p} for data \textbf{d}
-   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
-        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
-   \EndFor
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{Timeout}{PIT entry $p$}
-   \For{\textbf{each} outgoing interface \textbf{out} in \textbf{p}}
-        \State $O_{out} \leftarrow O_{out} - 1$ \Comment{``return'' token}
-   \EndFor
-\EndFunction
-
-\end{algorithmic}
-
-\end{algorithm}
-
-As we show in Section~\ref{sec:evaluation}, this algorithm provides partial relief from Interest flooding attacks, allowing legitimate users to successfully fetch Data for 15--20\% of their expressed Interests.
-We note that while this algorithm might be reasonable for ensuring limited fairness in an NDN network, it is ineffective in protecting legitimate users from malicious ones. 
-Attackers are able to successfully thwart access to content for legitimate users by sending a relatively modest volume of malicious Interests.
-
-%At the same time, the Physical limits with or without fair queueing allows attackers to send a relatively small volume of Interests in order to significantly impact service for the legitimate users.
-%Therefore, to successfully solve the problem, we need a fundamentally different, more intelligent approach, allowing localization of the attack traffic as close as possible to the attack origin.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-The key drawback of the {\it Token bucket with per interface fairness} algorithm is that it still admits a relatively large number of Interests from malicious users.
-A considerable percentage of these malicious Interests are forwarded all the way to content producers, thereby reducing resources available to serve legitimate users.
-This algorithm attempts to ensure that each interface does not forward more than its fair share of Interests, but in doing so, it drops both legitimate and malicious Interests.
-For any strategy to be effective in defending against Interest flooding attacks, it must be able to detect and differentiate malicious requests from legitimate ones.
-% `Good' Interests from legitimate users must be admited and forwarded appropriately. 
-Thus, the key question is how can we devise mitigation algorithms that allow a router to distinguish between `good' and `bad' Interests?
-
-%One can try a black- or whitelisting approach.
-However, besides the fact that source black- and whitelisting cannot work in %NDN as it does not feature source addresses, it requires extraneous knowledge to classify the incoming Interests.
-
-%Priya: I have added the below point specifically to point out that a router cannot determine from the prefix name alone whether /parc is good  or bad...
-
-%{\color{red} \textbf{Alex: This paragraph is confusing to me.
-I would remove it.} In NDN one cannot easily distinguish a `good' prefix from a `bad' one.
-Content producers must be able to support %dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded %to the producer for possible dynamic Data packet generation.
-%Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the prefix name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain %namespaces  will be inefficient and likely ineffective.
-}
-
-% Alex: I'm not sure that this part is relevant... The point I see is that blacklisting and whitelisting is not 100% effective, but it can be used in both worlds
-
-% In today's host-based Internet architecture where DDoS mitigation techniques rely on blacklisting of ``dark'' IP prefixes or whitelisting of good IP prefixes.
-% Unlike IP, in NDN one cannot easily distinguish a `good' prefix from a `bad' one. 
-% Content producers must be able to support dynamic generation of Data packets to satisfy incoming Interest packets---thus, an Interest that cannot be satisfied by matching Data from any intermediate router's cache is necessarily forwarded to the producer for possible dynamic Data packet generation.
-% Thus intermediate routers cannot determine if the prefix is `good' or `bad' based on the name alone---DDoS mitigation techniques that rely on whitelisting or blacklisting of certain namespaces  will be inefficient and likely ineffective.
-
-\subsection{Intelligent attack mitigation}
-\label{sec:intelligent mitigating}
-
-%While the Interest limit is the key building block to suppress mechanisms of the Interest flooding attack, legitimate Interests need to be somehow prioritized and malicious Interests need to be somehow penalized in order to completely suppress the attack.
-%That is, instead of processing Interests always based on the first-in-first-serve rule, NDN routers need some basis to treat the incoming Interests differently.
-%Thus, the primary task in bringing intelligence to the Interest flooding attack mitigation is to proactively distinguish between legitimate and malicious Interests.
-
-In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets.
-Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guaranteed to see if an Interest it forwarded resulted in a matching Data packet or timed out.
-%The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
-Since malicious Interests are not likely to bring data back (as discussed in Section~\ref{sec:interest-flooding}), this information can be utilized by routers in differentiating attack and legitimate traffic.
-%Therefore, intermediate routers can classify the ones that brings data back as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}
-%Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}
-
-This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved.
-However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest should be forwarded or dropped.
-For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to reasonably predict whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout if forwarded.
-Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc.
-that can further improve the estimates.
-A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but don't result in a returning Data packet.
-In order to allow negative statistics to build up fast and positive statistics to  deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.
-
-%Choosing the right balance between these contradictory requirements is a challenge and we explore this topic further  in the evaluation section.
-%{\color{red} \it Priya: we should address the one that works best such as exponentially weighted moving average in eval section - it doesn't belong %here.}
-
-%The devil is always in the details.
-%From the one hand, such statistics needs to start penalizing adversaries as soon as possible (i.e., negative stats should build up fast).
-%On the other hand, the positive statistics should not deteriorate too fast (i.e., positive stats should be relatively long-term).
-%Our preliminary experiments showed that the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window, provides a good balance between the two contradictory requirements.
-
-% \subsubsection{\textbf{Data plane performance tracking}}
-% \label{sec:stats}
-
-% Note that there is a condition (line 6 in Pseudocode~\ref{alg:probabilistic model}) to check if there is a valid statistics point.
-% This condition is extremely important, because it first provides a basis to distinguish between known facts (i.e., good or bad satisfaction ratio for the incoming interface) and unknown facts (e.g., the first time an Interests arrives on the interfaces).
-% Second, it gives an opportunity to recover from a bad history (history of unsatisfied Interests) after malicious Interests are ceased to flow in.
-% Essentially, this recovery relies on statistics module to perform time-based invalidation of historical data (timely, but not too quickly\footnote{Otherwise, attackers may send short bursts of malicious Interests, successfully avoiding differential Interest treatment}).
-
-Pseudocode~\ref{algo:interest stats} formally defines how statistics can be generated for  each incoming interface.
-Note that in order to ensure decaying of relative statistics (e.g., ratio between the number of unsatisfied and forwarded Interests), only unsatisfied statistics needs to be exponentially smoothed (lines 23--26).
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Interest satisfaction statistics}
-\label{algo:interest stats}
-\begin{algorithmic}[1]
-
-\For{\textbf{each} interface \textbf{if}}
-    \State $F_{if} \leftarrow 0$ \Comment{forwarded Interests from interface \textbf{if}}
-    \State $\hat F_{if} \leftarrow 0$ \Comment{averaged value of $F_{if}$}
-
-    \State $U_{if} \leftarrow 0$ \Comment{unsatisfied Interests from interface \textbf{if}}
-    \State $\hat U_{if} \leftarrow 0$ \Comment{averaged value of $U_{if}$}
-\EndFor
-
-\vspace{0.1cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}}
-  \State $F_{in} \leftarrow F_{in} + 1$
-  \State record \textbf{\emph{in}} in the list of incoming interfaces for \textbf{\emph{i}}
-\EndFunction
-
-\vspace{0.1cm}
-\Function{InterestTimeout}{Interest \textbf{i}}
-    \State lookup the list of incoming interfaces for \textbf{\emph{i}}
-
-    \For{\textbf{each} interface \textbf{if} in the list}
-        \State $U_{if} \leftarrow U_{if} + 1$
-    \EndFor
-\EndFunction
-
-\vspace{0.1cm}
-
-\State {} \Comment{\textit{Exponentially weighted moving average smoothing}}
-\Function{EWMA}{} \Comment{Every second}
-\State $\alpha \leftarrow e^{-1.0/30.0}$  %\Comment{$\approx$ 30~sec average}
-
-\For{\textbf{each} interface \textbf{if}}
-    \State $\hat U_{if} \leftarrow \alpha \cdot \hat U_{if} + (1 - \alpha) \cdot U_{if}$ 
-    \State $U_{if} \leftarrow 0$
-
-    \If{$F_{if} > 0$} \Comment{To ensure decaying of ratio $U_{if}/F_{if}$}
-        \State $\hat F_{if} \leftarrow \alpha \cdot \hat F_{if} + (1 - \alpha) \cdot I_{if}$ 
-        \State $F_{if} \leftarrow 0$ \Comment{Reset counters}
-    \EndIf
-\EndFor
-
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-Fig.~\ref{fig:ratio example} illustrates the resulting dynamics of the statistic during and after an Interest flooding attack.
-The attack duration is from 10 to 70~seconds.
-Prior to start of the attack, the percentage of unsatisfied Interests is zero.
-The statistics build up rapidly as soon as Interests start to time out, which happens approximately one second after the start of the attack.
-%\footnote{Again, we are assuming that Interests are admitted for a maximum period one second.}
-For the duration of the attack (10--70~seconds), the percentage of unsatisfied Interests is close to 100\%: 
-when the ratio is close to 100\%, routers drop all incoming Interests, resulting in decaying of the statistics until a new Interest is admitted, which eventually brings statistics back near 100\% point.
-Finally, the ratio exponentially decays after the attack ceases.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.8]{limits}
-  % \vspace{-0.3cm}
-  \caption{Dynamics of  unsatisfied Interests statistics on a gateway's interface towards the attacker}
-  \label{fig:ratio example}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Satisfaction-based Interest acceptance}}
-\label{sec:probabilistic}
-
-Having successfully implemented a technique to gather statistics on Interest satisfaction ratios, our next challenge is in using these ratios to penalize malicious Interests.
-A straightforward method to achieve this enforcement is to use the Interest satisfaction ratio as a direct probability for accepting (forwarding) or rejecting an incoming Interest (see Pseudocode~\ref{alg:probabilistic model}).
-%Apart from the Interest satisfaction statistics generation, there is a question how this statistics can be used to actually enforce prioritization and penalizing of Interests.
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Satisfaction-based Interest acceptance}
-\label{alg:probabilistic model}
-\begin{algorithmic}[1]
-\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-
-\vspace{0.1cm}
-\Function{OutInterest}{Interest \textbf{i}, InInterface \textbf{in}, OutInterface \textbf{out}}
-
-    \State{} \Comment{Use uniform probability distribution model $P(X)$}
-    \State{} \Comment{$P(X) : \forall x \in [0,1] \Rightarrow P(x) = x$}
-
-    \If{$F_{in} > \theta $} \Comment{At least some Interests were forwarded before}
-        \State $s \leftarrow (1 - U_{in} / F_{in})$
-        \State Drop interest with probability $P(s)$
-    \EndIf
-
-    \State{forward the Interest, subjecting to token bucket limits}
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-Parameter $\theta$ on line 5 of Pseudocode~\ref{alg:probabilistic model} ensures that the probabilistic model is not enforced when the volume of Interests arriving at a particular interface is small.
-This step is critical to provide an opportunity for legitimate users to regain their share of resources after temporary Data delivery failures.
-
-A drawback of the satisfaction-based Interest acceptance method is that each router on the path makes an independent decision on whether to forward or drop an Interest. 
-As a result of these independent decisions,  the probability of legitimate Interests being forwarded decreases rapidly as the number of hops between the content requester and producer grows; worsening the Interest satisfaction statistics and resulting in further drops.
-In our example in Fig.~\ref{fig:flooding example}, the router A observes 50\% satisfaction rate for \texttt{eth1} and 0\% rate for \texttt{eth0}. 
-At the same time, router B observes a 30\% satisfaction rate for its \texttt{eth0} interface.
-Next time a legitimate Interest arrives at router A, it has a 50\% chance of being forwarded further, and if forwarded, it has only a $50\% \times 30\% = 15\%$ probability of being forwarded further towards the data producer.
-With each increasing hop in the network, the probability of being forwarded to the next hop decreases significantly.
-One way to prevent this overreaction and unfair penalization is to ensure that the decision taken at each router on whether to forward or drop the Interest is not independent of the decision taken at preceding routers.
-An explicit notification such as a gossip protocol between neighboring NDN routers might alleviate the problem, but we leave the design and evaluation of it to future work.
-%{\color{red}Alex: we should state that it is out of scope of the paper to evaluate this issue}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{\textbf{Satisfaction-based pushback}}
-\label{sec:dynamic limits}
-
-% Differential treatment of Interests received from different interfaces can be achieved in a more elegant way, without reverting to probabilistic methods.
-
-The previous algorithm---the satisfaction-based Interest acceptance---divides the available forwarding tokens among all interfaces in proportion to their Interest satisfaction ratios.
-% Given the drawbacks of this algorithm, the same effect can be achieved without relying on probabilistic models. 
-An alternate algorithm for proportional token distribution without overreaction is to enable and enforce explicit Interest limit for each incoming interface, where the value of the limit depends directly on the interface's Interest satisfaction ratio.
-Routers need to announce these limits to their downstream neighbors, ensuring that any Interest forwarded from the downstream router is allowed to get through, resulting in genuine Interest satisfaction statistics.
-
-The formal definition of the satisfaction-based pushback algorithm is presented in Pseudocode~\ref{alg:dynamic limits}, while Fig.~\ref{fig:dynamic limits example} illustrates how the algorithm will work in our example in Fig.~\ref{fig:flooding example}.
-Assuming an initial token bucket limit $L=10$ and the current satisfaction ratio for router A is 50\% for \texttt{eth1} and 0\% for \texttt{eth0}, and for router B the ratio is 30\% for \texttt{eth0}, each node will set and announce the following  incoming interface limit $L'$:
-\begin{enumerate}
-\item router B will set and announce the incoming interface limit $L'=3$;
-\item router A, after receiving announcement from B will readjust its incoming interface limits to $L'_{eth1} = 1.5$ and $L'_{eth0} = 0$; and
-\item both legitimate users and adversaries may either obey or ignore the announced limit, which will in any case be enforced by router A.
-\end{enumerate}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.3]{dynamic-limits}
-  \caption{Satisfaction-based pushback example
-%: routers explicitly tell neighbors how many Interest packets they can deliver to the Data producer%
-}
-  \label{fig:dynamic limits example}
-\end{figure}
-
-\floatname{algorithm}{\small Pseudocode}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{ 
-\begin{algorithm}[t]
-\footnotesize
-\caption{\small Satisfaction-based pushback}
-\label{alg:dynamic limits}
-\begin{algorithmic}[1]
-% \State{}\Comment{Same initialization, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-\State{} \Comment{Same init, InData and Timeout functions as in Pseudocode~\ref{alg:queuing}}
-\vspace{0.1cm}
-\State{$\forall f \in \mathrm{interfaces} : L'_{f} \leftarrow L_{f}$} \Comment{Per-incoming interface Interest limit}
-
-\vspace{0.1cm}
-
-\State{} \Comment{\textit{Announcement from the neighbor}}
-\Function{InLimits}{InInterface $in$, Limit $L'$}
-    \State $L_{in} \leftarrow L'$
-\EndFunction
-
-\vspace{0.1cm}
-
-\Function{AnnounceLimits}{} \Comment{\textit{E.g., every second}}
-\For{\textbf{each} outgoing interface $out$}
-
-   \For{\textbf{each} incoming interface $in$}
-        \State $L'_{in}= {L_{out}} \times (1 - U_{in}/F_{in})$
-        \State AnnounceLimit($in$, $L'_{in}$)
-   \EndFor
-
-\EndFor
-\EndFunction
-
-\end{algorithmic}
-\end{algorithm}
-
-The zero limit for the adversary's link implies that  router A is temporarily not willing to accept any Interests from this interface until the statistics decay to an appropriate level (recall Fig.~\ref{fig:ratio example}).
-At the next iteration of the satisfaction-based pushback algorithm, a legitimate user will be able to gradually improve the statistics on both routers A and B as all Interests from the user will get through and return Data, eventually resulting in a full allowance ($L'=L=10$) in the links between the routers A and B, and the user and router A.
-
-We note that while in the description of the satisfaction-based pushback algorithm we explicitly used ``outgoing'' and ``incoming'' interfaces,  all interfaces can be both incoming and outgoing.
-Thus, it may not be entirely clear which outgoing limit $L_{out}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{in}$.
-To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
-That is, for each FIB entry we set a separate Interest limit for each incoming interface (${L'}_{in}^{fib}$) based on the sum of FIB entry limits for each outgoing interface $L=\sum{L_{out}^{fib}}$.
-
-Both satisfaction-based Interest acceptance and satisfaction-based pushback algorithms are forms of a well-known push-back mechanism~\cite{Pushback}, but with several core differences. 
-First, we are suppressing (pushing back) unwanted requests for data, not actual data itself.
-Second, differentiating between good and bad Interests is based on the traffic symmetry principle of NDN.
-% Alex: I'm not entirely sure about this point... 
-Finally, both intelligent attack mitigation algorithms can be deployed at all times without degrading network performance even when there are no active attackers.
-
-\section{Evaluation of Interest flooding mitigation methods}
-\label{sec:evaluation}
-
-% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.
-
-% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers,
-
-% alex: what's a point of latency?  it would matter only for queueing method and we not really pushing this method
-% Latency for good clients, good versus bad interests as a function of time
-
-In this section, we present an in-depth evaluation study, aiming to quantify the effectiveness of all our Interest flooding attack mitigation methods.
-We used the open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator (\url{http://www.nsnam.org/}), to run simulations for a variety of network topologies and scenarios.
-We extended ndnSIM with our three mitigation algorithms---token bucket with per interface fairness, satisfaction-based Interest acceptance, and satisfaction-based pushback---and evaluated the effectiveness of each algorithm independently.
-
-% For evaluating the effectiveness of each mitigation algorithm, every router in the simulated topology runs the mitigation algorithm under study.
-
-% why we chose small scale topology
-% what point we wanted to show we small scale
-% what points we wanted to verify with larger-scale internet like topology
-
-% Metrics
-% not sure if i already explained that. our essential qualitative metric is .  
-% To quantify the effectiveness of the mitigation mechanism this  metric we use satisfaction percentages of user Interests.
-
-The metric we choose to quantify the effectiveness of our algorithms is the {\it percentage of satisfied Interests for legitimate users}.
-This metric corresponds to the quality of service experienced by legitimate users when the network is under attack.
-In other words, if the network implements a mitigation method $X$ and a high percentage of user-expressed Interests are satisfied even while the network is under attack, then one can conclude that method $X$ is highly effective at mitigating the attack.% We also ensure that all Interests expressed by legitimate users during a period of no-attack are satisfied.
-
-%Quality of the attack mitigation methods directly corresponds to the quality of service for the legitimate users during an ongoing attack, which in NDN network can be quantified through percentage of satisfied Interest.
-%For example, if the network implements a mitigation method $X$ and under the attack majority of user-expressed Interests are getting satisfied, then the method $X$ can be seen as highly effective.
-%At the same time, if only a small percentage of the expressed Interest are getting satisfied during the attack, the method $X$ can be called ineffective.
-
-% Traffic pattern
-In our experiments, we assumed that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution.
-We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering.
-To quantify the behavior of our mitigation strategies under a worst-case attack scenario, we assumed that all the attackers send junk Interests as fast as they can.
-Further, no Interest---including legitimate ones---can be satisfied from caches.
-We also configured routers for single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
-%(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).
-
-% Alex: not sure how to argue about the traffic pattern
-%Although this pattern may seem not truly realistic, it approximates a good statistical mix of traffic from all network users without excessive network buffering.
-
-%In addition to that, in each run of the simulation we ensure that all Interests expressed by the legitimate users during a no-attack period are satisfied.
-%For simplicity, we also equalized the average rates with which the legitimate users express Interests.
-%At the same time, the attackers are sending junk Interests as much as they can get through (remember, that Interest limits will not allow real f%looding of Intersests in all of the designed mitigation algorithms).
-
-We ran our simulations on two different network topologies---a smaller binary tree topology and a much larger ISP-like topology.
-We use a binary tree topology as it represents one of the worst cases to defend against Interest flooding DDoS attacks.
-The larger ISP topology reflects how our mitigation methods would perform when deployed on the real Internet.
-Again, to study the performance of our mitigation strategies under a range of conditions, we varied the percentage of attackers in the network---the values ranged from 6\% attackers to over 50\% attackers in the network.
-% Fixed parameters
-We set the \emph{delay} and \emph{data size} parameters for the Interest limit calculation (formula \ref{eq:interest limit}) to a fixed 
-value for every node in the simulated topology.
-In particular, for the small-scale binary tree topology, we set delay to 80~ms, while for the large-scale ISP topology we set it to 330~ms (the order of the largest RTT).
-The data size is 1100~bytes for all simulation runs and topologies.
-% THIS IS BULLSHIT!
-There is absolutely no logic to set the delay to the same value on all nodes in the network.
-We discussed multiple times that you should fix it so that the delays are realistic and gets smaller as the nodes gets closer to the producer...
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Small-scale evaluations}
-\label{sec:small-scale}
-
-% Topology description
-%To assess baseline quality of the designed Interest flooding attack mitigation methods, we evaluated them first using a %simplistic small-scale binary tree topology 
-In Fig.~\ref{fig:small-scale}, we depict the binary-tree topology that we used for our initial experiments.
-Legitimate users as well as attackers were placed on leaf nodes (top row of red nodes) as shown in the figure.
-There are 16 end users (both legitimate and attackers) in this topology, each expressing Interests that are routed towards a single data producer, placed at the root of the tree.
-Each link in this topology is assigned a bandwidth of 10~Mbps and a randomized propagation delay ranging from 1 to 10 ms.
-
-% Alex: should we mention that?
-%The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS %attacks.
-%That is, sharing of the network links exponentially increases as decreasing level of the binary tree.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.2]{topo-tree-evil-5-good-0-producer-gw}
-  \caption{Small-scale binary tree topology}
-  \label{fig:small-scale}
-  \vspace{-0.3cm}
-\end{figure}
-
-% in 10 independent runs of each simulation, where we randomized position of the adversaries along the legitimate users.
-In all runs, the total number of legitimate and malicious uses were fixed, meaning that when we increase number of attackers, we decrease the number of legitimate users.
-
-\subsubsection{Effectiveness of the three mitigation algorithms}
-
-%The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
-%For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).
-
-Our goal is to compare the effectiveness of each mitigation method and quantify the percentage of Interests satisfied for all legitimate users while the network is under attack.
-For each mitigation algorithm, we perform 10 independent simulation runs, where we randomly choose 7 client nodes to represent adversaries while the remaining 9 client nodes represent legitimate users.
-In each run we simulate a 10-minute attack window (total simulation time was 30 minutes, with attack starting at the 10-minute mark).
-We plot the minimum and maximum range for observed Interest satisfaction percentages for all legitimate users aggregated across the 10 simulation runs as a function of time for each mitigation algorithm in Fig.~\ref{fig:small-scale attack progress}.
-Token bucket with per-interface fair queuing performs the worst, while satisfaction-based pushback performs the best, with almost a 100\%  satisfied Interests for all legitimate users.
-
-%A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
-
-\begin{figure}[]
-  \centering
-  \hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
-  % \vspace{-.3cm}
-  \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
-  \label{fig:small-scale attack progress}
-  % \vspace{-.4cm}
-\end{figure}
-
-%\paragraph{\textbf{Simple token bucket}}
-
-%{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}
-
-%Let us take a deeper look on what is happening with the simple token bucket algorithm.
-%Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as token bucket restricts the number of forwarded Intersets!).
-%This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
-%In this example we assume that both the legitimate user and the adversary send Interests in about the same time.
-%
-%\begin{figure}[t]
-%  \centering
-%  \includegraphics[scale=0.3]{physical-limits-sync-problem}
-%  \caption{Three-router topology, with one legitimate and one malicious user}
-%  \label{fig:three router example}
-%\end{figure}
-%
-%Both router L and router X will forward the Interests, as both of them have a free token available.
-%At router A, two cases are possible, either of Interests can arrive first, resulting in a quite different effects.
-%When legitimate Interest arrives first, then there are no problem. 
-%Router A will capture the token, forward the Interest, which will be quickly satisfied, releasing the token for future uses.
-%In the mean time, malicious Interest will be dropped at router A, and router X will release the hold for the token in one second (i.e., after the maximum time Interests are admitted), enabling a new round of competition for router A's resources.
-%
-%In the case when malicious Interest is sent a little bit earlier, then router A will forward malicious Interests, dropping a legitimate one, and causing ``lock out'' for one second.
-%In the instant when the token gets released at router X, an adversary is able to push new Interest towards router A, which may arrive in the exact time A's token gets released (assuming an idealistic environment).
-%As a result, the adversary recaptures router A's token and extends the ``lock out'' for another second, denying service to the legitimate user without sending any massive numbers of Interests.
-
-\paragraph{\textbf{Token bucket with per interface fairness}}
-
-We observe a successful DDoS attack, where 40\% attackers succeed in significantly shutting down the remaining 60\% legitimate users---a mere 15\% of their Interests are satisfied by Data from the producer.
-Contrary to expectations, the 60\% legitimate users do not receive at least 60\% of network resources.
-As described in the previous section, the key limitation of this algorithm is that it still admits Interests from attackers and causes congestion and packet drops near the victim.
-%Significantly reducing the number of accepted malicious Interests is fundamental for improving the effectiveness of any mitigation algorithm.
-
-%The described problem arises from the clocking effect and can be solved in a number different ways.
-%Augmenting token bucket algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
-%That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
-%However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
-%Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
-%We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.
-
-\paragraph{\textbf{Satisfaction-based Interest acceptance}}
-
-The effectiveness of this algorithm stems from the fact that routers can differentiate and limit malicious Interests into the network%, thereby ensuring availability of network resources for serving legitimate users
-.
-The observed periodic dips in the Interest satisfaction ratios of legitimate users in Fig.~\ref{fig:small-scale attack progress} is a direct result of Interest satisfaction rate statistics decaying with time.
-The 50-second period approximately corresponds to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx$20\% within 50~seconds.
- % that ranges from 30~seconds to 50~seconds. 
-%The primary reason that such minimum peaks exist is the fact that 
-When Interests from attackers start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe mixed traffic from legitimate and malicious users).
-Consequently, this degradation reduces the probability of legitimate Interests getting through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' again to the edge.
-
-%When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
-%That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
-
-\paragraph{\textbf{Satisfaction-based pushback}}
-
-In our simulations, this mitigation algorithm was able to effectively shut down attackers and ensure almost all the Interests from legitimate users are satisfied. 
-%The only potential problem with the satisfaction-based pushback algorithm is that it features 
-We observe a  sharp dip in the satisfaction ratio curve at the start of the attack as it takes a few seconds for all routers to be fully aware of the attack.
-However, recovery is quick as malicious Interests start to time out and explicit Interest limit announcements start to succeed in containing malicious Interests close to the attacker.
-Till then, the network, for a short period of time (under 10~seconds for all simulation runs), fails to provide 100\% service for legitimate users.
-Once the malicious Interests are effectively shut down, all Interests from legitimate users are satisfied.
-Unlike the satisfaction-based Interest acceptance scenario, we do not observe any periodic dips in the satisfaction curve, as the pushback algorithm effectively guarantees that once an Interest is admitted, it will likely be routed all the way to the data producer.
-
-\subsubsection{Network reaction to varying number of attackers}
-
-Our next goal is to study the effectiveness of our mitigation algorithms as a function of increasing adversaries in the network.
-To this end, we vary the percentage of attackers in the topology from 6\% to over 50\%.
-Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases.
-All other parameters and experimental setup are consistent with the previous experiment.
-As before, for each mitigation algorithm, we perform 10 independent simulation runs.
-%The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
-%To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.
-
-%Since at this point the overall attack dynamics of all the attack mitigation algorithms is relatively clear, 
-% In other words, each point captured in the box plot graph corresponds to 1-second averaged satisfaction ratio for a user in an individual simulation run.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
-  % \vspace{-.3cm}
-  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}
-  \label{fig:small-scale-topo boxplot}
-  % \vspace{-0.5cm}
-\end{figure}
-
-In Fig.\ref{fig:small-scale-topo boxplot} we present  the Interest satisfaction ratio for legitimate users aggregated over the 10 simulation runs for the first minute of the attack.
-The results are as expected---for all three mitigation algorithms, as the percentage of attackers in the network increases, the lower is the Interest satisfaction ratio for legitimate users.
-In the case of token bucket with per-interface fairness algorithm, just 3 attackers can halve the quality of service for the remaining 13 legitimate users.
-While the two intelligent attack mitigation algorithms also show a decline in service quality as the percentage of attackers increases, this decline is much more gradual and marginal.
-In the case of satisfaction-based pushback algorithm, during the first minute of the attack over 90\% of Interests from legitimate users are satisfied even if 50\% of end nodes are malicious.
-
-% \begin{figure}[htbp]
-%   \centering
-%   \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min-after-1-min}
-%   \caption{Average consumer Interest satisfaction ratios (second minute)}
-%   \label{fig:small-scale-topo 2}
-% \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Large scale simulations}
-\label{sec:largescale}
-
-%To check validity of the small-scale experiment results, we performed a larger-scale evaluation based on a modified version of
-
-In this section, we investigate the behavior of our mitigation strategies under a more realistic, large-scale network topology.
-The ISP topology we used is based on a modified version of Rocketfuel's AT\&T topology~\cite{rocketfuel}.
-%In order to approximate the general structure of the Internet,
-% (scale-free structure, customer-provider, and peer-to-peer relations)
-We extract the largest connected component comprising of 562 nodes from this original topology and separate the nodes into three categories: clients, gateways, and backbones.
-Nodes having degree less than four are classified as clients (344 red nodes as shown in Fig.~\ref{fig:large-scale}), nodes directly connected to clients are classified as gateways (109 green nodes), and the remaining nodes are classified as backbones (109 blue nodes).
-%(To ensure that paths in the topology are ``valley-free,'' we augmented the topology with necessary backbone-to-backbone links.) 
-We assign bandwidth and  delay values to links based on their type---both values are random numbers within the respective ranges as shown in Table~\ref{tab:large-scale}.
-We experiment with placing the data producer at both a gateway node as well as backbone node, which we randomly pick for each simulation run.
-Similar to the binary tree topology experiments, we fix the number of malicious nodes at approximately 40\% (140 out of 344 client nodes in the topology) and randomly pick these nodes for each simulation run.
-We conduct 10 simulation runs for each mitigation algorithm, with the attack duration spanning a 5-minute interval.
-
-\begin{figure}[t]
-  \centering
-  % \vspace{-.1cm}
-  \includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
-  % \vspace{-0.3cm}
-  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
-  \label{fig:large-scale-topo}
-\end{figure}
-
-\begin{table}[t]
-\centering
-\caption{Large-scale topology link bandwidth and delay ranges}
-% \vspace{-0.3cm}
-\label{tab:large-scale}
-\begin{tabular}{|l||c|c||c|c|}
-  \hline
-  \multirow{2}{*}{\bf Link type} &  \multicolumn{2}{|c||}{\bf Delay} &  \multicolumn{2}{|c|}{\bf Bandwidth} \tabularnewline
-  \cline{2-5}
-                        &  Min & Max                       &  Min & Max \tabularnewline
-  \hline \hline
-  Backbone--Backbone    & 5~ms & 10~ms   & 40~Mbps & 100~Mbps \tabularnewline
-  \hline
-  Gateway--Backbone,    & \multirow{2}{*}{5~ms} & \multirow{2}{*}{10~ms}   
-                        & \multirow{2}{*}{10~Mbps} & \multirow{2}{*}{20~Mbps} \tabularnewline
-  Gateway--Gateway      & & & & \\
-  \hline
-  Client--Gateway       & 10~ms & 70~ms   & 1~Mbps  & 3~Mbps \\
-  \hline
-\end{tabular}
-% \vspace{-0.3cm}
-\end{table}
-
-%Priya: Leaving out this in the interest of space...
-%Topological location of the data producer plays a key role in its resilience to Interest flooding attacks.
-For a data producer that %is connected to a client node via a low-bandwidth link, even a small number of junk Interests can impact services for legitimate %users.
-For a producer located at the backbone with rich connectivity through many high-bandwidth links, an attack might not %be as severe as a majority of legitimate users might not be on the attack path.
-
-% The results for all attack mitigation algorithms and all runs are aggregated in Fig.~\ref{fig:small-scale attack progress}, where Y-axis represents a minimum and maximum range for observed Interest satisfaction percentages among all nodes and all simulation runs.
-% A short and simplistic summary of the results is that the first two attack mitigation methods do not work at all, and the last two are working quite good.
-
-In Fig.~\ref{fig:large-scale}, we summarize our results aggregated over all simulations runs for each mitigation algorithm for the scenario where the data producer is placed at a gateway node.
-We observe similar results for the data producer placed at a backbone node as well.
-Unlike the binary-tree topology experiments, we observe that the satisfaction-based pushback is the most effective algorithm, while both the token bucket with per interface fairness and satisfaction-based Interest acceptance have poor performance.
-Interest satisfaction percentage for legitimate users are close to 100\% and approximately 30\% and 25\% respectively for these mitigation methodologies.
-
-%
-%The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.
-
-\begin{figure}[t]
- \centering
- \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
- % \vspace{-.3cm}
- \caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}
- % producer on a gateway node
- \label{fig:large-scale}
- % \vspace{-.7cm}
-\end{figure}
-
-Satisfaction-based Interest acceptance algorithm, which was very effective for binary-tree topology, is completely ineffective when deployed in a larger and more realistic topology.
-For the duration of the attack, legitimate users experience poor quality of service with only 25\% of their Interests being satisfied and continue to experience degraded service long after the attack has stopped.
-This poor performance, as detailed in Section~\ref{sec:probabilistic}, is due to the fact that each router on the path makes an independent, uncoordinated decision on whether to forward or drop an Interest.
-In the case of the larger-topology, with much higher average hop count, Interest packets from legitimate users have a very low probability of reaching the data producer, resulting in poor Interest satisfaction statistics and further penalization of new Interests from them.
-
-All our evaluations leave us to conclude that among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most promising one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network.
-%The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
-As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.
-
-% Alex: Anything else here?
-
-% Alex: I also experimented with placing producer at the backbone, getting slightly better results for all algorithms.  Though I'm not sure there is any value to put those results in the paper
-
-% \input{simulation-emulation.tex}
-
-\subsection{Limitations}
-%{\color{red} I gave up the idea of seperate discussion section after trying for some time, as given the space limitation, there is no way to write a reasonably comprehensive and  broad discussion section that justifies a separate section.
-Instead, I decided to have a scoped down version here that confesses upon the limiations of our evaluations only.
-Whoever has time (I need to sleep few hours), please go ahead and write 1-2 paragraphs as I outlined below.
--Ersin}
-
-%This section should roughly say: Our results show that the two features, namely the symmetric traffic and stateful routing, give NDN routers the ability to observe and characterize traffic in real time.
-Through our evaluations, we demonstrated that a mitigation algorithm that leverages such ability has great potential in mitigating various DDoS attacks that could otherwise have grave effect on the network.
-However, as the first step in exploring the problem and the solution space, this paper has obvious limitations: (1) We assume a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations.
-Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step is evaluating the above described solutions with more sophisticated and adaptive attackers.
-(2)   Although most (such as single-path routing, no-caches in the network, single homed victim, etc) are aimed to test the proposed solutions under worst-case scenario, we made many assumptions in simulations/evaluations about the configurations, topology and the traffic that maybe poor-representative of realistic conditions.
-(3) As NDN being an ongoing research effort itself, our evaluations fully depend on simulations and done over a snapshot of its codebase.
-
-% The main contribution of the paper and this section in particular is a proof that two inherent properties of NDN architecture, namely the symmetric traffic and stateful forwarding, give NDN routers the ability to characterize traffic and react in real time.
-% We demonstrated that satisfaction-based pushback algorithm, leveraging this ability, has great potential in mitigating various DDoS attacks that could otherwise have a grave effect on the network. 
-% However, as the first step in exploring the problem and the solution space, our paper has obvious limitations.
-% First, we assumed a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations. 
-% Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step that we are leaving out for future work is evaluating the above described solutions with more sophisticated and adaptive attackers.
-% Second, while aiming to test the designed algorithms under worst-case conditions, the future work needs to address behavior in more realistic scenarios, including investigation of multi-path routing, in network caches, as well as multi-homed victims.
-
-This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space. 
-While designing our mitigation algorithms, we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic.
-We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology, % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
-as well as a more realistic ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network. 
-While our results are promising and show a great potential in mitigating Interest flooding DDoS attacks, there are certain limitations which should be addressed in future research.
-
-First, in our evaluations we used a simple and static attacker model---attackers send junk Interests as fast as possible. 
-In future work, we plan to explore the impact of models where the attackers are more sophisticated and dynamically adapt their behavior and Interest sending patterns based on the network reaction. 
-Second, we assumed that Interests are not satisfied by an intermediate router's cache and always forwarded all the way to the producer.  
-In future, we plan to study the impact of Interest flooding attacks in more realistic scenarios with multi-path routing enabled, more realistic traffic patterns, and the presence of in-network caches.
-% We also ignored NDN's strategy layer that routes around failure and congestion in the network. 
-% In future work, we plan to study the impact of turning on these features. 
-%Finally, we also plan to perform more extensive simulations on other realistic Internet-like topologies and traffic patterns.
-
-\section{Related work}
-\label{sec:related-work}
-
-As a new Internet architecture proposal, Named Data Networking has attracted attention from the security community. 
-Lauinger~\cite{Lauinger:2010:Security--scalability} showed several possible attacks against some specific design choices implemented in CCNx software (\url{http://www.ccnx.org/}); in particular~\cite{Lauinger:2010:Security--scalability} explored the issue of user privacy, assuming users are concentrated on the same edge router only and one can obtain complete knowledge of cached content.
-W\"ahlisch et al.~\cite{Wahlisch:2012:Backscatter-from} explore security and stability threats in the general area of information-centric networks (ICN), using CCNx software as an example.  
-While this work aims to generalize findings for all ICNs, it largely does not go beyond the current design choices of CCNx.
-% (which is an example, but not the final word in NDN) 
-% Gasti et al.~\cite{gasti2012ddos} identified several NDN architecture-specific attacks (Interest flooding and content/cache poisoning) and proposed potential solutions, without devising particular algorithms.
-In this paper we follow the suggestions by Gasti et al.~\cite{gasti2012ddos} and utilize the properties provided by the NDN architecture to mitigate DDoS attacks, and tackle the Interest flooding problem as a first step in this direction.
-More specifically our attack mitigation design relies on NDN's stateful forwarding plane that allows us to
-maintain statistics on unsatisfied Interests.  
-Similar approaches are also explored by Yi et al.~\cite{adaptive-forwarding,adaptive-tr} and Rozhnova et al.~\cite{rozhnova2012effective} to facilitate NDN network performance.
-
-The general area of mitigating denial of service attacks is amongst the hottest topics in recent years.
-% Among all the body of work, 
-The most relevant works to this paper are the solutions to brute force IP packet flooding, such as DDoS detection techniques~\cite{Chen:2007:Collaborative-detection, Jun:2011:DDoS-flooding}, methods of pushing back malicious traffic to edges using various filtering techniques~\cite{Pushback, Tupakula:2003:A-practical-method, Argyraki:2005:Active-internet, Oikonomou:2006:A-framework-for-a-collaborative, Liu:2008:To-filter-or-to-authorize:, Chou:2009:Proactive-surge, Liu:2010:NetFence:-preventing},
-overlay-based filtering~\cite{Stone:2000:CenterTrack:-An-IP-overlay, Keromytis:2004:SOS:-An-architecture, Kline:2011:Shield:-DoS-filtering}, 
-various ticketing systems with conditional admission of traffic in to the network~\cite{Yaar:2004:SIFF:-A-stateless, Yang:2005:A-DoS-limiting-network, Wendlandt:2006:Fastpass:-Providing, Natu:2007:Fine-grained-capabilities, Portcullis, Capabilities},
-and systems that attempt to use approximate IP traffic symmetry to estimate and filter out malicious traffic~\cite{Wang:2002:Detecting-SYN-flooding, Kreibich:2005:Using-packet, Mahimkar:2007:dFence:-Transparent}.
-Identifying malicious traffic requires establishing certain state at routers, and the above mentioned solutions differ in the specifics on what state to use and how to establish it.
-By design NDN's forwarding plane keeps per packet state at every router, the finest granularity state to support any and all mitigation solutions---we simply take full advantage of this state to develop desired solutions.
-
-% Our design for the Interest flooding attack mitigation borrows
-
-% This paper talks about attacks on content centric infrastructure (not specifically to NDN).
-% \cite{Wahlisch:2012:Backscatter-from}
-
-% % Collaborative detection of DDoS attacks over multiple network domains
-% \cite{Chen:2007:Collaborative-detection} distributed change-point detection
-
-% % DDoS flooding attack detection through a step-by-step investigation
-% \cite{Jun:2011:DDoS-flooding}
-
-% % A practical method to counteract denial of service attacks
-% \cite{Tupakula:2003:A-practical-method}
-
-% Alex: We should not include this reference for the review, but afterwards
-% Previous work on DDoS and DoS~\cite{gasti2012ddos}
-
-% Network level (Flooding)
-% % 2002
-% Pushback~\cite{Pushback} (hop-by-hop push back) aggregate- based congestion control/congestion signatures (e.g., per-destination), rate-limiting, explicit notification
-% AITF~\cite{Argyraki:2005:Active-internet} (active filtering requests; path recording, last-point of trust detecting)?
-% DefCOM \cite{Oikonomou:2006:A-framework-for-a-collaborative} Communication between src, core, and dst to provide collaborative defense.
-Dst raises alerts, src differentiate bad/good, packet tagging.
-Core rate-limit, congestion-aware re-tag.
-Traffic prioritization.
-% StopIt \cite{Liu:2008:To-filter-or-to-authorize:} (filtering) tagging with passports, tagged prioritization, dst- invoked filter instantiation
-% NetFence \cite{Liu:2010:NetFence:-preventing} congestion policing: fair queuing (one leaky bucket per {src,L}, L- bottleneck), secure "ticketing" with signals for AIMD to increase/decrease bandwidth allowance
-% PSP \cite{Chou:2009:Proactive-surge} topology as origin-destination pairs, packet tagging, OD traffic isolation, sharing based on historic bandwidth demand
-
-% SIFF~\cite{Yaar:2004:SIFF:-A-stateless} (time-based tickets, capabilities)
-% TVA \cite{Yang:2005:A-DoS-limiting-network} like SIFF, traffic- based tickets, hierarchical per- AS, per-source fair queuing
-% FastPass \cite{Wendlandt:2006:Fastpass:-Providing} (tokens: various puzzles, other methods) traffic authorization, routers verify and filter.
-% \cite{Natu:2007:Fine-grained-capabilities} based on TVA/SIFF: specifies previously unspecified mechanisms to grant "tickets" for requesters, extends capabilities to include priorities, changing tickets to be only destination- dependent, not path dependent
-% % LazySusan \cite{Crowcroft:2007:Lazy-Susan:} TR (latency-based proof of work--- computational puzzles)
-% Portcullis \cite{Portcullis} Protecting connection setup with computational proof of work, tickets and traffic prioritization for the rest, per- computational fairness; DNS to disseminate puzzles
-% There are many other puzzle- based schemes, on which Portcullis is based or which problems it solves
-
-% PacketSymmetry \cite{Kreibich:2005:Using-packet} (leverages packet symmetry to detect and remove bad traffic) packet asymmetry - number of transmitted packets (tx) to received packets (rx); negative values when rx outweighs tx, positive values when tx outweighs rx, and zero in the case of perfectly balanced traffic)
-% % Detecting SYN flooding attacks
-% \cite{Wang:2002:Detecting-SYN-flooding} based on the protocol behavior of TCP SYN-FIN (RST) pairs, and is an instance of the Seqnential Change Point Detection
-% dFence \cite{Mahimkar:2007:dFence:-Transparent} (middleboxes) TCP connection proxying, rate estimation and TCP/ACK modification
-
-% Overlays:
-% CenterTrack \cite{Stone:2000:CenterTrack:-An-IP-overlay} (overlay) reroute suspicious traffic to a special routers with diagnostic capabilities using an overlay
-% SOS \cite{Keromytis:2004:SOS:-An-architecture}
-% Shield \cite{Kline:2011:Shield:-DoS-filtering}
-
-% NDN and other future information centric architectures were lacking any DDoS mitigation techniques, so we put efforts in understanding DDoS defensive systems, which were made for IP architecture, for the purpose of possible incorporation of them in NDN.
-In this section we will overview generic directions of DDoS mitigation designs and try to think about which tricks could be used in NDN.
-
-% Capability-based systems allow routers to negotiate, perform and enforce limitations on bandwidth consumption on router-to-router and router-to-client links.
-Usually such systems require an extensive trust infrastructure in order to validate secure keys used by routers and clients.
-This implies that each client must pass through an authentication process prior to using any bandwidth~\cite{Capabilities}.
-We believe that for NDN this method doesn't fit really well for the following reasons.
-First, this method is very questionable in terms of scalability and mobility support since it requires tight trust connections between routers and hosts.
-Thus, it neglects one of the main advantages (mobility) of NDN.
-Second, the design of trust infrastructure for NDN is not well defined yet, which means that we cannot really make assumptions in our design of mitigation techniques.
-
-% Computation-based systems provide each client an access to the network resources only after performing a significant computations such as solving puzzles.
-Spending a huge amounts of computational resources can effectively slow down a flooding attack by the botnet, however it also creates additional computational burden for legitimate clients.
-One of the main difficulties in such systems is the question of puzzle dessimination.
-In ~\cite{Portcullis} authors suggested to propagate puzzles using DNS system.
-In NDN since routers have caching abilities, we can propagate puzzles just like a normal data packets, using Interest-Data exchange.
-Overall, this method looks interesting and deserves being investigated in a future work.
-
-% Congestion control systems do per flow traffic analysis and drop of packets belonging to misbehaving flows.
-For instance, Random Early Detect (RED)~\cite{RED} identifies flows that do not comply with TCP-friendly end-to-end congestion control, and preferentially drop them.
-Such techniques, if largely deployed, could perform well, however, they cannot provide effective defense against non-greedy botnets that are creating a huge amount of low-bandwidth flows.
-Since NDN routers maintain a richer per-packet state, which translates into a better per-flow statistics, these techniques can become much more effective when applied to NDN.
-
-% Push back systems are trying to detect bad and good traffic flows on each router, and once attack is detected by one of the routers, it starts a coordinated push back by downrating incoming flows with a bad traffic in order to provide more capacity for a good traffic.
-This process is reiterating downstream till it reaches edge routers, which are directly connected to attacking bot machines~\cite{Pushback}.
-In general this technique can be applied to NDN architecture thanks to its decentralized coordination of downrating bad traffic flows.
-Moreover, NDN provides better capabilities for accurate flow detection.
-
-%were looking for getting accustomed
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-% Main take out from the paper:  could be a problem, but problem is solvable.  
-% One of the key components in the Named Data Networking architecture is its stateful data delivery model, which potentially can be abused by new types of denial of service attacks.
-% However, one should not forget that the same stateful data delivery provides effective mechanisms to fight back against such attacks.
-
-%In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
-%The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data path symmetry and full receiver-based traffic control.
-%In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Interests can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.
-%
-%Other forms of attack may require different mitigation mechanisms.  
-%However, the granularity of the NDN state---per each Interest packet---is what giving NDN an opportunity to stand against existing and new forms of attacks.
-%
-%NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution.
-
-NDN being a newly proposed future Internet architecture, it is important to address its resilience in face of DDoS attacks.
-As an initial step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks namely Interest flooding and the severe service degradation such an attack may cause to legitimate users.
-We then leveraged the key features of the NDN architecture to design, develop, and evaluate three mitigation strategies.
-We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
-The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers, so that they cause little or no service impact to legitimate users.
-
-NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balance (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding}.
-Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.
+\input{01-intro}
+\input{02-ndn-overview}
+\input{03-interest-flooding}
+\input{04-flooding-mitigation}
+\input{05-evals}
+\input{06-related}
+\input{07-conclusion}
 
